### 2012-03-07 paper.tex
copied introduction

\documentclass{llncs}

\usepackage{verbatim}
\usepackage{url}

\title{Quality Criteria for SKOS Vocabularies}
\author{Christian Mader\inst{1} \and Bernhard Haslhofer\inst{2}}
\institute{
	University of Vienna, Faculty of Computer Science\\\email{christian.mader@univie.ac.at}
	\and Cornell University, Information Science\\\email{bernhard.haslhofer@cornell.edu}}

\begin{document}

\maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}
The Simple Knowledge Organization System (SKOS\footnote{Simple Knowledge Organization System, \url{http://www.w3.org/2004/02/skos/}}) has become a de-facto standard for expressing controlled vocabularies on the Web. Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} have created SKOS representations of their controlled vocabularies and published them on the Web so that they can easily be navigated and reused by humans and, most importantly, also by applications. Each vocabulary is the result of a specific design process that reflects domain-specific requirements as well as the target audience the vocabulary is created for. Orthogonal to the design process, vocabulary \textbf{designers and maintainers} usually apply existing guidelines or follow their own rules when defining concepts, in order to meet their \textbf{quality requirements} as, for instance, described in \cite{Coronado2009}. As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality, which can affect their interoperability and applicability for tasks like query expansion, faceted browsing, clustering, or auto-complete suggestions.

The following representative examples, which we identified by looking at real-world SKOS vocabularies, illustrate the \textbf{quality problems} applications could face when making use of them:
\begin{itemize}
	\item The SKOS version of Agrovoc defines concepts in 25 different languages. However, almost all concepts have an English description, 38\% of all concepts don’t have German labels attached. This can be a problem for applications that use Agrovoc and rely on German translations.

	\item The previous version of the STW thesaurus, contained 5 pairs of concepts with identical labels. As a result, the auto-complete function of the online search interface suggested identical entries, with no disambiguation information.

	\item The vocabulary developed by the Austrian Armed Forces (LVAk thesaurus\footnote{Non-public thesaurus developed by the Austrian Armed Forces}), which contains 11 disconnected concept clusters. Confronting the thesaurus maintainer with these structures, they recognized them as “forgotten” test data that has no practical significance.

	\item In the DBpedia category\footnote{\url{http://downloads.dbpedia.org/3.7/en/skos_categories_en.nt.bz2}} hierarchy, more than 10 percent of the categories not linked to any other category. When other vocabularies link to the DBPedia categories, e.g., to enable query expansion, it can negatively affect recall and reduce navigability.
\end{itemize}

One reason for these quality problems is that SKOS currently only defines a set of \textbf{low-level integrity conditions}, which, when being enforced, ensure the structural and semantic requirements of the SKOS specifications but fail to capture \textbf{higher-level quality issues}, as those mentioned in the examples before. Another problem is that existing vocabulary design guidelines and best practices purely rely on \textbf{human assessment}, which is highly subjective and doesn’t scale when vocabulary quality assessment should be performed on larger, possibly linked Web vocabularies.

We believe, and recent developments of quality checking tools (e.g., PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}}, qSKOS\footnote{\url{https://github.com/cmader/qSKOS}}, SKOSify\footnote{\url{http://code.google.com/p/skosify/}}) support this motivation. This, however, requires a formalization of the notion of quality with respect to SKOS vocabularies, which can be used in order to consistently implement quality assessment procedures across tools. Since, the notion of “quality” with respect to SKOS vocabularies naturally varies across application domains it is hard, if not impossible, to come up with a general definition of quality. However, we believe that vocabulary designers can apply a set of \textbf{formal quality criteria} on given vocabularies in order to assess whether or not a vocabulary fulfills their requirements. Since these criteria are based on a formal definition, they can be calculated by automated tools, which helps vocabulary designers in assessing the quality of available or newly created vocabularies and provide important feedback to the overall vocabulary design process.

The main contributions of this work can be summarized as follows:
\begin{itemize}
	\item We derived a \textbf{quality criteria catalogue} from existing literature, tools, and public mailing list discussions in the community. We \textbf{formalized} each criterion and implemented them in the \textbf{qSKOS quality assessment tool}.

	\item We \textbf{analyzed} a representative \textbf{set of existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.
\end{itemize}

The results from our studies show that....TBD

\section{SKOS Quality Model}

\subsection{SKOS Baseline Model}

\subsection{Graph-based Quality Criteria / Network Measures}

\subsection{Structure-Centric Quality Criteria / Structural Measures}

\subsection{Linked Data Specific Criteria / Linked Data Measures}

\subsection{SKOS-Specific Criteria / SKOS Semantic Measures}

\subsection{Labeling Issues}

\subsection{Other Criteria}

\section{Analysis of Existing SKOS Vocabularies}

\subsection{The qSKOS Quality Checking Tool}

\subsection{Vocabularies}

\subsection{Results}

\section{Related Work}

\section{Conclusions and Future Work}

\bibliography{lit}
\bibliographystyle{splncs03}

\end{document}

### 2012-03-07 paper.tex
started skos baseline model

@@
 
-The results from our studies show that....TBD
+The results from our studies show that... TBD
 
-\section{SKOS Quality Model}
+\section{A Quality Model for SKOS}
+SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption.
+Established quality notions from closed-world systems, such as constraints, referential integrity or schema validation, don’t hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false.
+While trust and provenance models for Web data are being developed \cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets \cite{Heath2011}.
+
+Based on the findings from a literature survey we now define a set of quantifiable quality criteria for SKOS vocabularies.
+For each \textbf{criterion} we explain our design rationale, and provide a semi-formal definition, which is based on a set-theoretic conception of the SKOS model.
+Tools can implement these criteria as functions defined on-top of a the baseline SKOS model.
+
+\begin{definition} The SKOS Baseline Model is defined as follows:
+\begin{itemize}
+	\item R be the set of all resources, as defined in [Web Architecture Document]
+	\item V = {C, A, LL, LR, SR} be one specific SKOS vocabulary, with
+	\item C ⊆ R being the set of conceptual resources of type skos:Concept.
+	\item A ⊆ R being the set of aggregation and grouping resources in SKOS, hence skos:ConceptSchema and skos:Collection.
+	\item LL being the set lexical labels, which are instances of RDF plain literals.
+	\item LR ⊆ C x LL being the set of lexical relations associating conceptual resources with lexical labels, hence instances of skos:prefLabel, skos:altLabel, or skos:hiddenLabel.
+\item SR ⊆ C x C being the set of semantic relations associating conceptual resources with concepts, hence instances of skos:semanticRelation and subproperties thereof.
+\item AR ⊆ C x A being the set of aggregation (and grouping) relations associating conceptual resources with instances of aggregation and grouping resources.
+\end{itemize}
+\end{definition}
 

### 2012-03-09 paper.tex
added baseline model and loose concepts

@@
 	\item The vocabulary developed by the Austrian Armed Forces (LVAk thesaurus\footnote{Non-public thesaurus developed by the Austrian Armed Forces}), which contains 11 disconnected concept clusters.
-Confronting the thesaurus maintainer with these structures, they recognized them as “forgotten” test data that has no practical significance.
+Confronting the thesaurus maintainers with these structures, they recognized them as “forgotten” test data that has no practical significance.
 
@@
 
-\begin{definition} The SKOS Baseline Model is defined as follows:
+\begin{definition} \textbf{The SKOS Baseline Model} is defined as follows:
+Let R be the set of all resources, as defined in [Web Architecture Document] and \[V = (C, A, LL, LR, SR, AR)\] be one specific SKOS vocabulary, with
+
 \begin{itemize}
-	\item R be the set of all resources, as defined in [Web Architecture Document]
-	\item V = {C, A, LL, LR, SR} be one specific SKOS vocabulary, with
-	\item C ⊆ R being the set of conceptual resources of type skos:Concept.
-	\item A ⊆ R being the set of aggregation and grouping resources in SKOS, hence skos:ConceptSchema and skos:Collection.
-	\item LL being the set lexical labels, which are instances of RDF plain literals.
-	\item LR ⊆ C x LL being the set of lexical relations associating conceptual resources with lexical labels, hence instances of skos:prefLabel, skos:altLabel, or skos:hiddenLabel.
-\item SR ⊆ C x C being the set of semantic relations associating conceptual resources with concepts, hence instances of skos:semanticRelation and subproperties thereof.
-\item AR ⊆ C x A being the set of aggregation (and grouping) relations associating conceptual resources with instances of aggregation and grouping resources.
+	\item \(C \subseteq R\) being the set of \textbf{conceptual resources} of type \texttt{skos:Concept}.
+	\item \(A \subseteq R\) being the set of aggregation and grouping resources in SKOS, hence \texttt{skos:ConceptSchema} and \texttt{skos:Collection}.
+	\item LL being the set \textbf{lexical labels}, which are instances of RDF plain literals.
+	\item \(LR \subseteq C \times LL\) being the set of \textbf{lexical relations} associating conceptual resources with lexical labels, hence instances of \texttt{skos:prefLabel}, \texttt{skos:altLabel}, or \texttt{skos:hiddenLabel}.
+\item \(SR \subseteq C \times C\) being the set of \textbf{semantic relations} associating conceptual resources with concepts, hence instances of \texttt{skos:semanticRelation} and subproperties thereof.
+\item \(AR \subseteq C \times A\) being the set of \textbf{aggregation (and grouping) relations} associating conceptual resources with instances of aggregation and grouping resources.
 \end{itemize}
@@
 
-\subsection{SKOS Baseline Model}
+\subsection{Graph-based Quality Criteria / Network Measures}
+The following quality criteria are all derived from a graph-based view on a given vocabulary \(v\), which we can then consider as a directed graph \(G=(N,E)\) consisting of a set of nodes \(N\) and edges \(E\).
 
-\subsection{Graph-based Quality Criteria / Network Measures}
+\subsubsection{Loose Concepts} are very similar to what is also referred to as ``orphan terms” in the literature, which are terms without any associative or hierarchical relationships \cite{Z39.19:2005,Hedden2010}.
+In a SKOS vocabulary, we define a loose concept as a concept that has no semantic or aggregation relations with other conceptual, aggregation or grouping resources.
+Although they might have attached lexical labels, they lack valuable context information.
+Checking for orphan terms is common in existing thesaurus development applications and suggested by \cite{Z39.19:2005}.
+Depending on the vocabulary development policy, loose concepts may be tolerated or considered to be a defect.
+
+To calculate the number of loose concepts, we let \(G = (C, SR \cup AR)\)  and apply \(deg(c)\) as a function that calculates the degree, hence the number of in- and outgoing edges of a node n in a graph g.
+We can then define this quality criterion as a function \(looseConcepts : G \rightarrow ℕ0\), with
+\begin{definition}
+looseConcepts(g) = \left\|\left\{c \in C : deg(c) = 0\right\}}\right\|
+\end{definition}
 

### 2012-03-09 paper.tex
added wcc and cycles

@@
 \usepackage{url}
+\usepackage{amssymb}
 
@@
 
+\begin{definition}
 To calculate the number of loose concepts, we let \(G = (C, SR \cup AR)\)  and apply \(deg(c)\) as a function that calculates the degree, hence the number of in- and outgoing edges of a node n in a graph g.
-We can then define this quality criterion as a function \(looseConcepts : G \rightarrow ℕ0\), with
+We can then define this quality criterion as a function \(looseConcepts : G \rightarrow \mathbb{N}_{0}\), with \[looseConcepts(g) = \left\|\left\{c \in C : deg(c) = 0\right\}\right\|\]
+\end{definition}
+
+\subsubsection{Weakly Connected Components} cause the vocabulary to split into separate disconnected components.
+This is very similar to the ``loose concepts” criterion introduced before and might be caused by incomplete data acquisition, ``forgotten" test data, outdated terms, accidental deletion of relations and the like.
+In a practical setting, existence of weakly connected components could render the vocabulary less suitable for operations that rely on navigating a strongly connected vocabulary structure, such as query expansion or suggestion of related terms.
+
 \begin{definition}
-looseConcepts(g) = \left\|\left\{c \in C : deg(c) = 0\right\}}\right\|
+To evaluate this criterion we consider a graph \(G = (AC, SRAR)\).
+The function \(components(g) : G \rightarrow  \mathfrak{P}(G)\) calculates all weakly connected components of a graph by replacing all directed edges by undirected edges and utilizing “Tarjan’s algorithm” \cite{Hopcroft1973}.
+Based on that function, we can express this criterion as a function \(wcc : G \rightarrow \mathbb{N}_{0}\), with \[wcc(g) = \left\|components(g)\right\|\]
+\end{definition}
+
+\subsubsection{Cyclic Hierarchical Relations} have been mentioned numerous times in thesaurus development literature.
+\cite{Soergel2002} suggests a ``check for hierarchy cycles" since they ``throw the program for a loop in the generation of a complete hierarchical structure”.
+However, the SKOS documentation does not state, how exactly hierarchical relationships are to be interpreted.
+There exist common forms like, e.g., “generic-specific”, “instance-of” or “whole-part” \cite{Hedden2011,Harpring2010,Aitchison2000} and hierarchical cycles for some of these interpretations in various domains or usage scenarios might be perfectly valid, whereas they would be treated as failures in others.
+
+\begin{definition}
+In the context of this work, we define a cycle in a SKOS vocabulary as a logical contradiction in the broader/narrower hierarchy.
+Let \(HB \subseteq SR\) be the set of broader hierarchical relations associating two conceptual resources with instances of \texttt{skos:broader}, \texttt{skos:broaderTransitive}, \texttt{skos:broadMatch} or subproperties thereof.
+\(HB\) also associates conceptual resources related with instances \texttt{skos:narrower}, \texttt{skos:narrowTransitive}, \texttt{skos:narrowMatch} or subproperties thereof in reverse order.
+Likewise, \(HN \subseteq SR\) can be defined as the set of narrower hierarchical relations.
+We consider two graphs \(GB = (C,HB)\) and \(GN=(C,HN)\) and a function \(cycleNodes:GB \cup GN \rightarrow \mathfrak{P}(C)\) identifying all nodes in a graph, that are part of a cycle.
+Furthermore we consider a function \(stronglyConnectedSets: GB \cup GN \rightarrow \mathfrak{P}(C)\) that calculates all strongly connected undirected subgraphs of a graph.
+This criterion can be defined as a function \(chr:GB \cup GN \rightarrow \mathbb{N}_{0}\) with \[chr(g)=\left\|\left\{s \in stronglyConnectedSets(g) : cn \in cycleNodes(g), cn \in s\right\}\right\|\]
 \end{definition}

### 2012-03-09 paper.tex
added structural criteria/measures

@@
 However, the SKOS documentation does not state, how exactly hierarchical relationships are to be interpreted.
-There exist common forms like, e.g., “generic-specific”, “instance-of” or “whole-part” \cite{Hedden2011,Harpring2010,Aitchison2000} and hierarchical cycles for some of these interpretations in various domains or usage scenarios might be perfectly valid, whereas they would be treated as failures in others.
+There exist common forms like, e.g., “generic-specific”, “instance-of” or “whole-part” \cite{Hedden2010,Harpring2010,Aitchison2000}.
+Hierarchical cycles for some of these interpretations in various domains or usage scenarios might be perfectly valid, whereas they would be treated as failures in others.
 
@@
 \subsection{Structure-Centric Quality Criteria / Structural Measures}
+
+\subsubsection{Redundant Associative Relations} \cite{ISO25964-1:2011} suggests that terms that share a common broader term but don’t have an overlapping meaning, should not be related associatively.
+This is also advocated by \cite{Hedden2010} and \cite{Aitchison2000} who also mentions ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships", having a negative effect on precision.
+
+\begin{definition}
+Let \(ASR \subseteq SR\) be the set of associative relations in SKOS, namely \texttt{skos:related} and \texttt{skos:relatedMatch}.
+These relations are symmetric, so \((c1,c2) \in ASR \Rightarrow (c2,c1) \in ASR\).
+Formally, this criterion can be expressed as a function \(rar:V \rightarrow \mathbb{N}_{0}\) with \[rar(v)=\left\|\left\{(c1,c2) \in ASR : c3 \in C, (c1,c3) \in HB, (c2,c3) \in HB\right\}\right\|\]
+\end{definition}
+
+\subsubsection{Number of Hierarchically and Associatively Related Concepts} \cite{Aitchison2000} mentions a ``common error in manually produced thesauri" when concepts are related both hierarchically and associatively (F1.3.2).
+\cite{Hedden2010} also proposes to check for ``pairs of terms that have more than one kind of relationship" as a feasible rule, enforced by thesaurus management software.
+
+\begin{definition}
+This criterion can be expressed as a function \(har:V \righarrow \mathbb{N}_{0}\) with \[har(v)=\left\|\left\{c \in C : c' \in C, (c,c') \in HB \cup HN, (c,c') \in ASR\right\}\right\|\]
+\end{definition}
+
+\subsubsection{Unidirectionally Related Concepts} \cite{Z39.19:2005} suggests thesaurus maintenance software to automatically add reciprocal relations (e.g., broader/narrower, related) to the resulting thesaurus.
+Vocabularies created in that manner are expected, e.g., to be better browsable for humans and provide better search results when used in systems without reasoning support.
+
+\begin{definition}
+Let \(ISR \subseteq R \times R\) be a set that associates resources defined in \(V\) that are related by a SKOS property that has an inverse SKOS property defined.
+Furthermore, ISR also associates resources that are related by a symmetric SKOS property.
+In an ideal setting \((r,r') \in ISR \iff (r',r) \in ISR\).
+Thus we can express this criterion as function \(urc:V \rightarrow \mathbb{N}_{0}\) with \[urc(v)=\left\|\left\{c \in C : r \in R, (c,r) \in ISR, (r,c) \notin ISR\right\}\right\|\]
+\end{definition}
+
+\subsubsection{Solely Transitively Related Concepts} Two concepts are related using only transitive hierarchical relations which are, according to the SKOS reference document, ``not used to make assertions".
+Transitive hierarchical relations in SKOS are meant to be infered by the vocabulary user, which is reflected in the SKOS schema by, e.g., broader being a subproperty of broaderTransitive.
+
+\begin{definition}
+Let \(TR \subseteq SR\) be the set of all conceptual resources being transitively related by \texttt{skos:broaderTransitive} respectively \texttt{skos:narrowerTransitive}, not by subproperties thereof.
+Furthermore, let \(HR \subseteq SR\) be the set of all conceptual resources being related by \textt{skos:broader} and \texttt{skos:narrower} with \((c,c') \in HR \rightarrow (c',c) \in HR\).
+We can write this criterion as a function \(str:V \rightarrow \mathbb{N}_{0}\) with \[str(v)=\left\|\left\{c \in C : c' \in C, (c,c') \in TR, (c,c') \notin HR\right\}\right\|\]
+\end{definition}
 

### 2012-03-09 paper.tex
added ld specific criteria/measures

@@
 Let \(TR \subseteq SR\) be the set of all conceptual resources being transitively related by \texttt{skos:broaderTransitive} respectively \texttt{skos:narrowerTransitive}, not by subproperties thereof.
-Furthermore, let \(HR \subseteq SR\) be the set of all conceptual resources being related by \textt{skos:broader} and \texttt{skos:narrower} with \((c,c') \in HR \rightarrow (c',c) \in HR\).
+Furthermore, let \(HR \subseteq SR\) be the set of all conceptual resources being related by \texttt{skos:broader} and \texttt{skos:narrower} with \((c,c') \in HR \Rightarrow (c',c) \in HR\).
 We can write this criterion as a function \(str:V \rightarrow \mathbb{N}_{0}\) with \[str(v)=\left\|\left\{c \in C : c' \in C, (c,c') \in TR, (c,c') \notin HR\right\}\right\|\]
@@
 \subsection{Linked Data Specific Criteria / Linked Data Measures}
+SKOS has been developed for creating knowledge organization systems that are used ``within the framework of the semantic web" \cite{Bernerslee2001}.
+Therefore we identified some criteria targeting issues related to best practises in publishing Linked Data, the underlying technology for establishing a Semantic Web \cite{Heath2011}.
+
+\subsubsection{Concept External Link Average} The ``Web of Data" consists of globally interconnected datasets, ``enabling seamless connections between data sets" \cite{Heath2011}.
+These links can be established between various SKOS vocabularies by ``external links", i.e., references from conceptual resources in a ``source vocabulary" to resources identified by an HTTP URI and available at a different host.
+
+\begin{definition}
+Let \(EL=C \times R\) be the set of external links with \(host(c) \neq host(r)\).
+This criterion can then be written as a function \(elc:V \righarrow \mathbb{ℚ}\) with \[elc(v)=\frac{\left\|EL\right\|}{\left\|C\right\|}\]
+\end{definition}
+
+\subsection{HTTP URI Scheme Violation} One of the key concept of Linked Data is that URIs should be dereferencable in order to browse through data in the same way as through ``traditional" Web pages.
+Using HTTP URIs therefore is the logical consequence and mentioned numerous time in literature \cite{Heath2011}.
+However, some vocabularies use other URI schemes such as URNs and DOIs when defining resources, which impedes data lookup and crawling purposes.
+
+\begin{definition}
+Let \(VR \subseteq C \cup A\) be the set of vocabulary resources identified by an URI (not by a blank node).
+We can define a function \(httpScheme:R \rightarrow \left\{0,1\right\}\) with \(httpScheme(r)=1\) if the scheme part of the URI is http or https, 0 otherwise.
+Then this criterion can be written as a function \(usv:V \rightarrow \mathbb{N}_{0}\) with \[usv(v)=\left\|\left\{vr \in VR : httpScheme(vr)=0\right\}\right\|\]
+\end{definition}
+
+\subsubsection{Link Target Unavailability} Just as in the ``traditional" Web, resources in the Web of Data might also be unavailable, i.e.
+resolving their URI leads to an erroneous HTTP response or no response at all.
+An erroneous HTTP response in that case can be defined as a response code (after a possible redirection) other than 200.
+Since these ``broken links" hinder information gathering, they should be avoided.
+
+\begin{definition}
+Let \(LR \subseteq R\) be the set of all resources being related to conceptual, aggregational and grouping resources.
+The function \(resp:R \rightarrow \mathbb{N}\) assigns a resource its HTTP response code after following all redirections.
+We can therefore write this criterion as function \(ltu:V \rightarrow \mathbb{N}_{0}\) with \[ltu(v)=\left\|\left\{r \in LR \cup VR : resp(r)=200\right\}\right\|\]
+\end{definition}
+
+\subsubsection{Average Concept In-degree} A periodically updated version of a diagram visualizing ``the data sets in the LOD cloud as well as their interlinkage relationships” is published online \footnote{http://www4.wiwiss.fu-berlin.de/lodcloud/state/}.
+In these diagrams, DBpedia \footnote{http://dbpedia.org/About} is shown as the most intensely linked resource, i.e.
+a large number of vocabularies link to resources in that dataset.
+Therefore a dataset with a large number of other datasets referencing it, can be assumed to be of great value for the community.
+Accordingly, estimating the number of ``incoming links" of SKOS concepts defined in a vocabulary (henceforth called the in-degree of a concept) would give some hint about how established or accepted a controlled vocabulary is.
+A method to carry out these estimations would be utilizing existing Linked Data indices like, e.g., Sindice \footnote{http://sindice.com/} that provide a SPARQL endpoint.
+
+\begin{definition}
+Let \(U\) be the universe of all datasets on the Web and \(V \in U\).
+The set \(RR \subseteq R \times R\) contains all resources in distinct datasets related by an RDF property with \((r1,r2) \in RR \Rightarrow host(r1) \neq host(r2)\).
+This criterion can be written as a function \(aci:V \rightarrow \mathbb{ℚ}\) with \[aci(v)=\frac{\left\|\left\{r \in R : c \in C, (r,c) \in RR\right\}\right|}{\left\|C\right\|}\]
+\end{definition}
 

### 2012-03-09 paper.tex
added lncs files

@@
 
-\subsubsection{Number of Hierarchically and Associatively Related Concepts} \cite{Aitchison2000} mentions a ``common error in manually produced thesauri" when concepts are related both hierarchically and associatively (F1.3.2).
+\subsubsection{Number of Hierarchically and Associatively Related Concepts}\label{harc} \cite{Aitchison2000} mentions a ``common error in manually produced thesauri" when concepts are related both hierarchically and associatively (F1.3.2).
 \cite{Hedden2010} also proposes to check for ``pairs of terms that have more than one kind of relationship" as a feasible rule, enforced by thesaurus management software.
@@
 
-\subsection{HTTP URI Scheme Violation} One of the key concept of Linked Data is that URIs should be dereferencable in order to browse through data in the same way as through ``traditional" Web pages.
+\subsubsection{HTTP URI Scheme Violation} One of the key concept of Linked Data is that URIs should be dereferencable in order to browse through data in the same way as through ``traditional" Web pages.
 Using HTTP URIs therefore is the logical consequence and mentioned numerous time in literature \cite{Heath2011}.
@@
 
-\subsubsection{Average Concept In-degree} A periodically updated version of a diagram visualizing ``the data sets in the LOD cloud as well as their interlinkage relationships” is published online \footnote{http://www4.wiwiss.fu-berlin.de/lodcloud/state/}.
+\subsubsection{Average Concept In-degree} A periodically updated version of a diagram visualizing ``the data sets in the LOD cloud as well as their interlinkage relationships” is published online\footnote{http://www4.wiwiss.fu-berlin.de/lodcloud/state/}.
 In these diagrams, DBpedia \footnote{http://dbpedia.org/About} is shown as the most intensely linked resource, i.e.
@@
 Accordingly, estimating the number of ``incoming links" of SKOS concepts defined in a vocabulary (henceforth called the in-degree of a concept) would give some hint about how established or accepted a controlled vocabulary is.
-A method to carry out these estimations would be utilizing existing Linked Data indices like, e.g., Sindice \footnote{http://sindice.com/} that provide a SPARQL endpoint.
+A method to carry out these estimations would be utilizing existing Linked Data indices like, e.g., Sindice\footnote{http://sindice.com/} that provide a SPARQL endpoint.
 
@@
 \subsection{SKOS-Specific Criteria / SKOS Semantic Measures}
+\subsubsection{Associative vs.
+Hierarchical Relation Clashes} This criterion is similar to criterion ??\ref{harc}??, however it strictly covers integrity condition S27 from the SKOS reference document, i.e.
+involving the transitive hull of hierarchical relations, not taking into account hierarchical mapping properties.
+
+\begin{definition}
+Let \(CBR \subseteq SR\) and \(CNR \subseteq SR\) be the set of conceptual resources being hierarchically broader respectively narrower related within the same concept scheme by the properties \texttt{skos:broader} and \texttt{skos:narrower}.
+Furthermore, the set \(REL \subseteq SR\) contains all conceptual resources related by the \texttt{skos:related} property.
+We consider two directed graphs \(GB=(C,CBR)\) and \(GN=(C,CNR)\) and a function hierarchical:C \times C \rightarrow \left\{0,1\right\} with \(hierarchical((c,c'))=1\) if a path between c and c’ exists in either \(GB\) or \(GN\), 0 otherwise.
+This criterion can then be written as a function \(ahrc:G \rightarrow \mathbb{N}_{0}\) with \[ahrc(g)=\left\|\left\{(c,c') \in REL:hierarchical((c,c'))=1\right\}\right\|\]
+\end{definition}
+
+\subsubsection{Exact vs.
+Associative and Hierarchical Mapping Clashes} Integrity condition S46 of the SKOS reference document states disjointness of the property \texttt{skos:exactMatch} with \texttt{skos:broadMatch} and \texttt{skos:relatedMatch}.
+
+\begin{definition}
+Let \(EM \subseteq SR\), \(BM \subseteq SR\), \(RM \subseteq SR\) be the set of conceptual resources related by \texttt{skos:exactMatch}, \texttt{skos:broadMatch}, and \texttt{skos:relatedMatch}.
+In functional form, this criteria can be written as \(eahmc:V \rightarrow \mathbb{N}_{0}\) with \[eahmc(v)=\left\|\left\{em \in EM : em \in BM \cup RM\right\}\right|\]
+\end{definition}
+
+\subsubsection{Illegal SKOS Terms} Vocabularies expressed in the SKOS language can be easily be extended by proprietary classes or properties in order to meet certain requirements of the publishing organizations that cannot (yet) be expressed within the SKOS schema.
+However, there seems to exist a misunderstanding in some vocabularies about the correct way of introducing new classes or properties in an OWL document.
+In some cases, vocabularies ``invent" new terms in the SKOS namespace that cannot be resolved.
+This criterion has been identified as ``Use of undefined classes and properties" in \cite{Hogan2010}.
+
+\subsubsection{Deprecated Property Usage} With the SKOS W3C recommendation maturing, some properties have been removed from the current version of the schema.
+Vocabularies using these ``deprecated" properties hence contain parts of their information in a non ``standard"-compliant way, having negative effects when, e.g., crawling vocabularies to gather specific information.
+
+\begin{definition}
+We define a set that contains all deprecated properties DP=\left\{\texttt{skos:symbol}, \texttt{skos:prefSymbol}, \texttt{skos:altSymbol}, \texttt{skos:CollectableProperty}, \texttt{skos:subject}, \texttt{skos:isSubjectOf}, \texttt{skos:primarySubject}, \texttt{skos:isPrimarySubjectOf}, \texttt{skos:subjectIndicator}\right\}.
+Let \(DR \subseteq RV \times RV\) with \(RV \subseteq R\) being the set of all RDF resources in V that are related by a property in DP.
+This criterion can then be written as a function \(dpu:V \rightarrow \mathbb{N}_{0}\) with \[dpu(v)=\left\|DR\right\|\]
+\end{definition}
 

### 2012-03-09 analysis.tex
split files

--- 2012-03-09 paper.tex
@@
-\documentclass{llncs}
-
-\usepackage{verbatim}
-\usepackage{url}
-\usepackage{amssymb}
-
-\title{Quality Criteria for SKOS Vocabularies}
-\author{Christian Mader\inst{1} \and Bernhard Haslhofer\inst{2}}
-\institute{
-	University of Vienna, Faculty of Computer Science\\\email{christian.mader@univie.ac.at}
-	\and Cornell University, Information Science\\\email{bernhard.haslhofer@cornell.edu}}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-\end{abstract}
-
-\section{Introduction}
-The Simple Knowledge Organization System (SKOS\footnote{Simple Knowledge Organization System, \url{http://www.w3.org/2004/02/skos/}}) has become a de-facto standard for expressing controlled vocabularies on the Web.
-Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} have created SKOS representations of their controlled vocabularies and published them on the Web so that they can easily be navigated and reused by humans and, most importantly, also by applications.
-Each vocabulary is the result of a specific design process that reflects domain-specific requirements as well as the target audience the vocabulary is created for.
-Orthogonal to the design process, vocabulary \textbf{designers and maintainers} usually apply existing guidelines or follow their own rules when defining concepts, in order to meet their \textbf{quality requirements} as, for instance, described in \cite{Coronado2009}.
-As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality, which can affect their interoperability and applicability for tasks like query expansion, faceted browsing, clustering, or auto-complete suggestions.
-
-The following representative examples, which we identified by looking at real-world SKOS vocabularies, illustrate the \textbf{quality problems} applications could face when making use of them:
-\begin{itemize}
-	\item The SKOS version of Agrovoc defines concepts in 25 different languages.
-However, almost all concepts have an English description, 38\% of all concepts don’t have German labels attached.
-This can be a problem for applications that use Agrovoc and rely on German translations.
-
-	\item The previous version of the STW thesaurus, contained 5 pairs of concepts with identical labels.
-As a result, the auto-complete function of the online search interface suggested identical entries, with no disambiguation information.
-
-	\item The vocabulary developed by the Austrian Armed Forces (LVAk thesaurus\footnote{Non-public thesaurus developed by the Austrian Armed Forces}), which contains 11 disconnected concept clusters.
-Confronting the thesaurus maintainers with these structures, they recognized them as “forgotten” test data that has no practical significance.
-
-	\item In the DBpedia category\footnote{\url{http://downloads.dbpedia.org/3.7/en/skos_categories_en.nt.bz2}} hierarchy, more than 10 percent of the categories not linked to any other category.
-When other vocabularies link to the DBPedia categories, e.g., to enable query expansion, it can negatively affect recall and reduce navigability.
-\end{itemize}
-
-One reason for these quality problems is that SKOS currently only defines a set of \textbf{low-level integrity conditions}, which, when being enforced, ensure the structural and semantic requirements of the SKOS specifications but fail to capture \textbf{higher-level quality issues}, as those mentioned in the examples before.
-Another problem is that existing vocabulary design guidelines and best practices purely rely on \textbf{human assessment}, which is highly subjective and doesn’t scale when vocabulary quality assessment should be performed on larger, possibly linked Web vocabularies.
-
-We believe, and recent developments of quality checking tools (e.g., PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}}, qSKOS\footnote{\url{https://github.com/cmader/qSKOS}}, SKOSify\footnote{\url{http://code.google.com/p/skosify/}}) support this motivation.
-This, however, requires a formalization of the notion of quality with respect to SKOS vocabularies, which can be used in order to consistently implement quality assessment procedures across tools.
-Since, the notion of “quality” with respect to SKOS vocabularies naturally varies across application domains it is hard, if not impossible, to come up with a general definition of quality.
-However, we believe that vocabulary designers can apply a set of \textbf{formal quality criteria} on given vocabularies in order to assess whether or not a vocabulary fulfills their requirements.
-Since these criteria are based on a formal definition, they can be calculated by automated tools, which helps vocabulary designers in assessing the quality of available or newly created vocabularies and provide important feedback to the overall vocabulary design process.
-
-The main contributions of this work can be summarized as follows:
-\begin{itemize}
-	\item We derived a \textbf{quality criteria catalogue} from existing literature, tools, and public mailing list discussions in the community.
-We \textbf{formalized} each criterion and implemented them in the \textbf{qSKOS quality assessment tool}.
-
-	\item We \textbf{analyzed} a representative \textbf{set of existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.
-\end{itemize}
-
-The results from our studies show that... TBD
-
-\section{A Quality Model for SKOS}
-SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption.
-Established quality notions from closed-world systems, such as constraints, referential integrity or schema validation, don’t hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false.
-While trust and provenance models for Web data are being developed \cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets \cite{Heath2011}.
-
-Based on the findings from a literature survey we now define a set of quantifiable quality criteria for SKOS vocabularies.
-For each \textbf{criterion} we explain our design rationale, and provide a semi-formal definition, which is based on a set-theoretic conception of the SKOS model.
-Tools can implement these criteria as functions defined on-top of a the baseline SKOS model.
-
-\begin{definition} \textbf{The SKOS Baseline Model} is defined as follows:
-Let R be the set of all resources, as defined in [Web Architecture Document] and \[V = (C, A, LL, LR, SR, AR)\] be one specific SKOS vocabulary, with
-
-\begin{itemize}
-	\item \(C \subseteq R\) being the set of \textbf{conceptual resources} of type \texttt{skos:Concept}.
-	\item \(A \subseteq R\) being the set of aggregation and grouping resources in SKOS, hence \texttt{skos:ConceptSchema} and \texttt{skos:Collection}.
-	\item LL being the set \textbf{lexical labels}, which are instances of RDF plain literals.
-	\item \(LR \subseteq C \times LL\) being the set of \textbf{lexical relations} associating conceptual resources with lexical labels, hence instances of \texttt{skos:prefLabel}, \texttt{skos:altLabel}, or \texttt{skos:hiddenLabel}.
-\item \(SR \subseteq C \times C\) being the set of \textbf{semantic relations} associating conceptual resources with concepts, hence instances of \texttt{skos:semanticRelation} and subproperties thereof.
-\item \(AR \subseteq C \times A\) being the set of \textbf{aggregation (and grouping) relations} associating conceptual resources with instances of aggregation and grouping resources.
-\end{itemize}
-\end{definition}
-
-\subsection{Graph-based Quality Criteria / Network Measures}
-The following quality criteria are all derived from a graph-based view on a given vocabulary \(v\), which we can then consider as a directed graph \(G=(N,E)\) consisting of a set of nodes \(N\) and edges \(E\).
-
-\subsubsection{Loose Concepts} are very similar to what is also referred to as ``orphan terms” in the literature, which are terms without any associative or hierarchical relationships \cite{Z39.19:2005,Hedden2010}.
-In a SKOS vocabulary, we define a loose concept as a concept that has no semantic or aggregation relations with other conceptual, aggregation or grouping resources.
-Although they might have attached lexical labels, they lack valuable context information.
-Checking for orphan terms is common in existing thesaurus development applications and suggested by \cite{Z39.19:2005}.
-Depending on the vocabulary development policy, loose concepts may be tolerated or considered to be a defect.
-
-\begin{definition}
-To calculate the number of loose concepts, we let \(G = (C, SR \cup AR)\)  and apply \(deg(c)\) as a function that calculates the degree, hence the number of in- and outgoing edges of a node n in a graph g.
-We can then define this quality criterion as a function \(looseConcepts : G \rightarrow \mathbb{N}_{0}\), with \[looseConcepts(g) = \left\|\left\{c \in C : deg(c) = 0\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Weakly Connected Components} cause the vocabulary to split into separate disconnected components.
-This is very similar to the ``loose concepts” criterion introduced before and might be caused by incomplete data acquisition, ``forgotten" test data, outdated terms, accidental deletion of relations and the like.
-In a practical setting, existence of weakly connected components could render the vocabulary less suitable for operations that rely on navigating a strongly connected vocabulary structure, such as query expansion or suggestion of related terms.
-
-\begin{definition}
-To evaluate this criterion we consider a graph \(G = (AC, SRAR)\).
-The function \(components(g) : G \rightarrow  \mathfrak{P}(G)\) calculates all weakly connected components of a graph by replacing all directed edges by undirected edges and utilizing “Tarjan’s algorithm” \cite{Hopcroft1973}.
-Based on that function, we can express this criterion as a function \(wcc : G \rightarrow \mathbb{N}_{0}\), with \[wcc(g) = \left\|components(g)\right\|\]
-\end{definition}
-
-\subsubsection{Cyclic Hierarchical Relations} have been mentioned numerous times in thesaurus development literature.
-\cite{Soergel2002} suggests a ``check for hierarchy cycles" since they ``throw the program for a loop in the generation of a complete hierarchical structure”.
-However, the SKOS documentation does not state, how exactly hierarchical relationships are to be interpreted.
-There exist common forms like, e.g., “generic-specific”, “instance-of” or “whole-part” \cite{Hedden2010,Harpring2010,Aitchison2000}.
-Hierarchical cycles for some of these interpretations in various domains or usage scenarios might be perfectly valid, whereas they would be treated as failures in others.
-
-\begin{definition}
-In the context of this work, we define a cycle in a SKOS vocabulary as a logical contradiction in the broader/narrower hierarchy.
-Let \(HB \subseteq SR\) be the set of broader hierarchical relations associating two conceptual resources with instances of \texttt{skos:broader}, \texttt{skos:broaderTransitive}, \texttt{skos:broadMatch} or subproperties thereof.
-\(HB\) also associates conceptual resources related with instances \texttt{skos:narrower}, \texttt{skos:narrowTransitive}, \texttt{skos:narrowMatch} or subproperties thereof in reverse order.
-Likewise, \(HN \subseteq SR\) can be defined as the set of narrower hierarchical relations.
-We consider two graphs \(GB = (C,HB)\) and \(GN=(C,HN)\) and a function \(cycleNodes:GB \cup GN \rightarrow \mathfrak{P}(C)\) identifying all nodes in a graph, that are part of a cycle.
-Furthermore we consider a function \(stronglyConnectedSets: GB \cup GN \rightarrow \mathfrak{P}(C)\) that calculates all strongly connected undirected subgraphs of a graph.
-This criterion can be defined as a function \(chr:GB \cup GN \rightarrow \mathbb{N}_{0}\) with \[chr(g)=\left\|\left\{s \in stronglyConnectedSets(g) : cn \in cycleNodes(g), cn \in s\right\}\right\|\]
-\end{definition}
-
-\subsection{Structure-Centric Quality Criteria / Structural Measures}
-
-\subsubsection{Redundant Associative Relations} \cite{ISO25964-1:2011} suggests that terms that share a common broader term but don’t have an overlapping meaning, should not be related associatively.
-This is also advocated by \cite{Hedden2010} and \cite{Aitchison2000} who also mentions ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships", having a negative effect on precision.
-
-\begin{definition}
-Let \(ASR \subseteq SR\) be the set of associative relations in SKOS, namely \texttt{skos:related} and \texttt{skos:relatedMatch}.
-These relations are symmetric, so \((c1,c2) \in ASR \Rightarrow (c2,c1) \in ASR\).
-Formally, this criterion can be expressed as a function \(rar:V \rightarrow \mathbb{N}_{0}\) with \[rar(v)=\left\|\left\{(c1,c2) \in ASR : c3 \in C, (c1,c3) \in HB, (c2,c3) \in HB\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Number of Hierarchically and Associatively Related Concepts} \cite{Aitchison2000} mentions a ``common error in manually produced thesauri" when concepts are related both hierarchically and associatively (F1.3.2).
-\cite{Hedden2010} also proposes to check for ``pairs of terms that have more than one kind of relationship" as a feasible rule, enforced by thesaurus management software.
-
-\begin{definition}
-This criterion can be expressed as a function \(har:V \righarrow \mathbb{N}_{0}\) with \[har(v)=\left\|\left\{c \in C : c' \in C, (c,c') \in HB \cup HN, (c,c') \in ASR\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Unidirectionally Related Concepts} \cite{Z39.19:2005} suggests thesaurus maintenance software to automatically add reciprocal relations (e.g., broader/narrower, related) to the resulting thesaurus.
-Vocabularies created in that manner are expected, e.g., to be better browsable for humans and provide better search results when used in systems without reasoning support.
-
-\begin{definition}
-Let \(ISR \subseteq R \times R\) be a set that associates resources defined in \(V\) that are related by a SKOS property that has an inverse SKOS property defined.
-Furthermore, ISR also associates resources that are related by a symmetric SKOS property.
-In an ideal setting \((r,r') \in ISR \iff (r',r) \in ISR\).
-Thus we can express this criterion as function \(urc:V \rightarrow \mathbb{N}_{0}\) with \[urc(v)=\left\|\left\{c \in C : r \in R, (c,r) \in ISR, (r,c) \notin ISR\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Solely Transitively Related Concepts} Two concepts are related using only transitive hierarchical relations which are, according to the SKOS reference document, ``not used to make assertions".
-Transitive hierarchical relations in SKOS are meant to be infered by the vocabulary user, which is reflected in the SKOS schema by, e.g., broader being a subproperty of broaderTransitive.
-
-\begin{definition}
-Let \(TR \subseteq SR\) be the set of all conceptual resources being transitively related by \texttt{skos:broaderTransitive} respectively \texttt{skos:narrowerTransitive}, not by subproperties thereof.
-Furthermore, let \(HR \subseteq SR\) be the set of all conceptual resources being related by \textt{skos:broader} and \texttt{skos:narrower} with \((c,c') \in HR \rightarrow (c',c) \in HR\).
-We can write this criterion as a function \(str:V \rightarrow \mathbb{N}_{0}\) with \[str(v)=\left\|\left\{c \in C : c' \in C, (c,c') \in TR, (c,c') \notin HR\right\}\right\|\]
-\end{definition}
-
-\subsection{Linked Data Specific Criteria / Linked Data Measures}
-
-\subsection{SKOS-Specific Criteria / SKOS Semantic Measures}
-
-\subsection{Labeling Issues}
-
-\subsection{Other Criteria}
-
-\section{Analysis of Existing SKOS Vocabularies}
+\section{Analysis of Existing SKOS Vocabularies}\label{sec:analysis}
 
@@
 \subsection{Results}
-
-\section{Related Work}
-
-\section{Conclusions and Future Work}
-
-\bibliography{lit}
-\bibliographystyle{splncs03}
-
-\end{document}

### 2012-03-09 conclusions.tex
split files

\section{Conclusions and Future Work}\label{sec:conclusions}

### 2012-03-09 introduction.tex
split files

--- 2012-03-09 paper.tex
@@
-\documentclass{llncs}
+\section{Introduction}\label{sec:introduction}
 
-\usepackage{verbatim}
-\usepackage{url}
-\usepackage{amssymb}
-
-\title{Quality Criteria for SKOS Vocabularies}
-\author{Christian Mader\inst{1} \and Bernhard Haslhofer\inst{2}}
-\institute{
-	University of Vienna, Faculty of Computer Science\\\email{christian.mader@univie.ac.at}
-	\and Cornell University, Information Science\\\email{bernhard.haslhofer@cornell.edu}}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-\end{abstract}
-
-\section{Introduction}
 The Simple Knowledge Organization System (SKOS\footnote{Simple Knowledge Organization System, \url{http://www.w3.org/2004/02/skos/}}) has become a de-facto standard for expressing controlled vocabularies on the Web.
@@
 The results from our studies show that... TBD
-
-\section{A Quality Model for SKOS}
-SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption.
-Established quality notions from closed-world systems, such as constraints, referential integrity or schema validation, don’t hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false.
-While trust and provenance models for Web data are being developed \cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets \cite{Heath2011}.
-
-Based on the findings from a literature survey we now define a set of quantifiable quality criteria for SKOS vocabularies.
-For each \textbf{criterion} we explain our design rationale, and provide a semi-formal definition, which is based on a set-theoretic conception of the SKOS model.
-Tools can implement these criteria as functions defined on-top of a the baseline SKOS model.
-
-\begin{definition} \textbf{The SKOS Baseline Model} is defined as follows:
-Let R be the set of all resources, as defined in [Web Architecture Document] and \[V = (C, A, LL, LR, SR, AR)\] be one specific SKOS vocabulary, with
-
-\begin{itemize}
-	\item \(C \subseteq R\) being the set of \textbf{conceptual resources} of type \texttt{skos:Concept}.
-	\item \(A \subseteq R\) being the set of aggregation and grouping resources in SKOS, hence \texttt{skos:ConceptSchema} and \texttt{skos:Collection}.
-	\item LL being the set \textbf{lexical labels}, which are instances of RDF plain literals.
-	\item \(LR \subseteq C \times LL\) being the set of \textbf{lexical relations} associating conceptual resources with lexical labels, hence instances of \texttt{skos:prefLabel}, \texttt{skos:altLabel}, or \texttt{skos:hiddenLabel}.
-\item \(SR \subseteq C \times C\) being the set of \textbf{semantic relations} associating conceptual resources with concepts, hence instances of \texttt{skos:semanticRelation} and subproperties thereof.
-\item \(AR \subseteq C \times A\) being the set of \textbf{aggregation (and grouping) relations} associating conceptual resources with instances of aggregation and grouping resources.
-\end{itemize}
-\end{definition}
-
-\subsection{Graph-based Quality Criteria / Network Measures}
-The following quality criteria are all derived from a graph-based view on a given vocabulary \(v\), which we can then consider as a directed graph \(G=(N,E)\) consisting of a set of nodes \(N\) and edges \(E\).
-
-\subsubsection{Loose Concepts} are very similar to what is also referred to as ``orphan terms” in the literature, which are terms without any associative or hierarchical relationships \cite{Z39.19:2005,Hedden2010}.
-In a SKOS vocabulary, we define a loose concept as a concept that has no semantic or aggregation relations with other conceptual, aggregation or grouping resources.
-Although they might have attached lexical labels, they lack valuable context information.
-Checking for orphan terms is common in existing thesaurus development applications and suggested by \cite{Z39.19:2005}.
-Depending on the vocabulary development policy, loose concepts may be tolerated or considered to be a defect.
-
-\begin{definition}
-To calculate the number of loose concepts, we let \(G = (C, SR \cup AR)\)  and apply \(deg(c)\) as a function that calculates the degree, hence the number of in- and outgoing edges of a node n in a graph g.
-We can then define this quality criterion as a function \(looseConcepts : G \rightarrow \mathbb{N}_{0}\), with \[looseConcepts(g) = \left\|\left\{c \in C : deg(c) = 0\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Weakly Connected Components} cause the vocabulary to split into separate disconnected components.
-This is very similar to the ``loose concepts” criterion introduced before and might be caused by incomplete data acquisition, ``forgotten" test data, outdated terms, accidental deletion of relations and the like.
-In a practical setting, existence of weakly connected components could render the vocabulary less suitable for operations that rely on navigating a strongly connected vocabulary structure, such as query expansion or suggestion of related terms.
-
-\begin{definition}
-To evaluate this criterion we consider a graph \(G = (AC, SRAR)\).
-The function \(components(g) : G \rightarrow  \mathfrak{P}(G)\) calculates all weakly connected components of a graph by replacing all directed edges by undirected edges and utilizing “Tarjan’s algorithm” \cite{Hopcroft1973}.
-Based on that function, we can express this criterion as a function \(wcc : G \rightarrow \mathbb{N}_{0}\), with \[wcc(g) = \left\|components(g)\right\|\]
-\end{definition}
-
-\subsubsection{Cyclic Hierarchical Relations} have been mentioned numerous times in thesaurus development literature.
-\cite{Soergel2002} suggests a ``check for hierarchy cycles" since they ``throw the program for a loop in the generation of a complete hierarchical structure”.
-However, the SKOS documentation does not state, how exactly hierarchical relationships are to be interpreted.
-There exist common forms like, e.g., “generic-specific”, “instance-of” or “whole-part” \cite{Hedden2010,Harpring2010,Aitchison2000}.
-Hierarchical cycles for some of these interpretations in various domains or usage scenarios might be perfectly valid, whereas they would be treated as failures in others.
-
-\begin{definition}
-In the context of this work, we define a cycle in a SKOS vocabulary as a logical contradiction in the broader/narrower hierarchy.
-Let \(HB \subseteq SR\) be the set of broader hierarchical relations associating two conceptual resources with instances of \texttt{skos:broader}, \texttt{skos:broaderTransitive}, \texttt{skos:broadMatch} or subproperties thereof.
-\(HB\) also associates conceptual resources related with instances \texttt{skos:narrower}, \texttt{skos:narrowTransitive}, \texttt{skos:narrowMatch} or subproperties thereof in reverse order.
-Likewise, \(HN \subseteq SR\) can be defined as the set of narrower hierarchical relations.
-We consider two graphs \(GB = (C,HB)\) and \(GN=(C,HN)\) and a function \(cycleNodes:GB \cup GN \rightarrow \mathfrak{P}(C)\) identifying all nodes in a graph, that are part of a cycle.
-Furthermore we consider a function \(stronglyConnectedSets: GB \cup GN \rightarrow \mathfrak{P}(C)\) that calculates all strongly connected undirected subgraphs of a graph.
-This criterion can be defined as a function \(chr:GB \cup GN \rightarrow \mathbb{N}_{0}\) with \[chr(g)=\left\|\left\{s \in stronglyConnectedSets(g) : cn \in cycleNodes(g), cn \in s\right\}\right\|\]
-\end{definition}
-
-\subsection{Structure-Centric Quality Criteria / Structural Measures}
-
-\subsubsection{Redundant Associative Relations} \cite{ISO25964-1:2011} suggests that terms that share a common broader term but don’t have an overlapping meaning, should not be related associatively.
-This is also advocated by \cite{Hedden2010} and \cite{Aitchison2000} who also mentions ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships", having a negative effect on precision.
-
-\begin{definition}
-Let \(ASR \subseteq SR\) be the set of associative relations in SKOS, namely \texttt{skos:related} and \texttt{skos:relatedMatch}.
-These relations are symmetric, so \((c1,c2) \in ASR \Rightarrow (c2,c1) \in ASR\).
-Formally, this criterion can be expressed as a function \(rar:V \rightarrow \mathbb{N}_{0}\) with \[rar(v)=\left\|\left\{(c1,c2) \in ASR : c3 \in C, (c1,c3) \in HB, (c2,c3) \in HB\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Number of Hierarchically and Associatively Related Concepts} \cite{Aitchison2000} mentions a ``common error in manually produced thesauri" when concepts are related both hierarchically and associatively (F1.3.2).
-\cite{Hedden2010} also proposes to check for ``pairs of terms that have more than one kind of relationship" as a feasible rule, enforced by thesaurus management software.
-
-\begin{definition}
-This criterion can be expressed as a function \(har:V \righarrow \mathbb{N}_{0}\) with \[har(v)=\left\|\left\{c \in C : c' \in C, (c,c') \in HB \cup HN, (c,c') \in ASR\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Unidirectionally Related Concepts} \cite{Z39.19:2005} suggests thesaurus maintenance software to automatically add reciprocal relations (e.g., broader/narrower, related) to the resulting thesaurus.
-Vocabularies created in that manner are expected, e.g., to be better browsable for humans and provide better search results when used in systems without reasoning support.
-
-\begin{definition}
-Let \(ISR \subseteq R \times R\) be a set that associates resources defined in \(V\) that are related by a SKOS property that has an inverse SKOS property defined.
-Furthermore, ISR also associates resources that are related by a symmetric SKOS property.
-In an ideal setting \((r,r') \in ISR \iff (r',r) \in ISR\).
-Thus we can express this criterion as function \(urc:V \rightarrow \mathbb{N}_{0}\) with \[urc(v)=\left\|\left\{c \in C : r \in R, (c,r) \in ISR, (r,c) \notin ISR\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Solely Transitively Related Concepts} Two concepts are related using only transitive hierarchical relations which are, according to the SKOS reference document, ``not used to make assertions".
-Transitive hierarchical relations in SKOS are meant to be infered by the vocabulary user, which is reflected in the SKOS schema by, e.g., broader being a subproperty of broaderTransitive.
-
-\begin{definition}
-Let \(TR \subseteq SR\) be the set of all conceptual resources being transitively related by \texttt{skos:broaderTransitive} respectively \texttt{skos:narrowerTransitive}, not by subproperties thereof.
-Furthermore, let \(HR \subseteq SR\) be the set of all conceptual resources being related by \textt{skos:broader} and \texttt{skos:narrower} with \((c,c') \in HR \rightarrow (c',c) \in HR\).
-We can write this criterion as a function \(str:V \rightarrow \mathbb{N}_{0}\) with \[str(v)=\left\|\left\{c \in C : c' \in C, (c,c') \in TR, (c,c') \notin HR\right\}\right\|\]
-\end{definition}
-
-\subsection{Linked Data Specific Criteria / Linked Data Measures}
-
-\subsection{SKOS-Specific Criteria / SKOS Semantic Measures}
-
-\subsection{Labeling Issues}
-
-\subsection{Other Criteria}
-
-\section{Analysis of Existing SKOS Vocabularies}
-
-\subsection{The qSKOS Quality Checking Tool}
-
-\subsection{Vocabularies}
-
-\subsection{Results}
-
-\section{Related Work}
-
-\section{Conclusions and Future Work}
-
-\bibliography{lit}
-\bibliographystyle{splncs03}
-
-\end{document}

### 2012-03-09 paper.tex
addes skos-related issues

@@
 To calculate the number of loose concepts, we let \(G = (C, SR \cup AR)\)  and apply \(deg(c)\) as a function that calculates the degree, hence the number of in- and outgoing edges of a node n in a graph g.
-We can then define this quality criterion as a function \(looseConcepts : G \rightarrow \mathbb{N}_{0}\), with \[looseConcepts(g) = \left\|\left\{c \in C : deg(c) = 0\right\}\right\|\]
+We can then define this quality criterion as a function \(looseConcepts : G \rightarrow \mathbb{N}_{0}\), with \[looseConcepts(g) = \left|\left\{c \in C : deg(c) = 0\right\}\right|\]
 \end{definition}
@@
 The function \(components(g) : G \rightarrow  \mathfrak{P}(G)\) calculates all weakly connected components of a graph by replacing all directed edges by undirected edges and utilizing “Tarjan’s algorithm” \cite{Hopcroft1973}.
-Based on that function, we can express this criterion as a function \(wcc : G \rightarrow \mathbb{N}_{0}\), with \[wcc(g) = \left\|components(g)\right\|\]
+Based on that function, we can express this criterion as a function \(wcc : G \rightarrow \mathbb{N}_{0}\), with \[wcc(g) = \left|components(g)\right|\]
 \end{definition}
@@
 Furthermore we consider a function \(stronglyConnectedSets: GB \cup GN \rightarrow \mathfrak{P}(C)\) that calculates all strongly connected undirected subgraphs of a graph.
-This criterion can be defined as a function \(chr:GB \cup GN \rightarrow \mathbb{N}_{0}\) with \[chr(g)=\left\|\left\{s \in stronglyConnectedSets(g) : cn \in cycleNodes(g), cn \in s\right\}\right\|\]
+This criterion can be defined as a function \(chr:GB \cup GN \rightarrow \mathbb{N}_{0}\) with \[chr(g)=\left|\left\{s \in stronglyConnectedSets(g) : cn \in cycleNodes(g), cn \in s\right\}\right|\]
 \end{definition}
@@
 These relations are symmetric, so \((c1,c2) \in ASR \Rightarrow (c2,c1) \in ASR\).
-Formally, this criterion can be expressed as a function \(rar:V \rightarrow \mathbb{N}_{0}\) with \[rar(v)=\left\|\left\{(c1,c2) \in ASR : c3 \in C, (c1,c3) \in HB, (c2,c3) \in HB\right\}\right\|\]
+Formally, this criterion can be expressed as a function \(rar:V \rightarrow \mathbb{N}_{0}\) with \[rar(v)=\left|\left\{(c1,c2) \in ASR : c3 \in C, (c1,c3) \in HB, (c2,c3) \in HB\right\}\right|\]
 \end{definition}
@@
 \begin{definition}
-This criterion can be expressed as a function \(har:V \righarrow \mathbb{N}_{0}\) with \[har(v)=\left\|\left\{c \in C : c' \in C, (c,c') \in HB \cup HN, (c,c') \in ASR\right\}\right\|\]
+This criterion can be expressed as a function \(har:V \righarrow \mathbb{N}_{0}\) with \[har(v)=\left|\left\{c \in C : c' \in C, (c,c') \in HB \cup HN, (c,c') \in ASR\right\}\right|\]
 \end{definition}
@@
 In an ideal setting \((r,r') \in ISR \iff (r',r) \in ISR\).
-Thus we can express this criterion as function \(urc:V \rightarrow \mathbb{N}_{0}\) with \[urc(v)=\left\|\left\{c \in C : r \in R, (c,r) \in ISR, (r,c) \notin ISR\right\}\right\|\]
+Thus we can express this criterion as function \(urc:V \rightarrow \mathbb{N}_{0}\) with \[urc(v)=\left|\left\{c \in C : r \in R, (c,r) \in ISR, (r,c) \notin ISR\right\}\right|\]
 \end{definition}
@@
 Furthermore, let \(HR \subseteq SR\) be the set of all conceptual resources being related by \texttt{skos:broader} and \texttt{skos:narrower} with \((c,c') \in HR \Rightarrow (c',c) \in HR\).
-We can write this criterion as a function \(str:V \rightarrow \mathbb{N}_{0}\) with \[str(v)=\left\|\left\{c \in C : c' \in C, (c,c') \in TR, (c,c') \notin HR\right\}\right\|\]
+We can write this criterion as a function \(str:V \rightarrow \mathbb{N}_{0}\) with \[str(v)=\left|\left\{c \in C : c' \in C, (c,c') \in TR, (c,c') \notin HR\right\}\right|\]
 \end{definition}
@@
 Let \(EL=C \times R\) be the set of external links with \(host(c) \neq host(r)\).
-This criterion can then be written as a function \(elc:V \righarrow \mathbb{ℚ}\) with \[elc(v)=\frac{\left\|EL\right\|}{\left\|C\right\|}\]
+This criterion can then be written as a function \(elc:V \righarrow \mathbb{ℚ}\) with \[elc(v)=\frac{\left|EL\right|}{\left|C\right|}\]
 \end{definition}
@@
 We can define a function \(httpScheme:R \rightarrow \left\{0,1\right\}\) with \(httpScheme(r)=1\) if the scheme part of the URI is http or https, 0 otherwise.
-Then this criterion can be written as a function \(usv:V \rightarrow \mathbb{N}_{0}\) with \[usv(v)=\left\|\left\{vr \in VR : httpScheme(vr)=0\right\}\right\|\]
+Then this criterion can be written as a function \(usv:V \rightarrow \mathbb{N}_{0}\) with \[usv(v)=\left|\left\{vr \in VR : httpScheme(vr)=0\right\}\right|\]
 \end{definition}
@@
 The function \(resp:R \rightarrow \mathbb{N}\) assigns a resource its HTTP response code after following all redirections.
-We can therefore write this criterion as function \(ltu:V \rightarrow \mathbb{N}_{0}\) with \[ltu(v)=\left\|\left\{r \in LR \cup VR : resp(r)=200\right\}\right\|\]
+We can therefore write this criterion as function \(ltu:V \rightarrow \mathbb{N}_{0}\) with \[ltu(v)=\left|\left\{r \in LR \cup VR : resp(r)=200\right\}\right|\]
 \end{definition}
@@
 The set \(RR \subseteq R \times R\) contains all resources in distinct datasets related by an RDF property with \((r1,r2) \in RR \Rightarrow host(r1) \neq host(r2)\).
-This criterion can be written as a function \(aci:V \rightarrow \mathbb{ℚ}\) with \[aci(v)=\frac{\left\|\left\{r \in R : c \in C, (r,c) \in RR\right\}\right|}{\left\|C\right\|}\]
+This criterion can be written as a function \(aci:V \rightarrow \mathbb{ℚ}\) with \[aci(v)=\frac{\left|\left\{r \in R : c \in C, (r,c) \in RR\right\}\right|}{\left|C\right|}\]
 \end{definition}
@@
 We consider two directed graphs \(GB=(C,CBR)\) and \(GN=(C,CNR)\) and a function hierarchical:C \times C \rightarrow \left\{0,1\right\} with \(hierarchical((c,c'))=1\) if a path between c and c’ exists in either \(GB\) or \(GN\), 0 otherwise.
-This criterion can then be written as a function \(ahrc:G \rightarrow \mathbb{N}_{0}\) with \[ahrc(g)=\left\|\left\{(c,c') \in REL:hierarchical((c,c'))=1\right\}\right\|\]
+This criterion can then be written as a function \(ahrc:G \rightarrow \mathbb{N}_{0}\) with \[ahrc(g)=\left|\left\{(c,c') \in REL:hierarchical((c,c'))=1\right\}\right|\]
 \end{definition}
@@
 Let \(EM \subseteq SR\), \(BM \subseteq SR\), \(RM \subseteq SR\) be the set of conceptual resources related by \texttt{skos:exactMatch}, \texttt{skos:broadMatch}, and \texttt{skos:relatedMatch}.
-In functional form, this criteria can be written as \(eahmc:V \rightarrow \mathbb{N}_{0}\) with \[eahmc(v)=\left\|\left\{em \in EM : em \in BM \cup RM\right\}\right|\]
+In functional form, this criteria can be written as \(eahmc:V \rightarrow \mathbb{N}_{0}\) with \[eahmc(v)=\left|\left\{em \in EM : em \in BM \cup RM\right\}\right|\]
 \end{definition}
@@
 \begin{definition}
-We define a set that contains all deprecated properties DP=\left\{\texttt{skos:symbol}, \texttt{skos:prefSymbol}, \texttt{skos:altSymbol}, \texttt{skos:CollectableProperty}, \texttt{skos:subject}, \texttt{skos:isSubjectOf}, \texttt{skos:primarySubject}, \texttt{skos:isPrimarySubjectOf}, \texttt{skos:subjectIndicator}\right\}.
+We define a set that contains all deprecated properties DP=\{\texttt{skos:symbol}, \texttt{skos:prefSymbol}, \texttt{skos:altSymbol}, \texttt{skos:CollectableProperty}, \texttt{skos:subject}, \texttt{skos:isSubjectOf}, \texttt{skos:primarySubject}, \texttt{skos:isPrimarySubjectOf}, \texttt{skos:subjectIndicator}\}.
 Let \(DR \subseteq RV \times RV\) with \(RV \subseteq R\) being the set of all RDF resources in V that are related by a property in DP.
-This criterion can then be written as a function \(dpu:V \rightarrow \mathbb{N}_{0}\) with \[dpu(v)=\left\|DR\right\|\]
+This criterion can then be written as a function \(dpu:V \rightarrow \mathbb{N}_{0}\) with \[dpu(v)=\left|DR\right|\]
+\end{definition}
+
+\subsubsection{Omitted Top Concepts} The SKOS language provides ConceptSchemes which are a facility for grouping related concepts.
+In order to provide entry points to such a group of concepts, one or more concepts can be marked as top concepts.
+This helps to provide “efficient access”\footnote{SKOS primer, \url{http://www.w3.org/TR/skos-primer/}} and simplifies orientation in the vocabulary.
+
+\begin{definition}
+Let \(TCR \subseteq AR\) be the set of concepts related to a \texttt{skos:ConceptScheme} by the properties \texttt{skos:topConceptOf} or \texttt{skos:hasTopConcept}.
+Furthermore, \(CS \subseteq A\) is the set of ConceptSchemes defined in a vocabulary.
+We can then define this criterion as a function \(otc:V \rightarrow \left\{0,1\right\}\) with \[otc(v)=0 \iff \forall cs \in CS.
+\exists (c,cs) \in TCR, 1 otherwise\]
+\end{definition}
+
+\subsubsection{Top Concepts Having Broader Concepts} \cite{Allemang2011} proposes to “not indicate any concepts internal to the tree as top concepts”, i.e.
+top concepts in a concept scheme should not have broader concepts.
+
+\begin{definition}
+Let \(CBR \subseteq SR\) be the set of conceptual resources having broader concepts within the same concept scheme, i.e.
+being related to another concept by the property \texttt{skos:broader}.
+\(tcb:V \rightarrow \mathbb{N}_{0}\) with \[tcb(v)=\left|\left\{c \in C : (c,cs) \in TCR, (c,c') \in CBR\right\}\right|\]
 \end{definition}

### 2012-03-09 main.tex
renamed stuff

--- 2012-03-09 paper.tex
@@
 
-\title{Quality Criteria for SKOS Vocabularies}
+\usepackage{color}
+
+\newcommand{\todo}[2]{\textbf{\textcolor{red}{(TODO [#1]: #2)}}}
+
+\title{Quality Metrics for SKOS Vocabularies}
 \author{Christian Mader\inst{1} \and Bernhard Haslhofer\inst{2}}
@@
 \begin{abstract}
+
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
 \end{abstract}
 
-\section{Introduction}
-The Simple Knowledge Organization System (SKOS\footnote{Simple Knowledge Organization System, \url{http://www.w3.org/2004/02/skos/}}) has become a de-facto standard for expressing controlled vocabularies on the Web.
-Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} have created SKOS representations of their controlled vocabularies and published them on the Web so that they can easily be navigated and reused by humans and, most importantly, also by applications.
-Each vocabulary is the result of a specific design process that reflects domain-specific requirements as well as the target audience the vocabulary is created for.
-Orthogonal to the design process, vocabulary \textbf{designers and maintainers} usually apply existing guidelines or follow their own rules when defining concepts, in order to meet their \textbf{quality requirements} as, for instance, described in \cite{Coronado2009}.
-As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality, which can affect their interoperability and applicability for tasks like query expansion, faceted browsing, clustering, or auto-complete suggestions.
+\input{introduction}
 
-The following representative examples, which we identified by looking at real-world SKOS vocabularies, illustrate the \textbf{quality problems} applications could face when making use of them:
-\begin{itemize}
-	\item The SKOS version of Agrovoc defines concepts in 25 different languages.
-However, almost all concepts have an English description, 38\% of all concepts don’t have German labels attached.
-This can be a problem for applications that use Agrovoc and rely on German translations.
+\input{metrics}
 
-	\item The previous version of the STW thesaurus, contained 5 pairs of concepts with identical labels.
-As a result, the auto-complete function of the online search interface suggested identical entries, with no disambiguation information.
+\input{analysis}
 
-	\item The vocabulary developed by the Austrian Armed Forces (LVAk thesaurus\footnote{Non-public thesaurus developed by the Austrian Armed Forces}), which contains 11 disconnected concept clusters.
-Confronting the thesaurus maintainers with these structures, they recognized them as “forgotten” test data that has no practical significance.
+\input{related_work}
 
-	\item In the DBpedia category\footnote{\url{http://downloads.dbpedia.org/3.7/en/skos_categories_en.nt.bz2}} hierarchy, more than 10 percent of the categories not linked to any other category.
-When other vocabularies link to the DBPedia categories, e.g., to enable query expansion, it can negatively affect recall and reduce navigability.
-\end{itemize}
-
-One reason for these quality problems is that SKOS currently only defines a set of \textbf{low-level integrity conditions}, which, when being enforced, ensure the structural and semantic requirements of the SKOS specifications but fail to capture \textbf{higher-level quality issues}, as those mentioned in the examples before.
-Another problem is that existing vocabulary design guidelines and best practices purely rely on \textbf{human assessment}, which is highly subjective and doesn’t scale when vocabulary quality assessment should be performed on larger, possibly linked Web vocabularies.
-
-We believe, and recent developments of quality checking tools (e.g., PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}}, qSKOS\footnote{\url{https://github.com/cmader/qSKOS}}, SKOSify\footnote{\url{http://code.google.com/p/skosify/}}) support this motivation.
-This, however, requires a formalization of the notion of quality with respect to SKOS vocabularies, which can be used in order to consistently implement quality assessment procedures across tools.
-Since, the notion of “quality” with respect to SKOS vocabularies naturally varies across application domains it is hard, if not impossible, to come up with a general definition of quality.
-However, we believe that vocabulary designers can apply a set of \textbf{formal quality criteria} on given vocabularies in order to assess whether or not a vocabulary fulfills their requirements.
-Since these criteria are based on a formal definition, they can be calculated by automated tools, which helps vocabulary designers in assessing the quality of available or newly created vocabularies and provide important feedback to the overall vocabulary design process.
-
-The main contributions of this work can be summarized as follows:
-\begin{itemize}
-	\item We derived a \textbf{quality criteria catalogue} from existing literature, tools, and public mailing list discussions in the community.
-We \textbf{formalized} each criterion and implemented them in the \textbf{qSKOS quality assessment tool}.
-
-	\item We \textbf{analyzed} a representative \textbf{set of existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.
-\end{itemize}
-
-The results from our studies show that... TBD
-
-\section{A Quality Model for SKOS}
-SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption.
-Established quality notions from closed-world systems, such as constraints, referential integrity or schema validation, don’t hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false.
-While trust and provenance models for Web data are being developed \cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets \cite{Heath2011}.
-
-Based on the findings from a literature survey we now define a set of quantifiable quality criteria for SKOS vocabularies.
-For each \textbf{criterion} we explain our design rationale, and provide a semi-formal definition, which is based on a set-theoretic conception of the SKOS model.
-Tools can implement these criteria as functions defined on-top of a the baseline SKOS model.
-
-\begin{definition} \textbf{The SKOS Baseline Model} is defined as follows:
-Let R be the set of all resources, as defined in [Web Architecture Document] and \[V = (C, A, LL, LR, SR, AR)\] be one specific SKOS vocabulary, with
-
-\begin{itemize}
-	\item \(C \subseteq R\) being the set of \textbf{conceptual resources} of type \texttt{skos:Concept}.
-	\item \(A \subseteq R\) being the set of aggregation and grouping resources in SKOS, hence \texttt{skos:ConceptSchema} and \texttt{skos:Collection}.
-	\item LL being the set \textbf{lexical labels}, which are instances of RDF plain literals.
-	\item \(LR \subseteq C \times LL\) being the set of \textbf{lexical relations} associating conceptual resources with lexical labels, hence instances of \texttt{skos:prefLabel}, \texttt{skos:altLabel}, or \texttt{skos:hiddenLabel}.
-\item \(SR \subseteq C \times C\) being the set of \textbf{semantic relations} associating conceptual resources with concepts, hence instances of \texttt{skos:semanticRelation} and subproperties thereof.
-\item \(AR \subseteq C \times A\) being the set of \textbf{aggregation (and grouping) relations} associating conceptual resources with instances of aggregation and grouping resources.
-\end{itemize}
-\end{definition}
-
-\subsection{Graph-based Quality Criteria / Network Measures}
-The following quality criteria are all derived from a graph-based view on a given vocabulary \(v\), which we can then consider as a directed graph \(G=(N,E)\) consisting of a set of nodes \(N\) and edges \(E\).
-
-\subsubsection{Loose Concepts} are very similar to what is also referred to as ``orphan terms” in the literature, which are terms without any associative or hierarchical relationships \cite{Z39.19:2005,Hedden2010}.
-In a SKOS vocabulary, we define a loose concept as a concept that has no semantic or aggregation relations with other conceptual, aggregation or grouping resources.
-Although they might have attached lexical labels, they lack valuable context information.
-Checking for orphan terms is common in existing thesaurus development applications and suggested by \cite{Z39.19:2005}.
-Depending on the vocabulary development policy, loose concepts may be tolerated or considered to be a defect.
-
-\begin{definition}
-To calculate the number of loose concepts, we let \(G = (C, SR \cup AR)\)  and apply \(deg(c)\) as a function that calculates the degree, hence the number of in- and outgoing edges of a node n in a graph g.
-We can then define this quality criterion as a function \(looseConcepts : G \rightarrow \mathbb{N}_{0}\), with \[looseConcepts(g) = \left\|\left\{c \in C : deg(c) = 0\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Weakly Connected Components} cause the vocabulary to split into separate disconnected components.
-This is very similar to the ``loose concepts” criterion introduced before and might be caused by incomplete data acquisition, ``forgotten" test data, outdated terms, accidental deletion of relations and the like.
-In a practical setting, existence of weakly connected components could render the vocabulary less suitable for operations that rely on navigating a strongly connected vocabulary structure, such as query expansion or suggestion of related terms.
-
-\begin{definition}
-To evaluate this criterion we consider a graph \(G = (AC, SRAR)\).
-The function \(components(g) : G \rightarrow  \mathfrak{P}(G)\) calculates all weakly connected components of a graph by replacing all directed edges by undirected edges and utilizing “Tarjan’s algorithm” \cite{Hopcroft1973}.
-Based on that function, we can express this criterion as a function \(wcc : G \rightarrow \mathbb{N}_{0}\), with \[wcc(g) = \left\|components(g)\right\|\]
-\end{definition}
-
-\subsubsection{Cyclic Hierarchical Relations} have been mentioned numerous times in thesaurus development literature.
-\cite{Soergel2002} suggests a ``check for hierarchy cycles" since they ``throw the program for a loop in the generation of a complete hierarchical structure”.
-However, the SKOS documentation does not state, how exactly hierarchical relationships are to be interpreted.
-There exist common forms like, e.g., “generic-specific”, “instance-of” or “whole-part” \cite{Hedden2010,Harpring2010,Aitchison2000}.
-Hierarchical cycles for some of these interpretations in various domains or usage scenarios might be perfectly valid, whereas they would be treated as failures in others.
-
-\begin{definition}
-In the context of this work, we define a cycle in a SKOS vocabulary as a logical contradiction in the broader/narrower hierarchy.
-Let \(HB \subseteq SR\) be the set of broader hierarchical relations associating two conceptual resources with instances of \texttt{skos:broader}, \texttt{skos:broaderTransitive}, \texttt{skos:broadMatch} or subproperties thereof.
-\(HB\) also associates conceptual resources related with instances \texttt{skos:narrower}, \texttt{skos:narrowTransitive}, \texttt{skos:narrowMatch} or subproperties thereof in reverse order.
-Likewise, \(HN \subseteq SR\) can be defined as the set of narrower hierarchical relations.
-We consider two graphs \(GB = (C,HB)\) and \(GN=(C,HN)\) and a function \(cycleNodes:GB \cup GN \rightarrow \mathfrak{P}(C)\) identifying all nodes in a graph, that are part of a cycle.
-Furthermore we consider a function \(stronglyConnectedSets: GB \cup GN \rightarrow \mathfrak{P}(C)\) that calculates all strongly connected undirected subgraphs of a graph.
-This criterion can be defined as a function \(chr:GB \cup GN \rightarrow \mathbb{N}_{0}\) with \[chr(g)=\left\|\left\{s \in stronglyConnectedSets(g) : cn \in cycleNodes(g), cn \in s\right\}\right\|\]
-\end{definition}
-
-\subsection{Structure-Centric Quality Criteria / Structural Measures}
-
-\subsubsection{Redundant Associative Relations} \cite{ISO25964-1:2011} suggests that terms that share a common broader term but don’t have an overlapping meaning, should not be related associatively.
-This is also advocated by \cite{Hedden2010} and \cite{Aitchison2000} who also mentions ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships", having a negative effect on precision.
-
-\begin{definition}
-Let \(ASR \subseteq SR\) be the set of associative relations in SKOS, namely \texttt{skos:related} and \texttt{skos:relatedMatch}.
-These relations are symmetric, so \((c1,c2) \in ASR \Rightarrow (c2,c1) \in ASR\).
-Formally, this criterion can be expressed as a function \(rar:V \rightarrow \mathbb{N}_{0}\) with \[rar(v)=\left\|\left\{(c1,c2) \in ASR : c3 \in C, (c1,c3) \in HB, (c2,c3) \in HB\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Number of Hierarchically and Associatively Related Concepts} \cite{Aitchison2000} mentions a ``common error in manually produced thesauri" when concepts are related both hierarchically and associatively (F1.3.2).
-\cite{Hedden2010} also proposes to check for ``pairs of terms that have more than one kind of relationship" as a feasible rule, enforced by thesaurus management software.
-
-\begin{definition}
-This criterion can be expressed as a function \(har:V \righarrow \mathbb{N}_{0}\) with \[har(v)=\left\|\left\{c \in C : c' \in C, (c,c') \in HB \cup HN, (c,c') \in ASR\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Unidirectionally Related Concepts} \cite{Z39.19:2005} suggests thesaurus maintenance software to automatically add reciprocal relations (e.g., broader/narrower, related) to the resulting thesaurus.
-Vocabularies created in that manner are expected, e.g., to be better browsable for humans and provide better search results when used in systems without reasoning support.
-
-\begin{definition}
-Let \(ISR \subseteq R \times R\) be a set that associates resources defined in \(V\) that are related by a SKOS property that has an inverse SKOS property defined.
-Furthermore, ISR also associates resources that are related by a symmetric SKOS property.
-In an ideal setting \((r,r') \in ISR \iff (r',r) \in ISR\).
-Thus we can express this criterion as function \(urc:V \rightarrow \mathbb{N}_{0}\) with \[urc(v)=\left\|\left\{c \in C : r \in R, (c,r) \in ISR, (r,c) \notin ISR\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Solely Transitively Related Concepts} Two concepts are related using only transitive hierarchical relations which are, according to the SKOS reference document, ``not used to make assertions".
-Transitive hierarchical relations in SKOS are meant to be infered by the vocabulary user, which is reflected in the SKOS schema by, e.g., broader being a subproperty of broaderTransitive.
-
-\begin{definition}
-Let \(TR \subseteq SR\) be the set of all conceptual resources being transitively related by \texttt{skos:broaderTransitive} respectively \texttt{skos:narrowerTransitive}, not by subproperties thereof.
-Furthermore, let \(HR \subseteq SR\) be the set of all conceptual resources being related by \texttt{skos:broader} and \texttt{skos:narrower} with \((c,c') \in HR \Rightarrow (c',c) \in HR\).
-We can write this criterion as a function \(str:V \rightarrow \mathbb{N}_{0}\) with \[str(v)=\left\|\left\{c \in C : c' \in C, (c,c') \in TR, (c,c') \notin HR\right\}\right\|\]
-\end{definition}
-
-\subsection{Linked Data Specific Criteria / Linked Data Measures}
-SKOS has been developed for creating knowledge organization systems that are used ``within the framework of the semantic web" \cite{Bernerslee2001}.
-Therefore we identified some criteria targeting issues related to best practises in publishing Linked Data, the underlying technology for establishing a Semantic Web \cite{Heath2011}.
-
-\subsubsection{Concept External Link Average} The ``Web of Data" consists of globally interconnected datasets, ``enabling seamless connections between data sets" \cite{Heath2011}.
-These links can be established between various SKOS vocabularies by ``external links", i.e., references from conceptual resources in a ``source vocabulary" to resources identified by an HTTP URI and available at a different host.
-
-\begin{definition}
-Let \(EL=C \times R\) be the set of external links with \(host(c) \neq host(r)\).
-This criterion can then be written as a function \(elc:V \righarrow \mathbb{ℚ}\) with \[elc(v)=\frac{\left\|EL\right\|}{\left\|C\right\|}\]
-\end{definition}
-
-\subsection{HTTP URI Scheme Violation} One of the key concept of Linked Data is that URIs should be dereferencable in order to browse through data in the same way as through ``traditional" Web pages.
-Using HTTP URIs therefore is the logical consequence and mentioned numerous time in literature \cite{Heath2011}.
-However, some vocabularies use other URI schemes such as URNs and DOIs when defining resources, which impedes data lookup and crawling purposes.
-
-\begin{definition}
-Let \(VR \subseteq C \cup A\) be the set of vocabulary resources identified by an URI (not by a blank node).
-We can define a function \(httpScheme:R \rightarrow \left\{0,1\right\}\) with \(httpScheme(r)=1\) if the scheme part of the URI is http or https, 0 otherwise.
-Then this criterion can be written as a function \(usv:V \rightarrow \mathbb{N}_{0}\) with \[usv(v)=\left\|\left\{vr \in VR : httpScheme(vr)=0\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Link Target Unavailability} Just as in the ``traditional" Web, resources in the Web of Data might also be unavailable, i.e.
-resolving their URI leads to an erroneous HTTP response or no response at all.
-An erroneous HTTP response in that case can be defined as a response code (after a possible redirection) other than 200.
-Since these ``broken links" hinder information gathering, they should be avoided.
-
-\begin{definition}
-Let \(LR \subseteq R\) be the set of all resources being related to conceptual, aggregational and grouping resources.
-The function \(resp:R \rightarrow \mathbb{N}\) assigns a resource its HTTP response code after following all redirections.
-We can therefore write this criterion as function \(ltu:V \rightarrow \mathbb{N}_{0}\) with \[ltu(v)=\left\|\left\{r \in LR \cup VR : resp(r)=200\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Average Concept In-degree} A periodically updated version of a diagram visualizing ``the data sets in the LOD cloud as well as their interlinkage relationships” is published online \footnote{http://www4.wiwiss.fu-berlin.de/lodcloud/state/}.
-In these diagrams, DBpedia \footnote{http://dbpedia.org/About} is shown as the most intensely linked resource, i.e.
-a large number of vocabularies link to resources in that dataset.
-Therefore a dataset with a large number of other datasets referencing it, can be assumed to be of great value for the community.
-Accordingly, estimating the number of ``incoming links" of SKOS concepts defined in a vocabulary (henceforth called the in-degree of a concept) would give some hint about how established or accepted a controlled vocabulary is.
-A method to carry out these estimations would be utilizing existing Linked Data indices like, e.g., Sindice \footnote{http://sindice.com/} that provide a SPARQL endpoint.
-
-\begin{definition}
-Let \(U\) be the universe of all datasets on the Web and \(V \in U\).
-The set \(RR \subseteq R \times R\) contains all resources in distinct datasets related by an RDF property with \((r1,r2) \in RR \Rightarrow host(r1) \neq host(r2)\).
-This criterion can be written as a function \(aci:V \rightarrow \mathbb{ℚ}\) with \[aci(v)=\frac{\left\|\left\{r \in R : c \in C, (r,c) \in RR\right\}\right|}{\left\|C\right\|}\]
-\end{definition}
-
-\subsection{SKOS-Specific Criteria / SKOS Semantic Measures}
-
-\subsection{Labeling Issues}
-
-\subsection{Other Criteria}
-
-\section{Analysis of Existing SKOS Vocabularies}
-
-\subsection{The qSKOS Quality Checking Tool}
-
-\subsection{Vocabularies}
-
-\subsection{Results}
-
-\section{Related Work}
-
-\section{Conclusions and Future Work}
+\input{conclusions}
 

### 2012-03-10 background.tex
wrote abstract, modified intro (not finished yet)

--- 2012-03-09 paper.tex
@@
-\documentclass{llncs}
+%!TEX root = main.tex
 
-\usepackage{verbatim}
-\usepackage{url}
-\usepackage{amssymb}
+\section{Background and Definitions}
 
-\title{Quality Criteria for SKOS Vocabularies}
-\author{Christian Mader\inst{1} \and Bernhard Haslhofer\inst{2}}
-\institute{
-	University of Vienna, Faculty of Computer Science\\\email{christian.mader@univie.ac.at}
-	\and Cornell University, Information Science\\\email{bernhard.haslhofer@cornell.edu}}
+% About Data Quality and SKOS
 
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-\end{abstract}
-
-\section{Introduction}
-The Simple Knowledge Organization System (SKOS\footnote{Simple Knowledge Organization System, \url{http://www.w3.org/2004/02/skos/}}) has become a de-facto standard for expressing controlled vocabularies on the Web.
-Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} have created SKOS representations of their controlled vocabularies and published them on the Web so that they can easily be navigated and reused by humans and, most importantly, also by applications.
-Each vocabulary is the result of a specific design process that reflects domain-specific requirements as well as the target audience the vocabulary is created for.
-Orthogonal to the design process, vocabulary \textbf{designers and maintainers} usually apply existing guidelines or follow their own rules when defining concepts, in order to meet their \textbf{quality requirements} as, for instance, described in \cite{Coronado2009}.
-As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality, which can affect their interoperability and applicability for tasks like query expansion, faceted browsing, clustering, or auto-complete suggestions.
-
-The following representative examples, which we identified by looking at real-world SKOS vocabularies, illustrate the \textbf{quality problems} applications could face when making use of them:
-\begin{itemize}
-	\item The SKOS version of Agrovoc defines concepts in 25 different languages.
-However, almost all concepts have an English description, 38\% of all concepts don’t have German labels attached.
-This can be a problem for applications that use Agrovoc and rely on German translations.
-
-	\item The previous version of the STW thesaurus, contained 5 pairs of concepts with identical labels.
-As a result, the auto-complete function of the online search interface suggested identical entries, with no disambiguation information.
-
-	\item The vocabulary developed by the Austrian Armed Forces (LVAk thesaurus\footnote{Non-public thesaurus developed by the Austrian Armed Forces}), which contains 11 disconnected concept clusters.
-Confronting the thesaurus maintainers with these structures, they recognized them as “forgotten” test data that has no practical significance.
-
-	\item In the DBpedia category\footnote{\url{http://downloads.dbpedia.org/3.7/en/skos_categories_en.nt.bz2}} hierarchy, more than 10 percent of the categories not linked to any other category.
-When other vocabularies link to the DBPedia categories, e.g., to enable query expansion, it can negatively affect recall and reduce navigability.
-\end{itemize}
-
-One reason for these quality problems is that SKOS currently only defines a set of \textbf{low-level integrity conditions}, which, when being enforced, ensure the structural and semantic requirements of the SKOS specifications but fail to capture \textbf{higher-level quality issues}, as those mentioned in the examples before.
-Another problem is that existing vocabulary design guidelines and best practices purely rely on \textbf{human assessment}, which is highly subjective and doesn’t scale when vocabulary quality assessment should be performed on larger, possibly linked Web vocabularies.
-
-We believe, and recent developments of quality checking tools (e.g., PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}}, qSKOS\footnote{\url{https://github.com/cmader/qSKOS}}, SKOSify\footnote{\url{http://code.google.com/p/skosify/}}) support this motivation.
-This, however, requires a formalization of the notion of quality with respect to SKOS vocabularies, which can be used in order to consistently implement quality assessment procedures across tools.
-Since, the notion of “quality” with respect to SKOS vocabularies naturally varies across application domains it is hard, if not impossible, to come up with a general definition of quality.
-However, we believe that vocabulary designers can apply a set of \textbf{formal quality criteria} on given vocabularies in order to assess whether or not a vocabulary fulfills their requirements.
-Since these criteria are based on a formal definition, they can be calculated by automated tools, which helps vocabulary designers in assessing the quality of available or newly created vocabularies and provide important feedback to the overall vocabulary design process.
-
-The main contributions of this work can be summarized as follows:
-\begin{itemize}
-	\item We derived a \textbf{quality criteria catalogue} from existing literature, tools, and public mailing list discussions in the community.
-We \textbf{formalized} each criterion and implemented them in the \textbf{qSKOS quality assessment tool}.
-
-	\item We \textbf{analyzed} a representative \textbf{set of existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.
-\end{itemize}
-
-The results from our studies show that... TBD
-
-\section{A Quality Model for SKOS}
 SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption.
@@
 
-Based on the findings from a literature survey we now define a set of quantifiable quality criteria for SKOS vocabularies.
-For each \textbf{criterion} we explain our design rationale, and provide a semi-formal definition, which is based on a set-theoretic conception of the SKOS model.
-Tools can implement these criteria as functions defined on-top of a the baseline SKOS model.
+% What kind of quality criteria are defined in SKOS
+
+\todo{CM}{write a short paragraph about the quality criteria in the SKOS specification.}
+
+% This definition is not a quality criterions, henec it is in the background section (we need to discuss that)
 
@@
 \end{definition}
-
-\subsection{Graph-based Quality Criteria / Network Measures}
-The following quality criteria are all derived from a graph-based view on a given vocabulary \(v\), which we can then consider as a directed graph \(G=(N,E)\) consisting of a set of nodes \(N\) and edges \(E\).
-
-\subsubsection{Loose Concepts} are very similar to what is also referred to as ``orphan terms” in the literature, which are terms without any associative or hierarchical relationships \cite{Z39.19:2005,Hedden2010}.
-In a SKOS vocabulary, we define a loose concept as a concept that has no semantic or aggregation relations with other conceptual, aggregation or grouping resources.
-Although they might have attached lexical labels, they lack valuable context information.
-Checking for orphan terms is common in existing thesaurus development applications and suggested by \cite{Z39.19:2005}.
-Depending on the vocabulary development policy, loose concepts may be tolerated or considered to be a defect.
-
-\begin{definition}
-To calculate the number of loose concepts, we let \(G = (C, SR \cup AR)\)  and apply \(deg(c)\) as a function that calculates the degree, hence the number of in- and outgoing edges of a node n in a graph g.
-We can then define this quality criterion as a function \(looseConcepts : G \rightarrow \mathbb{N}_{0}\), with \[looseConcepts(g) = \left\|\left\{c \in C : deg(c) = 0\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Weakly Connected Components} cause the vocabulary to split into separate disconnected components.
-This is very similar to the ``loose concepts” criterion introduced before and might be caused by incomplete data acquisition, ``forgotten" test data, outdated terms, accidental deletion of relations and the like.
-In a practical setting, existence of weakly connected components could render the vocabulary less suitable for operations that rely on navigating a strongly connected vocabulary structure, such as query expansion or suggestion of related terms.
-
-\begin{definition}
-To evaluate this criterion we consider a graph \(G = (AC, SRAR)\).
-The function \(components(g) : G \rightarrow  \mathfrak{P}(G)\) calculates all weakly connected components of a graph by replacing all directed edges by undirected edges and utilizing “Tarjan’s algorithm” \cite{Hopcroft1973}.
-Based on that function, we can express this criterion as a function \(wcc : G \rightarrow \mathbb{N}_{0}\), with \[wcc(g) = \left\|components(g)\right\|\]
-\end{definition}
-
-\subsubsection{Cyclic Hierarchical Relations} have been mentioned numerous times in thesaurus development literature.
-\cite{Soergel2002} suggests a ``check for hierarchy cycles" since they ``throw the program for a loop in the generation of a complete hierarchical structure”.
-However, the SKOS documentation does not state, how exactly hierarchical relationships are to be interpreted.
-There exist common forms like, e.g., “generic-specific”, “instance-of” or “whole-part” \cite{Hedden2010,Harpring2010,Aitchison2000}.
-Hierarchical cycles for some of these interpretations in various domains or usage scenarios might be perfectly valid, whereas they would be treated as failures in others.
-
-\begin{definition}
-In the context of this work, we define a cycle in a SKOS vocabulary as a logical contradiction in the broader/narrower hierarchy.
-Let \(HB \subseteq SR\) be the set of broader hierarchical relations associating two conceptual resources with instances of \texttt{skos:broader}, \texttt{skos:broaderTransitive}, \texttt{skos:broadMatch} or subproperties thereof.
-\(HB\) also associates conceptual resources related with instances \texttt{skos:narrower}, \texttt{skos:narrowTransitive}, \texttt{skos:narrowMatch} or subproperties thereof in reverse order.
-Likewise, \(HN \subseteq SR\) can be defined as the set of narrower hierarchical relations.
-We consider two graphs \(GB = (C,HB)\) and \(GN=(C,HN)\) and a function \(cycleNodes:GB \cup GN \rightarrow \mathfrak{P}(C)\) identifying all nodes in a graph, that are part of a cycle.
-Furthermore we consider a function \(stronglyConnectedSets: GB \cup GN \rightarrow \mathfrak{P}(C)\) that calculates all strongly connected undirected subgraphs of a graph.
-This criterion can be defined as a function \(chr:GB \cup GN \rightarrow \mathbb{N}_{0}\) with \[chr(g)=\left\|\left\{s \in stronglyConnectedSets(g) : cn \in cycleNodes(g), cn \in s\right\}\right\|\]
-\end{definition}
-
-\subsection{Structure-Centric Quality Criteria / Structural Measures}
-
-\subsubsection{Redundant Associative Relations} \cite{ISO25964-1:2011} suggests that terms that share a common broader term but don’t have an overlapping meaning, should not be related associatively.
-This is also advocated by \cite{Hedden2010} and \cite{Aitchison2000} who also mentions ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships", having a negative effect on precision.
-
-\begin{definition}
-Let \(ASR \subseteq SR\) be the set of associative relations in SKOS, namely \texttt{skos:related} and \texttt{skos:relatedMatch}.
-These relations are symmetric, so \((c1,c2) \in ASR \Rightarrow (c2,c1) \in ASR\).
-Formally, this criterion can be expressed as a function \(rar:V \rightarrow \mathbb{N}_{0}\) with \[rar(v)=\left\|\left\{(c1,c2) \in ASR : c3 \in C, (c1,c3) \in HB, (c2,c3) \in HB\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Number of Hierarchically and Associatively Related Concepts} \cite{Aitchison2000} mentions a ``common error in manually produced thesauri" when concepts are related both hierarchically and associatively (F1.3.2).
-\cite{Hedden2010} also proposes to check for ``pairs of terms that have more than one kind of relationship" as a feasible rule, enforced by thesaurus management software.
-
-\begin{definition}
-This criterion can be expressed as a function \(har:V \righarrow \mathbb{N}_{0}\) with \[har(v)=\left\|\left\{c \in C : c' \in C, (c,c') \in HB \cup HN, (c,c') \in ASR\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Unidirectionally Related Concepts} \cite{Z39.19:2005} suggests thesaurus maintenance software to automatically add reciprocal relations (e.g., broader/narrower, related) to the resulting thesaurus.
-Vocabularies created in that manner are expected, e.g., to be better browsable for humans and provide better search results when used in systems without reasoning support.
-
-\begin{definition}
-Let \(ISR \subseteq R \times R\) be a set that associates resources defined in \(V\) that are related by a SKOS property that has an inverse SKOS property defined.
-Furthermore, ISR also associates resources that are related by a symmetric SKOS property.
-In an ideal setting \((r,r') \in ISR \iff (r',r) \in ISR\).
-Thus we can express this criterion as function \(urc:V \rightarrow \mathbb{N}_{0}\) with \[urc(v)=\left\|\left\{c \in C : r \in R, (c,r) \in ISR, (r,c) \notin ISR\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Solely Transitively Related Concepts} Two concepts are related using only transitive hierarchical relations which are, according to the SKOS reference document, ``not used to make assertions".
-Transitive hierarchical relations in SKOS are meant to be infered by the vocabulary user, which is reflected in the SKOS schema by, e.g., broader being a subproperty of broaderTransitive.
-
-\begin{definition}
-Let \(TR \subseteq SR\) be the set of all conceptual resources being transitively related by \texttt{skos:broaderTransitive} respectively \texttt{skos:narrowerTransitive}, not by subproperties thereof.
-Furthermore, let \(HR \subseteq SR\) be the set of all conceptual resources being related by \texttt{skos:broader} and \texttt{skos:narrower} with \((c,c') \in HR \Rightarrow (c',c) \in HR\).
-We can write this criterion as a function \(str:V \rightarrow \mathbb{N}_{0}\) with \[str(v)=\left\|\left\{c \in C : c' \in C, (c,c') \in TR, (c,c') \notin HR\right\}\right\|\]
-\end{definition}
-
-\subsection{Linked Data Specific Criteria / Linked Data Measures}
-SKOS has been developed for creating knowledge organization systems that are used ``within the framework of the semantic web" \cite{Bernerslee2001}.
-Therefore we identified some criteria targeting issues related to best practises in publishing Linked Data, the underlying technology for establishing a Semantic Web \cite{Heath2011}.
-
-\subsubsection{Concept External Link Average} The ``Web of Data" consists of globally interconnected datasets, ``enabling seamless connections between data sets" \cite{Heath2011}.
-These links can be established between various SKOS vocabularies by ``external links", i.e., references from conceptual resources in a ``source vocabulary" to resources identified by an HTTP URI and available at a different host.
-
-\begin{definition}
-Let \(EL=C \times R\) be the set of external links with \(host(c) \neq host(r)\).
-This criterion can then be written as a function \(elc:V \righarrow \mathbb{ℚ}\) with \[elc(v)=\frac{\left\|EL\right\|}{\left\|C\right\|}\]
-\end{definition}
-
-\subsection{HTTP URI Scheme Violation} One of the key concept of Linked Data is that URIs should be dereferencable in order to browse through data in the same way as through ``traditional" Web pages.
-Using HTTP URIs therefore is the logical consequence and mentioned numerous time in literature \cite{Heath2011}.
-However, some vocabularies use other URI schemes such as URNs and DOIs when defining resources, which impedes data lookup and crawling purposes.
-
-\begin{definition}
-Let \(VR \subseteq C \cup A\) be the set of vocabulary resources identified by an URI (not by a blank node).
-We can define a function \(httpScheme:R \rightarrow \left\{0,1\right\}\) with \(httpScheme(r)=1\) if the scheme part of the URI is http or https, 0 otherwise.
-Then this criterion can be written as a function \(usv:V \rightarrow \mathbb{N}_{0}\) with \[usv(v)=\left\|\left\{vr \in VR : httpScheme(vr)=0\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Link Target Unavailability} Just as in the ``traditional" Web, resources in the Web of Data might also be unavailable, i.e.
-resolving their URI leads to an erroneous HTTP response or no response at all.
-An erroneous HTTP response in that case can be defined as a response code (after a possible redirection) other than 200.
-Since these ``broken links" hinder information gathering, they should be avoided.
-
-\begin{definition}
-Let \(LR \subseteq R\) be the set of all resources being related to conceptual, aggregational and grouping resources.
-The function \(resp:R \rightarrow \mathbb{N}\) assigns a resource its HTTP response code after following all redirections.
-We can therefore write this criterion as function \(ltu:V \rightarrow \mathbb{N}_{0}\) with \[ltu(v)=\left\|\left\{r \in LR \cup VR : resp(r)=200\right\}\right\|\]
-\end{definition}
-
-\subsubsection{Average Concept In-degree} A periodically updated version of a diagram visualizing ``the data sets in the LOD cloud as well as their interlinkage relationships” is published online \footnote{http://www4.wiwiss.fu-berlin.de/lodcloud/state/}.
-In these diagrams, DBpedia \footnote{http://dbpedia.org/About} is shown as the most intensely linked resource, i.e.
-a large number of vocabularies link to resources in that dataset.
-Therefore a dataset with a large number of other datasets referencing it, can be assumed to be of great value for the community.
-Accordingly, estimating the number of ``incoming links" of SKOS concepts defined in a vocabulary (henceforth called the in-degree of a concept) would give some hint about how established or accepted a controlled vocabulary is.
-A method to carry out these estimations would be utilizing existing Linked Data indices like, e.g., Sindice \footnote{http://sindice.com/} that provide a SPARQL endpoint.
-
-\begin{definition}
-Let \(U\) be the universe of all datasets on the Web and \(V \in U\).
-The set \(RR \subseteq R \times R\) contains all resources in distinct datasets related by an RDF property with \((r1,r2) \in RR \Rightarrow host(r1) \neq host(r2)\).
-This criterion can be written as a function \(aci:V \rightarrow \mathbb{ℚ}\) with \[aci(v)=\frac{\left\|\left\{r \in R : c \in C, (r,c) \in RR\right\}\right|}{\left\|C\right\|}\]
-\end{definition}
-
-\subsection{SKOS-Specific Criteria / SKOS Semantic Measures}
-
-\subsection{Labeling Issues}
-
-\subsection{Other Criteria}
-
-\section{Analysis of Existing SKOS Vocabularies}
-
-\subsection{The qSKOS Quality Checking Tool}
-
-\subsection{Vocabularies}
-
-\subsection{Results}
-
-\section{Related Work}
-
-\section{Conclusions and Future Work}
-
-\bibliography{lit}
-\bibliographystyle{splncs03}
-
-\end{document}

### 2012-03-10 introduction.tex
fixed cardinality issue
wrote abstract, modified intro (not finished yet)

@@
+%!TEX root = main.tex
+
 \section{Introduction}\label{sec:introduction}
 
-The Simple Knowledge Organization System (SKOS\footnote{Simple Knowledge Organization System, \url{http://www.w3.org/2004/02/skos/}}) has become a de-facto standard for expressing controlled vocabularies on the Web.
-Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} have created SKOS representations of their controlled vocabularies and published them on the Web so that they can easily be navigated and reused by humans and, most importantly, also by applications.
-Each vocabulary is the result of a specific design process that reflects domain-specific requirements as well as the target audience the vocabulary is created for.
-Orthogonal to the design process, vocabulary \textbf{designers and maintainers} usually apply existing guidelines or follow their own rules when defining concepts, in order to meet their \textbf{quality requirements} as, for instance, described in \cite{Coronado2009}.
-As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality, which can affect their interoperability and applicability for tasks like query expansion, faceted browsing, clustering, or auto-complete suggestions.
+% What is SKOS?
 
-The following representative examples, which we identified by looking at real-world SKOS vocabularies, illustrate the \textbf{quality problems} applications could face when making use of them:
+The Simple Knowledge Organization System (SKOS) \todo{CM}{reference, no footnote} is a standard model for sharing and linking controlled vocabularies on the Web.
+Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} have created SKOS representations of their controlled vocabularies and published them on the Web so that they can easily be accessed and by humans and machines.
+
+% What does "quality" mean in this context?
+
+Each vocabulary reflects domain- and application-specific needs and vocabulary designers usually apply some guidelines or rules (cf.,~\cite{Coronado2009}) to meet certain quality requirements.
+However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments.
+As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality.
+The following examples illustrate that this can affect their applicability for tasks like query expansion, faceted browsing, clustering, or auto-complete suggestions.
+
 \begin{itemize}
+
 	\item The SKOS version of Agrovoc defines concepts in 25 different languages.
@@
 
-	\item In the DBpedia category\footnote{\url{http://downloads.dbpedia.org/3.7/en/skos_categories_en.nt.bz2}} hierarchy, more than 10 percent of the categories not linked to any other category.
+    % \item In the DBpedia category\footnote{\url{http://downloads.dbpedia.org/3.7/en/skos_categories_en.nt.bz2}} hierarchy, more than 10 percent of the categories not linked to any other category.
 When other vocabularies link to the DBPedia categories, e.g., to enable query expansion, it can negatively affect recall and reduce navigability.
+
 \end{itemize}
 
+% How can we improve quality?
+
+%When a machine agent finds a vocabulary on the Web, it can check whether or not a vocabulary fulfills the low-level integrity conditions demanded by the SKOS specification. However, these
 One reason for these quality problems is that SKOS currently only defines a set of \textbf{low-level integrity conditions}, which, when being enforced, ensure the structural and semantic requirements of the SKOS specifications but fail to capture \textbf{higher-level quality issues}, as those mentioned in the examples before.

### 2012-03-10 main.tex
wrote abstract, modified intro (not finished yet)

@@
 \newcommand{\todo}[2]{\textbf{\textcolor{red}{(TODO [#1]: #2)}}}
+
+% metrics = quantitative indicator of sth
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+The Simple Knowledge Organization System (SKOS) has become the standard model for expressing and publishing controlled vocabularies on the Web.
+However, SKOS vocabularies are often heterogeneous in terms of quality, which reduces their applicability across system boundaries.
+Here we investigate how we can support domain experts with quantitative indicators to judge the quality of SKOS vocabularies.
+We identified existing \textbf{quality criteria} and formalized them into computable quality metrics.
+We implemented them in the qSKOS quality assessment tool and used it to analyze the quality of existing vocabularies.
+Our results indicate that \todo{CM,BH}{summarize results in one sentence}.
 
@@
 \input{introduction}
+
+\input{background}
 

### 2012-03-11 introduction.tex
updated abstract + intro

@@
 
+% BACKGROUND
+
 % What is SKOS?
-
 The Simple Knowledge Organization System (SKOS) \todo{CM}{reference, no footnote} is a standard model for sharing and linking controlled vocabularies on the Web.
@@
 % What does "quality" mean in this context?
-
-Each vocabulary reflects domain- and application-specific needs and vocabulary designers usually apply some guidelines or rules (cf.,~\cite{Coronado2009}) to meet certain quality requirements.
+Each vocabulary reflects domain- and application-specific needs and vocabulary designers usually apply their own guidelines and rules (cf.,~\cite{Coronado2009}\todo{CM}{is this correct?}) to meet certain quality requirements.
 However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments.
 As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality.
-The following examples illustrate that this can affect their applicability for tasks like query expansion, faceted browsing, clustering, or auto-complete suggestions.
+The following examples illustrate that this can affect their applicability for tasks like query expansion, faceted browsing, clustering, or auto-completion:
 
@@
 
-	\item The SKOS version of Agrovoc defines concepts in 25 different languages.
-However, almost all concepts have an English description, 38\% of all concepts don’t have German labels attached.
+	\item The SKOS representation of Agrovoc defines concepts in 25 different languages.
+However, while most concepts have an English description, only 38\% of all concepts have German labels attached.
 This can be a problem for applications that use Agrovoc and rely on German translations.
@@
 	\item The previous version of the STW thesaurus, contained 5 pairs of concepts with identical labels.
-As a result, the auto-complete function of the online search interface suggested identical entries, with no disambiguation information.
+As a result, the auto-complete function of the online search interface suggested identical entries, without giving disambiguation information.
 
-	\item The vocabulary developed by the Austrian Armed Forces (LVAk thesaurus\footnote{Non-public thesaurus developed by the Austrian Armed Forces}), which contains 11 disconnected concept clusters.
-Confronting the thesaurus maintainers with these structures, they recognized them as “forgotten” test data that has no practical significance.
+% Note: examples related to "defense / army & co" are always a bit tricky; maybe we find a better example.
+
+	\item The vocabulary developed by the Austrian Armed Forces (LVAk thesaurus\footnote{Non-public thesaurus developed by the Austrian Armed Forces}) contains 11 disconnected concept clusters.
+When we confronted the thesaurus maintainers with these structures, they recognized them as ``forgotten'' test data that has no practical significance.
+
+% Note: I am still having problems to imagine why and how one would implement query expansion based on the DBPedia categories...as long as this is not clear, better skip the example.
 
@@
 
-% How can we improve quality?
+% PROBLEM / RESEARCH QUESTION
 
-%When a machine agent finds a vocabulary on the Web, it can check whether or not a vocabulary fulfills the low-level integrity conditions demanded by the SKOS specification. However, these
-One reason for these quality problems is that SKOS currently only defines a set of \textbf{low-level integrity conditions}, which, when being enforced, ensure the structural and semantic requirements of the SKOS specifications but fail to capture \textbf{higher-level quality issues}, as those mentioned in the examples before.
-Another problem is that existing vocabulary design guidelines and best practices purely rely on \textbf{human assessment}, which is highly subjective and doesn’t scale when vocabulary quality assessment should be performed on larger, possibly linked Web vocabularies.
+The SKOS specification doesn't make any explicit statements about vocabulary quality.
+It defines a set of \textbf{integrity conditions} that state ``whether or not given data are consistent with respect to the SKOS data model'' [\todo{SKOS reference}].
+Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to verify that a given vocabulary fulfills these conditions.
+However, these conditions fail to capture \textbf{quality criteria} such as those mentioned in the examples before; criteria that go beyond the SKOS data model.
+Such criteria might be part of design rules and guidelines, but rely on \textbf{human assessment}, which is highly subjective and doesn’t scale for larger, possibly linked Web vocabularies.
 
-We believe, and recent developments of quality checking tools (e.g., PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}}, qSKOS\footnote{\url{https://github.com/cmader/qSKOS}}, SKOSify\footnote{\url{http://code.google.com/p/skosify/}}) support this motivation.
-This, however, requires a formalization of the notion of quality with respect to SKOS vocabularies, which can be used in order to consistently implement quality assessment procedures across tools.
-Since, the notion of “quality” with respect to SKOS vocabularies naturally varies across application domains it is hard, if not impossible, to come up with a general definition of quality.
-However, we believe that vocabulary designers can apply a set of \textbf{formal quality criteria} on given vocabularies in order to assess whether or not a vocabulary fulfills their requirements.
-Since these criteria are based on a formal definition, they can be calculated by automated tools, which helps vocabulary designers in assessing the quality of available or newly created vocabularies and provide important feedback to the overall vocabulary design process.
+% CONTRIBUTION
 
+The goal of our work is to identify possible quality criteria for controlled vocabularies and to provide a set of quantitative quality indicators for SKOS vocabularies.
+We believe that this can help domain experts in judging the quality of existing or newly created vocabularies and provide important feedback to the overall vocabulary design process.
 The main contributions of this work can be summarized as follows:
+
 \begin{itemize}
-	\item We derived a \textbf{quality criteria catalogue} from existing literature, tools, and public mailing list discussions in the community.
-We \textbf{formalized} each criterion and implemented them in the \textbf{qSKOS quality assessment tool}.
+
+	\item We identified \textbf{quality criteria} for controlled vocabularies by examing existing literature, tools, and public mailing list discussions.
+
+	\item We \textbf{formalized} them into computable \textbf{quality metrics} and implemented them in the \textbf{qSKOS quality assessment tool}.
 
 	\item We \textbf{analyzed} a representative \textbf{set of existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.
+
 \end{itemize}
 
-The results from our studies show that... TBD
+The results from our studies show that...
+\todo{BH,CM}{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}

### 2012-03-11 main.tex
updated abstract + intro

@@
 Here we investigate how we can support domain experts with quantitative indicators to judge the quality of SKOS vocabularies.
-We identified existing \textbf{quality criteria} and formalized them into computable quality metrics.
+We identified existing \textbf{quality criteria} and formalized them into computable \textbf{quality metrics}.
 We implemented them in the qSKOS quality assessment tool and used it to analyze the quality of existing vocabularies.
-Our results indicate that \todo{CM,BH}{summarize results in one sentence}.
+The results from this analysis indicate that \todo{CM,BH}{summarize results in one sentence}.
 

### 2012-03-11 background.tex
structured contents; added TODOs

@@
 
-\section{Background and Definitions}
+\section{Background and Methodology}
 
-% About Data Quality and SKOS
+% About Controlled Vocabulary Quality
 
-SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption.
-Established quality notions from closed-world systems, such as constraints, referential integrity or schema validation, don’t hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false.
+\todo{CM}{After the introduction it is very common to introduce the problem in more detail.
+We should write a page about quality in controlled vocabularies and explain the sources for our quality metics.
+Maybe you can pull parts from the related work section.}
+
+% Methodology
+
+\todo{CM}{How did we identify the criteria we present in the following section?}
+
+%SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption.
+Established quality notions from closed-world systems, such as referential integrity or schema validation, don’t hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false.
 While trust and provenance models for Web data are being developed \cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets \cite{Heath2011}.
-
-% What kind of quality criteria are defined in SKOS
-
-\todo{CM}{write a short paragraph about the quality criteria in the SKOS specification.}
-
-% This definition is not a quality criterions, henec it is in the background section (we need to discuss that)
-
-\begin{definition} \textbf{The SKOS Baseline Model} is defined as follows:
-Let R be the set of all resources, as defined in [Web Architecture Document] and \[V = (C, A, LL, LR, SR, AR)\] be one specific SKOS vocabulary, with
-
-\begin{itemize}
-	\item \(C \subseteq R\) being the set of \textbf{conceptual resources} of type \texttt{skos:Concept}.
-	\item \(A \subseteq R\) being the set of aggregation and grouping resources in SKOS, hence \texttt{skos:ConceptSchema} and \texttt{skos:Collection}.
-	\item LL being the set \textbf{lexical labels}, which are instances of RDF plain literals.
-	\item \(LR \subseteq C \times LL\) being the set of \textbf{lexical relations} associating conceptual resources with lexical labels, hence instances of \texttt{skos:prefLabel}, \texttt{skos:altLabel}, or \texttt{skos:hiddenLabel}.
-\item \(SR \subseteq C \times C\) being the set of \textbf{semantic relations} associating conceptual resources with concepts, hence instances of \texttt{skos:semanticRelation} and subproperties thereof.
-\item \(AR \subseteq C \times A\) being the set of \textbf{aggregation (and grouping) relations} associating conceptual resources with instances of aggregation and grouping resources.
-\end{itemize}
-\end{definition}

### 2012-03-11 introduction.tex
structured contents; added TODOs

@@
 However, these conditions fail to capture \textbf{quality criteria} such as those mentioned in the examples before; criteria that go beyond the SKOS data model.
-Such criteria might be part of design rules and guidelines, but rely on \textbf{human assessment}, which is highly subjective and doesn’t scale for larger, possibly linked Web vocabularies.
+Such criteria might be part of design rules and guidelines, but rely on \textbf{human judgement}, which is subjective and does not scale for larger, possibly linked Web vocabularies.
 
@@
 
-The goal of our work is to identify possible quality criteria for controlled vocabularies and to provide a set of quantitative quality indicators for SKOS vocabularies.
+The goal of our work is to provide a set of quantitative quality indicators for SKOS vocabularies.
 We believe that this can help domain experts in judging the quality of existing or newly created vocabularies and provide important feedback to the overall vocabulary design process.
@@
 
-	\item We identified \textbf{quality criteria} for controlled vocabularies by examing existing literature, tools, and public mailing list discussions.
+	\item We identified \textbf{quality criteria} for controlled vocabularies by examining existing literature, tools, and public mailing list discussions.
+Then we \textbf{formalized} them into computable \textbf{quality metrics} so that they can be implemented consistently by different tools.
 
-	\item We \textbf{formalized} them into computable \textbf{quality metrics} and implemented them in the \textbf{qSKOS quality assessment tool}.
+	\item We implemented these metrics in the \textbf{qSKOS quality assessment tool}.
 

### 2012-03-11 analysis.tex
structured contents; added TODOs
minor additions

@@
+%!TEX root = main.tex
+
 \section{Analysis of Existing SKOS Vocabularies}\label{sec:analysis}
@@
 
-\subsection{Vocabularies}
+\todo{BH}{make clear that tool also provides reports not only numeric values}
+
+\subsection{Vocabulary Data Set}
+
+\todo{CM}{Add dataset table so that we know how much space this will take.}
+\begin{table}[h]
+\caption{Analyzed vocabularies}
+\begin{tabular}{|p{2.5cm}|p{6cm}|p{2cm}|p{.5cm}|p{.5cm}|p{.5cm}|p{.5cm}|p{.5cm}|}
+\hline
+\textbf{Domain} & \textbf{Vocabulary} & \textbf{CO} & \textbf{LR} & \textbf{SR} & \textbf{AR} & \textbf{CS} & \textbf{CL}\\
+\hline
+Media & GTAA & & & & & & \\
+\hline
+Science & Geonames Ontology &&&&&& \\
+\hline
+& MeSH &&&&&& \\
+\hline
+& Peroxisome Knowledge Base &&&&&& \\
+\hline
+Government & Eurovoc &&&&&& \\
+\hline
+& IPSV &&&&&& \\
+\hline
+\\
+\hline
+
+\end{tabular}
+\end{table}
 
 \subsection{Results}
+
+\todo{CM}{Add the result table, with one row for the lc metric.}
+
+\todo{CM}{Add result interpretation for this one metric}

### 2012-03-11 introduction.tex
minor additions

@@
 % What is SKOS?
-The Simple Knowledge Organization System (SKOS) \todo{CM}{reference, no footnote} is a standard model for sharing and linking controlled vocabularies on the Web.
+The Simple Knowledge Organization System (SKOS) \cite{Miles2005} is a standard model for sharing and linking controlled vocabularies on the Web.
 Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} have created SKOS representations of their controlled vocabularies and published them on the Web so that they can easily be accessed and by humans and machines.
@@
 % Note: I am still having problems to imagine why and how one would implement query expansion based on the DBPedia categories...as long as this is not clear, better skip the example.
+% mein fantasie-szenario ist folgendes: jmd hat einen korpus an dokumenten und will diesen nach kategorien indizieren.
+also sucht man ein existierendes vocab das man verwenden könnte (irgendwelche subject headings oder eben die dbpedia kategorien weil die eben schon in SKOS verfügbar sind und dbpedia sowieso das zentrum der ld-welt darstellt :).
+Also verschlagwortet man den dokumentkorpus mit dbpedia-categories und kommt dann, aufgrund der loose concepts drauf, dass dokumente die in ähnliche kategorien (broader/narrower) fallen, nicht gefunden werden können, also den recall verschlechtern.
+ist das unrealistisch?
 

### 2012-03-11 main.tex
minor additions

@@
 Here we investigate how we can support domain experts with quantitative indicators to judge the quality of SKOS vocabularies.
-We identified existing \textbf{quality criteria} and formalized them into computable \textbf{quality metrics}.
+[cm: Based on existing guidelines and best practices for creating controlled vocabularies, we] We identified existing \textbf{quality criteria} and formalized them into computable \textbf{quality metrics}.
 We implemented them in the qSKOS quality assessment tool and used it to analyze the quality of existing vocabularies.
@@
 
-\bibliography{lit}
+\bibliography{references}
 \bibliographystyle{splncs03}

### 2012-03-11 analysis.tex
added vocab table draft

@@
 \subsection{Vocabulary Data Set}
-
-\todo{CM}{Add dataset table so that we know how much space this will take.}
+\todo{CM}{add info about data gathering process and vocab changes/fixes to parse them}
 \begin{table}[h]
 \caption{Analyzed vocabularies}
-\begin{tabular}{|p{2.5cm}|p{6cm}|p{2cm}|p{.5cm}|p{.5cm}|p{.5cm}|p{.5cm}|p{.5cm}|}
+\begin{tabular}{|p{2cm}|p{6cm}|p{1.5cm}|p{.8cm}|p{.8cm}|p{.8cm}|p{.8cm}|p{.8cm}|}
 \hline
-\textbf{Domain} & \textbf{Vocabulary} & \textbf{CO} & \textbf{LR} & \textbf{SR} & \textbf{AR} & \textbf{CS} & \textbf{CL}\\
+\textbf{Domain} & \textbf{Vocabulary} & \textbf{CO\footnote{concepts}} & \textbf{LR\footnote{lexical relations}} & \textbf{SR\footnote{semantic relations}} & \textbf{AR\footnote{associative relations}} & \textbf{CS\footnote{concept schemes}} & \textbf{CL\footnote{collections}}\\
 \hline
@@
 \hline
+Publications & Agrovoc &&&&&& \\
+\hline
+& DBpedia Categories &&&&&& \\
+\hline
+& Pressinfo &&&&&& \\
+\hline
+& NYT people &&&&&& \\
+\hline
+& LCSH &&&&&& \\
+\hline
+Cross-domain & Meketre &&&&&& \\
+\hline
+Economy & STW &&&&&& \\
+\hline
+& NAICS &&&&&& \\
+\hline
+Military & LVAk &&&&&&
 \\

### 2012-03-12 analysis.tex
added acknowledgements draft and updated analyzed vocab table

--- 2012-03-11 analysis.tex
@@
 \subsection{Vocabulary Data Set}
+Our vocabulary dataset covers XY vocabularies from various domains differing in statistical properties (cf.
+Table~\ref{vocabs}).
+The data was gathered in different ways.
+Some vocabularies where downloaded from their respective project websites or, in the cases of IPSV, Peroxisome Knowledge Base, and LVAk requested directly from the creators.
+The MeSH dataset was created by \cite{Assem2006} and is available for download\footnote{\url{http://thesauri.cs.vu.nl/eswc06/}}.
+We created the SKOS version of LVAk thesaurus from CSV files provided by the vocabulary maintainers.
+The vocabulary structure was uncomplex, so the conversion process to SKOS turned out as being rather straightforward.
+\todo{CM}{should we elaborate more on the conversion process?}
 
-\todo{CM}{Add dataset table so that we know how much space this will take.}
+Our syntactical checks showed that only the Agrovoc vocabulary contained invalid datatypes and characters.
+After some minor syntax modifications, which don’t influence the evaluation against our criteria, we were also able to include this vocabulary.
+We also informed the AGROVOC team about this problem, which will try to fix it.
+
 \begin{table}[h]
 \caption{Analyzed vocabularies}
-\begin{tabular}{|p{2.5cm}|p{6cm}|p{2cm}|p{.5cm}|p{.5cm}|p{.5cm}|p{.5cm}|p{.5cm}|}
+\begin{tabular}{|p{2cm}|p{6cm}|p{1.5cm}|p{.8cm}|p{.8cm}|p{.8cm}|p{.8cm}|p{.8cm}|}
 \hline
@@
 \hline
-Media & GTAA & & & & & & \\
+Media & Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & & & & & & \\
 \hline
@@
 \hline
-& MeSH &&&&&& \\
+& Medical Subject Headings (MeSH) &&&&&& \\
 \hline
@@
 \hline
-& IPSV &&&&&& \\
+& Integrated Public Sector Vocabulary (IPSV) &&&&&& \\
 \hline
+Publications & Agrovoc &&&&&& \\
+\hline
+& DBpedia Categories &&&&&& \\
+\hline
+& University of Southampton Pressinfo &&&&&& \\
+\hline
+& New York Times People &&&&&& \\
+\hline
+& Library of Congress Subject Headings (LCSH) &&&&&& \\
+\hline
+Cross-domain & Meketre &&&&&& \\
+\hline
+Economy & Thesaurus for Economics (STW) &&&&&& \\
+\hline
+& North American Industry Classification System (NAICS) &&&&&& \\
+\hline
+Military & Thesaurus Landesverteidigungsakademie (LVAk) &&&&&&
 \\
 \hline
-
 \end{tabular}
+\label{vocabs}
 \end{table}

### 2012-03-12 analysis.tex
added table statistics data

@@
 
-Our syntactical checks showed that only the Agrovoc vocabulary contained invalid datatypes and characters.
+Our syntactical checks showed that only the AGROVOC vocabulary contained invalid datatypes and characters.
 After some minor syntax modifications, which don’t influence the evaluation against our criteria, we were also able to include this vocabulary.
@@
 \caption{Analyzed vocabularies}
-\begin{tabular}{|p{2cm}|p{6cm}|p{1.5cm}|p{.8cm}|p{.8cm}|p{.8cm}|p{.8cm}|p{.8cm}|}
+\begin{tabular}{lp{5cm}cccccc}
+\textbf{Domain} & \textbf{Vocabulary} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Lexical Rel.}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
+\toprule
+Media & Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
 \hline
-\textbf{Domain} & \textbf{Vocabulary} & \textbf{CO} & \textbf{LR} & \textbf{SR} & \textbf{AR} & \textbf{CS} & \textbf{CL}\\
+Science & Geonames Ontology & 671 & 671 & 0 & 671 & 9 & 0 \\
 \hline
-Media & Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & & & & & & \\
+& Medical Subject Headings (MeSH) & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
 \hline
-Science & Geonames Ontology &&&&&& \\
+& Peroxisome Knowledge Base & 2112 & 3628 & 2695 & 1716 & 1 & 0 \\
 \hline
-& Medical Subject Headings (MeSH) &&&&&& \\
+Government & Eurovoc & 6797 & 457788 & 18491 & 15512 & 128 & 0 \\
 \hline
-& Peroxisome Knowledge Base &&&&&& \\
+& Integrated Public Sector Vocabulary (IPSV) & 4732 & 7945 & 13843 & 4483 & 3 & 0 \\
 \hline
-Government & Eurovoc &&&&&& \\
+Publications & Agrovoc & 31993 & 572138 & 63936 & 32043 & 1 & 0 \\
 \hline
-& Integrated Public Sector Vocabulary (IPSV) &&&&&& \\
+& DBpedia Categories & 743410 & 740352 & 1490316 & 0 & 0 & 0 \\
 \hline
-Publications & Agrovoc &&&&&& \\
+& University of Southampton Pressinfo & 1125 & 0 & 0 & 0 & 0 & 0 \\
 \hline
-& DBpedia Categories &&&&&& \\
+& New York Times People & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
 \hline
-& University of Southampton Pressinfo &&&&&& \\
+& Library of Congress Subject Headings (LCSH) & 459182 & 746076 & 595754 & 815816 & 19 & 0 \\
 \hline
-& New York Times People &&&&&& \\
+Cross-domain & Meketre & 422 & 569 & 1698 & 6 & 2 & 0 \\
 \hline
-& Library of Congress Subject Headings (LCSH) &&&&&& \\
+Economy & Thesaurus for Economics (STW) & 6524 & 31189 & 57907 & 6531 & 1 & 0 \\
 \hline
-Cross-domain & Meketre &&&&&& \\
+& North American Industry Classification System (NAICS) & 4175 & 0 & 8684 & 2235 & 1 & 0 \\
 \hline
-Economy & Thesaurus for Economics (STW) &&&&&& \\
-\hline
-& North American Industry Classification System (NAICS) &&&&&& \\
-\hline
-Military & Thesaurus Landesverteidigungsakademie (LVAk) &&&&&&
-\\
-\hline
+Military & Thesaurus Landesverteidigungsakademie (LVAk) & 13411 & 17250 & 16346 & 0 & 0 & 0 \\
+\bottomrule
 \end{tabular}

### 2012-03-12 introduction.tex
added table statistics data

@@
 % What does "quality" mean in this context?
-Each vocabulary reflects domain- and application-specific needs and vocabulary designers usually apply their own guidelines and rules (cf.,~\cite{Coronado2009}\todo{CM}{is this correct?}) to meet certain quality requirements.
+Each vocabulary reflects domain- and application-specific needs and vocabulary designers usually apply their own guidelines and rules (cf.,~\cite{Coronado2009} who utilize a combination of automated and manual checks and reviews) to meet certain quality requirements.
 However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments.
@@
 The SKOS specification doesn't make any explicit statements about vocabulary quality.
-It defines a set of \textbf{integrity conditions} that state ``whether or not given data are consistent with respect to the SKOS data model'' [\todo{SKOS reference}].
+It defines a set of \textbf{integrity conditions} that state ``whether or not given data are consistent with respect to the SKOS data model''\footnote{\url{http://www.w3.org/TR/skos-reference/}}.
 Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to verify that a given vocabulary fulfills these conditions.

### 2012-03-12 analysis.tex
added results for lc metrics

@@
 \caption{Analyzed vocabularies}
-\begin{tabular}{lp{5cm}cccccc}
+\begin{tabular}{lp{4.7cm}cccccc}
 \textbf{Domain} & \textbf{Vocabulary} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Lexical Rel.}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
@@
 \hline
-& Peroxisome Knowledge Base & 2112 & 3628 & 2695 & 1716 & 1 & 0 \\
+& Peroxisome Knowledge Base (PXV) & 2112 & 3628 & 2695 & 1716 & 1 & 0 \\
 \hline
@@
 \hline
-& New York Times People & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
+& New York Times People (NYTP) & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
 \hline
@@
 
-\todo{CM}{Add the result table, with one row for the lc metric.}
+\begin{table}[h]
+\caption{Results of the proposed metrics}
+\begin{tabular}{lccccccccccccccc}
+\textbf{Metric} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
+\toprule
+Loose Concepts & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 77062 & 1125 & 0 & 0 & 0 & 0 & 0 & 21 \\
+\bottomrule
+\end{tabular}
+\end{table}
 

### 2012-03-13 introduction.tex
considered antoine's comments in abstract + intro

--- 2012-03-11 introduction.tex
@@
 % What is SKOS?
-The Simple Knowledge Organization System (SKOS) \cite{Miles2005} is a standard model for sharing and linking controlled vocabularies on the Web.
+The Simple Knowledge Organization System (SKOS)~\cite{Miles2005} is a standard model for sharing and linking controlled vocabularies on the Web.
 Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} have created SKOS representations of their controlled vocabularies and published them on the Web so that they can easily be accessed and by humans and machines.
@@
 % What does "quality" mean in this context?
-Each vocabulary reflects domain- and application-specific needs and vocabulary designers usually apply their own guidelines and rules (cf.,~\cite{Coronado2009}\todo{CM}{is this correct?}) to meet certain quality requirements.
+Each vocabulary reflects domain- and application-specific needs and vocabulary designers often follow existing standards [\todo{cm}{ref}] or apply their own hand-crafted checks (cf.,~\cite{Coronado2009}) to meet certain quality requirements.
 However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments.
@@
 
-	\item The previous version of the STW thesaurus, contained 5 pairs of concepts with identical labels.
+	\item \todo{CM}{An earlier version of the STW thesaurus contained 5 pairs of concepts with identical labels}.
 As a result, the auto-complete function of the online search interface suggested identical entries, without giving disambiguation information.
@@
 The SKOS specification doesn't make any explicit statements about vocabulary quality.
-It defines a set of \textbf{integrity conditions} that state ``whether or not given data are consistent with respect to the SKOS data model'' [\todo{SKOS reference}].
+It defines a set of \textbf{integrity conditions} that state ``whether or not given data are consistent with respect to the SKOS data model''~\cite{Miles2005}.
 Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to verify that a given vocabulary fulfills these conditions.
-However, these conditions fail to capture \textbf{quality criteria} such as those mentioned in the examples before; criteria that go beyond the SKOS data model.
-Such criteria might be part of design rules and guidelines, but rely on \textbf{human judgement}, which is subjective and does not scale for larger, possibly linked Web vocabularies.
+However, these conditions fail to capture \textbf{quality criteria} such as those mentioned in the examples before; criteria that go beyond integrity conditions of the SKOS data model.
+Such criteria might be part of design rules and guidelines, but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger, possibly linked Web vocabularies.
 
@@
 
-	\item We identified \textbf{quality criteria} for controlled vocabularies by examining existing literature, tools, and public mailing list discussions.
-Then we \textbf{formalized} them into computable \textbf{quality metrics} so that they can be implemented consistently by different tools.
+	\item We identified existing \textbf{quality criteria} for controlled vocabularies by examining existing guidelines and \textbf{formalized} them into computable \textbf{quality metrics} so that they can be implemented consistently by different tools.
 
-	\item We implemented these metrics in the \textbf{qSKOS quality assessment tool}.
+	\item We implemented these metrics in the \textbf{qSKOS quality assessment tool}, which can be used as software library or command line tool.
 
-	\item We \textbf{analyzed} a representative \textbf{set of existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.
+	\item We \textbf{analyzed} a representative set of \textbf{existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.
 
@@
 
-The results from our studies show that...
+The results from our analysis show that...
 \todo{BH,CM}{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.

### 2012-03-13 main.tex
added table statistics data
considered antoine's comments in abstract + intro

--- 2012-03-11 main.tex
@@
 \usepackage{amssymb}
-
+\usepackage{rotating}
 \usepackage{color}
+\usepackage{booktabs}
 
@@
 Here we investigate how we can support domain experts with quantitative indicators to judge the quality of SKOS vocabularies.
-We identified existing \textbf{quality criteria} and formalized them into computable \textbf{quality metrics}.
+Based on existing guidelines and best practices for creating controlled vocabularies, we identified existing \textbf{quality criteria} and formalized them into computable \textbf{quality metrics}.
 We implemented them in the qSKOS quality assessment tool and used it to analyze the quality of existing vocabularies.

### 2012-03-13 introduction.tex
added stw example version info

@@
 
-	\item \todo{CM}{An earlier version of the STW thesaurus contained 5 pairs of concepts with identical labels}.
-As a result, the auto-complete function of the online search interface suggested identical entries, without giving disambiguation information.
+	\item \todo{CM}{An earlier version, the STW thesaurus (8.06) contained 5 pairs of concepts with identical labels}.
+As a result, the auto-complete function of the online search interface at that time suggested identical entries, without giving disambiguation information.
 

### 2012-03-13 background.tex
structured section 2

@@
 
-% About Controlled Vocabulary Quality
+% About Quality in SKOS vocabularies
+
+SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption.
+Established quality notions from closed-world systems, such as referential integrity or schema validation, don’t hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false.
+While trust and provenance models for Web data are being developed~\cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}.
+
+The quality of a given SKOS vocabulary can have a direct impact on the following application areas of controlled vocabularies: \todo{CM}{write a paragraph}
+
+SKOS consistency and integrity means that
+-
 
@@
 \todo{CM}{How did we identify the criteria we present in the following section?}
-
-%SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption.
-Established quality notions from closed-world systems, such as referential integrity or schema validation, don’t hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false.
-While trust and provenance models for Web data are being developed \cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets \cite{Heath2011}.

### 2012-03-13 introduction.tex
structured section 2

--- 2012-03-13 introduction.tex
@@
 The goal of our work is to provide a set of quantitative quality indicators for SKOS vocabularies.
-We believe that this can help domain experts in judging the quality of existing or newly created vocabularies and provide important feedback to the overall vocabulary design process.
+They can be used by domain experts and vocabulary designers for judging the quality of existing or newly created vocabularies and provide important feedback to the overall vocabulary design process.
 The main contributions of this work can be summarized as follows:
@@
 
-	\item We identified existing \textbf{quality criteria} for controlled vocabularies by examining existing guidelines and \textbf{formalized} them into computable \textbf{quality metrics} so that they can be implemented consistently by different tools.
+	\item We identified existing \textbf{quality criteria} for controlled vocabularies by examining existing guidelines and formalized them into computable \textbf{quality metrics} so that they can be implemented consistently by different tools.
 

### 2012-03-13 background.tex
drafted background section

@@
 
-SKOS consistency and integrity means that
--
-
-\todo{CM}{After the introduction it is very common to introduce the problem in more detail.
-We should write a page about quality in controlled vocabularies and explain the sources for our quality metics.
-Maybe you can pull parts from the related work section.}
+Interoperability between applications has been the major motivation for specifying in total XX \textbf{SKOS integrity conditions}.
+An integrity condition is a statement that defines under which circumstances data are consistent with the SKOS data model.
+An example condition is ``A resource has no more than one value of skos:prefLabel per language tag''.
+Tools can check whether these integrity conditions are met for given data.
+Poolparty implements XX integrity conditions, SKOSify YY.
+\todo{CM}{summarize how existing tools implement these conditions}
 
@@
 
-\todo{CM}{How did we identify the criteria we present in the following section?}
+Our goal was to identify quality criteria that go beyond SKOS integrity conditions.
+These criteria do not primarily address interoperability on the data model level but usability and interoperability in the application areas mentioned before.
+We used the following sources for our investigation:
+
+\begin{itemize}
+    \item Existing literature
+    \item Mailing list discussions
+    \item \ldots
+\end{itemize}
+
+After we identified an initial set of criteria, we formalized them into computable metrics and applied them on existing SKOS vocabularies to learn about the real-world occurrences of these criteria.
+During that process we also learned about additional quality issues in real world SKOS data, refined already identified criteria and included additional ones in a SKOS quality criteria catalogue, which we published at \url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}.

### 2012-03-13 background.tex
added related work

@@
 
-The quality of a given SKOS vocabulary can have a direct impact on the following application areas of controlled vocabularies: \todo{CM}{write a paragraph}
+% SKOS Integrity Conditions (http://www.w3.org/TR/skos-reference/):
+% S9    skos:ConceptScheme is disjoint with skos:Concept.
+% S13   skos:prefLabel, skos:altLabel and skos:hiddenLabel are pairwise disjoint properties. (* NOT expressed formally *)
+% S14   A resource has no more than one value of skos:prefLabel per language tag. (* NOT expressed formally *)
+% S27   skos:related is disjoint with the property skos:broaderTransitive. (* NOT expressed formally *)
+% S37   skos:Collection is disjoint with each of skos:Concept and skos:ConceptScheme.
+% S46   skos:exactMatch is disjoint with each of the properties skos:broadMatch and skos:relatedMatch. (* NOT expressed formally *)
+% -> 2 of 6 are expressed formally in OWL; the others cannot be expressed because OWL doesn't support disjoint properties
 
-Interoperability between applications has been the major motivation for specifying in total XX \textbf{SKOS integrity conditions}.
+% Poolparty quality checker implementation:
+% S13, S14, S27, S46
+% syntactic checks: URI, character encoding
+% missing language tags, missing labels
+
+% Mapping qSKOS Integrity Conditions <-> qSKOS quality criteria
+% S13 + S14 combined in "Ambigious labels"
+% S27 + S46 combined in "Associative vs. Hierarchical Relation Clashes" and "Exact vs. Associative and Hierarchical Mapping Clashes"
+
+Interoperability between applications has been the major motivation for specifying in total six \textbf{SKOS integrity conditions}~\cite{Miles2005}.
 An integrity condition is a statement that defines under which circumstances data are consistent with the SKOS data model.
@@
 Tools can check whether these integrity conditions are met for given data.
-Poolparty implements XX integrity conditions, SKOSify YY.
-\todo{CM}{summarize how existing tools implement these conditions}
+Two of the six integrity conditions are defined formally in the OWL representation of SKOS and can therefore be verified by any OWL reasoner.
+Poolparty and SKOSify implement all these integrity checks plus \todo{CM}{summarize how existing tools implement these conditions}
+
+% Argue why we need higher-level criteria
+
+The quality of a given SKOS vocabulary can have a direct impact on the following application areas of controlled vocabularies: \todo{CM}{write a paragraph}
 

### 2012-03-13 background.tex
added TODO to metrics

@@
 SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption.
-Established quality notions from closed-world systems, such as referential integrity or schema validation, don’t hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false.
+Established quality notions from closed-world systems, such as referential integrity or schema validation, don't hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false.
 While trust and provenance models for Web data are being developed~\cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}.
+\todo{CM}{check what the recent paper by Christophe Gueret is about.}
 
@@
 
-The quality of a given SKOS vocabulary can have a direct impact on the following application areas of controlled vocabularies: \todo{CM}{write a paragraph}
+\todo{CM}{argue why quality criteria beyond integrity conditions are needed; provide some good arguments and refer to the literature.
+The focus of this paragraph should be on quality in the controlled vocabulary domain...}
 
@@
     \item Mailing list discussions
-    \item \ldots
+    \item \ldots \todo{cm}{think about and finish this paragraph and lists.}
 \end{itemize}

### 2012-03-13 background.tex
added citations

@@
 While trust and provenance models for Web data are being developed~\cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}.
-\todo{CM}{check what the recent paper by Christophe Gueret is about.}
+In the course of the LATC project, Gueret et al.
+propose an infrastructure that utilizes crowd-sourcing technology to semi-automatically create links between datasets of the LOD cloud.
+To ensure the quality of the resulting network, human judgement is supported by calculating a report of locally approximated network measures.
+\todo{BH}{ich denke antoine hat das paper gemeint: http://www.mendeley.com/download/public/18928/4084690763/56bdde328dfbba2cb8594b57152c0e132ef00a40/dl.pdf .
+Leider fehlen da etliche Details um sich ein konkretes Bild machen zu können}
 
@@
 After we identified an initial set of criteria, we formalized them into computable metrics and applied them on existing SKOS vocabularies to learn about the real-world occurrences of these criteria.
-During that process we also learned about additional quality issues in real world SKOS data, refined already identified criteria and included additional ones in a SKOS quality criteria catalogue, which we published at \url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}.
+During that process we also learned about additional quality issues in real world SKOS data, refined already identified criteria and included additional ones in a SKOS quality criteria catalogue, which we published online\footnote{\url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}}.

### 2012-03-13 introduction.tex
minor example fix
added citations

@@
 % What does "quality" mean in this context?
-Each vocabulary reflects domain- and application-specific needs and vocabulary designers often follow existing standards [\todo{cm}{ref}] or apply their own hand-crafted checks (cf.,~\cite{Coronado2009}) to meet certain quality requirements.
+Each vocabulary reflects domain- and application-specific needs and vocabulary designers often follow existing standards \cite{ISO25964-1:2011,Z39.19:2005} or apply their own hand-crafted checks (cf.,~\cite{Coronado2009}) to meet certain quality requirements.
 However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments.
@@
 
-	\item \todo{CM}{An earlier version, the STW thesaurus (8.06) contained 5 pairs of concepts with identical labels}.
+	\item An earlier version (v.8.06) of the STW thesaurus contained 5 pairs of concepts with identical labels.
 As a result, the auto-complete function of the online search interface at that time suggested identical entries, without giving disambiguation information.

### 2012-03-14 background.tex
added pp and skosify criteria coverage

@@
 % Poolparty quality checker implementation:
-% S13, S14, S27, S46
-% syntactic checks: URI, character encoding
-% missing language tags, missing labels
+% S13, S14, S27, S46 plus the formally defined S9, S37
+% syntactic checks: URI, character encoding, whitespaces
+% missing language tags: in SKOS labels and textual content)
+% missing labels: prefLabels for skos:Concepts and rdfs:labels for skos:ConceptSchemes)
+% loose concepts: concepts that are no top concepts and have no broaders
+
+% SKOSify
+% S13, S14, S27
 
@@
 Two of the six integrity conditions are defined formally in the OWL representation of SKOS and can therefore be verified by any OWL reasoner.
-Poolparty and SKOSify implement all these integrity checks plus \todo{CM}{summarize how existing tools implement these conditions}
+
+The PoolParty Thesaurus Consistency Checker implements all these conditions and introduces the following new checks: \textbf{URI validation} checks for invalid characters like, e.g.
+whitespaces in the URI string.
+\textbf{Definition of labels} is tested for conceptual resources and concept schemes.
+Furthermore, SKOS labels and textual content is checked for \textbf{missing language tags} and the notion of \textbf{loose concepts} is defined: it encompasses conceptual resources that are no top concepts and have no broader concept.
+
+The SKOSify tool implements three of the above mentioned SKOS integrity conditions as well as the \textbf{missing language tags} and \textbf{loose concepts} measures introduced by the PoolParty checker.
+It introduces \textbf{hierarchy cycle detection} and detection of \textbf{extra whitespace} for SKOS label or documentation properties.
 

### 2012-03-14 background.tex
added some comments by antoine

@@
 % Argue why we need higher-level criteria
+With controlled vocabularies being available in the Web of Data, they are adopted for use-cases or domains not originally intended by the creators.
+These use-cases often have specific and overlapping requirements regarding, e.g., structure, availability or documentation of the underlying controlled vocabularies.
+To give some examples, loose concepts might negatively impact retrieval recall, missing entry points to an aggregated set of concepts impedes orientation for human users, and inconsistent relations hinder queries across distinct datsets.
+Thus there is a need for higher-level quality criteria that go beyond the integrity conditions given in the SKOS data model, which take into account characteristics of the intended application areas.
+\todo{CM}{provide references}
 
-\todo{CM}{argue why quality criteria beyond integrity conditions are needed; provide some good arguments and refer to the literature.
-The focus of this paragraph should be on quality in the controlled vocabulary domain...}
+%\todo{CM}{argue why quality criteria beyond integrity conditions are needed; provide some good arguments and refer to the literature.
+%The focus of this paragraph should be on quality in the controlled vocabulary domain...}
 
@@
     \item Mailing list discussions
-    \item \ldots \todo{cm}{think about and finish this paragraph and lists.}
+		\item Practices in current vocabulary development projects
+		\item Review of online available vocabularies from different domains
+    \item Feedback from experts in vocabulary creation
+%\ldots \todo{cm}{think about and finish this paragraph and lists.}
 \end{itemize}

### 2012-03-15 background.tex
polished background section

--- 2012-03-13 background.tex
@@
 
-\section{Background and Methodology}
+\section{Background}
 
@@
 While trust and provenance models for Web data are being developed~\cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}.
-In the course of the LATC project, Gueret et al.
+Gueret et al.
+[\todo{CM}{find the right reference in google scholar}], for instance, calculate network measures to support human judgement on the quality of Linked Data \todo{CM}{?} graphs.
+
+%In the course of the LATC project, Gueret et al.
 propose an infrastructure that utilizes crowd-sourcing technology to semi-automatically create links between datasets of the LOD cloud.
@@
 
-Interoperability between applications has been the major motivation for specifying in total six \textbf{SKOS integrity conditions}~\cite{Miles2005}.
-An integrity condition is a statement that defines under which circumstances data are consistent with the SKOS data model.
-An example condition is ``A resource has no more than one value of skos:prefLabel per language tag''.
-Tools can check whether these integrity conditions are met for given data.
-Two of the six integrity conditions are defined formally in the OWL representation of SKOS and can therefore be verified by any OWL reasoner.
-Poolparty and SKOSify implement all these integrity checks plus \todo{CM}{summarize how existing tools implement these conditions}
+Interoperability between applications has been the major motivation for specifying in total six \textbf{SKOS integrity conditions}~\cite{Miles2005}, each of which is a statement that defines under which circumstances data are consistent with the SKOS data model.
+An example condition is ``a resource has no more than one value of skos:prefLabel per language tag''.
+Tools that can check whether these integrity conditions are met for given data are already available: two of the six integrity conditions are defined formally in the OWL representation of SKOS and can therefore be validated by any OWL reasoner \todo{CM}{true?}.
+For validating a SKOS vocabulary against the integrity conditions, one can use tools such as the online \textbf{PoolParty Thesaurus Consistency Checker}, or the \textbf{Skosify} command line utility, which can validate SKOS vocabularies and also correct some detected quality problems.
 
-% Argue why we need higher-level criteria
+% Argue why we need criteria that go beyond low-level integrity constraints and why we need to formalize them
 
-\todo{CM}{argue why quality criteria beyond integrity conditions are needed; provide some good arguments and refer to the literature.
-The focus of this paragraph should be on quality in the controlled vocabulary domain...}
+Typical application areas of controlled vocabularies are as classification, indexing, autocompletion, query reformulation/expansion, or serving as a glossary.
+As we discussed in detail in our earlier work [\ref{CM}{iSem paper?}], these application areas have specific requirements with respect to vocabulary features, such as structure, availability, and documentation of conceptual resources.
+A vocabulary that doesn't fulfill these requirements can have a negative effect on an application's output and would therefore be judged by the application designers and potentially also by users as being a low-quality vocabulary.
+Missing relations between conceptual resources, for instance, can reduce retrieval recall when a vocabulary is used for query expansion.
+Missing entry points to concepts in a vocabulary can impede orientation for human users.
+Inconsistent relations can hinder queries across distinct datasets\todo{cm}{this example is unclear}, to name some examples.
 
-% Methodology
+% Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
+Thus, in order to help vocabulary and application designers in judging the quality of SKOS vocabularies, we need higher-level quality criteria that go beyond low-level integrity conditions, which define data model consistency.
+Such quality criteria are already well-established and have extensively been discussed in standardized guidelines [\todo{CM}{ISO refs}], manuals [\todo{CM}{hedden book, skosify ref 3}], and scholarly articles [\todo{cm}{e.g., skosify refs 16/17}].
+% TODO: bitte hier einfach nur die referenzen auf die wir uns beziehen zusammenfassen und kategorisieren. Schau dir dazu auch nochmals die SKOSify referenzen und die aus eurem iSemantics paper an.
+If we want to apply these criteria on SKOS vocabularies, we first need to identify them and determine how to evaluate them given the syntax, structure and semantics of SKOS.
+Since we want to provide tool support for quality checking, we must formalize these criteria into computable metrics, in order to ensure consistent implementation and interpretation across tools.
 
-Our goal was to identify quality criteria that go beyond SKOS integrity conditions.
-These criteria do not primarily address interoperability on the data model level but usability and interoperability in the application areas mentioned before.
-We used the following sources for our investigation:
+% I think for the big picture it is not necessary to go into such details. We can do this later when introducting the metrics
 
-\begin{itemize}
-    \item Existing literature
-    \item Mailing list discussions
-    \item \ldots \todo{cm}{think about and finish this paragraph and lists.}
-\end{itemize}
-
-After we identified an initial set of criteria, we formalized them into computable metrics and applied them on existing SKOS vocabularies to learn about the real-world occurrences of these criteria.
-During that process we also learned about additional quality issues in real world SKOS data, refined already identified criteria and included additional ones in a SKOS quality criteria catalogue, which we published online\footnote{\url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}}.
+% The PoolParty Thesaurus Consistency Checker implements all these conditions and introduces the following new checks: \textbf{URI validation} checks for invalid characters like, e.g.
+whitespaces in the URI string.
+\textbf{Definition of labels} is tested for conceptual resources and concept schemes.
+Furthermore, SKOS labels and textual content is checked for \textbf{missing language tags} and the notion of \textbf{loose concepts} is defined: it encompasses conceptual resources that are no top concepts and have no broader concept.
+% 
+% The SKOSify tool implements three of the above mentioned SKOS integrity conditions as well as the \textbf{missing language tags} and \textbf{loose concepts} measures introduced by the PoolParty checker.
+It introduces \textbf{hierarchy cycle detection} and detection of \textbf{extra whitespace} for SKOS label or documentation properties.

### 2012-03-18 analysis.tex
added some comments by antoine
changed (parts) of skos quality model to conform to RDF formal semantics; changed definition of loose concepts and recomputed tabular values.
added result description for lc and wcc and an analysis of wcc

@@
 The vocabulary structure was uncomplex, so the conversion process to SKOS turned out as being rather straightforward.
-\todo{CM}{should we elaborate more on the conversion process?}
 
@@
 \caption{Results of the proposed metrics}
-\begin{tabular}{lccccccccccccccc}
+\begin{tabular}{p{4cm}ccccccccccccccc}
 \textbf{Metric} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
 \toprule
-Loose Concepts & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 77062 & 1125 & 0 & 0 & 0 & 0 & 0 & 21 \\
+Loose Concepts & 162000 & 671 & 0 & 2 & 7 & 0 & 0 & 77062 & 1125 & 4979 & 172364 & 0 & 4 & 0 & 21 \\
+Weakly Connected Components & 621 & 0 & & & 4 & 1 & 4 && 0 & 0 && 5 & 1 & 1 & 11 \\
 \bottomrule
@@
 
+The \textbf{Loose Concepts} metrics provides insights on the structural complexity of vocabularies.
+The large number of loose concepts in GTAA can be explained by the fact that it contains names (e.g., persons or places) that arent't connected using skos properties.
+This is also the case for Geonames, NYTP and Pressinfo where the number of total conceps is equal to the number of loose concepts, indicating that no concept is semantically related to another concept.
+
+The large number of \textbf{Weakly Connected Components} in GTAA is caused by many ``minimal'' components, containing only 2 concepts connected by a \texttt{skos:related} property.
+Due to the fact that loose concepts are not counted as weakly connected components, Geonames, NYTP and Pressinfo evaluate to zero components.
+
 \todo{CM}{Add result interpretation for this one metric}

### 2012-03-19 criteria.tex
changed from metric to crtieria

%!TEX root = main.tex

\section{Quality Criteria for SKOS Vocabularies}\label{sec:criteria}

% Briefly describe methodology

We identified quality criteria in existing literature and manually checking existing vocabularies against these criteria. We published our preliminary results online\footnote{\url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}} and requested feedback from experts via public mailing list and informal face to face discussions. Based on the responses we received, we selected a subset \todo{CM}{due to lack of space, we cannot present all criteria. Do we have a good argument, why we present only a subset here? What were our selection criteria?} and formalized them into computable quality filtering function, which, in combination, can serve as quantitative quality indicators for SKOS vocabularies. Since each function operates on a given SKOS vocabulary, they are based on the following SKOS data model definition.

\begin{definition}[SKOS Vocabulary] Let the fully entailed RDFS interpretation~\cite{RDFSEM2012} of a SKOS vocabulary be a tuple of of the form $V = <IR, C, A, SR>$, with

%    Based on the RDFS Interpretation $\mathcal{I}$ we define a vocabulary $V = (IR, C, A, LL, LR, SR, AR)$ (cf.~\cite{Hitzler2009}). V is expected to be fully entailed, based on the deduction rules for RDFS entailment defined in \cite{RDFSEM2012}. Let

\begin{itemize}
	\item \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) be the set of all resources in V, as defined in \cite{RDFSEM2012}.

	\item \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) be the set of \textbf{conceptual resources}.

  \item \(A = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I}) \cup I_{CEXT}(\texttt{skos:Collection}^\mathcal{I})\) be the set of \textbf{aggregation and grouping resources}.

%	\item LL being the set of \textbf{lexical labels}, which are instances of RDF plain literals.
%	\item \(LR \subseteq C \times LL\) being the set of \textbf{lexical relations} associating conceptual resources with lexical labels, e.g., via \texttt{rdfs:label} or subproperties thereof.

	\item \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) be the set of \textbf{semantic relations} associating conceptual resources with one another.

%\item \(AR \subseteq C \times A\) being the set of \textbf{aggregation relations} associating conceptual resources with instances of aggregation and grouping resources, hence instances of, e.g., \texttt{skos:inScheme} or \texttt{skos:member} or subproperties thereof.
\end{itemize}

\end{definition}

The quality criteria we identified have in common that they are applied on a given SKOS vocabulary and identify a set of resources, which do not fulfill that criterion. Therefore, we can regard a quality criterion as being an abstract filtering function $F$ that takes a given vocabulary graph $V$ as input and returns a set of affected resources $IR$ \todo{CM}{think about it and try to formalize this.} Each quality criterion we found can be implemented as a realization of such an abstract filtering function. Since the return value is a set of resources, statistical analyses can be computed on the number of resources in that set.

% Structure for each metric description
%- origin (refs) and design rationale
%- formal definition that specifies how to compute the metric

In the following, we describe the origins and design rationale for each metric and provide a semi-formal definition that specifies how to implement them in tools. We categorized the metrics \todo{CM,BH}{Briefly describe how we organize/structure the criteria}

% LEXICAL AND DOCUMENTATION CRITERIA

\subsection{Labeling and Documentation Criteria}\todo{CM}{describe}

\subsubsection{Omitted Language Tags}\todo{CM}{describe}

\subsubsection{Incomplete Language Coverage}\todo{CM}{describe}

\subsubsection{Undocumented Concepts}\todo{CM}{describe}

\subsubsection{Potentially Semantically Related Concepts}\todo{CM}{describe}

% STRUCTURAL METRICS

\subsection{Structural Criteria}

The commonality of the following metrics is that they apply a graph-based view on a given vocabulary \(v\), which we can then consider as a directed graph \(G=(N,E)\) consisting of a set of nodes \(N\) and edges \(E\).

\subsubsection{Loose Concepts} is a metric motivated by the notion of ``orphan terms'' in the literature~\cite{Hedden2010}, which are are terms without any associative or hierarchical relationships. Checking for them is common in existing thesaurus development applications and also suggested by \cite{Z39.19:2005}. When we apply this to SKOS vocabularies, a loose concept is a concept that has no semantic relations with other conceptual resources. Although they might have attached lexical labels, they lack valuable context information. The number of loose concepts in a vocabulary can be computed as follows: \todo{CM}{describe computation}

% \begin{definition}
% Let \(G_{lc} = (C, SR)\) and \(deg(c)\) be the degree, hence the number of in- and outgoing edges, of a node $c \in C$ in the graph $G_{lc}$. We can then define loose concepts as a function \(lc : G \rightarrow \mathbb{N}_{0}\), with \[lc(g) = \left|\left\{c \in C : deg(c) = 0\right\}\right|\]

% \end{definition}

\subsubsection{Weakly Connected Components} indicate that the vocabulary is split into separate ``clusters''. Presence of several WCC might be caused by incomplete data acquisition, ``forgotten'' test data, outdated terms, accidental deletion of relations and the like. In a practical setting, existence of weakly connected components could render the vocabulary less suitable for operations that rely on navigating a connected vocabulary structure, such as query expansion or suggestion of related terms. \todo{CM}{explain better, get rid of def}

% \begin{definition}
% To evaluate this criterion we consider a graph \(G_{wcc} = (C - lc(G_{lc}), SR)\). The function \(components(g) : G \rightarrow  \mathfrak{P}(G)\) calculates all weakly connected components of a graph by replacing all directed edges by undirected edges and utilizing “Tarjan’s algorithm” \cite{Hopcroft1973}. Based on that function, we can express this criterion as a function \(wcc : G \rightarrow \mathbb{N}_{0}\), with \[wcc(g) = \left|components(g)\right|\]
% \end{definition}

\subsubsection{Cyclic Hierarchical Relations} have been mentioned numerous times in thesaurus development literature. \cite{Soergel2002} suggests a ``check for hierarchy cycles" since they ``throw the program for a loop in the generation of a complete hierarchical structure''. However, SKOS does not define a formal constraint regarding hierarchy cycles but the SKOS reference document mentions them as potential problems. The SKOS documentation also does not state, how exactly hierarchical relationships are to be interpreted. There exist common forms like, e.g., ``generic-specific'', ``instance-of'' or ``whole-part'' \cite{Hedden2010,Harpring2010,Aitchison2000} where cycles would be considered a logical contradiction.

% \begin{definition}
% Let \(H_{br} \subseteq SR\) be the set of pairs of hierarchically broader related resources, i.e. \(I_{EXT}(\texttt{skos:broader}^\mathcal{I}) \cup I_{EXT}(\texttt{skos:broaderTransitive}^\mathcal{I}) \cup I_{EXT}(\texttt{skos:broadMatch}^\mathcal{I})\). \(H_{br}\) also includes the extensions of the respecitive inverse properties with each pair in reverse order. Likewise, \(H_{nar} \subseteq SR\) can be defined as the set of hierarchically narrower related resources. We consider two graphs \(G_{br} = (C,H_{br})\) and \(G_{nar}=(C,H_{nar})\) and a function \(cycleNodes:G \rightarrow \mathfrak{P}(C)\) identifying all nodes in a graph, that are part of a cycle. Furthermore we consider a function \(stronglyConnectedSets: G \rightarrow \mathfrak{P}(C)\) that calculates all sets of nodes contained in a strongly connected subgraph of $G$. This criterion can be defined as a function \(chr:G \rightarrow \mathbb{N}_{0}\) with \[chr(g)=\left|\left\{s \in stronglyConnectedSets(g) : cn \in cycleNodes(g), cn \in s\right\}\right|\]
% \end{definition}

\subsubsection{Valueless Associative Relations}\todo{CM}{add}

\subsubsection{Solely Transitively Related Concepts}\todo{CM}{add}

\subsubsection{Omitted Top Concepts}\todo{CM}{add}

\subsubsection{Top Concept Having Broader Concepts}\todo{CM}{add}

% LINKED-DATA SPECIFIC CRITERIA

\subsection{Linked Data Specific Criteria}\todo{CM}{add}

\subsubsection{Missing In-Links}\todo{CM}{add}

\subsubsection{Missing Out-Links}\todo{CM}{add}

\subsubsection{HTTP URI Schema Violation}\todo{CM}{add}

\subsubsection{Link Target Unavailability}\todo{CM}{add}

% OTHER CRITERIA

\subsection{Other Criteria}

\subsubsection{Undefined SKOS Property Usage}\todo{CM}{Merge 15 and 16}

### 2012-03-19 introduction.tex
polished background section
changed from metric to crtieria

@@
 % What does "quality" mean in this context?
-Each vocabulary reflects domain- and application-specific needs and vocabulary designers often follow existing standards \cite{ISO25964-1:2011,Z39.19:2005} or apply their own hand-crafted checks (cf.,~\cite{Coronado2009}) to meet certain quality requirements.
+Each vocabulary reflects domain- and application-specific needs and taxonomists often follow existing standards \cite{ISO25964-1:2011,Z39.19:2005} or apply their own hand-crafted checks (cf.,~\cite{Coronado2009}) to meet certain quality requirements.
 However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments.
@@
 
-The goal of our work is to provide a set of quantitative quality indicators for SKOS vocabularies.
-They can be used by domain experts and vocabulary designers for judging the quality of existing or newly created vocabularies and provide important feedback to the overall vocabulary design process.
+The goal of our work to help taxonomists in judging the quality of SKOS vocabularies, by giving them a set of computable quality criteria that can identify possible quality issues and serve as quantitative indicator for the quality of a given SKOS vocabulary.
+In combination with the taxonomists' experience and domain expertise, these criteria provide important feedback to the overall vocabulary design process.
 The main contributions of this work can be summarized as follows:
@@
 
-	\item We identified existing \textbf{quality criteria} for controlled vocabularies by examining existing guidelines and formalized them into computable \textbf{quality metrics} so that they can be implemented consistently by different tools.
+	\item We identified existing \textbf{quality criteria} for controlled vocabularies by examining existing guidelines and formalized them into computable \textbf{filtering functions} that identify possibly affected resources in a given SKOS vocabulary.
 
-	\item We implemented these metrics in the \textbf{qSKOS quality assessment tool}, which can be used as software library or command line tool.
+	\item With the \textbf{qSKOS quality assessment tool} we provide a reference implementation of these filtering functions.
 

### 2012-03-19 main.tex
drafted background section
changed (parts) of skos quality model to conform to RDF formal semantics; changed definition of loose concepts and recomputed tabular values.
changed from metric to crtieria

--- 2012-03-11 main.tex
@@
 
+\usepackage{url}
+
 \usepackage{verbatim}
-\usepackage{url}
 \usepackage{amssymb}
+\usepackage{rotating}
+\usepackage{booktabs}
 
@@
 
-\title{Quality Metrics for SKOS Vocabularies}
+\title{Quality Criteria for SKOS Vocabularies}
 \author{Christian Mader\inst{1} \and Bernhard Haslhofer\inst{2}}
@@
 However, SKOS vocabularies are often heterogeneous in terms of quality, which reduces their applicability across system boundaries.
-Here we investigate how we can support domain experts with quantitative indicators to judge the quality of SKOS vocabularies.
-We identified existing \textbf{quality criteria} and formalized them into computable \textbf{quality metrics}.
-We implemented them in the qSKOS quality assessment tool and used it to analyze the quality of existing vocabularies.
-The results from this analysis indicate that \todo{CM,BH}{summarize results in one sentence}.
+Here we investigate how we can support taxonomists in judging the quality of SKOS vocabularies by quality criteria that go beyond the low-level data model integrity constraints defined in the SKOS specification.
+Based on existing guidelines and best practices for creating controlled vocabularies, we identified existing \textbf{quality criteria}, formalized them into computable \textbf{filtering functions} that identify  affected resources and implemented them in the qSKOS quality assessment tool.
+We used that tool to analyze existing vocabularies and found that \todo{CM,BH}{summarize results in one sentence}.
 
@@
 
-\input{metrics}
+\input{criteria}
 

### 2012-03-20 criteria.tex
added labeling and documentation criteria

@@
 The quality criteria we identified have in common that they are applied on a given SKOS vocabulary and identify a set of resources, which do not fulfill that criterion.
-Therefore, we can regard a quality criterion as being an abstract filtering function $F$ that takes a given vocabulary graph $V$ as input and returns a set of affected resources $IR$ \todo{CM}{think about it and try to formalize this.} Each quality criterion we found can be implemented as a realization of such an abstract filtering function.
+Therefore, we can regard a quality criterion as being an abstract filtering function $F$, mapping a given vocabulary $V$ to the powerset $\mathfrak{P}(IR)$ of its resources.\todo{CM}{think about it and try to formalize this.} Each quality criterion we found can be implemented as a realization of such an abstract filtering function.
 Since the return value is a set of resources, statistical analyses can be computed on the number of resources in that set.
@@
 
-\subsection{Labeling and Documentation Criteria}\todo{CM}{describe}
+\subsection{Labeling and Documentation Criteria}
+The criteria defined in this section..\todo{CM}{describe}.
+Their filtering function \(f:V \rightarrow \mathfrak{P}(C)\) yields all sets of \textbf{conceptual resources} violating the respective criterion.
 
-\subsubsection{Omitted Language Tags}\todo{CM}{describe}
+\subsubsection{Omitted Language Tags}
+Some controlled vocabularies contain literals in natural language, but without information what language has actually been used.
+Using private language tags (see RFC3066) or omitting them at all limits, e.g., language-dependent queries.
 
-\subsubsection{Incomplete Language Coverage}\todo{CM}{describe}
+\subsubsection{Incomplete Language Coverage}
+As stated above, vocabularies should combine plain literals with language tags.
+Furthermore, to support, e.g., internationalization or translation use cases, every concept should have defined literal values in the same set of languages than the other concepts.
 
-\subsubsection{Undocumented Concepts}\todo{CM}{describe}
+\subsubsection{Undocumented Concepts}
+\cite{Aitchison2000} cites Svenonius to advocate ``inclusion of as much definition material as possible''.
+The SKOS language specification defines various properties that are intended to hold this kind of information, subsumed as ``documentation properties'' in the SKOS reference.
 
-\subsubsection{Potentially Semantically Related Concepts}\todo{CM}{describe}
+\subsubsection{Potentially Semantically Related Concepts} \todo{All}{reformulate criterion title}
+This criterion is an extension of a statement from the SKOS primer, recommending ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
+Given the fact that (i) many vocabularies don’t make use of concept schemes and (ii) also identical altLabels or hiddenLabels can have a negative effect in some use-cases (e.g, auto-completion of concept labels based on user input), we follow a more general approach: identification of all pairs of concepts with their respective prefLabel, altLabel or hiddenLabel meeting a threshold of a certain similarity function $sim:LV \times LV \rightarrow [0,1]$.
+For the analysis of the criterion in this document, we define the similarity function  to check for case-insensitive string equality and the threshold to equal 1.
 

### 2012-03-20 criteria.tex
added structural criteria

@@
 
-\begin{definition}[SKOS Vocabulary] Let the fully entailed RDFS interpretation~\cite{RDFSEM2012} of a SKOS vocabulary be a tuple of of the form $V = <IR, C, A, SR>$, with
+\begin{definition}[SKOS Vocabulary] Let the fully entailed RDFS interpretation~\cite{RDFSEM2012} of a SKOS vocabulary be a tuple of of the form $V = \langle IR, C, SR, LV \rangle$, with
 
@@
 
-  \item \(A = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I}) \cup I_{CEXT}(\texttt{skos:Collection}^\mathcal{I})\) be the set of \textbf{aggregation and grouping resources}.
+%\item \(A = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I}) \cup I_{CEXT}(\texttt{skos:Collection}^\mathcal{I})\) be the set of \textbf{aggregation and grouping resources}.
 
@@
 	\item \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) be the set of \textbf{semantic relations} associating conceptual resources with one another.
+
+	\item $LV = I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$
 
@@
 
-The commonality of the following metrics is that they apply a graph-based view on a given vocabulary \(v\), which we can then consider as a directed graph \(G=(N,E)\) consisting of a set of nodes \(N\) and edges \(E\).
+%The commonality of the following metrics is that they apply a graph-based view on a given vocabulary \(v\), which we can then consider as a directed graph \(G=(N,E)\) consisting of a set of nodes \(N\) and edges \(E\).
 
-\subsubsection{Loose Concepts} is a metric motivated by the notion of ``orphan terms'' in the literature~\cite{Hedden2010}, which are are terms without any associative or hierarchical relationships.
+\subsubsection{Loose Concepts} is a criterion motivated by the notion of ``orphan terms'' in the literature~\cite{Hedden2010}, which are are terms without any associative or hierarchical relationships.
 Checking for them is common in existing thesaurus development applications and also suggested by \cite{Z39.19:2005}.
@@
 Although they might have attached lexical labels, they lack valuable context information.
-The number of loose concepts in a vocabulary can be computed as follows: \todo{CM}{describe computation}
+Loose concepts in a vocabulary are those conceptual resources that do not occur in any of the pairs yielded by $SR$.
 
@@
 We can then define loose concepts as a function \(lc : G \rightarrow \mathbb{N}_{0}\), with \[lc(g) = \left|\left\{c \in C : deg(c) = 0\right\}\right|\]
-
 % \end{definition}
@@
 In a practical setting, existence of weakly connected components could render the vocabulary less suitable for operations that rely on navigating a connected vocabulary structure, such as query expansion or suggestion of related terms.
-\todo{CM}{explain better, get rid of def}
+To calculate WCC, we create an undirected graph whose set of nodes constitutes all non-loose concepts and whose edges are defined by $SR$.
+We then utilize ``Tarjan’s algorithm''\cite{Hopcroft1973} that finds all connected components of the graph, i.e.
+all sets of conceptual resources that can reach each other by a path of semantic relations.
 
@@
 There exist common forms like, e.g., ``generic-specific'', ``instance-of'' or ``whole-part'' \cite{Hedden2010,Harpring2010,Aitchison2000} where cycles would be considered a logical contradiction.
+To calculate this criterion, we assume all OWL inverse properties of the SKOS ontology properly entailed and construct two graphs, $G_{br}$ and $G_{nar}$, with the set of nodes being C.
+The set of edges in $G_{br}$ are all pairs identified by $I_{EXT}(\texttt{skos:broaderTransitive}^\mathcal{I})$, likewise those of $G_{nar}$ are $I_{EXT}(\texttt{skos:narrowerTransitive}^\mathcal{I})$.
+For each graph we now identify those nodes that are part of a cycle and return the set of strongly connected components they are contained in.
+
+%Erkärung: ein knoten (konzept) liegt oft in vielen überlappenden kreisen und es würde keinen sinn machen, diese alle auszugeben.
+deshalb berechne ich mir von jedem knoten der in einem kreis liegt, in welcher starken zusammenhangskomponente er liegt.
+das sind dann per definition alle knoten, die mit irgendeinem kreis in dem das konzept liegt was zu tun haben, weil eine starke zusammenhangskomponente ja eigentlich nur aus kreisen besteht (von jedem knoten gibt es einen gerichteten weg zu jedem anderen knoten)
 
@@
 \subsubsection{Valueless Associative Relations}\todo{CM}{add}
+The ISO/DIS 25964-1 standard suggests that terms that share a common broader term but don’t have an overlapping meaning, should not be related associatively.
+This is also advocated by [Hedden2011] and [Aitchison2000] who also mentions “the risk that thesaurus compilers may overload the thesaurus with valueless relationships”, having a negative effect on precision.
 

### 2012-03-20 criteria.tex
added all structural criteria

@@
 
-\begin{definition}[SKOS Vocabulary] Let the fully entailed RDFS interpretation~\cite{RDFSEM2012} of a SKOS vocabulary be a tuple of of the form $V = \langle IR, C, SR, LV \rangle$, with
+\begin{definition}[SKOS Vocabulary] Let the fully entailed RDFS interpretation~\cite{RDFSEM2012} (enriched by entailment of OWL inverse properties) of a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV \rangle$, with
 
@@
 
-\subsubsection{Valueless Associative Relations}\todo{CM}{add}
+\subsubsection{Valueless Associative Relations}
 The ISO/DIS 25964-1 standard suggests that terms that share a common broader term but don’t have an overlapping meaning, should not be related associatively.
-This is also advocated by [Hedden2011] and [Aitchison2000] who also mentions “the risk that thesaurus compilers may overload the thesaurus with valueless relationships”, having a negative effect on precision.
+This is also advocated by \cite{Hedden2010} and \cite{Aitchison2000} who also mentions ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships'', having a negative effect on precision.
+This criterion identifies a set of pairs of conceptual resources that share the same broader or narrower concept while also being associatively related, i.e.
+there exists a pair in $I_{EXT}(\texttt{skos:related}^\mathcal{I})$ that contains both of these conceptual resources.
+Computation of these criterion again relies on full entailment of the inverse hierarchical relations in the SKOS ontology.
 
-\subsubsection{Solely Transitively Related Concepts}\todo{CM}{add}
+\subsubsection{Solely Transitively Related Concepts}
+Two concepts are related using only transitive hierarchical relations which are, according to the SKOS reference document, ``not used to make assertions''.
+Transitive hierarchical relations in SKOS are meant to be infered by the vocabulary user, which is reflected in the SKOS schema by, e.g., broader being a subproperty of broaderTransitive.
+This criterion identifies the set $I_{EXT}(\texttt{skos:broaderTransitive}^\mathcal{I}) \cup I_{EXT}(\texttt{skos:narrowerTransitive}^\mathcal{I})$ \textbf{without} RDFS subproperty entailment.
 
-\subsubsection{Omitted Top Concepts}\todo{CM}{add}
+\subsubsection{Omitted Top Concepts}
+The SKOS language provides ConceptSchemes which are a facility for grouping related concepts.
+In order to provide entry points to such a group of concepts, one or more concepts can be marked as top concepts.
+This helps to provide ``efficient access'' (SKOS primer) and simplifies orientation in the vocabulary.
+Thus, this criterion returns the subset of $C$ whose elements are not contained in any of the pairs obtained by $I_{EXT}(\texttt{skos:hasTopConcept}^\mathcal{I})$.
 
-\subsubsection{Top Concept Having Broader Concepts}\todo{CM}{add}
+\subsubsection{Top Concept Having Broader Concepts}
+\cite{Allemang2011} proposes to ``not indicate any concepts internal to the tree as top concepts'', i.e.
+top concepts should not have broader concepts.
+Accordingly, this criterion finds the set of Top Concepts violating this constraint.
 

### 2012-03-20 criteria.tex
added linked data criteria

@@
 The criteria defined in this section..\todo{CM}{describe}.
-Their filtering function \(f:V \rightarrow \mathfrak{P}(C)\) yields all sets of \textbf{conceptual resources} violating the respective criterion.
+Their filtering function \(f:V \rightarrow \mathfrak{P}(IR)\) yields all sets of \textbf{conceptual resources} violating the respective criterion.
 
@@
 
-\subsubsection{Missing In-Links}\todo{CM}{add}
+\subsubsection{Missing In-Links}
+A periodically updated version of a diagram visualizing ``the data sets in the LOD cloud as well as their interlinkage relationships'' is publised online\footnote{\url{http://www4.wiwiss.fu-berlin.de/lodcloud/state/}}.
+In these diagrams, dbpedia is shown as the most intensely linked resource, i.e.
+a large number of vocabularies link to resources in that dataset.
+Therefore a dataset with a large number of other datasets referencing it, can be assumed to be of great value for the community.
+Accordingly, estimating the number of In-Links of SKOS concepts defined in a vocabulary (henceforth called the in-degree of a concept) would give some hint about how established or accepted a controlled vocabulary is.
+A method to carry out these estimations would be utilizing existing Linked Data indices like, e.g., Sindice\footnote{\url{http://sindice.com/}} that provide a SPARQL endpoint.
+Accordingly, this criterion identifies the set of all conceptual resources that lack any In-Links.
 
-\subsubsection{Missing Out-Links}\todo{CM}{add}
+\subsubsection{Missing Out-Links}
+The Web of Data consists of globally interconnected datasets, ``enabling seamless connections between data sets''\cite{Heath2011}.
+These links can be established between various SKOS vocabularies by Out-Links, i.e., references from conceptual resources in the ``source vocabulary'' $V$ to resources identified by an HTTP URI and available at a different host.
+Similar to the criterion above, this criterion identifies the set of all conceptual resources that lack such Out-Links.
 
-\subsubsection{HTTP URI Schema Violation}\todo{CM}{add}
+\subsubsection{HTTP URI Schema Violation}\todo{All}{We don't have any evidence this really happens in existing vocabularies, although it is very likely. Maybe we should skip this.}
 
-\subsubsection{Link Target Unavailability}\todo{CM}{add}
+\subsubsection{Link Target Unavailability}
+This criterion identifies a set of all resources that have been identified as unavailable, i.e.
+resolving their URI leads to an erroneous HTTP response or no response at all.
+An erroneous HTTP response in that case can be defined as a response code (after a possible redirection) other than 200.
+Just as in the ``traditional'' Web, these ``broken links'' hinder information gathering and should be avoided.
 

### 2012-03-20 criteria.tex
reworked model definition

@@
 
-\begin{definition}[SKOS Vocabulary] Let the fully entailed RDFS interpretation~\cite{RDFSEM2012} (enriched by entailment of OWL inverse properties) of a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV \rangle$, with
+\begin{definition}[SKOS Vocabulary] Let the fully entailed RDFS interpretation~\cite{RDFSEM2012} (enriched by entailment of \texttt{owl:inverseOf} properties) of a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV \rangle$, with
 
@@
 \begin{itemize}
-	\item \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) be the set of all resources in V, as defined in \cite{RDFSEM2012}.
+	\item \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of resources,
 
-	\item \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) be the set of \textbf{conceptual resources}.
+	\item $LV = I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of literal values,
+
+	\item \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{conceptual resources},
 
@@
 
-	\item \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) be the set of \textbf{semantic relations} associating conceptual resources with one another.
-
-	\item $LV = I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$
+	\item \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating conceptual resources with one another.
 
@@
 The quality criteria we identified have in common that they are applied on a given SKOS vocabulary and identify a set of resources, which do not fulfill that criterion.
-Therefore, we can regard a quality criterion as being an abstract filtering function $F$, mapping a given vocabulary $V$ to the powerset $\mathfrak{P}(IR)$ of its resources.\todo{CM}{think about it and try to formalize this.} Each quality criterion we found can be implemented as a realization of such an abstract filtering function.
+Therefore, we can regard a quality criterion as being an abstract filtering function $f:V \rightarrow \mathfrak{P}(IR)$, mapping a given vocabulary to the powerset of its resources.
+Each quality criterion we found can be implemented as a realization of such an abstract filtering function.
 Since the return value is a set of resources, statistical analyses can be computed on the number of resources in that set.
@@
 \subsection{Labeling and Documentation Criteria}
-The criteria defined in this section..\todo{CM}{describe}.
-Their filtering function \(f:V \rightarrow \mathfrak{P}(IR)\) yields all sets of \textbf{conceptual resources} violating the respective criterion.
+The criteria defined in this section primarily focus on supporting interaction with human users that either work with the vocabulary itself or interact with a system using the vocabulary for, e.g., search and retrieval purposes.
 
@@
 There exist common forms like, e.g., ``generic-specific'', ``instance-of'' or ``whole-part'' \cite{Hedden2010,Harpring2010,Aitchison2000} where cycles would be considered a logical contradiction.
-To calculate this criterion, we assume all OWL inverse properties of the SKOS ontology properly entailed and construct two graphs, $G_{br}$ and $G_{nar}$, with the set of nodes being C.
+To calculate this criterion, we construct two graphs, $G_{br}$ and $G_{nar}$, with the set of nodes being C.
 The set of edges in $G_{br}$ are all pairs identified by $I_{EXT}(\texttt{skos:broaderTransitive}^\mathcal{I})$, likewise those of $G_{nar}$ are $I_{EXT}(\texttt{skos:narrowerTransitive}^\mathcal{I})$.
@@
 
-\subsubsection{Undefined SKOS Property Usage}\todo{CM}{Merge 15 and 16}
+\subsubsection{Undefined SKOS Property Usage}
+Some vocabularies reference resources in the SKOS namespace that cannot be resolved.
+A common reason for this is, that there seems to exist a misunderstanding about the correct way of introducing new classes or properties in an OWL document.
+In some cases, vocabularies ``invent'' new terms in the SKOS namespace in order to meet certain requirements of the publishing organizations that cannot (yet) be expressed within the SKOS schema.
+Another reason for the presence of unresolvable resource references in the SKOS namespace is that the vocabulary might be outdated.
+With the SKOS W3C recommendation maturing, some properties have been removed from the current version of the schema.
+Vocabularies using these ``deprecated'' properties hence contain parts of their information in a non ``standard"-compliant way, having negative effects when, e.g., crawling vocabularies to gather specific information.

### 2012-03-20 criteria.tex
simplified some criteria "definitions"

@@
 
-%The commonality of the following metrics is that they apply a graph-based view on a given vocabulary \(v\), which we can then consider as a directed graph \(G=(N,E)\) consisting of a set of nodes \(N\) and edges \(E\).
+The commonality of the following metrics is that they identify possible weaknesses when $V$ is used in scenarios exploiting the structure of its RDF graph.
 
@@
 Checking for them is common in existing thesaurus development applications and also suggested by \cite{Z39.19:2005}.
-When we apply this to SKOS vocabularies, a loose concept is a concept that has no semantic relations with other conceptual resources.
-Although they might have attached lexical labels, they lack valuable context information.
-Loose concepts in a vocabulary are those conceptual resources that do not occur in any of the pairs yielded by $SR$.
+When we apply this to SKOS vocabularies, a loose concept is a concept that has no semantic relations with other conceptual resources and thus do not occur in any of the pairs yielded by $SR$.
+Although they might have attached lexical labels, they lack valuable context information that is considered essential for, e.g., search query expansion.
 
@@
 There exist common forms like, e.g., ``generic-specific'', ``instance-of'' or ``whole-part'' \cite{Hedden2010,Harpring2010,Aitchison2000} where cycles would be considered a logical contradiction.
-To calculate this criterion, we construct two graphs, $G_{br}$ and $G_{nar}$, with the set of nodes being C.
-The set of edges in $G_{br}$ are all pairs identified by $I_{EXT}(\texttt{skos:broaderTransitive}^\mathcal{I})$, likewise those of $G_{nar}$ are $I_{EXT}(\texttt{skos:narrowerTransitive}^\mathcal{I})$.
+To calculate this criterion, we construct two graphs, with the set of nodes being $C$.
+The edges in one graph only point towards the broader concepts, the edges of the other graph towards the narrower concepts.
 For each graph we now identify those nodes that are part of a cycle and return the set of strongly connected components they are contained in.
@@
 This criterion identifies a set of pairs of conceptual resources that share the same broader or narrower concept while also being associatively related, i.e.
-there exists a pair in $I_{EXT}(\texttt{skos:related}^\mathcal{I})$ that contains both of these conceptual resources.
-Computation of these criterion again relies on full entailment of the inverse hierarchical relations in the SKOS ontology.
+all pairs in $I_{EXT}(\texttt{skos:related}^\mathcal{I})$ that contain both of these conceptual resources.
 
@@
 Two concepts are related using only transitive hierarchical relations which are, according to the SKOS reference document, ``not used to make assertions''.
-Transitive hierarchical relations in SKOS are meant to be infered by the vocabulary user, which is reflected in the SKOS schema by, e.g., broader being a subproperty of broaderTransitive.
+Transitive hierarchical relations in SKOS are meant to be infered by the vocabulary user, which is reflected in the SKOS schema by, e.g., \texttt{broader} being a subproperty of \texttt{broaderTransitive}.
 This criterion identifies the set $I_{EXT}(\texttt{skos:broaderTransitive}^\mathcal{I}) \cup I_{EXT}(\texttt{skos:narrowerTransitive}^\mathcal{I})$ \textbf{without} RDFS subproperty entailment.
@@
 This helps to provide ``efficient access'' (SKOS primer) and simplifies orientation in the vocabulary.
-Thus, this criterion returns the subset of $C$ whose elements are not contained in any of the pairs obtained by $I_{EXT}(\texttt{skos:hasTopConcept}^\mathcal{I})$.
+
+%Thus, this criterion returns the subset of $C$ whose elements are not contained in any of the pairs obtained by $I_{EXT}(\texttt{skos:hasTopConcept}^\mathcal{I})$.
 
 \subsubsection{Top Concept Having Broader Concepts}
-\cite{Allemang2011} proposes to ``not indicate any concepts internal to the tree as top concepts'', i.e.
-top concepts should not have broader concepts.
-Accordingly, this criterion finds the set of Top Concepts violating this constraint.
+\cite{Allemang2011} proposes to ``not indicate any concepts internal to the tree as top concepts'', i. e. top concepts should not have broader concepts.
 
@@
 
-\subsection{Linked Data Specific Criteria}\todo{CM}{add}
+\subsection{Linked Data Specific Criteria}
+
+This section identifies criteria related to a vocabulary's interaction with other datasets in the LOD cloud.
 
@@
 
-\subsubsection{HTTP URI Schema Violation}\todo{All}{We don't have any evidence this really happens in existing vocabularies, although it is very likely. Maybe we should skip this.}
+%\subsubsection{HTTP URI Schema Violation}\todo{All}{We don't have any evidence this really happens in existing vocabularies, although it is very likely. Maybe we should skip this.}
 

### 2012-03-20 background.tex
minor consistency fixes in secs 1-3

@@
 
-\section{Background}
+\section{Background}\label{sec:background}
 
@@
 SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption.
-Established quality notions from closed-world systems, such as referential integrity or schema validation, don't hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false.
+Established quality notions from closed-world systems, such as referential integrity or schema validation, don't hold anymore, because available information may be incomplete and non-explicitly stated facts cannot be determined as true or false.
 While trust and provenance models for Web data are being developed~\cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}.
-Gueret et al.
+
+% MOVE TO RELATED WORK: Gueret et al.
 [\todo{CM}{find the right reference in google scholar}], for instance, calculate network measures to support human judgement on the quality of Linked Data \todo{CM}{?} graphs.
@@
 % Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
-Thus, in order to help vocabulary and application designers in judging the quality of SKOS vocabularies, we need higher-level quality criteria that go beyond low-level integrity conditions, which define data model consistency.
+Thus, in order to help vocabulary and application designers in judging the quality of SKOS vocabularies, we need higher-level quality criteria that go beyond low-level integrity conditions defining data model consistency.
 Such quality criteria are already well-established and have extensively been discussed in standardized guidelines [\todo{CM}{ISO refs}], manuals [\todo{CM}{hedden book, skosify ref 3}], and scholarly articles [\todo{cm}{e.g., skosify refs 16/17}].
 % TODO: bitte hier einfach nur die referenzen auf die wir uns beziehen zusammenfassen und kategorisieren. Schau dir dazu auch nochmals die SKOSify referenzen und die aus eurem iSemantics paper an.
-If we want to apply these criteria on SKOS vocabularies, we first need to identify them and determine how to evaluate them given the syntax, structure and semantics of SKOS.
+If we want check existing SKOS vocabularies against these criteria, we first need to identify them and determine how to evaluate them given the syntax, structure and semantics of SKOS.
 Since we want to provide tool support for quality checking, we must formalize these criteria into computable metrics, in order to ensure consistent implementation and interpretation across tools.

### 2012-03-20 main.tex
minor consistency fixes in secs 1-3

@@
 
-The Simple Knowledge Organization System (SKOS) has become the standard model for expressing and publishing controlled vocabularies on the Web.
+The Simple Knowledge Organization System (SKOS) has become a standard model for controlled Web vocabularies.
 However, SKOS vocabularies are often heterogeneous in terms of quality, which reduces their applicability across system boundaries.
 Here we investigate how we can support taxonomists in judging the quality of SKOS vocabularies by quality criteria that go beyond the low-level data model integrity constraints defined in the SKOS specification.
-Based on existing guidelines and best practices for creating controlled vocabularies, we identified existing \textbf{quality criteria}, formalized them into computable \textbf{filtering functions} that identify  affected resources and implemented them in the qSKOS quality assessment tool.
-We used that tool to analyze existing vocabularies and found that \todo{CM,BH}{summarize results in one sentence}.
+We identified existing \textbf{quality criteria}, formalized them into computable \textbf{quality checking functions} that identify affected resources in a given SKOS vocabulary.
+We implemented these functions in the qSKOS quality assessment tool, analyzed \todo{CM}{XX} existing vocabularies and found possible quality issues in \todo{CM}{YY} vocabularies.
 

### 2012-03-20 background.tex
fixed notion of metrics

@@
 If we want check existing SKOS vocabularies against these criteria, we first need to identify them and determine how to evaluate them given the syntax, structure and semantics of SKOS.
-Since we want to provide tool support for quality checking, we must formalize these criteria into computable metrics, in order to ensure consistent implementation and interpretation across tools.
+Since we want to provide tool support for quality checking, we must formalize these criteria into computable quality checking functions, in order to ensure consistent implementation and interpretation across tools.
 

### 2012-03-20 criteria.tex
added computation info for the criteria

@@
 \subsubsection{Omitted Language Tags}
-Some controlled vocabularies contain literals in natural language, but without information what language has actually been used.
+Some controlled vocabularies contain literals in natural language without information about what language has actually been used.
 Using private language tags (see RFC3066) or omitting them at all limits, e.g., language-dependent queries.
+To identfy omitted language tags we iterate over all conceptual resources in $C$ and collect those that have relations to untyped literals lacking language information as described above.
 
 \subsubsection{Incomplete Language Coverage}
-As stated above, vocabularies should combine plain literals with language tags.
+According to the previous criterion, vocabularies should combine plain literals with language tags.
 Furthermore, to support, e.g., internationalization or translation use cases, every concept should have defined literal values in the same set of languages than the other concepts.
+Calculation of the affected resources is done by iterating over all conceptual resources in $C$, building a global list of distinct languages throughout all literals assigned to every concept.
+Additionally, a list of used languages per conceptual resource is created.
+The criterion identifies all conceptual resources having a language list not equal to the global language list.
 
@@
 The SKOS language specification defines various properties that are intended to hold this kind of information, subsumed as ``documentation properties'' in the SKOS reference.
+To identify the affected conceptual resources, we iterate over all elements in $C$ to find those that are not related to one of the documentation properties.
 
@@
 For the analysis of the criterion in this document, we define the similarity function  to check for case-insensitive string equality and the threshold to equal 1.
+Calculation of this criterion is done by applying the similarity function to every label of every possible pair of conceptual concepts in $C$ and filtering those that meet or exceed a specified threshold.
 
@@
 Although they might have attached lexical labels, they lack valuable context information that is considered essential for, e.g., search query expansion.
+Calculation can be done by iterating over all elements in $C$, filtering those not having a semantic relation to any other conceptual resource.
 
@@
 This helps to provide ``efficient access'' (SKOS primer) and simplifies orientation in the vocabulary.
+To calculate this criterion, we identify all ConceptSchemes $I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})$ not contained in any of the pairs in $I_{EXT}(\texttt{skos:hasTopConcept}^\mathcal{I})$.
 
@@
 \subsubsection{Top Concept Having Broader Concepts}
-\cite{Allemang2011} proposes to ``not indicate any concepts internal to the tree as top concepts'', i. e. top concepts should not have broader concepts.
+\cite{Allemang2011} proposes to ``not indicate any concepts internal to the tree as top concepts'', i.
+e.
+top concepts should not have broader concepts.
+This criteria identifies all elements from $C$ that occur in both $I_{EXT}(\texttt{skos:topConceptOf}^\mathcal{I})$ and as first element of each pair from $I_{EXT}(\texttt{skos:broader}^\mathcal{I})$.
 
@@
 A method to carry out these estimations would be utilizing existing Linked Data indices like, e.g., Sindice\footnote{\url{http://sindice.com/}} that provide a SPARQL endpoint.
-Accordingly, this criterion identifies the set of all conceptual resources that lack any In-Links.
+In order to estimate the number of In-Links for a conceptual resource, we iterate over all elements in $C$ and query the Sindice SPARQL endpoint for triples containing the concept's URI in the object part.
+Those concepts having an empty query result, are missing any In-Links and are thus included in the result set of this criterion.
 
@@
 Similar to the criterion above, this criterion identifies the set of all conceptual resources that lack such Out-Links.
+Calculation of the result set is done by iterating over all elements $c \in C$ and investigating the host part of all related resources.
+If none of these host names differs from the host part of $c$, it has no Out-Links and is thus included into the resources identified by this criterion.
 
@@
 Just as in the ``traditional'' Web, these ``broken links'' hinder information gathering and should be avoided.
+Calculation of this criterion is performed by iterating over all resources in $IR$, performing an HTTP request and include those resources in the result set that are unavailable.
 
@@
 
-\subsubsection{Undefined SKOS Property Usage}
+\subsubsection{Undefined SKOS Resource Usage}
 Some vocabularies reference resources in the SKOS namespace that cannot be resolved.
@@
 Vocabularies using these ``deprecated'' properties hence contain parts of their information in a non ``standard"-compliant way, having negative effects when, e.g., crawling vocabularies to gather specific information.
+A method to identify these undefined SKOS resources is to iterate over all resources in $IR$, including (i) those resources in the resulting set that are contained in the list of deprecated resources or (ii) have an URI in the SKOS namespace but are not defined in the SKOS ontology.

### 2012-03-20 introduction.tex

@@
 The Simple Knowledge Organization System (SKOS)~\cite{Miles2005} is a standard model for sharing and linking controlled vocabularies on the Web.
-Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} have created SKOS representations of their controlled vocabularies and published them on the Web so that they can easily be accessed and by humans and machines.
+Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} published SKOS representations of their controlled vocabularies on the Web so that they can easily be accessed and by humans and machines.
 
@@
 
-	\item The SKOS representation of Agrovoc defines concepts in 25 different languages.
+	\item The SKOS representation of AGROVOC defines concepts in 25 different languages.
 However, while most concepts have an English description, only 38\% of all concepts have German labels attached.
@@
 
-	\item The vocabulary developed by the Austrian Armed Forces (LVAk thesaurus\footnote{Non-public thesaurus developed by the Austrian Armed Forces}) contains 11 disconnected concept clusters.
+	\item The non-public vocabulary developed by the Austrian Armed Forces (LVAk) contains 11 disconnected concept clusters.
 When we confronted the thesaurus maintainers with these structures, they recognized them as ``forgotten'' test data that has no practical significance.
@@
 
-The goal of our work to help taxonomists in judging the quality of SKOS vocabularies, by giving them a set of computable quality criteria that can identify possible quality issues and serve as quantitative indicator for the quality of a given SKOS vocabulary.
+The goal of our work is to help taxonomists in judging the quality of SKOS vocabularies, by giving them a set of computable quality criteria that can identify possible quality issues and serve as quantitative indicator for the quality of a given SKOS vocabulary.
 In combination with the taxonomists' experience and domain expertise, these criteria provide important feedback to the overall vocabulary design process.
@@
 
-	\item We identified existing \textbf{quality criteria} for controlled vocabularies by examining existing guidelines and formalized them into computable \textbf{filtering functions} that identify possibly affected resources in a given SKOS vocabulary.
+	\item We identified \todo{CM}{XX} \textbf{quality criteria} for SKOS vocabularies by examining existing guidelines and formalized them into computable \textbf{filtering functions} that identify possibly affected resources in a given SKOS vocabulary.
 
@@
 
-The results from our analysis show that...
-\todo{BH,CM}{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+In the following, we will first (Section~\ref{sec:background}) elaborate on the meaning of quality in SKOS vocabularies and then present the set of quality criteria we identified (Section~\ref{sec:criteria}).
+In Section~\ref{sec:analysis} we describe our analysis and discuss the results, which show that \todo{BH,CM}{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
 Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.}.

### 2012-03-20 criteria.tex
fixed intro of 3

--- 2012-03-20 criteria.tex
@@
 
-We identified quality criteria in existing literature and manually checking existing vocabularies against these criteria.
-We published our preliminary results online\footnote{\url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}} and requested feedback from experts via public mailing list and informal face to face discussions.
-Based on the responses we received, we selected a subset \todo{CM}{due to lack of space, we cannot present all criteria.
-Do we have a good argument, why we present only a subset here?
-What were our selection criteria?} and formalized them into computable quality filtering function, which, in combination, can serve as quantitative quality indicators for SKOS vocabularies.
-Since each function operates on a given SKOS vocabulary, they are based on the following SKOS data model definition.
+We identified an initial set of quality criteria for SKOS vocabularies by reviewing existing literature and manually examining existing vocabularies.
+We published our findings online\footnote{\url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}} and requested feedback from experts via public mailing list and informal face to face discussions.
+Based on the responses we received, we then selected a subset of these criteria and formalized them into computable \textbf{quality checking functions}.
+Each of these functions operates on a SKOS vocabulary, which we define, for the purpose of this work, as follows:
 
-\begin{definition}[SKOS Vocabulary] Let the fully entailed RDFS interpretation~\cite{RDFSEM2012} (enriched by entailment of \texttt{owl:inverseOf} properties) of a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV \rangle$, with
-
-%    Based on the RDFS Interpretation $\mathcal{I}$ we define a vocabulary $V = (IR, C, A, LL, LR, SR, AR)$ (cf.~\cite{Hitzler2009}).
-V is expected to be fully entailed, based on the deduction rules for RDFS entailment defined in \cite{RDFSEM2012}.
-Let
+\begin{definition}[SKOS Vocabulary] Let the fully entailed RDFS interpretation~\cite{RDFSEM2012} (enriched by entailment of \texttt{owl:inverseOf} properties \todo{CM}{why?}) of a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV \rangle$, with
 
@@
 
-%\item \(A = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I}) \cup I_{CEXT}(\texttt{skos:Collection}^\mathcal{I})\) be the set of \textbf{aggregation and grouping resources}.
-
-%	\item LL being the set of \textbf{lexical labels}, which are instances of RDF plain literals.
-%	\item \(LR \subseteq C \times LL\) being the set of \textbf{lexical relations} associating conceptual resources with lexical labels, e.g., via \texttt{rdfs:label} or subproperties thereof.
-
 	\item \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating conceptual resources with one another.
 
-%\item \(AR \subseteq C \times A\) being the set of \textbf{aggregation relations} associating conceptual resources with instances of aggregation and grouping resources, hence instances of, e.g., \texttt{skos:inScheme} or \texttt{skos:member} or subproperties thereof.
 \end{itemize}
@@
 
-The quality criteria we identified have in common that they are applied on a given SKOS vocabulary and identify a set of resources, which do not fulfill that criterion.
-Therefore, we can regard a quality criterion as being an abstract filtering function $f:V \rightarrow \mathfrak{P}(IR)$, mapping a given vocabulary to the powerset of its resources.
-Each quality criterion we found can be implemented as a realization of such an abstract filtering function.
-Since the return value is a set of resources, statistical analyses can be computed on the number of resources in that set.
+The commonality of all quality checking functions is that they take a given SKOS vocabulary as input and return a (nested) set, containing the resources that do \todo{CM}{not - sure?} fulfill the quality criterion.
+Therefore, we can formalize a quality criterion as being an abstract quality checking function $f:V \rightarrow \mathcal{P}(IR)$, mapping a given vocabulary $v \in V$ to the powerset of its resources.
+Each quality criterion we found can be implemented as a realization of such an abstract filtering function and statistical analysis can be computed on top of the return values.
 
-% Structure for each metric description
+% Structure for each criterion description
 %- origin (refs) and design rationale
@@
 
-In the following, we describe the origins and design rationale for each metric and provide a semi-formal definition that specifies how to implement them in tools.
-We categorized the metrics \todo{CM,BH}{Briefly describe how we organize/structure the criteria}
+In the following, we explain the origins and design rationale for each quality criterion and describe how we implemented the corresponding quality checking function.
+For better readability we provide semi-formal definitions only where necessary and refer to the online documentation or the implementation source code for further details.
+We also categorized the identified quality criteria into \emph{labeling and documentation criteria}, \emph{structural criteria}, \emph{Linked Data specific criteria}, and \emph{other criteria}.
 
@@
 \subsection{Labeling and Documentation Criteria}
+
 The criteria defined in this section primarily focus on supporting interaction with human users that either work with the vocabulary itself or interact with a system using the vocabulary for, e.g., search and retrieval purposes.

### 2012-03-20 criteria.tex
minor fixes in intro to 3

@@
 Based on the responses we received, we then selected a subset of these criteria and formalized them into computable \textbf{quality checking functions}.
-Each of these functions operates on a SKOS vocabulary, which we define, for the purpose of this work, as follows:
+Each function operates on a SKOS vocabulary, which we define, for the purpose of this work, as follows:
 
@@
 For better readability we provide semi-formal definitions only where necessary and refer to the online documentation or the implementation source code for further details.
-We also categorized the identified quality criteria into \emph{labeling and documentation criteria}, \emph{structural criteria}, \emph{Linked Data specific criteria}, and \emph{other criteria}.
+We also categorized the identified quality criteria into \emph{Labeling and Documentation Criteria}, \emph{Structural Criteria}, \emph{Linked Data Specific Criteria}, and \emph{Other Criteria}.
 

### 2012-03-20 introduction.tex
minor fixes in intro to 3

@@
 
-	\item We identified \todo{CM}{XX} \textbf{quality criteria} for SKOS vocabularies by examining existing guidelines and formalized them into computable \textbf{filtering functions} that identify possibly affected resources in a given SKOS vocabulary.
+	\item We identified \todo{CM}{XX} \textbf{quality criteria} for SKOS vocabularies by examining existing guidelines and formalized them into computable \textbf{quality checking functions} that identify possibly affected resources in a given SKOS vocabulary.
 

### 2012-03-20 criteria.tex
fixed intro to 3

@@
 We published our findings online\footnote{\url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}} and requested feedback from experts via public mailing list and informal face to face discussions.
-Based on the responses we received, we then selected a subset of these criteria and formalized them into computable \textbf{quality checking functions}.
+Based on the received responses, we then selected a subset of these criteria and formalized them into computable \textbf{quality checking functions}.
 Each function operates on a SKOS vocabulary, which we define, for the purpose of this work, as follows:
 
-\begin{definition}[SKOS Vocabulary] Let the fully entailed RDFS interpretation~\cite{RDFSEM2012} (enriched by entailment of \texttt{owl:inverseOf} properties \todo{CM}{why?}) of a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV \rangle$, with
-
-\begin{itemize}
-	\item \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of resources,
-
-	\item $LV = I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of literal values,
-
-	\item \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{conceptual resources},
-
-	\item \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating conceptual resources with one another.
-
-\end{itemize}
+\begin{definition}[SKOS Vocabulary] Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{conceptual resources}, $LV = I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of \textbf{literal values}, and \item \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating conceptual resources with one another.
+Further, we let $V$ be the fully entailed RDFS interpretation~\cite{RDFSEM2012} of the underlying RDF graph, enriched by entailment of \texttt{owl:inverseOf} properties.
 
@@
 
-The commonality of all quality checking functions is that they take a given SKOS vocabulary as input and return a (nested) set, containing the resources that do \todo{CM}{not - sure?} fulfill the quality criterion.
+The commonality of all quality checking functions is that they take a given SKOS vocabulary as input and return a (nested) set, containing the resources fulfill the quality criterion.
 Therefore, we can formalize a quality criterion as being an abstract quality checking function $f:V \rightarrow \mathcal{P}(IR)$, mapping a given vocabulary $v \in V$ to the powerset of its resources.
@@
 The criteria defined in this section primarily focus on supporting interaction with human users that either work with the vocabulary itself or interact with a system using the vocabulary for, e.g., search and retrieval purposes.
+
+The criteria defined in this section focus
 

### 2012-03-20 criteria.tex
fixed language criteria

@@
 
-\begin{definition}[SKOS Vocabulary] Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{conceptual resources}, $LV = I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of \textbf{literal values}, and \item \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating conceptual resources with one another.
+\begin{definition}[SKOS Vocabulary] Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{conceptual resources}, $LV = I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of \todo{CM}{\textbf{plain literals}?}, and \item \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating conceptual resources with one another.
 Further, we let $V$ be the fully entailed RDFS interpretation~\cite{RDFSEM2012} of the underlying RDF graph, enriched by entailment of \texttt{owl:inverseOf} properties.
@@
 
-In the following, we explain the origins and design rationale for each quality criterion and describe how we implemented the corresponding quality checking function.
-For better readability we provide semi-formal definitions only where necessary and refer to the online documentation or the implementation source code for further details.
+In the following, we explain the origins and design rationale for each quality criterion (QC) and describe how we implemented the corresponding quality checking function.
+For better readability we provide semi-formal definitions only where necessary and refer to the online documentation and the implementation source code for further details.
 We also categorized the identified quality criteria into \emph{Labeling and Documentation Criteria}, \emph{Structural Criteria}, \emph{Linked Data Specific Criteria}, and \emph{Other Criteria}.
@@
 
-The criteria defined in this section focus
+\paragraph{QC 1: Omitted or Invalid Language Tags}
 
-\subsubsection{Omitted Language Tags}
-Some controlled vocabularies contain literals in natural language without information about what language has actually been used.
-Using private language tags (see RFC3066) or omitting them at all limits, e.g., language-dependent queries.
-To identfy omitted language tags we iterate over all conceptual resources in $C$ and collect those that have relations to untyped literals lacking language information as described above.
+SKOS defines a set of properties that link resources with RDF Literals, which are plain text natural language strings with an optional language tag.
+This includes the labeling properties \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} or \texttt{skos:documentation}.
+Since omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could limit language-dependent structural queries, we check a SKOS vocabulary for omitted language tags by iterating over concepts \todo{not resources?
+any resource can have a prefLabel, right?
+and prefLabel has no domain specified} in $C$ and collect those that have relations to plain literals without or with invalid language tags.
+We check the validity of a language tag by comparing it to the list of tags defined in \todo{CM}{??}.\todo{CM}{is there any literature reference for this criterion?}
 
-\subsubsection{Incomplete Language Coverage}
-According to the previous criterion, vocabularies should combine plain literals with language tags.
-Furthermore, to support, e.g., internationalization or translation use cases, every concept should have defined literal values in the same set of languages than the other concepts.
-Calculation of the affected resources is done by iterating over all conceptual resources in $C$, building a global list of distinct languages throughout all literals assigned to every concept.
-Additionally, a list of used languages per conceptual resource is created.
-The criterion identifies all conceptual resources having a language list not equal to the global language list.
+\paragraph{QC 2: Incomplete Language Coverage}
 
-\subsubsection{Undocumented Concepts}
-\cite{Aitchison2000} cites Svenonius to advocate ``inclusion of as much definition material as possible''.
+A SKOS vocabulary that uses language tags with its literal values, should apply them consistently for all concepts.
+Hence, the set of language tags used by the literal values linked with a \todo{CM}{concept/resource} should be the same for all \todo{CM}{concepts/resources}.
+This is particularly important for applications that rely on internationalization and translation use cases.
+We calculate the affected resources by extracting the global set of language tags used in a vocabulary from all literal values attached to all \todo{CM}{concepts/resources}.
+Then we iterate over all \todo{CM}{conceptual resources} in $C$ and identify all conceptual resources having a set of language tags that is not equal to the global language set.
+\todo{CM}{literature reference?}
+
+\paragraph{QC 3: Undocumented Concepts}
+
+\cite{Aitchison2000} cites Svenonius \todo{CM}{cite original work} to advocate ``inclusion of as much definition material as possible''.
 The SKOS language specification defines various properties that are intended to hold this kind of information, subsumed as ``documentation properties'' in the SKOS reference.
-To identify the affected conceptual resources, we iterate over all elements in $C$ to find those that are not related to one of the documentation properties.
+To identify the affected conceptual resources, we iterate over all elements in $C$ to find those that are not using at least one of the documentation properties.\todo{CM}{rephrase}
 
-\subsubsection{Potentially Semantically Related Concepts} \todo{All}{reformulate criterion title}
+\paragraph{QC 4: Potentially Semantically Related Concepts} \todo{All}{reformulate criterion title}
+
 This criterion is an extension of a statement from the SKOS primer, recommending ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.

### 2012-03-21 criteria.tex
finished comments on literal criteria

@@
 Therefore, we can formalize a quality criterion as being an abstract quality checking function $f:V \rightarrow \mathcal{P}(IR)$, mapping a given vocabulary $v \in V$ to the powerset of its resources.
-Each quality criterion we found can be implemented as a realization of such an abstract filtering function and statistical analysis can be computed on top of the return values.
+Each quality criterion we found can be implemented as a realization of such an abstract filtering function, possibly with additional parameters.
+Statistical analysis can be computed on top of the return values.
 
@@
 
-\paragraph{QC 4: Potentially Semantically Related Concepts} \todo{All}{reformulate criterion title}
+\paragraph{QC 4: Potentially Semantically Related Concepts} \todo{All}{reformulate criterion title: Labeling Conflicts}
 
-This criterion is an extension of a statement from the SKOS primer, recommending ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
-Given the fact that (i) many vocabularies don’t make use of concept schemes and (ii) also identical altLabels or hiddenLabels can have a negative effect in some use-cases (e.g, auto-completion of concept labels based on user input), we follow a more general approach: identification of all pairs of concepts with their respective prefLabel, altLabel or hiddenLabel meeting a threshold of a certain similarity function $sim:LV \times LV \rightarrow [0,1]$.
+% avoid "given the fact, " sentences -> rephrase
+
+This criterion is an extension of a statement from the SKOS primer, recommending ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''~[\todo{CM}{ref}].
+Given the fact that (i) many vocabularies don’t make use of concept schemes and (ii) also identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} can have a negative effect in some use-cases (e.g, auto-completion of concept labels based on user input), we follow a more general approach: identification of all pairs of concepts with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} meeting a threshold of a certain similarity function $sim:LV \times LV \rightarrow [0,1]$.
 For the analysis of the criterion in this document, we define the similarity function  to check for case-insensitive string equality and the threshold to equal 1.
-Calculation of this criterion is done by applying the similarity function to every label of every possible pair of conceptual concepts in $C$ and filtering those that meet or exceed a specified threshold.
+Calculation of this criterion is done by applying the similarity function to every label of every possible pair \todo{CM}{crossproduct?} of conceptual concepts in $C$ and filtering those that meet or exceed a specified threshold.
 

### 2012-03-21 criteria.tex
changed qc1

@@
 SKOS defines a set of properties that link resources with RDF Literals, which are plain text natural language strings with an optional language tag.
-This includes the labeling properties \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} or \texttt{skos:documentation}.
-Since omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could limit language-dependent structural queries, we check a SKOS vocabulary for omitted language tags by iterating over concepts \todo{not resources?
-any resource can have a prefLabel, right?
-and prefLabel has no domain specified} in $C$ and collect those that have relations to plain literals without or with invalid language tags.
-We check the validity of a language tag by comparing it to the list of tags defined in \todo{CM}{??}.\todo{CM}{is there any literature reference for this criterion?}
+This includes the labeling properties \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} and subproperties thereof.
+Since omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could limit language-dependent structural queries, we check a SKOS vocabulary for omitted language tags by iterating over resources in $IR$ and collect those that have relations to plain literals without or with invalid language tags.
+We delegate validity checking of language tags to methods provided by the by OpenRDF\footnote{\url{http://www.openrdf.org/}} framework that in turn checks for conformance with RFC3066\footnote{\url{http://www.ietf.org/rfc/rfc3066.txt}}.\todo{CM}{is there any literature reference for this criterion?}
 

### 2012-03-21 criteria.tex
fixed some todos

@@
 
+\todo{All}{decide for either using "concept" or "conceptual resource"}
+
 % LEXICAL AND DOCUMENTATION CRITERIA
@@
 Since omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could limit language-dependent structural queries, we check a SKOS vocabulary for omitted language tags by iterating over resources in $IR$ and collect those that have relations to plain literals without or with invalid language tags.
-We delegate validity checking of language tags to methods provided by the by OpenRDF\footnote{\url{http://www.openrdf.org/}} framework that in turn checks for conformance with RFC3066\footnote{\url{http://www.ietf.org/rfc/rfc3066.txt}}.\todo{CM}{is there any literature reference for this criterion?}
+We delegate validity checking of language tags to methods provided by the by the OpenRDF\footnote{\url{http://www.openrdf.org/}} framework that in turn checks for conformance with RFC3066\footnote{\url{http://www.ietf.org/rfc/rfc3066.txt}}.\todo{CM}{is there any literature reference for this criterion?}
 
@@
 A SKOS vocabulary that uses language tags with its literal values, should apply them consistently for all concepts.
-Hence, the set of language tags used by the literal values linked with a \todo{CM}{concept/resource} should be the same for all \todo{CM}{concepts/resources}.
+Hence, the set of language tags used by the literal values linked with a concept should be the same for all concepts.
 This is particularly important for applications that rely on internationalization and translation use cases.
-We calculate the affected resources by extracting the global set of language tags used in a vocabulary from all literal values attached to all \todo{CM}{concepts/resources}.
-Then we iterate over all \todo{CM}{conceptual resources} in $C$ and identify all conceptual resources having a set of language tags that is not equal to the global language set.
+We calculate the affected concepts by extracting the global set of language tags used in a vocabulary from all literal values attached to all concepts in $C$.
+In a second pass we again iterate over this set of concepts and identify all conceptual resources having a set of language tags that is not equal to the global language set.
 \todo{CM}{literature reference?}
@@
 
-\cite{Aitchison2000} cites Svenonius \todo{CM}{cite original work} to advocate ``inclusion of as much definition material as possible''.
-The SKOS language specification defines various properties that are intended to hold this kind of information, subsumed as ``documentation properties'' in the SKOS reference.
-To identify the affected conceptual resources, we iterate over all elements in $C$ to find those that are not using at least one of the documentation properties.\todo{CM}{rephrase}
+\cite{Svenonius1997} advocates the ``inclusion of as much definition material as possible''.
+The SKOS language specification defines various properties that are intended to hold this kind of information, subsumed as ``documentation properties''~\cite{SkosReference2008}.
+To identify all undocumented concepts, we iterate over all concepts in $C$ and collect those for which we cannot find information linked by any of the documentation properties.
 
-\paragraph{QC 4: Potentially Semantically Related Concepts} \todo{All}{reformulate criterion title: Labeling Conflicts}
+\paragraph{QC 4: Label Conflicts}
 
-% avoid "given the fact, " sentences -> rephrase
-
-This criterion is an extension of a statement from the SKOS primer, recommending ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''~[\todo{CM}{ref}].
-Given the fact that (i) many vocabularies don’t make use of concept schemes and (ii) also identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} can have a negative effect in some use-cases (e.g, auto-completion of concept labels based on user input), we follow a more general approach: identification of all pairs of concepts with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} meeting a threshold of a certain similarity function $sim:LV \times LV \rightarrow [0,1]$.
+This criterion is an extension of a statement from \cite{Isaac2009}, recommending ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
+Based on our review of existing vocabularies, we could observe that (i) many vocabularies don’t make use of concept schemes and (ii) also identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} can have a negative effect in some use-cases (e.g, auto-completion of concept labels based on user input).
+Thus we follow the more general approach of finding all pairs of concepts with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} meeting a threshold of a certain similarity function $sim:LV \times LV \rightarrow [0,1]$.
 For the analysis of the criterion in this document, we define the similarity function to check for case-insensitive string equality and the threshold to equal 1.
-Calculation of this criterion is done by applying the similarity function to every label of every possible pair \todo{CM}{crossproduct?} of conceptual concepts in $C$ and filtering those that meet or exceed a specified threshold.
+Calculation of this criterion is done by iterating over all pairs of concepts, i.e., elements of $C \times C$.
+We then apply the $sim$ to every possible combination of labels between the members of the pairs and collect those pairs for which $sim$ meets or exceeds a specified threshold.
 
@@
 \cite{Soergel2002} suggests a ``check for hierarchy cycles" since they ``throw the program for a loop in the generation of a complete hierarchical structure''.
-However, SKOS does not define a formal constraint regarding hierarchy cycles but the SKOS reference document mentions them as potential problems.
+However, SKOS does not define a formal constraint regarding hierarchy cycles but \cite{SkosReference2008} mentions them as potential problems.
 The SKOS documentation also does not state, how exactly hierarchical relationships are to be interpreted.
@@
 \subsubsection{Solely Transitively Related Concepts}
-Two concepts are related using only transitive hierarchical relations which are, according to the SKOS reference document, ``not used to make assertions''.
+Two concepts are related using only transitive hierarchical relations which are, according to \cite{SkosReference2008}, ``not used to make assertions''.
 Transitive hierarchical relations in SKOS are meant to be infered by the vocabulary user, which is reflected in the SKOS schema by, e.g., \texttt{broader} being a subproperty of \texttt{broaderTransitive}.

### 2012-03-21 criteria.tex
resolved some todos

@@
 
-\begin{definition}[SKOS Vocabulary] Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{conceptual resources}, $LV = I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of \todo{CM}{\textbf{plain literals}?}, and \item \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating conceptual resources with one another.
+\begin{definition}[SKOS Vocabulary] Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, ULV \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{conceptual resources}, $ULV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of \textbf{untyped literal values}, and \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating conceptual resources with one another.
 Further, we let $V$ be the fully entailed RDFS interpretation~\cite{RDFSEM2012} of the underlying RDF graph, enriched by entailment of \texttt{owl:inverseOf} properties.
@@
 
-\todo{All}{decide for either using "concept" or "conceptual resource"}
+\todo{All}{decide for either using the term "concept" or "conceptual resource"}
 
@@
 Based on our review of existing vocabularies, we could observe that (i) many vocabularies don’t make use of concept schemes and (ii) also identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} can have a negative effect in some use-cases (e.g, auto-completion of concept labels based on user input).
-Thus we follow the more general approach of finding all pairs of concepts with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} meeting a threshold of a certain similarity function $sim:LV \times LV \rightarrow [0,1]$.
+Thus we follow the more general approach of finding all pairs of concepts with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} meeting a threshold of a certain similarity function $sim:ULV \times ULV \rightarrow [0,1]$.
 For the analysis of the criterion in this document, we define the similarity function to check for case-insensitive string equality and the threshold to equal 1.
@@
 In order to provide entry points to such a group of concepts, one or more concepts can be marked as top concepts.
-This helps to provide ``efficient access'' (SKOS primer) and simplifies orientation in the vocabulary.
+This helps to provide ``efficient access''~\cite{Isaac2009} and simplifies orientation in the vocabulary.
 To calculate this criterion, we identify all ConceptSchemes $I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})$ not contained in any of the pairs in $I_{EXT}(\texttt{skos:hasTopConcept}^\mathcal{I})$.

### 2012-03-21 criteria.tex
finalize labelling / documentation criteria

@@
 
-\begin{definition}[SKOS Vocabulary] Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, ULV \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{conceptual resources}, $ULV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of \textbf{untyped literal values}, and \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating conceptual resources with one another.
+\begin{definition}[SKOS Vocabulary] Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, ULV \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{conceptual resources}, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating conceptual resources with one another, and $ULV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of \textbf{untyped literal values}.
 Further, we let $V$ be the fully entailed RDFS interpretation~\cite{RDFSEM2012} of the underlying RDF graph, enriched by entailment of \texttt{owl:inverseOf} properties.
@@
 
-The commonality of all quality checking functions is that they take a given SKOS vocabulary as input and return a (nested) set, containing the resources fulfill the quality criterion.
+% @CM Are you sure about the term "untyped literal"? The RDF spec talkes about
+% plain literals
+
+The commonality of all quality checking functions is that they take a given SKOS vocabulary as input and return a (nested) set, containing the resources \todo{CM}{fulfill the quality criterion?}.
 Therefore, we can formalize a quality criterion as being an abstract quality checking function $f:V \rightarrow \mathcal{P}(IR)$, mapping a given vocabulary $v \in V$ to the powerset of its resources.
 Each quality criterion we found can be implemented as a realization of such an abstract filtering function, possibly with additional parameters.
-Statistical analysis can be computed on top of the return values.
+Statistical analysis can be computed on top of the return values.\todo{CM}{the term criterion still sounds strange.
+We must somehow clarify what passing/failing a criterion means there.}
 
@@
 This includes the labeling properties \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} and subproperties thereof.
-Since omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could limit language-dependent structural queries, we check a SKOS vocabulary for omitted language tags by iterating over resources in $IR$ and collect those that have relations to plain literals without or with invalid language tags.
-We delegate validity checking of language tags to methods provided by the by the OpenRDF\footnote{\url{http://www.openrdf.org/}} framework that in turn checks for conformance with RFC3066\footnote{\url{http://www.ietf.org/rfc/rfc3066.txt}}.\todo{CM}{is there any literature reference for this criterion?}
+Since omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could limit language-dependent structural queries, we check a SKOS vocabulary for omitted language tags.
+We iterate over all resources in $IR$ and collect those that have relations to plain literals with missing or invalid language tags, hence tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
+
+% This is implementation specific; let's stay with high-level descriptions of the algorithms
+%We delegate validity checking of language tags to methods provided by the by the OpenRDF\footnote{\url{http://www.openrdf.org/}} framework that in turn checks for conformance with RFC3066\footnote{\url{http://www.ietf.org/rfc/rfc3066.txt}}.\todo{CM}{is there any literature reference for this criterion?}
 
@@
 
-A SKOS vocabulary that uses language tags with its literal values, should apply them consistently for all concepts.
+A SKOS vocabulary that uses language tags with its literal values should apply them consistently for all concepts.
 Hence, the set of language tags used by the literal values linked with a concept should be the same for all concepts.
@@
 The SKOS language specification defines various properties that are intended to hold this kind of information, subsumed as ``documentation properties''~\cite{SkosReference2008}.
-To identify all undocumented concepts, we iterate over all concepts in $C$ and collect those for which we cannot find information linked by any of the documentation properties.
+To identify all undocumented concepts, we iterate over all concepts in $C$ and collect those that do not use any of these documentation properties.
 
@@
 
-This criterion is an extension of a statement from \cite{Isaac2009}, recommending ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
-Based on our review of existing vocabularies, we could observe that (i) many vocabularies don’t make use of concept schemes and (ii) also identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} can have a negative effect in some use-cases (e.g, auto-completion of concept labels based on user input).
-Thus we follow the more general approach of finding all pairs of concepts with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} meeting a threshold of a certain similarity function $sim:ULV \times ULV \rightarrow [0,1]$.
-For the analysis of the criterion in this document, we define the similarity function to check for case-insensitive string equality and the threshold to equal 1.
-Calculation of this criterion is done by iterating over all pairs of concepts, i.e., elements of $C \times C$.
-We then apply the $sim$ to every possible combination of labels between the members of the pairs and collect those pairs for which $sim$ meets or exceeds a specified threshold.
+This criterion is an extension of a statement from \cite{Isaac2009} that recommends that ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
+Based on our review of existing vocabularies, we could observe that (i) many vocabularies don’t use concept schemes and (ii) identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} can also negatively affect use cases such as auto-completion, which proposes labels based on the user input.
+Thus, this criterion generalizes this statement by finding all concept pairs with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} property values meeting a certain similarity threshold defined by a function $sim:ULV \times ULV \rightarrow [0,1]$.
+The default, built-in similarity function checks for case-insensitive string equality with a threshold equal to 1.
+This criterion is calculated by iterating over all pairs of concepts, i.e., elements of $C \times C$, applying $sim$ to every possible label combination, and collecting those pairs for which $sim$ meets or exceeds a specified threshold.
 

### 2012-03-21 criteria.tex
started structur criteria

@@
 
-The commonality of the following metrics is that they identify possible weaknesses when $V$ is used in scenarios exploiting the structure of its RDF graph.
+The commonality of the following criteria is that they identify possible weaknesses when $V$ is used in scenarios exploiting the structure of its RDF graph.
 
-\subsubsection{Loose Concepts} is a criterion motivated by the notion of ``orphan terms'' in the literature~\cite{Hedden2010}, which are are terms without any associative or hierarchical relationships.
+\paragraph{Loose Concepts}
+
+is a criterion motivated by the notion of ``orphan terms'' in the literature~\cite{Hedden2010}, which are are terms without any associative or hierarchical relationships.
 Checking for them is common in existing thesaurus development applications and also suggested by \cite{Z39.19:2005}.

### 2012-03-22 criteria.tex
addressed some of the todos

@@
 % plain literals
+% from the RDF simple interpretation: "6.
+A distinguished subset LV of IR, called the set of literal values, which contains all the plain literals in V"; "all plain literals" which doesn't state "only plain literals", so I think we need the subset here; Also, Hitzler defines LV as the set of literal values, "containing (at least) all untyped literals in V", which indicates that LV also contains typed literals.
 
-The commonality of all quality checking functions is that they take a given SKOS vocabulary as input and return a (nested) set, containing the resources \todo{CM}{fulfill the quality criterion?}.
+The commonality of all quality checking functions is that they can be applied on a given SKOS vocabulary and report a (nested) set of vocabulary resources, being the cause of anticipated quality degradations.
 Therefore, we can formalize a quality criterion as being an abstract quality checking function $f:V \rightarrow \mathcal{P}(IR)$, mapping a given vocabulary $v \in V$ to the powerset of its resources.
 Each quality criterion we found can be implemented as a realization of such an abstract filtering function, possibly with additional parameters.
-Statistical analysis can be computed on top of the return values.\todo{CM}{the term criterion still sounds strange.
-We must somehow clarify what passing/failing a criterion means there.}
+Statistical analysis can be computed on top of the return values.
+
+\todo{CM}{the term criterion still sounds strange. We must somehow clarify what passing/failing a criterion means there.}
+\todo{BH}{maybe we should use the term "criteria" for our initial quality findings published online and only speak of "quality functions" in this publication.
+A criterion implies a strict measure (pass/fail) whereas our functions only provide "hints" for later human judgement.
+they are "computable guidelines"}
 
@@
 
-\subsection{Labeling and Documentation Criteria}
+\subsection{Labeling and Documentation \textcolor{red}{Functions}}
 
@@
 \paragraph{QC 2: Incomplete Language Coverage}
-
-A SKOS vocabulary that uses language tags with its literal values should apply them consistently for all concepts.
+%A SKOS vocabulary that uses language tags with its literal values should apply them consistently for all concepts.
+\cite{Soergel1997} points out the problem that some concepts may not be lexicalized in every language the vocabulary seeks to support.
+Presence of such concepts may indicate a need for restructuring the vocabulary or include documentation about the differing meanings in all supported languages.
 Hence, the set of language tags used by the literal values linked with a concept should be the same for all concepts.
@@
 In a second pass we again iterate over this set of concepts and identify all conceptual resources having a set of language tags that is not equal to the global language set.
-\todo{CM}{literature reference?}
 

### 2012-03-22 criteria.tex
rephrased some quality function descriptions

@@
 
-\paragraph{Loose Concepts}
+\paragraph{\textbf{QF 5: Loose Concepts}} \todo{BH}{rename this to Orphan Concepts?}
 
-is a criterion motivated by the notion of ``orphan terms'' in the literature~\cite{Hedden2010}, which are are terms without any associative or hierarchical relationships.
+This quality function is motivated by the notion of ``orphan terms'' in the literature~\cite{Hedden2010}, which are are terms without any associative or hierarchical relationships.
 Checking for them is common in existing thesaurus development applications and also suggested by \cite{Z39.19:2005}.
-When we apply this to SKOS vocabularies, a loose concept is a concept that has no semantic relations with other conceptual resources and thus do not occur in any of the pairs yielded by $SR$.
+All vocabularies expressed in SKOS are concept-centric, thus we understand a loose concept is a concept that has no semantic relations with other conceptual resources i.e.
+it does not occur in any of the pairs yielded by $SR$.
 Although they might have attached lexical labels, they lack valuable context information that is considered essential for, e.g., search query expansion.
@@
 
-\subsubsection{Weakly Connected Components} indicate that the vocabulary is split into separate ``clusters''.
+\paragraph{\textbf{QF 6: Weakly Connected Components}} indicate that the vocabulary is split into separate ``clusters''.
 Presence of several WCC might be caused by incomplete data acquisition, ``forgotten'' test data, outdated terms, accidental deletion of relations and the like.
@@
 
-\subsubsection{Cyclic Hierarchical Relations} have been mentioned numerous times in thesaurus development literature.
+\paragraph{\textbf{QF 7: Cyclic Hierarchical Relations}} have been mentioned numerous times in thesaurus development literature.
 \cite{Soergel2002} suggests a ``check for hierarchy cycles" since they ``throw the program for a loop in the generation of a complete hierarchical structure''.
@@
 To calculate this criterion, we construct two graphs, with the set of nodes being $C$.
-The edges in one graph only point towards the broader concepts, the edges of the other graph towards the narrower concepts.
+The edges in one graph only point towards the broader concepts, the edges of the other graph point towards the narrower concepts.
 For each graph we now identify those nodes that are part of a cycle and return the set of strongly connected components they are contained in.
@@
 
-\subsubsection{Valueless Associative Relations}
-The ISO/DIS 25964-1 standard suggests that terms that share a common broader term but don’t have an overlapping meaning, should not be related associatively.
+\paragraph{\textbf{QF 8: Valueless Associative Relations}}
+The ISO/DIS 25964-1 standard suggests that terms that share a common broader term but do not have an overlapping meaning, should not be related associatively.
 This is also advocated by \cite{Hedden2010} and \cite{Aitchison2000} who also mentions ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships'', having a negative effect on precision.
-This criterion identifies a set of pairs of conceptual resources that share the same broader or narrower concept while also being associatively related, i.e.
-all pairs in $I_{EXT}(\texttt{skos:related}^\mathcal{I})$ that contain both of these conceptual resources.
+This function identifies a set of pairs of conceptual resources that share the same broader or narrower concept while also being associatively related by the property \texttt{skos:related}.
 
-\subsubsection{Solely Transitively Related Concepts}
+\paragraph{\textbf{QF 9: Solely Transitively Related Concepts}}
 Two concepts are related using only transitive hierarchical relations which are, according to \cite{SkosReference2008}, ``not used to make assertions''.
-Transitive hierarchical relations in SKOS are meant to be infered by the vocabulary user, which is reflected in the SKOS schema by, e.g., \texttt{broader} being a subproperty of \texttt{broaderTransitive}.
-This criterion identifies the set $I_{EXT}(\texttt{skos:broaderTransitive}^\mathcal{I}) \cup I_{EXT}(\texttt{skos:narrowerTransitive}^\mathcal{I})$ \textbf{without} RDFS subproperty entailment.
+Transitive hierarchical relations in SKOS are meant to be infered by the vocabulary user, which is reflected in the SKOS schema by, e.g., \texttt{skos:broader} being a subproperty of \texttt{skos:broaderTransitive}.
+This fuction iterates over all pairs of concepts $C \times C$ that are \textbf{explicitly} related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive}, i.e.
+\textbf{without} RDFS subproperty entailment.
 
-\subsubsection{Omitted Top Concepts}
-The SKOS language provides ConceptSchemes which are a facility for grouping related concepts.
+\paragraph{\textbf{QF 10: Omitted Top Concepts}}
+The SKOS language provides concept schemes, which are a facility for grouping related concepts.
 In order to provide entry points to such a group of concepts, one or more concepts can be marked as top concepts.
 This helps to provide ``efficient access''~\cite{Isaac2009} and simplifies orientation in the vocabulary.
-To calculate this criterion, we identify all ConceptSchemes $I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})$ not contained in any of the pairs in $I_{EXT}(\texttt{skos:hasTopConcept}^\mathcal{I})$.
-
-%Thus, this criterion returns the subset of $C$ whose elements are not contained in any of the pairs obtained by $I_{EXT}(\texttt{skos:hasTopConcept}^\mathcal{I})$.
+To calculate this function, we iterate over all \texttt{skos:ConceptScheme}s in $V$ and collect those that occur in relations established by the properties \texttt{skos:hasTopConcept} or \texttt{skos:topConceptOf}.
 

### 2012-03-22 criteria.tex
added comments/updated result table

@@
 This criterion is an extension of a statement from \cite{Isaac2009} that recommends that ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
-Based on our review of existing vocabularies, we could observe that (i) many vocabularies don’t use concept schemes and (ii) identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} can also negatively affect use cases such as auto-completion, which proposes labels based on the user input.
+Based on our review of existing vocabularies, we could observe that (i) many vocabularies don’t use concept schemes and (ii) identical alternative or hidden can also negatively affect use cases such as auto-completion, which proposes labels based on the user input.
 Thus, this criterion generalizes this statement by finding all concept pairs with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} property values meeting a certain similarity threshold defined by a function $sim:ULV \times ULV \rightarrow [0,1]$.
@@
 
-\subsubsection{Top Concept Having Broader Concepts}
+\paragraph{\textbf{QF 11: Top Concept Having Broader Concepts}}
 \cite{Allemang2011} proposes to ``not indicate any concepts internal to the tree as top concepts'', i.
@@
 top concepts should not have broader concepts.
-This criteria identifies all elements from $C$ that occur in both $I_{EXT}(\texttt{skos:topConceptOf}^\mathcal{I})$ and as first element of each pair from $I_{EXT}(\texttt{skos:broader}^\mathcal{I})$.
+This criteria iterates over all \texttt{skos:TopConcept}s defined in $V$ and collects those that are related to a resource by the \texttt{skos:broader} property.
 
@@
 A periodically updated version of a diagram visualizing ``the data sets in the LOD cloud as well as their interlinkage relationships'' is publised online\footnote{\url{http://www4.wiwiss.fu-berlin.de/lodcloud/state/}}.
-In these diagrams, dbpedia is shown as the most intensely linked resource, i.e.
+In these diagrams, DBpedia is shown as the most intensely linked resource, i.e.
 a large number of vocabularies link to resources in that dataset.
-Therefore a dataset with a large number of other datasets referencing it, can be assumed to be of great value for the community.
-Accordingly, estimating the number of In-Links of SKOS concepts defined in a vocabulary (henceforth called the in-degree of a concept) would give some hint about how established or accepted a controlled vocabulary is.
+This indicates that a dataset with a large number of other datasets referencing it, can be assumed to be of great value for the community, adding cohesion to the LOD cloud.
+Accordingly, estimating the number of In-Links of SKOS concepts defined in a vocabulary (henceforth called the in-degree of a concept) gives some hint about how established or accepted a controlled vocabulary is.
 A method to carry out these estimations would be utilizing existing Linked Data indices like, e.g., Sindice\footnote{\url{http://sindice.com/}} that provide a SPARQL endpoint.
@@
 Calculation of the result set is done by iterating over all elements $c \in C$ and investigating the host part of all related resources.
-If none of these host names differs from the host part of $c$, it has no Out-Links and is thus included into the resources identified by this criterion.
+If none of these host names differ from the host part of $c$, it has no Out-Links and is thus included into the resources identified by this criterion.
 
@@
 
-\subsubsection{Link Target Unavailability}
+\subsubsection{Link Target Unavailability} \todo{BH}{should we just call this "Broken Links" because that's essentially what it's all about}
 This criterion identifies a set of all resources that have been identified as unavailable, i.e.

### 2012-03-22 criteria.tex
finished labeling and documentation issues

@@
 
-\section{Quality Criteria for SKOS Vocabularies}\label{sec:criteria}
+\section{Possible Quality Issues in SKOS Vocabularies}\label{sec:criteria}
 
@@
 
-We identified an initial set of quality criteria for SKOS vocabularies by reviewing existing literature and manually examining existing vocabularies.
+We identified an initial set of possible quality issues in SKOS vocabularies by reviewing existing literature and manually examining existing vocabularies.
 We published our findings online\footnote{\url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}} and requested feedback from experts via public mailing list and informal face to face discussions.
-Based on the received responses, we then selected a subset of these criteria and formalized them into computable \textbf{quality checking functions}.
+Based on the received responses, we then selected a subset of these issues and formalized them into computable \textbf{quality checking functions}.
 Each function operates on a SKOS vocabulary, which we define, for the purpose of this work, as follows:
 
-\begin{definition}[SKOS Vocabulary] Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, ULV \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{conceptual resources}, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating conceptual resources with one another, and $ULV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of \textbf{untyped literal values}.
+\begin{definition}[SKOS Vocabulary] Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, ULV \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{concepts}, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating conceptual resources with one another, and $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}.
 Further, we let $V$ be the fully entailed RDFS interpretation~\cite{RDFSEM2012} of the underlying RDF graph, enriched by entailment of \texttt{owl:inverseOf} properties.
@@
 
-% @CM Are you sure about the term "untyped literal"? The RDF spec talkes about
-% plain literals
-% from the RDF simple interpretation: "6.
-A distinguished subset LV of IR, called the set of literal values, which contains all the plain literals in V"; "all plain literals" which doesn't state "only plain literals", so I think we need the subset here; Also, Hitzler defines LV as the set of literal values, "containing (at least) all untyped literals in V", which indicates that LV also contains typed literals.
+A quality checking function is applied on a given SKOS vocabulary and finds all vocabulary resources that match a certain issue and might degrade the overall quality of a vocabulary.
+Therefore, we can formalize a quality issue in terms of an abstract function $f:V \rightarrow \mathcal{P}(IR)$ that maps a given vocabulary $v \in V$ to the powerset of its resources.
+Each quality issue we found can be implemented as a realization of that abstract function and possibly take additional parameters.
+Statistical analysis can be computed on top of the result set.
 
-The commonality of all quality checking functions is that they can be applied on a given SKOS vocabulary and report a (nested) set of vocabulary resources, being the cause of anticipated quality degradations.
-Therefore, we can formalize a quality criterion as being an abstract quality checking function $f:V \rightarrow \mathcal{P}(IR)$, mapping a given vocabulary $v \in V$ to the powerset of its resources.
-Each quality criterion we found can be implemented as a realization of such an abstract filtering function, possibly with additional parameters.
-Statistical analysis can be computed on top of the return values.
+In the following, we explain the origins and design rationale for each quality issue (QI) and define the corresponding quality checking function.
+For better readability and due to lack of space we provide only semi-formal definitions and refer to the online documentation and the implementation source code for further details.
+We also categorized the identified quality issues into \emph{Labeling and Documentation Issues}, \emph{Structural Issues}, \emph{Linked Data Specific Issues}, and \emph{Other Issues}.
 
-\todo{CM}{the term criterion still sounds strange. We must somehow clarify what passing/failing a criterion means there.}
-\todo{BH}{maybe we should use the term "criteria" for our initial quality findings published online and only speak of "quality functions" in this publication.
-A criterion implies a strict measure (pass/fail) whereas our functions only provide "hints" for later human judgement.
-they are "computable guidelines"}
+% LABELING AND DOCUMENTATION ISSUES
 
-% Structure for each criterion description
-%- origin (refs) and design rationale
-%- formal definition that specifies how to compute the metric
+\subsection{Labeling and Documentation Issues}
 
-In the following, we explain the origins and design rationale for each quality criterion (QC) and describe how we implemented the corresponding quality checking function.
-For better readability we provide semi-formal definitions only where necessary and refer to the online documentation and the implementation source code for further details.
-We also categorized the identified quality criteria into \emph{Labeling and Documentation Criteria}, \emph{Structural Criteria}, \emph{Linked Data Specific Criteria}, and \emph{Other Criteria}.
+The following issues primarily focus on possible problems that might arise when human users work with a SKOS vocabulary or interact with a system that uses the vocabulary for, e.g., search and retrieval purposes.
 
-\todo{All}{decide for either using the term "concept" or "conceptual resource"}
+\paragraph{QI 1: Omitted or Invalid Language Tags}
 
-% LEXICAL AND DOCUMENTATION CRITERIA
-
-\subsection{Labeling and Documentation \textcolor{red}{Functions}}
-
-The criteria defined in this section primarily focus on supporting interaction with human users that either work with the vocabulary itself or interact with a system using the vocabulary for, e.g., search and retrieval purposes.
-
-\paragraph{QC 1: Omitted or Invalid Language Tags}
-
+% Origin and rationale
 SKOS defines a set of properties that link resources with RDF Literals, which are plain text natural language strings with an optional language tag.
 This includes the labeling properties \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} and subproperties thereof.
-Since omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could limit language-dependent structural queries, we check a SKOS vocabulary for omitted language tags.
-We iterate over all resources in $IR$ and collect those that have relations to plain literals with missing or invalid language tags, hence tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
+Omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could unintentionally limit the result set of language-dependent structural queries.
+% Function defintion
+We can check a SKOS vocabulary for omitted and invalid language tags by defining a quality checking function $oilt$ that iterates over all resources in $IR$ and finds those that have relations to plain literals with missing or invalid language tags, hence tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
 
-% This is implementation specific; let's stay with high-level descriptions of the algorithms
-%We delegate validity checking of language tags to methods provided by the by the OpenRDF\footnote{\url{http://www.openrdf.org/}} framework that in turn checks for conformance with RFC3066\footnote{\url{http://www.ietf.org/rfc/rfc3066.txt}}.\todo{CM}{is there any literature reference for this criterion?}
+\paragraph{QI 2: Incomplete Language Coverage}
 
-\paragraph{QC 2: Incomplete Language Coverage}
-%A SKOS vocabulary that uses language tags with its literal values should apply them consistently for all concepts.
-\cite{Soergel1997} points out the problem that some concepts may not be lexicalized in every language the vocabulary seeks to support.
-Presence of such concepts may indicate a need for restructuring the vocabulary or include documentation about the differing meanings in all supported languages.
-Hence, the set of language tags used by the literal values linked with a concept should be the same for all concepts.
+% Origin and rationale
+Soergel et al.~\cite{Soergel1997} point out that ``the problem that has bedeviled many developers of multilingual thesauri is that a concept lexicalized in one language may not be lexicalized in another...''.
+In the context of SKOS, this means that the set of language tags used by the literal values linked with a concept should be the same for all concepts.
 This is particularly important for applications that rely on internationalization and translation use cases.
-We calculate the affected concepts by extracting the global set of language tags used in a vocabulary from all literal values attached to all concepts in $C$.
-In a second pass we again iterate over this set of concepts and identify all conceptual resources having a set of language tags that is not equal to the global language set.
+% Function defintion
+We identify affected the concepts by a function $ilc$ that first extracts the global set of language tags used in a vocabulary from all literal values attached to all concepts in $C$.
+In a second iteration over all concepts it identifies all concepts having a set of language tags that is not equal to the global language set.
 
-\paragraph{QC 3: Undocumented Concepts}
+\paragraph{QI 3: Undocumented Concepts}
 
-\cite{Svenonius1997} advocates the ``inclusion of as much definition material as possible''.
-The SKOS language specification defines various properties that are intended to hold this kind of information, subsumed as ``documentation properties''~\cite{SkosReference2008}.
-To identify all undocumented concepts, we iterate over all concepts in $C$ and collect those that do not use any of these documentation properties.
+% Origin and rationale
+Svenonius~\cite{Svenonius1997} advocates the ``inclusion of as much definition material as possible'' and the SKOS language specification~\cite{SkosReference2008} defines a set of properties, denoted as ``documentation properties'', that are intended to hold this kind of information.
+% Function defintion
+To identify all undocumented concepts, we define a function $uc$ we iterate over all concepts in $C$ and by default collect those that do not use any of these documentation properties.
 
-\paragraph{QC 4: Label Conflicts}
+\paragraph{QI 4: Label Conflicts}
 
-This criterion is an extension of a statement from \cite{Isaac2009} that recommends that ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
-Based on our review of existing vocabularies, we could observe that (i) many vocabularies don’t use concept schemes and (ii) identical alternative or hidden can also negatively affect use cases such as auto-completion, which proposes labels based on the user input.
-Thus, this criterion generalizes this statement by finding all concept pairs with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} property values meeting a certain similarity threshold defined by a function $sim:ULV \times ULV \rightarrow [0,1]$.
+% Origin and rationale
+This issue is an extension of a statement from the SKOS Primer~\cite{Isaac2009} that recommends that ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
+We reviewed existing vocabularies and applications and found that (i) many vocabularies don't use concept schemes and (ii) identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} can also negatively affect use cases such as auto-completion, which proposes labels based on the user input.
+% Function defintion
+Thus, we generalize this statement and define a function $lc$ that finds all concept pairs with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} property values meeting a certain similarity threshold defined by a function $sim:ULV \times ULV \rightarrow [0,1]$.
 The default, built-in similarity function checks for case-insensitive string equality with a threshold equal to 1.
-This criterion is calculated by iterating over all pairs of concepts, i.e., elements of $C \times C$, applying $sim$ to every possible label combination, and collecting those pairs for which $sim$ meets or exceeds a specified threshold.
+The function iterates over all concept pairs $C \times C$, applies $sim$ to every possible label combination, and collects those pairs with at least one label combination that meet or exceed a specified similarity threshold.
 

### 2012-03-22 background.tex

@@
 Interoperability between applications has been the major motivation for specifying in total six \textbf{SKOS integrity conditions}~\cite{Miles2005}, each of which is a statement that defines under which circumstances data are consistent with the SKOS data model.
-An example condition is ``a resource has no more than one value of skos:prefLabel per language tag''.
-Tools that can check whether these integrity conditions are met for given data are already available: two of the six integrity conditions are defined formally in the OWL representation of SKOS and can therefore be validated by any OWL reasoner \todo{CM}{true?}.
+An example condition is ``a resource has no more than one value of \texttt{skos:prefLabel} per language tag''.
+Tools that can check whether these integrity conditions are met for given data are already available: two of the six integrity conditions are defined formally in the OWL representation of SKOS and can therefore be validated by any OWL reasoner.
 For validating a SKOS vocabulary against the integrity conditions, one can use tools such as the online \textbf{PoolParty Thesaurus Consistency Checker}, or the \textbf{Skosify} command line utility, which can validate SKOS vocabularies and also correct some detected quality problems.
@@
 Typical application areas of controlled vocabularies are as classification, indexing, autocompletion, query reformulation/expansion, or serving as a glossary.
-As we discussed in detail in our earlier work [\ref{CM}{iSem paper?}], these application areas have specific requirements with respect to vocabulary features, such as structure, availability, and documentation of conceptual resources.
+As we discussed in detail in our earlier work \cite{Nagy2011}, these application areas have specific requirements with respect to vocabulary features, such as structure, availability, and documentation of conceptual resources.
 A vocabulary that doesn't fulfill these requirements can have a negative effect on an application's output and would therefore be judged by the application designers and potentially also by users as being a low-quality vocabulary.
@@
 Missing entry points to concepts in a vocabulary can impede orientation for human users.
-Inconsistent relations can hinder queries across distinct datasets\todo{cm}{this example is unclear}, to name some examples.
+Proprietary term definitions can hinder queries across distinct datasets, to name some examples.
 
@@
 Thus, in order to help vocabulary and application designers in judging the quality of SKOS vocabularies, we need higher-level quality criteria that go beyond low-level integrity conditions defining data model consistency.
-Such quality criteria are already well-established and have extensively been discussed in standardized guidelines [\todo{CM}{ISO refs}], manuals [\todo{CM}{hedden book, skosify ref 3}], and scholarly articles [\todo{cm}{e.g., skosify refs 16/17}].
+Such quality criteria are already well-established and have extensively been discussed in standardized guidelines \cite{ISO25964-1:2011,Z39.19:2005}, manuals \cite{Hedden2010,Aitchison2000,Harpring2010}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002}.
+
+%Whilst aformentioned literature also deals with online vocabulary publication and interoperability \cite{ISO25964-1:2011,Hedden2010}, covering requirements for publication on the Web of Data (as in, e.g., \cite{Heath2011,Hogan2010,Allemang2011}) goes beyond their scope.
+%On the other hand, publications targeting dataset and ontology development for the Web of Data don't elaborate on implications of the design decisions for controlled vocabularies.
+Our work seeks to narrow this gap by...
+
 % TODO: bitte hier einfach nur die referenzen auf die wir uns beziehen zusammenfassen und kategorisieren. Schau dir dazu auch nochmals die SKOSify referenzen und die aus eurem iSemantics paper an.
+
 If we want check existing SKOS vocabularies against these criteria, we first need to identify them and determine how to evaluate them given the syntax, structure and semantics of SKOS.

### 2012-03-22 introduction.tex

--- 2012-03-20 introduction.tex
@@
 
-	\item We identified \todo{CM}{XX} \textbf{quality criteria} for SKOS vocabularies by examining existing guidelines and formalized them into computable \textbf{filtering functions} that identify possibly affected resources in a given SKOS vocabulary.
+	\item We identified 15 \textbf{quality criteria} for SKOS vocabularies by examining existing guidelines and formalized them into computable \textbf{quality checking functions} that identify possibly affected resources in a given SKOS vocabulary.
 

### 2012-03-22 background.tex
contd. with structural criteria

@@
 
-Typical application areas of controlled vocabularies are as classification, indexing, autocompletion, query reformulation/expansion, or serving as a glossary.
+Typical application areas of controlled vocabularies are classification, indexing, autocompletion, query reformulation/expansion, or serving as a glossary.
 As we discussed in detail in our earlier work \cite{Nagy2011}, these application areas have specific requirements with respect to vocabulary features, such as structure, availability, and documentation of conceptual resources.

### 2012-03-22 criteria.tex
contd. with structural criteria

@@
 % Origin and rationale
-Soergel et al.~\cite{Soergel1997} point out that ``the problem that has bedeviled many developers of multilingual thesauri is that a concept lexicalized in one language may not be lexicalized in another...''.
-In the context of SKOS, this means that the set of language tags used by the literal values linked with a concept should be the same for all concepts.
+Soergel et al.~\cite{Soergel1997} point out the problem that ``...a concept lexicalized in one language may not be lexicalized in another and that the terms do exist often vary slightly in meaning, possibly giving rise to different relationships.'' As a consequence, for such cases the authors suggest revising the vocabulary structure and ``clearly instruct indexers in all languages how the term is to be used''.
+In the context of SKOS, this means that the set of language tags used by the literal values linked with a concept should be checked to be the same for all concepts.
+If this is not true for a vocabulary, appropriate actions like, e.g., splitting concepts or introducing scope notes should be taken by the creators.
 This is particularly important for applications that rely on internationalization and translation use cases.
@@
 % Function defintion
-Thus, we generalize this statement and define a function $lc$ that finds all concept pairs with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} property values meeting a certain similarity threshold defined by a function $sim:ULV \times ULV \rightarrow [0,1]$.
+Thus, we generalize this statement and define a function $lc$ that finds all concept pairs with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} property values meeting a certain similarity threshold defined by a function $sim:LV \times LV \rightarrow [0,1]$.
 The default, built-in similarity function checks for case-insensitive string equality with a threshold equal to 1.
@@
 
-\subsection{Structural Criteria}
+\subsection{Structural Issues}
 
-The commonality of the following criteria is that they identify possible weaknesses when $V$ is used in scenarios exploiting the structure of its RDF graph.
+The commonality of the following issues is that they can affect applications areas that exploit the underlying graph structure of a SKOS vocabulary.
 
-\paragraph{\textbf{QF 5: Loose Concepts}} \todo{BH}{rename this to Orphan Concepts?}
+\paragraph{QI 5: Orphan Concepts}
 
-This quality function is motivated by the notion of ``orphan terms'' in the literature~\cite{Hedden2010}, which are are terms without any associative or hierarchical relationships.
-Checking for them is common in existing thesaurus development applications and also suggested by \cite{Z39.19:2005}.
-All vocabularies expressed in SKOS are concept-centric, thus we understand a loose concept is a concept that has no semantic relations with other conceptual resources i.e.
-it does not occur in any of the pairs yielded by $SR$.
-Although they might have attached lexical labels, they lack valuable context information that is considered essential for, e.g., search query expansion.
-Calculation can be done by iterating over all elements in $C$, filtering those not having a semantic relation to any other conceptual resource.
+% Origin and rationale
+This issue is motivated by the notion of ``orphan terms'' in the literature (cf.,~\cite{Hedden2010}), which are are terms without any associative or hierarchical relationships.
+Checking for such terms is common in existing thesaurus development applications and also suggested by~\cite{Z39.19:2005}.
+Since SKOS is concept-centric, we understand an orphan concept as being a concept that has no semantic relation $sr \in SR$ with any other concept.
+Although it might have attached lexical labels, it lacks valuable context information, which can be essential for retrieval tasks such as search query expansion.
+% Function defintion
+In order to find orphan concepts in a SKOS vocabulary, we define a function $oc$ that iterates over all elements in $C$, filtering those not having a semantic relation to any other conceptual resource in $C$.
 
-% \begin{definition}
-% Let \(G_{lc} = (C, SR)\) and \(deg(c)\) be the degree, hence the number of in- and outgoing edges, of a node $c \in C$ in the graph $G_{lc}$.
-We can then define loose concepts as a function \(lc : G \rightarrow \mathbb{N}_{0}\), with \[lc(g) = \left|\left\{c \in C : deg(c) = 0\right\}\right|\]
-% \end{definition}
+\paragraph{QI 6: Weakly Connected Components}
 
-\paragraph{\textbf{QF 6: Weakly Connected Components}} indicate that the vocabulary is split into separate ``clusters''.
-Presence of several WCC might be caused by incomplete data acquisition, ``forgotten'' test data, outdated terms, accidental deletion of relations and the like.
-In a practical setting, existence of weakly connected components could render the vocabulary less suitable for operations that rely on navigating a connected vocabulary structure, such as query expansion or suggestion of related terms.
-To calculate WCC, we create an undirected graph whose set of nodes constitutes all non-loose concepts and whose edges are defined by $SR$.
-We then utilize ``Tarjan’s algorithm''\cite{Hopcroft1973} that finds all connected components of the graph, i.e.
-all sets of conceptual resources that can reach each other by a path of semantic relations.
+% Origin and rationale
+indicate that a vocabulary is split into separate ``clusters'', which can be caused by incomplete data acquisition, ``forgotten'' test data, outdated terms, accidental deletion of relations, etc.
+This can affect operations that rely on navigating a connected vocabulary structure, such as query expansion or suggestion of related terms.
+% Function defintion
+In order to find weakly connected components, we define a function $wcc$, which first creates an undirected graph having all non-orphan concepts (as defined above) as nodes and all semantic relations $SR$ as edges.
+It then applies ``Tarjan’s algorithm''~\cite{Hopcroft1973} to find all connected components, hence all sets of concepts that are connected by semantic relations.
 
-% \begin{definition}
-% To evaluate this criterion we consider a graph \(G_{wcc} = (C - lc(G_{lc}), SR)\).
-The function \(components(g) : G \rightarrow  \mathfrak{P}(G)\) calculates all weakly connected components of a graph by replacing all directed edges by undirected edges and utilizing “Tarjan’s algorithm” \cite{Hopcroft1973}.
-Based on that function, we can express this criterion as a function \(wcc : G \rightarrow \mathbb{N}_{0}\), with \[wcc(g) = \left|components(g)\right|\]
-% \end{definition}
+\paragraph{QI 7: Cyclic Hierarchical Relations}
 
-\paragraph{\textbf{QF 7: Cyclic Hierarchical Relations}} have been mentioned numerous times in thesaurus development literature.
-\cite{Soergel2002} suggests a ``check for hierarchy cycles" since they ``throw the program for a loop in the generation of a complete hierarchical structure''.
-However, SKOS does not define a formal constraint regarding hierarchy cycles but \cite{SkosReference2008} mentions them as potential problems.
-The SKOS documentation also does not state, how exactly hierarchical relationships are to be interpreted.
-There exist common forms like, e.g., ``generic-specific'', ``instance-of'' or ``whole-part'' \cite{Hedden2010,Harpring2010,Aitchison2000} where cycles would be considered a logical contradiction.
-To calculate this criterion, we construct two graphs, with the set of nodes being $C$.
-The edges in one graph only point towards the broader concepts, the edges of the other graph point towards the narrower concepts.
-For each graph we now identify those nodes that are part of a cycle and return the set of strongly connected components they are contained in.
+% Origin and rationale
+is a quality issue motivated by Soergel et al.~\cite{Soergel2002} who suggest a ``check for hierarchy cycles'' since they ``throw the program for a loop in the generation of a complete hierarchical structure''.
+Also Hedden~\cite{Hedden2010}, Harpring~\cite{Harpring2010} and Aitchison et al.~\cite{Aitchison2000} argue that there exist common forms like, e.g., ``generic-specific'', ``instance-of'' or ``whole-part'' where cycles would be considered a logical contradiction.
+% Function defintion
+We provide a function $chr$, which finds cyclic relations by constructing a graph with the set of nodes being $C$ and the set of edges being $\{s \in SR | s = skos:broader\}$ relations.
+It then identifies the sets of nodes that are involved in cycles.
+Since all function operate on the entailed RDF graph, this algorithm implicitly also considers \texttt{skos:narrower} relations.
 
-%Erkärung: ein knoten (konzept) liegt oft in vielen überlappenden kreisen und es würde keinen sinn machen, diese alle auszugeben.
-deshalb berechne ich mir von jedem knoten der in einem kreis liegt, in welcher starken zusammenhangskomponente er liegt.
-das sind dann per definition alle knoten, die mit irgendeinem kreis in dem das konzept liegt was zu tun haben, weil eine starke zusammenhangskomponente ja eigentlich nur aus kreisen besteht (von jedem knoten gibt es einen gerichteten weg zu jedem anderen knoten)
+\paragraph{QI 8: Valueless Associative Relations}
 
-% \begin{definition}
-% Let \(H_{br} \subseteq SR\) be the set of pairs of hierarchically broader related resources, i.e.
-\(I_{EXT}(\texttt{skos:broader}^\mathcal{I}) \cup I_{EXT}(\texttt{skos:broaderTransitive}^\mathcal{I}) \cup I_{EXT}(\texttt{skos:broadMatch}^\mathcal{I})\).
-\(H_{br}\) also includes the extensions of the respecitive inverse properties with each pair in reverse order.
-Likewise, \(H_{nar} \subseteq SR\) can be defined as the set of hierarchically narrower related resources.
-We consider two graphs \(G_{br} = (C,H_{br})\) and \(G_{nar}=(C,H_{nar})\) and a function \(cycleNodes:G \rightarrow \mathfrak{P}(C)\) identifying all nodes in a graph, that are part of a cycle.
-Furthermore we consider a function \(stronglyConnectedSets: G \rightarrow \mathfrak{P}(C)\) that calculates all sets of nodes contained in a strongly connected subgraph of $G$.
-This criterion can be defined as a function \(chr:G \rightarrow \mathbb{N}_{0}\) with \[chr(g)=\left|\left\{s \in stronglyConnectedSets(g) : cn \in cycleNodes(g), cn \in s\right\}\right|\]
-% \end{definition}
-
-\paragraph{\textbf{QF 8: Valueless Associative Relations}}
-The ISO/DIS 25964-1 standard suggests that terms that share a common broader term but do not have an overlapping meaning, should not be related associatively.
+% Origin and rationale
+The ISO/DIS 25964-1 standard~\todo{CM}{ref} suggests that terms that share a common broader term but do not have an overlapping meaning, should not be related associatively.
 This is also advocated by \cite{Hedden2010} and \cite{Aitchison2000} who also mentions ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships'', having a negative effect on precision.
+% Origin and rationale
 This function identifies a set of pairs of conceptual resources that share the same broader or narrower concept while also being associatively related by the property \texttt{skos:related}.
@@
 \paragraph{\textbf{QF 9: Solely Transitively Related Concepts}}
+
 Two concepts are related using only transitive hierarchical relations which are, according to \cite{SkosReference2008}, ``not used to make assertions''.

### 2012-03-22 criteria.tex
rephrased quality issues

@@
 % Function defintion
-We provide a function $chr$, which finds cyclic relations by constructing a graph with the set of nodes being $C$ and the set of edges being $\{s \in SR | s = skos:broader\}$ relations.
+We provide a function $chr$, which finds cyclic relations by constructing a graph with the set of nodes being $C$ and the set of edges being $I_{EXT}(\texttt{skos:broader}^\mathcal{I})$, i.e.
+all pairs of resources connected by \texttt{skos:broader} relations.
 It then identifies the sets of nodes that are involved in cycles.
-Since all function operate on the entailed RDF graph, this algorithm implicitly also considers \texttt{skos:narrower} relations.
+
+%Since all function operate on the entailed RDF graph, this algorithm implicitly also considers \texttt{skos:narrower} relations. CM: ist eigentlich aus def1 klar denke ich
 
@@
 % Origin and rationale
-The ISO/DIS 25964-1 standard~\todo{CM}{ref} suggests that terms that share a common broader term but do not have an overlapping meaning, should not be related associatively.
-This is also advocated by \cite{Hedden2010} and \cite{Aitchison2000} who also mentions ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships'', having a negative effect on precision.
+The ISO/DIS 25964-1 standard \cite{ISO25964-1:2011} suggests that terms that share a common broader term but do not have an overlapping meaning, should not be related associatively.
+This is advocated by \cite{Hedden2010,Aitchison2000} the latter also mentioning ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships'', having a negative effect on precision.
+% Function defintion
+The function \textit{var} identifies a set of pairs of conceptual resources that share the same broader or narrower concept while also being associatively related by the property \texttt{skos:related}.
+
+\paragraph{QI 9: Solely Transitively Related Concepts}
 % Origin and rationale
-This function identifies a set of pairs of conceptual resources that share the same broader or narrower concept while also being associatively related by the property \texttt{skos:related}.
+Two concepts that are \textbf{explicitly} related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} can be regarded a quality issue because, according to \cite{SkosReference2008}, they are ``not used to make assertions''.
+Transitive hierarchical relations in SKOS are meant to be infered by the vocabulary \textbf{consumer}, which is reflected in the SKOS schema by, e.g., \texttt{skos:broader} being a subproperty of \texttt{skos:broaderTransitive}.
+% Function definition
+This fuction \textit{strc} iterates over all pairs of concepts $C \times C$ that are directly related by the mentioned transitive properties, not by one of their subproperties.
 
-\paragraph{\textbf{QF 9: Solely Transitively Related Concepts}}
-
-Two concepts are related using only transitive hierarchical relations which are, according to \cite{SkosReference2008}, ``not used to make assertions''.
-Transitive hierarchical relations in SKOS are meant to be infered by the vocabulary user, which is reflected in the SKOS schema by, e.g., \texttt{skos:broader} being a subproperty of \texttt{skos:broaderTransitive}.
-This fuction iterates over all pairs of concepts $C \times C$ that are \textbf{explicitly} related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive}, i.e.
-\textbf{without} RDFS subproperty entailment.
-
-\paragraph{\textbf{QF 10: Omitted Top Concepts}}
+\paragraph{QI 10: Omitted Top Concepts}
+% Origin and rationale
 The SKOS language provides concept schemes, which are a facility for grouping related concepts.
@@
 This helps to provide ``efficient access''~\cite{Isaac2009} and simplifies orientation in the vocabulary.
-To calculate this function, we iterate over all \texttt{skos:ConceptScheme}s in $V$ and collect those that occur in relations established by the properties \texttt{skos:hasTopConcept} or \texttt{skos:topConceptOf}.
+% Function definition
+We provide a function \textit{otc} that iterates over all \texttt{skos:ConceptScheme}s in $V$ and collects those that do not occur in relations established by the properties \texttt{skos:hasTopConcept} or \texttt{skos:topConceptOf}.
 
-\paragraph{\textbf{QF 11: Top Concept Having Broader Concepts}}
-\cite{Allemang2011} proposes to ``not indicate any concepts internal to the tree as top concepts'', i.
-e.
-top concepts should not have broader concepts.
-This criteria iterates over all \texttt{skos:TopConcept}s defined in $V$ and collects those that are related to a resource by the \texttt{skos:broader} property.
+\paragraph{QI 11: Top Concept Having Broader Concepts}
+% Origin and rationale
+Allemang et al. \cite{Allemang2011} propose to ``not indicate any concepts internal to the tree as top concepts'', i. e. top concepts should not have broader concepts. 
+% Function definition
+The function \textit{tchbc} iterates over all \texttt{skos:TopConcept}s defined in $V$ and collects those that are related to a resource by the \texttt{skos:broader} property.
 
-% LINKED-DATA SPECIFIC CRITERIA
+% LINKED-DATA SPECIFIC ISSUES
 
-\subsection{Linked Data Specific Criteria}
+\subsection{Linked Data Specific Issues}
 
-This section identifies criteria related to a vocabulary's interaction with other datasets in the LOD cloud.
+This section identifies issues related to a vocabulary's interaction with other datasets in the LOD cloud.
 
-\subsubsection{Missing In-Links}
+\paragraph{QI 12: Missing In-Links}
+% Origin and rationale
 A periodically updated version of a diagram visualizing ``the data sets in the LOD cloud as well as their interlinkage relationships'' is publised online\footnote{\url{http://www4.wiwiss.fu-berlin.de/lodcloud/state/}}.
@@
 A method to carry out these estimations would be utilizing existing Linked Data indices like, e.g., Sindice\footnote{\url{http://sindice.com/}} that provide a SPARQL endpoint.
-In order to estimate the number of In-Links for a conceptual resource, we iterate over all elements in $C$ and query the Sindice SPARQL endpoint for triples containing the concept's URI in the object part.
-Those concepts having an empty query result, are missing any In-Links and are thus included in the result set of this criterion.
+% Function definition
+The function \textit{mil} estimates the number of In-Links for a conceptual resource, by iterating over all elements in $C$ and querying the Sindice SPARQL endpoint for triples containing the concept's URI in the object part.
+Those concepts having an empty query result, are missing any In-Links and are thus included in the result set of this issue.
 
-\subsubsection{Missing Out-Links}
+\paragraph{QI 13: Missing Out-Links}
+% Origin and rationale
 The Web of Data consists of globally interconnected datasets, ``enabling seamless connections between data sets''\cite{Heath2011}.
 These links can be established between various SKOS vocabularies by Out-Links, i.e., references from conceptual resources in the ``source vocabulary'' $V$ to resources identified by an HTTP URI and available at a different host.
-Similar to the criterion above, this criterion identifies the set of all conceptual resources that lack such Out-Links.
-Calculation of the result set is done by iterating over all elements $c \in C$ and investigating the host part of all related resources.
-If none of these host names differ from the host part of $c$, it has no Out-Links and is thus included into the resources identified by this criterion.
+Similar to QI 12, this issue identifies the set of all conceptual resources that lack such Out-Links.
+% Function definition
+We provide the function \textit{mol} that iterates over all elements $c \in C$ and investigates the host part of all related resources.
+If none of these host names differ from the host part of $c$, it has no Out-Links and is thus included into the resources identified by this issue.
 
-%\subsubsection{HTTP URI Schema Violation}\todo{All}{We don't have any evidence this really happens in existing vocabularies, although it is very likely. Maybe we should skip this.}
-
-\subsubsection{Link Target Unavailability} \todo{BH}{should we just call this "Broken Links" because that's essentially what it's all about}
+\subsubsection{QI 14: Link Target Unavailability} \todo{BH}{should we just call this "Broken Links" because that's essentially what it's all about}
+% Origin and rationale
 This criterion identifies a set of all resources that have been identified as unavailable, i.e.
@@
 Just as in the ``traditional'' Web, these ``broken links'' hinder information gathering and should be avoided.
+% Function definition
 Calculation of this criterion is performed by iterating over all resources in $IR$, performing an HTTP request and include those resources in the result set that are unavailable.

### 2012-03-22 criteria.tex
finished criteria

@@
 \subsection{Labeling and Documentation Issues}
-
-The following issues primarily focus on possible problems that might arise when human users work with a SKOS vocabulary or interact with a system that uses the vocabulary for, e.g., search and retrieval purposes.
 
@@
 
-The commonality of the following issues is that they can affect applications areas that exploit the underlying graph structure of a SKOS vocabulary.
-
 \paragraph{QI 5: Orphan Concepts}
@@
 
-%Since all function operate on the entailed RDF graph, this algorithm implicitly also considers \texttt{skos:narrower} relations. CM: ist eigentlich aus def1 klar denke ich
-
 \paragraph{QI 8: Valueless Associative Relations}
@@
 The ISO/DIS 25964-1 standard \cite{ISO25964-1:2011} suggests that terms that share a common broader term but do not have an overlapping meaning, should not be related associatively.
-This is advocated by \cite{Hedden2010,Aitchison2000} the latter also mentioning ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships'', having a negative effect on precision.
+This is advocated by Hedden~\cite{Hedden2010} and Aitchison et al.~\cite{,Aitchison2000} who point out ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships'', having a negative effect on precision.
 % Function defintion
@@
 \paragraph{QI 9: Solely Transitively Related Concepts}
+
 % Origin and rationale
-Two concepts that are \textbf{explicitly} related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} can be regarded a quality issue because, according to \cite{SkosReference2008}, they are ``not used to make assertions''.
-Transitive hierarchical relations in SKOS are meant to be infered by the vocabulary \textbf{consumer}, which is reflected in the SKOS schema by, e.g., \texttt{skos:broader} being a subproperty of \texttt{skos:broaderTransitive}.
+Two concepts that are explicitly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} can be regarded a quality issue because, according to \cite{SkosReference2008}, they are ``not used to make assertions''.
+Transitive hierarchical relations in SKOS are meant to be inferred by the vocabulary consumer, which is reflected in the SKOS schema by, e.g., \texttt{skos:broader} being a subproperty of \texttt{skos:broaderTransitive}.
 % Function definition
-This fuction \textit{strc} iterates over all pairs of concepts $C \times C$ that are directly related by the mentioned transitive properties, not by one of their subproperties.
+We encode this issue in a function \textit{strc} that iterates over all concept pairs $C \times C$ that are directly related by the mentioned transitive properties, not by one of their subproperties.
+
+% TODO CM: it is unclear what "mentioned" means in this context...
 
 \paragraph{QI 10: Omitted Top Concepts}
+
 % Origin and rationale
 The SKOS language provides concept schemes, which are a facility for grouping related concepts.
+This helps to provide ``efficient access''~\cite{Isaac2009} and simplifies orientation in the vocabulary.
 In order to provide entry points to such a group of concepts, one or more concepts can be marked as top concepts.
-This helps to provide ``efficient access''~\cite{Isaac2009} and simplifies orientation in the vocabulary.
 % Function definition
@@
 \paragraph{QI 11: Top Concept Having Broader Concepts}
+
 % Origin and rationale
-Allemang et al. \cite{Allemang2011} propose to ``not indicate any concepts internal to the tree as top concepts'', i. e. top concepts should not have broader concepts. 
+Allemang et al. \cite{Allemang2011} propose to ``not indicate any concepts internal to the tree as top concepts'', which means that top concepts should not have broader concepts. 
 % Function definition
@@
 
-This section identifies issues related to a vocabulary's interaction with other datasets in the LOD cloud.
+\paragraph{QI 12: Missing In-Links}
 
-\paragraph{QI 12: Missing In-Links}
 % Origin and rationale
-A periodically updated version of a diagram visualizing ``the data sets in the LOD cloud as well as their interlinkage relationships'' is publised online\footnote{\url{http://www4.wiwiss.fu-berlin.de/lodcloud/state/}}.
-In these diagrams, DBpedia is shown as the most intensely linked resource, i.e.
-a large number of vocabularies link to resources in that dataset.
-This indicates that a dataset with a large number of other datasets referencing it, can be assumed to be of great value for the community, adding cohesion to the LOD cloud.
-Accordingly, estimating the number of In-Links of SKOS concepts defined in a vocabulary (henceforth called the in-degree of a concept) gives some hint about how established or accepted a controlled vocabulary is.
-A method to carry out these estimations would be utilizing existing Linked Data indices like, e.g., Sindice\footnote{\url{http://sindice.com/}} that provide a SPARQL endpoint.
+SKOS concepts become linkable resources, when vocabularies are being published on the Web.
+Estimating the number of in-links and identifying the concepts without any in-links, can be an important indicator for the importance of a concept.
+The required in-links for such an estimation can be obtained from existing Linked Data indices like, e.g., Sindice\footnote{\url{http://sindice.com/}}.
 % Function definition
-The function \textit{mil} estimates the number of In-Links for a conceptual resource, by iterating over all elements in $C$ and querying the Sindice SPARQL endpoint for triples containing the concept's URI in the object part.
-Those concepts having an empty query result, are missing any In-Links and are thus included in the result set of this issue.
+The function \textit{mil} estimates the number of in-links referencing a concept, by iterating over all elements in $C$ and querying the Sindice SPARQL endpoint for triples containing the concept's URI in the object part.
+Empty query results are indicator for missing  in-links and are thus included in the result set of this function.
 
 \paragraph{QI 13: Missing Out-Links}
+
 % Origin and rationale
-The Web of Data consists of globally interconnected datasets, ``enabling seamless connections between data sets''\cite{Heath2011}.
-These links can be established between various SKOS vocabularies by Out-Links, i.e., references from conceptual resources in the ``source vocabulary'' $V$ to resources identified by an HTTP URI and available at a different host.
-Similar to QI 12, this issue identifies the set of all conceptual resources that lack such Out-Links.
+In the Linked Data context SKOS concepts should be linked with other related concepts on the Web, ``enabling seamless connections between data sets''\cite{Heath2011}.
+Similar to \emph{Missing In-Links}, this issue identifies the set of all conceptual resources that have no out-links.
 % Function definition
-We provide the function \textit{mol} that iterates over all elements $c \in C$ and investigates the host part of all related resources.
-If none of these host names differ from the host part of $c$, it has no Out-Links and is thus included into the resources identified by this issue.
+We provide the function \textit{mol} that iterates over all elements $c \in C$ and investigates \todo{CM}{mapping relations?} the host part of all related resource URIs.
+If none of these host names differ from the host part of $c$'s URI, it has no out-links and is thus included in the resources identified by this issue.
 
-\subsubsection{QI 14: Link Target Unavailability} \todo{BH}{should we just call this "Broken Links" because that's essentially what it's all about}
+\paragraph{QI 14: Broken Links}
+
 % Origin and rationale
-This criterion identifies a set of all resources that have been identified as unavailable, i.e.
-resolving their URI leads to an erroneous HTTP response or no response at all.
-An erroneous HTTP response in that case can be defined as a response code (after a possible redirection) other than 200.
-Just as in the ``traditional'' Web, these ``broken links'' hinder information gathering and should be avoided.
+This issue identifies vocabulary resources that return HTTP error responses or no response when being dereferenced.
+An erroneous HTTP response in that case can be defined as a response code other than 200 when taking possible redirections into account.
+Just as in the ``document'' Web, these ``broken links'' hinder navigability also in the Linked Data Web and and should therefore be avoided.
 % Function definition
-Calculation of this criterion is performed by iterating over all resources in $IR$, performing an HTTP request and include those resources in the result set that are unavailable.
+Broken links are identified by a function $bl$, which iterates over all resources in $IR$, dereferences each resource, follows possible redirects, and includes unavailable resources in the result set.
 
-% OTHER CRITERIA
+\paragraph{QI 15: Undefined SKOS Resources}
 
-\subsection{Other Criteria}
-
-\subsubsection{Undefined SKOS Resource Usage}
-Some vocabularies reference resources in the SKOS namespace that cannot be resolved.
-A common reason for this is, that there seems to exist a misunderstanding about the correct way of introducing new classes or properties in an OWL document.
-In some cases, vocabularies ``invent'' new terms in the SKOS namespace in order to meet certain requirements of the publishing organizations that cannot (yet) be expressed within the SKOS schema.
-Another reason for the presence of unresolvable resource references in the SKOS namespace is that the vocabulary might be outdated.
-With the SKOS W3C recommendation maturing, some properties have been removed from the current version of the schema.
-Vocabularies using these ``deprecated'' properties hence contain parts of their information in a non ``standard"-compliant way, having negative effects when, e.g., crawling vocabularies to gather specific information.
-A method to identify these undefined SKOS resources is to iterate over all resources in $IR$, including (i) those resources in the resulting set that are contained in the list of deprecated resources or (ii) have an URI in the SKOS namespace but are not defined in the SKOS ontology.
+% Origin and rationale
+SKOS defines a set of classes and properties, hence resources within the namespace \url{http://www.w3.org/2004/02/skos/core#}, for building controlled vocabularies.
+However, some vocabularies use resources from within this namespace, which are unresolvable for two main reasons: vocabulary creators ``invented'' new terms within the SKOS namespace instead of introducing them in a separate namespace, or they use ``deprecated'' SKOS properties.
+% Function definition
+In order to identify such undefined SKOS resources, we define a function $usr$  that iterates over all resources in $IR$ and returns those resources (i) that are contained in the list of deprecated resources or (ii) are identified by a URI in the SKOS namespace but are not defined in the current version of the SKOS ontology.

### 2012-03-22 main.tex
updated abstract

@@
 
-The Simple Knowledge Organization System (SKOS) has become a standard model for controlled Web vocabularies.
-However, SKOS vocabularies are often heterogeneous in terms of quality, which reduces their applicability across system boundaries.
-Here we investigate how we can support taxonomists in judging the quality of SKOS vocabularies by quality criteria that go beyond the low-level data model integrity constraints defined in the SKOS specification.
-We identified existing \textbf{quality criteria}, formalized them into computable \textbf{quality checking functions} that identify affected resources in a given SKOS vocabulary.
-We implemented these functions in the qSKOS quality assessment tool, analyzed \todo{CM}{XX} existing vocabularies and found possible quality issues in \todo{CM}{YY} vocabularies.
+The Simple Knowledge Organization System (SKOS) has become a standard model for controlled vocabularies on the Web.
+However, SKOS vocabularies often differ in terms of quality, which reduces their applicability across system boundaries.
+Here we investigate how we can support taxonomists in improving the quality of SKOS vocabularies by pointing out quality issues that go beyond the integrity constraints defined in the SKOS specification.
+We identified possible \textbf{quality issues} and formalized them into computable \textbf{quality checking functions} that can find affected resources in a given SKOS vocabulary.
+We implemented these functions in the qSKOS quality assessment tool, analyzed 15 existing vocabularies, and found possible quality issues in all of them.
 

### 2012-03-22 analysis.tex
added missing wcc analysis numbers
added all criteria to table to better estimate space left
added comments/updated result table
added TODO

@@
 \subsection{Vocabulary Data Set}
+
 Our vocabulary dataset covers XY vocabularies from various domains differing in statistical properties (cf.
@@
 We also informed the AGROVOC team about this problem, which will try to fix it.
+
+\todo{CM}{skip domain classification; this looks inconsistent and takes space.}
 
@@
 \toprule
+Omitted or Invalid Language Tags &&&&&&&&&&&&&&& \\
+
+Incomplete Language Coverage &&&&&&&&&&&&&&& \\
+
+Undocumented Concepts &&&&&&&&&&&&&&& \\
+
+Label Conflicts &&&&&&&&&&&&&&& \\
+
+\midrule
+
 Loose Concepts & 162000 & 671 & 0 & 2 & 7 & 0 & 0 & 77062 & 1125 & 4979 & 172364 & 0 & 4 & 0 & 21 \\
-Weakly Connected Components & 621 & 0 & & & 4 & 1 & 4 && 0 & 0 && 5 & 1 & 1 & 11 \\
+
+Weakly Connected Components & 621 & 0 & & 10 & 4 & 1 & 4 & 1506 & 0 & 0 & 22131 & 5 & 1 & 1 & 11 \\
+
+Cyclic Hierarchical Relations &&&&&&&&&&&&&&& \\
+
+Valueless Associative Relations &&&&&&&&&&&&&&& \\
+
+Solely Transitively Related Concepts &&&&&&&&&&&&&&& \\
+
+Omitted Top Concepts &&&&&&&&&&&&&&& \\
+
+Top Concept Having Broader Concepts &&&&&&&&&&&&&&& \\
+
+\midrule
+
+Missing In-Links &&&&&&&&&&&&&&& \\
+
+Missing Out-Links &&&&&&&&&&&&&&& \\
+
+Link Target Unavailability &&&&&&&&&&&&&&& \\
+
+\midrule
+
+Undefined SKOS Property Usage &&&&&&&&&&&&&&& \\
+
 \bottomrule

### 2012-03-22 criteria.tex
updated intro

@@
 The ISO/DIS 25964-1 standard \cite{ISO25964-1:2011} suggests that terms that share a common broader term but do not have an overlapping meaning, should not be related associatively.
-This is advocated by Hedden~\cite{Hedden2010} and Aitchison et al.~\cite{,Aitchison2000} who point out ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships'', having a negative effect on precision.
+This is advocated by Hedden~\cite{Hedden2010} and Aitchison et al.~\cite{Aitchison2000} who point out ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships'', having a negative effect on precision.
 % Function defintion

### 2012-03-22 introduction.tex
updated intro

@@
 
-% Note: I am still having problems to imagine why and how one would implement query expansion based on the DBPedia categories...as long as this is not clear, better skip the example.
-% mein fantasie-szenario ist folgendes: jmd hat einen korpus an dokumenten und will diesen nach kategorien indizieren.
-also sucht man ein existierendes vocab das man verwenden könnte (irgendwelche subject headings oder eben die dbpedia kategorien weil die eben schon in SKOS verfügbar sind und dbpedia sowieso das zentrum der ld-welt darstellt :).
-Also verschlagwortet man den dokumentkorpus mit dbpedia-categories und kommt dann, aufgrund der loose concepts drauf, dass dokumente die in ähnliche kategorien (broader/narrower) fallen, nicht gefunden werden können, also den recall verschlechtern.
-ist das unrealistisch?
-
     % \item In the DBpedia category\footnote{\url{http://downloads.dbpedia.org/3.7/en/skos_categories_en.nt.bz2}} hierarchy, more than 10 percent of the categories not linked to any other category.
@@
 Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to verify that a given vocabulary fulfills these conditions.
-However, these conditions fail to capture \textbf{quality criteria} such as those mentioned in the examples before; criteria that go beyond integrity conditions of the SKOS data model.
-Such criteria might be part of design rules and guidelines, but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger, possibly linked Web vocabularies.
+However, these conditions fail to capture quality aspects such as those mentioned in the examples before, aspects that go beyond integrity conditions of the SKOS data model.
+Existing guidelines manuals consider these aspects but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger, possibly linked vocabularies on the Web.
 
@@
 
-The goal of our work is to help taxonomists in judging the quality of SKOS vocabularies, by giving them a set of computable quality criteria that can identify possible quality issues and serve as quantitative indicator for the quality of a given SKOS vocabulary.
-In combination with the taxonomists' experience and domain expertise, these criteria provide important feedback to the overall vocabulary design process.
+The goal of our work is to help taxonomists in identifying possible quality issues, which go beyond data model integrity conditions, in SKOS vocabularies.
+We want to given them a set of computable quality checking functions that, in combination with the taxonomists' experience and domain expertise, can serve as quality indicators for vocabularies.
+We believe that finding such quality issues also gives important feedback in the overall vocabulary design process.
 The main contributions of this work can be summarized as follows:
@@
 
-	\item We identified 15 \textbf{quality criteria} for SKOS vocabularies by examining existing guidelines and formalized them into computable \textbf{quality checking functions} that identify possibly affected resources in a given SKOS vocabulary.
+	\item We identified 15 \textbf{quality issues} for SKOS vocabularies by examining existing guidelines and formalized them into computable \textbf{quality checking functions} that identify possibly affected resources in a given SKOS vocabulary.
 
@@
 
-	\item We \textbf{analyzed} a representative set of \textbf{existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.
+	\item We \textbf{analyzed} a representative set of 15 \textbf{existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.
 

### 2012-03-23 analysis.tex
added numeric values in analysis tables

@@
 
-\todo{BH}{make clear that tool also provides reports not only numeric values}
+We implemented the qSKOS tool that can be used for computing the quality checking functions introduced in \ref{sec:criteria} and made it publicly available\footnote{\url{https://github.com/cmader/qSKOS/}}.
+All data in the Tables \ref{tab:vocs} and \ref{tab:results} have been obtained by utilizing this tool.
+However, qSKOS is not only capable of returning numeric values, but can also provide a detailed report listing all resources returned by the quality checking functions alongside with the potential cause of the issue.
 
@@
 
-Our syntactical checks showed that only the AGROVOC vocabulary contained invalid datatypes and characters.
-After some minor syntax modifications, which don’t influence the evaluation against our criteria, we were also able to include this vocabulary.
-We also informed the AGROVOC team about this problem, which will try to fix it.
-
-\todo{CM}{skip domain classification; this looks inconsistent and takes space.}
-
 \begin{table}[h]
+\label{tab:vocs}
 \caption{Analyzed vocabularies}
-\begin{tabular}{lp{4.7cm}cccccc}
-\textbf{Domain} & \textbf{Vocabulary} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Lexical Rel.}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
+\centering
+\begin{tabular}{p{6cm}ccccccc}
+\textbf{Vocabulary} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
 \toprule
-Media & Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
+Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & ? & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
 \hline
-Science & Geonames Ontology & 671 & 671 & 0 & 671 & 9 & 0 \\
+Geonames Ontology & ? & 671 & 671 & 0 & 671 & 9 & 0 \\
 \hline
-& Medical Subject Headings (MeSH) & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
+Medical Subject Headings (MeSH) & ? & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
 \hline
-& Peroxisome Knowledge Base (PXV) & 2112 & 3628 & 2695 & 1716 & 1 & 0 \\
+Peroxisome Knowledge Base (PXV) & ? & 2112 & 3628 & 2695 & 1716 & 1 & 0 \\
 \hline
-Government & Eurovoc & 6797 & 457788 & 18491 & 15512 & 128 & 0 \\
+Eurovoc & ? & 6797 & 457788 & 18491 & 15512 & 128 & 0 \\
 \hline
-& Integrated Public Sector Vocabulary (IPSV) & 4732 & 7945 & 13843 & 4483 & 3 & 0 \\
+Integrated Public Sector Vocabulary (IPSV) & ? & 4732 & 7945 & 13843 & 4483 & 3 & 0 \\
 \hline
-Publications & Agrovoc & 31993 & 572138 & 63936 & 32043 & 1 & 0 \\
+AGROVOC & 1.3 & 32035 & 620629 & 65934 & 32085 & 1 & 0 \\
 \hline
-& DBpedia Categories & 743410 & 740352 & 1490316 & 0 & 0 & 0 \\
+DBpedia Categories & ? & 743410 & 740352 & 1490316 & 0 & 0 & 0 \\
 \hline
-& University of Southampton Pressinfo & 1125 & 0 & 0 & 0 & 0 & 0 \\
+University of Southampton Pressinfo & 2011/02/24 & 1125 & 0 & 0 & 0 & 0 & 0 \\
 \hline
-& New York Times People (NYTP) & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
+New York Times People (NYTP) & 2010/06/22 & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
 \hline
-& Library of Congress Subject Headings (LCSH) & 459182 & 746076 & 595754 & 815816 & 19 & 0 \\
+Library of Congress Subject Headings (LCSH) & ? & 459182 & 746076 & 595754 & 815816 & 19 & 0 \\
 \hline
-Cross-domain & Meketre & 422 & 569 & 1698 & 6 & 2 & 0 \\
+Meketre & 2011/07/07 & 422 & 569 & 1698 & 6 & 2 & 0 \\
 \hline
-Economy & Thesaurus for Economics (STW) & 6524 & 31189 & 57907 & 6531 & 1 & 0 \\
+Thesaurus for Economics (STW) & 8.06 & 6524 & 31189 & 57907 & 6531 & 1 & 0 \\
 \hline
-& North American Industry Classification System (NAICS) & 4175 & 0 & 8684 & 2235 & 1 & 0 \\
+North American Industry Classification System (NAICS) & 2012 & 4175 & 0 & 8684 & 2235 & 1 & 0 \\
 \hline
-Military & Thesaurus Landesverteidigungsakademie (LVAk) & 13411 & 17250 & 16346 & 0 & 0 & 0 \\
+Thesaurus Landesverteidigungsakademie (LVAk) & n/a & 13411 & 17250 & 16346 & 0 & 0 & 0 \\
 \bottomrule
@@
 \begin{table}[h]
-\caption{Results of the proposed metrics}
+\label{tab:results}
+\caption{Results of the quality checking functions (cardinality of the result set)}
 \begin{tabular}{p{4cm}ccccccccccccccc}
@@
 \toprule
-Omitted or Invalid Language Tags &&&&&&&&&&&&&&& \\
+Omitted or Invalid Language Tags &&&&&&& 0 & tba & 1224 & 0 & tba & 0 & 2 & 0 & 13411 \\
 
-Incomplete Language Coverage &&&&&&&&&&&&&&& \\
+Incomplete Language Coverage &&&&&&& 32035 & tba & 0 & 0 & tba & 420 & 6456 & 0 & 0 \\
 
-Undocumented Concepts &&&&&&&&&&&&&&& \\
+Undocumented Concepts &&&&&&& 32035 & tba & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\
 
-Label Conflicts &&&&&&&&&&&&&&& \\
+Label Conflicts &&&&&&& 2949 & tba & 0 & 0 & tba & 4 & 5 & 0 & 13 \\
 
@@
 
-Loose Concepts & 162000 & 671 & 0 & 2 & 7 & 0 & 0 & 77062 & 1125 & 4979 & 172364 & 0 & 4 & 0 & 21 \\
+Orphan Concepts & 162000 & 671 & 0 & 2 & 7 & 0 & 0 & 77062 & 1125 & 4979 & 172364 & 0 & 4 & 0 & 21 \\
 
@@
 
-Link Target Unavailability &&&&&&&&&&&&&&& \\
+Broken Links &&&&&&&&&&&&&&& \\
 
@@
 
-Undefined SKOS Property Usage &&&&&&&&&&&&&&& \\
+Undefined SKOS Resources &&&&&&&&&&&&&&& \\
 

### 2012-03-23 criteria.tex
added numeric values in analysis tables

@@
 % Function defintion
-We can check a SKOS vocabulary for omitted and invalid language tags by defining a quality checking function $oilt$ that iterates over all resources in $IR$ and finds those that have relations to plain literals with missing or invalid language tags, hence tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
+We can check a SKOS vocabulary for omitted and invalid language tags by defining a quality checking function $oilt$ that iterates over all resources in $IR$ and finds those that have relations to plain literals (using the above mentions SKOS properties) with missing or invalid language tags, hence tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
 
@@
 % Function definition
-We provide the function \textit{mol} that iterates over all elements $c \in C$ and investigates \todo{CM}{mapping relations?} the host part of all related resource URIs.
+We provide the function \textit{mol} that iterates over all elements $c \in C$ and investigates the host part of all related resource URIs.
 If none of these host names differ from the host part of $c$'s URI, it has no out-links and is thus included in the resources identified by this issue.

### 2012-03-23 background.tex
first attempt for related work section

@@
 Thus, in order to help vocabulary and application designers in judging the quality of SKOS vocabularies, we need higher-level quality criteria that go beyond low-level integrity conditions defining data model consistency.
-Such quality criteria are already well-established and have extensively been discussed in standardized guidelines \cite{ISO25964-1:2011,Z39.19:2005}, manuals \cite{Hedden2010,Aitchison2000,Harpring2010}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002}.
+Such quality criteria are already well-established and have extensively been discussed in standardized guidelines \cite{ISO25964-1:2011,Z39.19:2005}, manuals \cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002}.
 

### 2012-03-23 criteria.tex
first attempt for related work section

@@
 % Function definition
-We encode this issue in a function \textit{strc} that iterates over all concept pairs $C \times C$ that are directly related by the mentioned transitive properties, not by one of their subproperties.
-
-% TODO CM: it is unclear what "mentioned" means in this context...
+We encode this issue in a function \textit{strc} that iterates over all concept pairs $C \times C$ that are directly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} properties and not by one of their subproperties.
 

### 2012-03-23 related_work.tex
first attempt for related work section

\section{Related Work}\label{sec:related_work}

The problem of ``vocabulary quality'' is closely related to the more general problem of “data quality”, which has intensively been discussed in data and information systems research. \cite{Pipino2002,Batini2009} argue that dealing with data quality should involve both “subjective perceptions of the individuals” and “objective measurements based on the data set in question”. We see our work as a contribution to the latter and believe that the results of SKOS quality measures must be combined with domain knowledge, and therefore human expertise, to make final quality judgements.

A vast number of publications in the field of designing, validating and testing controlled vocabularies is available. Many of them propose properties \cite{Soergel1995}, design guidelines \cite{Svenonius2003,...} or metrics \cite{Elkin2002,Kless2010} aiming to improve, e.g., retrieval precision and recall, consistency and multilinguality. The work is based on various sources like, e.g., review of existing vocabularies~\cite{Soergel1995} or survey-based studies~\cite{Pinto2008}. However, there are hardly any formally defined quality indicators that can be automatically assessed without further knowledge about the application domain, targeted user group or usage scenario.

%For controlled vocabularies, \cite{Svenonius2003} argues precision and recall to be “the chief objectives of any retrieval language” and proposes a set of design guidelines (e.g., term selection, structural and syntactical considerations) aiming to improve these objectives. Elkin and XXX? [Elkin2002#] identify general quality metrics and structural and maintainability considerations for controlled vocabularies in the health domain, which cover issues like non-redundancy, consistency, and multilinguality of concepts? Soergel [Soergel1995#] mentions properties of “good” thesauri like, e.g., support for synonym and hierarchic expansion or request-oriented indexing. As negative properties of the AAT Soergel points out, e.g., missing cross-references, incomplete facet analysis, the monohierarchical layout and shortcomings in term form and choice. On the positive side he mentions, e.g., presence of scope notes, definition of related terms and some definitions of synonyms. Pinto [Pinto2008#] performs a survey-based study comparing perceived and expected properties (“variables”) of thesauri used in social science databases. The findings exposed need for “considerable improvement” in the structural perspective (e.g., equivalence and associative relationships), but also regarding “performance” variables (e.g., explanatory notes or expected performance) and “format” issues (e.g., ergonomics and display). Some of the identified variables (e.g, pre-coordination, searching options) are hard do assess automatically or are application dependent, others aren’t exactly defined or formalized. However, neither of them suggest any automatic assessment methods, which can be applied to controlled Web vocabularies.

Research on the notion of “data quality” has also been conducted in Semantic Web research. Hogan and ??? [Hogan2009#] identify four categories of common errors and shortcomings in RDF documents. Some of them are also of great importance and can be adopted for assessing the quality of SKOS vocabularies, especially considering interoperability issues like e.g., dereferencability and use of undefined classes and properties. However, the author’s focus lies on RDF datasets in general, thus features of controlled vocabularies are not covered. This is also the case for [Tartir2007#] who propose a framework for evaluation and ranking of Ontologies. Given the fact that vocabularies usually extend the SKOS schema only to a very limited degree by defining subclasses and subproperties, the metrics defined in [Tartir2007] are not considered applicable to these vocabularies.

[Arpinar2006#] define three types of conflicts that may occur in ontologies. Based on these types, the ontology maintainers can create rules in RuleML or SWRL to find violations in their ontologies. Although not using a rule language, we express quality criteria formally, following a very similar approach.

[Gangemi2005#] introduce three “measure types for ontology evaluation” (dimensions), i.e. structural, functional and usability-related measures. The structural exploits the graph structure of an ontology and defines a number of measure like, e.g., absolute, average or maximum depth and breadth, number of leaf nodes, number of siblings or density. While for many of the measures, its applicability for controlled vocabularies is not immediately clear, some (e.g., cycle ratio, inverse relations) resemble common patterns in controlled vocabularies and thus are represented in our catalog of quality criteria. Functional dimensions are measures related to how well an ontology fits its intended purpose like, e.g., recall, precision and accuracy. They are highly context-dependent, however, we expect most of our identified criteria to impact these dimensons. In the usability dimension, Gangemi et al. mention three analytical levels for usability profiling: recognition, efficiency, and interfacing. Since they don’t go into details on what the implications for thesauri are, we try to complement this in the rationale of our identified quality crtieria. [Brank2005#] provide a concise overview on ontology evaluation approaches
Linked Data Quality

[Yeganeh2011#] propose a method to convert semi-structured data (e.g., XML files) into “high-quality Linked Data”. Their notion of quality encompasses usage of HTTP URIs, URI dereferencability, linkage of related objects as well as merging and detection of duplicate resources.

### 2012-03-23 related_work.tex
removed # symbols

@@
+%!TEX root = main.tex
 \section{Related Work}\label{sec:related_work}
@@
 Hogan and ???
-[Hogan2009#] identify four categories of common errors and shortcomings in RDF documents.
+[Hogan2009] identify four categories of common errors and shortcomings in RDF documents.
 Some of them are also of great importance and can be adopted for assessing the quality of SKOS vocabularies, especially considering interoperability issues like e.g., dereferencability and use of undefined classes and properties.
 However, the author’s focus lies on RDF datasets in general, thus features of controlled vocabularies are not covered.
-This is also the case for [Tartir2007#] who propose a framework for evaluation and ranking of Ontologies.
+This is also the case for [Tartir2007] who propose a framework for evaluation and ranking of Ontologies.
 Given the fact that vocabularies usually extend the SKOS schema only to a very limited degree by defining subclasses and subproperties, the metrics defined in [Tartir2007] are not considered applicable to these vocabularies.
 
-[Arpinar2006#] define three types of conflicts that may occur in ontologies.
+[Arpinar2006] define three types of conflicts that may occur in ontologies.
 Based on these types, the ontology maintainers can create rules in RuleML or SWRL to find violations in their ontologies.
@@
 
-[Gangemi2005#] introduce three “measure types for ontology evaluation” (dimensions), i.e.
+[Gangemi2005] introduce three “measure types for ontology evaluation” (dimensions), i.e.
 structural, functional and usability-related measures.
@@
 Since they don’t go into details on what the implications for thesauri are, we try to complement this in the rationale of our identified quality crtieria.
-[Brank2005#] provide a concise overview on ontology evaluation approaches
+[Brank2005] provide a concise overview on ontology evaluation approaches
 Linked Data Quality
 
-[Yeganeh2011#] propose a method to convert semi-structured data (e.g., XML files) into “high-quality Linked Data”.
+[Yeganeh2011] propose a method to convert semi-structured data (e.g., XML files) into “high-quality Linked Data”.
 Their notion of quality encompasses usage of HTTP URIs, URI dereferencability, linkage of related objects as well as merging and detection of duplicate resources.

### 2012-03-23 analysis.tex
added tool description

@@
 
-We implemented the qSKOS tool that can be used for computing the quality checking functions introduced in \ref{sec:criteria} and made it publicly available\footnote{\url{https://github.com/cmader/qSKOS/}}.
-All data in the Tables \ref{tab:vocs} and \ref{tab:results} have been obtained by utilizing this tool.
-However, qSKOS is not only capable of returning numeric values, but can also provide a detailed report listing all resources returned by the quality checking functions alongside with the potential cause of the issue.
+With qSKOS\footnote{\url{https://github.com/cmader/qSKOS/}}, we provide a reference implementation of the previously introduced quality checking functions and a freely-available open source tool for assessing the quality of a given SKOS vocabulary and finding possible quality issues.
+Users can run the tool by passing a vocabulary and selecting the quality checking functions they want to perform.
+As a result, they obtain detailed reports listing possibly affected resources alongside with the potential cause of the issue.
+qSKOS is implemented in Java and can be used as standalone command-line tool or API in any other application.
+Its design is open for the introduction of additional quality functions.
 
@@
 \subsection{Results}
+
+Results have been generated by using the qSKOS tool against the previously
 

### 2012-03-23 introduction.tex
finished intro

@@
 However, these conditions fail to capture quality aspects such as those mentioned in the examples before, aspects that go beyond integrity conditions of the SKOS data model.
-Existing guidelines manuals consider these aspects but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger, possibly linked vocabularies on the Web.
+Existing guidelines and manuals consider these aspects but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger, possibly linked vocabularies on the Web.
 
@@
 
-The goal of our work is to help taxonomists in identifying possible quality issues, which go beyond data model integrity conditions, in SKOS vocabularies.
+The goal of our work is to help taxonomists in identifying possible quality issues in SKOS vocabularies, which go beyond data model integrity conditions.
 We want to given them a set of computable quality checking functions that, in combination with the taxonomists' experience and domain expertise, can serve as quality indicators for vocabularies.
-We believe that finding such quality issues also gives important feedback in the overall vocabulary design process.
+Finding such quality issues also gives important feedback on the overall vocabulary design process and should, at the end, lead to better vocabularies.
 The main contributions of this work can be summarized as follows:
@@
 
-In the following, we will first (Section~\ref{sec:background}) elaborate on the meaning of quality in SKOS vocabularies and then present the set of quality criteria we identified (Section~\ref{sec:criteria}).
-In Section~\ref{sec:analysis} we describe our analysis and discuss the results, which show that \todo{BH,CM}{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.}.
+In the following, we will first discuss what \emph{quality} means in the context of SKOS vocabularies and how it is currently support by the SKOS specification and existing tools.
+Then we introduce the quality issues we have identified and describe how we implemented them in the qSKOS quality assessment tool.
+Finally, we report on the results of an analysis we performed on 15 existing SKOS vocabularies and which shows that the quality issues we identified occur in reality.
+The reports we produced already lead to the improvement of at least two existing vocabularies.

### 2012-03-23 analysis.tex
polished tool description

@@
 
+To learn about possible quality issues in real-world vocabularies, we implemented the previously described quality checking function in the qSKOS tool and applied each function on a set of existing SKOS vocabularies.
+
 \subsection{The qSKOS Quality Checking Tool}
 
-With qSKOS\footnote{\url{https://github.com/cmader/qSKOS/}}, we provide a reference implementation of the previously introduced quality checking functions and a freely-available open source tool for assessing the quality of a given SKOS vocabulary and finding possible quality issues.
+With the qSKOS\footnote{\url{https://github.com/cmader/qSKOS/}} quality assessment tool, we provide an open source reference implementation for finding possible quality issues a given SKOS vocabulary.
 Users can run the tool by passing a vocabulary and selecting the quality checking functions they want to perform.
@@
 Its design is open for the introduction of additional quality functions.
+In our analysis, we used qSKOS version 0.2, which can be downloaded from: \url{https://github.com/cmader/qSKOS/releases/qSKOS-0.2.tar.gz}.
 
@@
 
-Our vocabulary dataset covers XY vocabularies from various domains differing in statistical properties (cf.
+Our vocabulary dataset covers 15 vocabularies from various domains differing in statistical properties (cf.
 Table~\ref{vocabs}).

### 2012-03-23 analysis.tex
added datase description

@@
 
-With the qSKOS\footnote{\url{https://github.com/cmader/qSKOS/}} quality assessment tool, we provide an open source reference implementation for finding possible quality issues a given SKOS vocabulary.
+The open-source qSKOS\footnote{\url{https://github.com/cmader/qSKOS/}} quality assessment tool can be used to find possible quality issues a given SKOS vocabulary.
 Users can run the tool by passing a vocabulary and selecting the quality checking functions they want to perform.
@@
 Its design is open for the introduction of additional quality functions.
-In our analysis, we used qSKOS version 0.2, which can be downloaded from: \url{https://github.com/cmader/qSKOS/releases/qSKOS-0.2.tar.gz}.
+In our analysis, we used qSKOS version 0.2., which can be downloaded from: \url{https://github.com/cmader/qSKOS/releases/qSKOS-0.2.tar.gz}.
 
@@
 
-Our vocabulary dataset covers 15 vocabularies from various domains differing in statistical properties (cf.
-Table~\ref{vocabs}).
-The data was gathered in different ways.
-Some vocabularies where downloaded from their respective project websites or, in the cases of IPSV, Peroxisome Knowledge Base, and LVAk requested directly from the creators.
-The MeSH dataset was created by \cite{Assem2006} and is available for download\footnote{\url{http://thesauri.cs.vu.nl/eswc06/}}.
-We created the SKOS version of LVAk thesaurus from CSV files provided by the vocabulary maintainers.
-The vocabulary structure was uncomplex, so the conversion process to SKOS turned out as being rather straightforward.
+We used Sindice and available listings\footnote{\url{http://www.w3.org/2001/sw/wiki/SKOS/Datasets}} to learn about existing SKOS vocabularies.
+Table~\ref{vocabs} lists our representative vocabulary selection and shows that the vocabularies differ in size and application domain: the \emph{Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA)} is vocabulary from the media domain, \emph{Eurovoc} and the \emph{Integrated Public Sector Vocabularies (PSV)} cover public sector concepts, the \emph{Medical Subject Headings (MeSH)} and \emph{Peroxisome Knowledge Base (PXV)} are from the (bio-)medical domain, the \emph{Geonames Ontology} covers locations, the \emph{Thesaurus for Economics (STW)} and \emph{North American Industry Classification System (NAICS)} are vocabularies from the economics and business area and the \emph{DBPedia Categories} reflect Wikipedia's user-generated categorization system.
+We also include the \emph{Meketre} vocabulary, which defines Egyptology-related concepts, and the non-public \emph{Thesaurus Landesverteidigungsakademie (LVAk)}, which we generated from CSV files provided by the vocabulary maintainers.
+A zip-file containing all 14 public vocabulariesx we used in our analysis, can be downloaded from: \url{http://www.github.com/cmader/???}.
 
@@
 \label{tab:vocs}
-\caption{Analyzed vocabularies}
+\caption{Analyzed SKOS vocabularies}
 \centering
-\begin{tabular}{p{6cm}ccccccc}
+\begin{tabular}{p{5cm}ccccccc}
 \textbf{Vocabulary} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
@@
 
-Results have been generated by using the qSKOS tool against the previously
+The results of this analysis are reported in Table~\ref{tab:results}, which shows the absolute number of possible affected resources for each function and vocabulary combination.
 
@@
 
-The \textbf{Loose Concepts} metrics provides insights on the structural complexity of vocabularies.
+\todo{BH,CM}{detailed interpretation}
+
+% The \textbf{Loose Concepts} metrics provides insights on the structural complexity of vocabularies.
 The large number of loose concepts in GTAA can be explained by the fact that it contains names (e.g., persons or places) that arent't connected using skos properties.
 This is also the case for Geonames, NYTP and Pressinfo where the number of total conceps is equal to the number of loose concepts, indicating that no concept is semantically related to another concept.
-
-The large number of \textbf{Weakly Connected Components} in GTAA is caused by many ``minimal'' components, containing only 2 concepts connected by a \texttt{skos:related} property.
+% 
+% The large number of \textbf{Weakly Connected Components} in GTAA is caused by many ``minimal'' components, containing only 2 concepts connected by a \texttt{skos:related} property.
 Due to the fact that loose concepts are not counted as weakly connected components, Geonames, NYTP and Pressinfo evaluate to zero components.
-
-\todo{CM}{Add result interpretation for this one metric}

### 2012-03-23 analysis.tex
added results

--- 2012-03-23 analysis.tex
@@
 
-With qSKOS\footnote{\url{https://github.com/cmader/qSKOS/}}, we provide a reference implementation of the previously introduced quality checking functions and a freely-available open source tool for assessing the quality of a given SKOS vocabulary and finding possible quality issues.
-Users can run the tool by passing a vocabulary and selecting the quality checking functions they want to perform.
-As a result, they obtain detailed reports listing possibly affected resources alongside with the potential cause of the issue.
-qSKOS is implemented in Java and can be used as standalone command-line tool or API in any other application.
-Its design is open for the introduction of additional quality functions.
+We implemented the qSKOS tool that can be used for computing the quality checking functions introduced in \ref{sec:criteria} and made it publicly available\footnote{\url{https://github.com/cmader/qSKOS/}}.
+All data in the Tables \ref{tab:vocs} and \ref{tab:results} have been obtained by utilizing this tool.
+However, qSKOS is not only capable of returning numeric values, but can also provide a detailed report listing all resources returned by the quality checking functions alongside with the potential cause of the issue.
 
@@
 \begin{tabular}{p{6cm}ccccccc}
-\textbf{Vocabulary} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
+\textbf{Vocabulary} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
 \toprule
-Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & ? & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
+Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & 2010/08/25 & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
 \hline
-Geonames Ontology & ? & 671 & 671 & 0 & 671 & 9 & 0 \\
+Geonames Ontology & 2.2.1 & 671 & 671 & 0 & 671 & 9 & 0 \\
 \hline
@@
 \hline
-Peroxisome Knowledge Base (PXV) & ? & 2112 & 3628 & 2695 & 1716 & 1 & 0 \\
+Peroxisome Knowledge Base (PXV) & 1.6 & 2112 & 3628 & 2695 & 1716 & 1 & 0 \\
 \hline
-Eurovoc & ? & 6797 & 457788 & 18491 & 15512 & 128 & 0 \\
+Eurovoc & 5.0 & 6797 & 457788 & 18491 & 15512 & 128 & 0 \\
 \hline
-Integrated Public Sector Vocabulary (IPSV) & ? & 4732 & 7945 & 13843 & 4483 & 3 & 0 \\
+Integrated Public Sector Vocabulary (IPSV) & 2.00 & 4732 & 7945 & 13843 & 4483 & 3 & 0 \\
 \hline
@@
 
-Results have been generated by using the qSKOS tool against the previously
-
 \begin{table}[h]
@@
 \toprule
-Omitted or Invalid Language Tags &&&&&&& 0 & tba & 1224 & 0 & tba & 0 & 2 & 0 & 13411 \\
+Omitted or Invalid Language Tags & 0 & 0 && 1578 & n/a & 0 & 0 & 0 & 1224 & 0 & 18 & 0 & 2 & n/a & 13411 \\
 
-Incomplete Language Coverage &&&&&&& 32035 & tba & 0 & 0 & tba & 420 & 6456 & 0 & 0 \\
+Incomplete Language Coverage & 0 & 0 && 0 & n/a & 0 & 32035 & 0 & 0 & 0 & 0 & 420 & 6456 & n/a & 0 \\
 
-Undocumented Concepts &&&&&&& 32035 & tba & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\
+Undocumented Concepts & 96850 & 0 && 1918 & 5341 & 4551 & 32035 & tba & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\
 
-Label Conflicts &&&&&&& 2949 & tba & 0 & 0 & tba & 4 & 5 & 0 & 13 \\
+Label Conflicts & 12404 & 18 & 0 & 7 & n/a & 0 & 2949 & 0 & 0 & 0 & tba & 4 & 5 & n/a & 13 \\
 
@@
 
-\midrule
-
 Undefined SKOS Resources &&&&&&&&&&&&&&& \\

### 2012-03-23 analysis.tex

--- 2012-03-23 analysis.tex
@@
 \centering
-\begin{tabular}{p{5cm}ccccccc}
-\textbf{Vocabulary} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
+\begin{tabular}{p{6cm}ccccccc}
+\textbf{Vocabulary} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
 \toprule
-Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & ? & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
+Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & 2010/08/25 & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
 \hline
-Geonames Ontology & ? & 671 & 671 & 0 & 671 & 9 & 0 \\
+Geonames Ontology & 2.2.1 & 671 & 671 & 0 & 671 & 9 & 0 \\
 \hline

### 2012-03-23 background.tex
shortened related work

--- 2012-03-22 background.tex
@@
 Thus, in order to help vocabulary and application designers in judging the quality of SKOS vocabularies, we need higher-level quality criteria that go beyond low-level integrity conditions defining data model consistency.
-Such quality criteria are already well-established and have extensively been discussed in standardized guidelines \cite{ISO25964-1:2011,Z39.19:2005}, manuals \cite{Hedden2010,Aitchison2000,Harpring2010}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002}.
+Such quality criteria are already well-established and have extensively been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, case studies~\cite{Soergel1995}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002,Elkin2002,Kless2010}.
+
+% TODO ADD TO THIS SECTION: a vast number of publications in the field of designing, validating and testing controlled vocabularies is available.
+Many of them propose properties \cite{Soergel1995}, design guidelines \cite{Svenonius2003,...} or metrics \cite{Elkin2002,Kless2010} aiming to improve, e.g., retrieval precision and recall, consistency and multilinguality.
+The work is based on various sources like, e.g., review of existing vocabularies~\cite{Soergel1995} or survey-based studies~\cite{Pinto2008}.
+However, there are hardly any formally defined quality indicators that can be automatically assessed without further knowledge about the application domain, targeted user group or usage scenario.
 

### 2012-03-23 related_work.tex
rephrased related work
shortened related work

@@
 
-The problem of ``vocabulary quality'' is closely related to the more general problem of “data quality”, which has intensively been discussed in data and information systems research.
-\cite{Pipino2002,Batini2009} argue that dealing with data quality should involve both “subjective perceptions of the individuals” and “objective measurements based on the data set in question”.
-We see our work as a contribution to the latter and believe that the results of SKOS quality measures must be combined with domain knowledge, and therefore human expertise, to make final quality judgements.
+% Data quality in general
 
-A vast number of publications in the field of designing, validating and testing controlled vocabularies is available.
-Many of them propose properties \cite{Soergel1995}, design guidelines \cite{Svenonius2003,...} or metrics \cite{Elkin2002,Kless2010} aiming to improve, e.g., retrieval precision and recall, consistency and multilinguality.
-The work is based on various sources like, e.g., review of existing vocabularies~\cite{Soergel1995} or survey-based studies~\cite{Pinto2008}.
-However, there are hardly any formally defined quality indicators that can be automatically assessed without further knowledge about the application domain, targeted user group or usage scenario.
+The problem of ``vocabulary quality'' is closely related to the more general problem of ``data quality`'', which has intensively been discussed in data and information systems research (cf.~\cite{Batini2009}).
+Pipino et al.~\cite{Pipino2002} argue that dealing with data quality should involve both ``subjective perceptions of the individuals'' and ``objective measurements based on the data set in question''.
+We see our work as a contribution to the latter and believe that the kind of quality assessment we support must be combined with domain knowledge, and therefore human expertise, to make final quality judgements.
 
-%For controlled vocabularies, \cite{Svenonius2003} argues precision and recall to be “the chief objectives of any retrieval language” and proposes a set of design guidelines (e.g., term selection, structural and syntactical considerations) aiming to improve these objectives.
-Elkin and XXX?
-[Elkin2002#] identify general quality metrics and structural and maintainability considerations for controlled vocabularies in the health domain, which cover issues like non-redundancy, consistency, and multilinguality of concepts?
-Soergel [Soergel1995#] mentions properties of “good” thesauri like, e.g., support for synonym and hierarchic expansion or request-oriented indexing.
-As negative properties of the AAT Soergel points out, e.g., missing cross-references, incomplete facet analysis, the monohierarchical layout and shortcomings in term form and choice.
-On the positive side he mentions, e.g., presence of scope notes, definition of related terms and some definitions of synonyms.
-Pinto [Pinto2008#] performs a survey-based study comparing perceived and expected properties (“variables”) of thesauri used in social science databases.
-The findings exposed need for “considerable improvement” in the structural perspective (e.g., equivalence and associative relationships), but also regarding “performance” variables (e.g., explanatory notes or expected performance) and “format” issues (e.g., ergonomics and display).
-Some of the identified variables (e.g, pre-coordination, searching options) are hard do assess automatically or are application dependent, others aren’t exactly defined or formalized.
-However, neither of them suggest any automatic assessment methods, which can be applied to controlled Web vocabularies.
+% Quality in Linked Data
 
-Research on the notion of “data quality” has also been conducted in Semantic Web research.
-Hogan and ???
-[Hogan2009] identify four categories of common errors and shortcomings in RDF documents.
-Some of them are also of great importance and can be adopted for assessing the quality of SKOS vocabularies, especially considering interoperability issues like e.g., dereferencability and use of undefined classes and properties.
-However, the author’s focus lies on RDF datasets in general, thus features of controlled vocabularies are not covered.
-This is also the case for [Tartir2007] who propose a framework for evaluation and ranking of Ontologies.
-Given the fact that vocabularies usually extend the SKOS schema only to a very limited degree by defining subclasses and subproperties, the metrics defined in [Tartir2007] are not considered applicable to these vocabularies.
+Data quality research has also been conducted in the Semantic Web and Linked Data research areas.
+Hogan et.
+al~\cite{Hogan2010} identify four categories of common errors and shortcomings in RDF documents and also Heath and Bizer~\cite{Heath2011} summarize best practices for publishing data on the Web.
+However, the authors focus on RDF datasets in general without considering SKOS-specific properties.
 
-[Arpinar2006] define three types of conflicts that may occur in ontologies.
-Based on these types, the ontology maintainers can create rules in RuleML or SWRL to find violations in their ontologies.
-Although not using a rule language, we express quality criteria formally, following a very similar approach.
+% Quality in ontology engineering
 
-[Gangemi2005] introduce three “measure types for ontology evaluation” (dimensions), i.e.
-structural, functional and usability-related measures.
-The structural exploits the graph structure of an ontology and defines a number of measure like, e.g., absolute, average or maximum depth and breadth, number of leaf nodes, number of siblings or density.
-While for many of the measures, its applicability for controlled vocabularies is not immediately clear, some (e.g., cycle ratio, inverse relations) resemble common patterns in controlled vocabularies and thus are represented in our catalog of quality criteria.
-Functional dimensions are measures related to how well an ontology fits its intended purpose like, e.g., recall, precision and accuracy.
-They are highly context-dependent, however, we expect most of our identified criteria to impact these dimensons.
-In the usability dimension, Gangemi et al.
-mention three analytical levels for usability profiling: recognition, efficiency, and interfacing.
-Since they don’t go into details on what the implications for thesauri are, we try to complement this in the rationale of our identified quality crtieria.
-[Brank2005] provide a concise overview on ontology evaluation approaches
-Linked Data Quality
-
-[Yeganeh2011] propose a method to convert semi-structured data (e.g., XML files) into “high-quality Linked Data”.
-Their notion of quality encompasses usage of HTTP URIs, URI dereferencability, linkage of related objects as well as merging and detection of duplicate resources.
+Ontology evaluation is task of measuring the quality of an ontology and has extensively been discussed by Vrandecic~[\todo{CM}{ref denny}].
+Gangemi [\todo{CM}{ref ?}] introduced structural, functional and usability-related measures for ontology evaluation, Arpinar [\todo{CM}{ref ?}] define three types of conflicts that may occur in ontologies, and also Tartir et al.[\todo{CM}{ref ?}] propose a framework for evaluation and ranking of ontologies.
+Although there are definitely overlaps between ontology evaluation and our research, the quality issues we identified are less tight to underlying data model and formal ontology definition language but, to a large extent, derived from manuals and guidelines taxonomist use in their daily work.

### 2012-03-23 background.tex
minor reformulation

@@
 % Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
-Thus, in order to help vocabulary and application designers in judging the quality of SKOS vocabularies, we need higher-level quality criteria that go beyond low-level integrity conditions defining data model consistency.
-Such quality criteria are already well-established and have extensively been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, case studies~\cite{Soergel1995}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002,Elkin2002,Kless2010}.
+Thus, in order to help vocabulary and application designers in improving the quality of SKOS vocabularies, we need to identify possible quality issues that go beyond integrity conditions defining data model consistency.
+Quality criteria for controlled vocabularies have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, case studies~\cite{Soergel1995}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002,Elkin2002,Kless2010}.
 

### 2012-03-23 analysis.tex
fixed table 1 columns

@@
 \centering
-\begin{tabular}{p{6cm}ccccccc}
-\textbf{Vocabulary} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
+\begin{tabular}{p{6cm}cccccccc}
+\textbf{Vocabulary} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth.
+Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
 \toprule
-Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & 2010/08/25 & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
+Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & 2010/08/25 & 171991 && 178776 & 50892 & 343980 & 9 & 0 \\
 \hline
-Geonames Ontology & 2.2.1 & 671 & 671 & 0 & 671 & 9 & 0 \\
+Geonames Ontology & 2.2.1 & 671 && 671 & 0 & 671 & 9 & 0 \\
 \hline
-Medical Subject Headings (MeSH) & ? & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
+Medical Subject Headings (MeSH) & ? & 24626 && 150617 & 38858 & 0 & 0 & 0 \\
 \hline
-Peroxisome Knowledge Base (PXV) & 1.6 & 2112 & 3628 & 2695 & 1716 & 1 & 0 \\
+Peroxisome Knowledge Base (PXV) & 1.6 & 2112 && 3628 & 2695 & 1716 & 1 & 0 \\
 \hline
-Eurovoc & 5.0 & 6797 & 457788 & 18491 & 15512 & 128 & 0 \\
+Eurovoc & 5.0 & 6797 && 457788 & 18491 & 15512 & 128 & 0 \\
 \hline
-Integrated Public Sector Vocabulary (IPSV) & 2.00 & 4732 & 7945 & 13843 & 4483 & 3 & 0 \\
+Integrated Public Sector Vocabulary (IPSV) & 2.00 & 4732 && 7945 & 13843 & 4483 & 3 & 0 \\
 \hline
-AGROVOC & 1.3 & 32035 & 620629 & 65934 & 32085 & 1 & 0 \\
+AGROVOC & 1.3 & 32035 && 620629 & 65934 & 32085 & 1 & 0 \\
 \hline
-DBpedia Categories & ? & 743410 & 740352 & 1490316 & 0 & 0 & 0 \\
+DBpedia Categories & ? & 743410 && 740352 & 1490316 & 0 & 0 & 0 \\
 \hline
-University of Southampton Pressinfo & 2011/02/24 & 1125 & 0 & 0 & 0 & 0 & 0 \\
+University of Southampton Pressinfo & 2011/02/24 & 1125 && 0 & 0 & 0 & 0 & 0 \\
 \hline
-New York Times People (NYTP) & 2010/06/22 & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
+New York Times People (NYTP) & 2010/06/22 & 4979 && 4979 & 0 & 4979 & 1 & 0 \\
 \hline
-Library of Congress Subject Headings (LCSH) & ? & 459182 & 746076 & 595754 & 815816 & 19 & 0 \\
+Library of Congress Subject Headings (LCSH) & ? & 459182 && 746076 & 595754 & 815816 & 19 & 0 \\
 \hline
-Meketre & 2011/07/07 & 422 & 569 & 1698 & 6 & 2 & 0 \\
+Meketre & 2011/07/07 & 422 && 569 & 1698 & 6 & 2 & 0 \\
 \hline
-Thesaurus for Economics (STW) & 8.06 & 6524 & 31189 & 57907 & 6531 & 1 & 0 \\
+Thesaurus for Economics (STW) & 8.06 & 6524 && 31189 & 57907 & 6531 & 1 & 0 \\
 \hline
-North American Industry Classification System (NAICS) & 2012 & 4175 & 0 & 8684 & 2235 & 1 & 0 \\
+North American Industry Classification System (NAICS) & 2012 & 4175 && 0 & 8684 & 2235 & 1 & 0 \\
 \hline
-Thesaurus Landesverteidigungsakademie (LVAk) & n/a & 13411 & 17250 & 16346 & 0 & 0 & 0 \\
+Thesaurus Landesverteidigungsakademie (LVAk) & n/a & 13411 && 17250 & 16346 & 0 & 0 & 0 \\
 \bottomrule

### 2012-03-23 background.tex
minor changes to background

@@
 % Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
-Thus, in order to help vocabulary and application designers in improving the quality of SKOS vocabularies, we need to identify possible quality issues that go beyond integrity conditions defining data model consistency.
-Quality criteria for controlled vocabularies have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, case studies~\cite{Soergel1995}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002,Elkin2002,Kless2010}.
+Thus, in order to help vocabulary and application designers in judging and improving the quality of SKOS vocabularies we must identify possible quality issues that go beyond integrity conditions defining data model consistency.
+We can identify such issues by examining quality criteria for controlled vocabularies that have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, case studies~\cite{Soergel1995}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002,Elkin2002,Kless2010}.
+Since we want to provide tool support for quality checking, we must formalize the identified issues into computable quality checking functions taking into account the syntax, structure and semantics of SKOS.
+This also ensures consistent implementation across tools.
 
@@
 
-If we want check existing SKOS vocabularies against these criteria, we first need to identify them and determine how to evaluate them given the syntax, structure and semantics of SKOS.
-Since we want to provide tool support for quality checking, we must formalize these criteria into computable quality checking functions, in order to ensure consistent implementation and interpretation across tools.
-
 % I think for the big picture it is not necessary to go into such details. We can do this later when introducting the metrics

### 2012-03-23 analysis.tex
started results interpretation

@@
 
-The results of this analysis are reported in Table~\ref{tab:results}, which shows the absolute number of possible affected resources for each function and vocabulary combination.
+The results of this analysis are reported in Table~\ref{tab:results}, which shows the absolute number of possibly affected resources for each quality checking function and vocabulary combination.
+The value 0 means that we haven't found any affected resource, N/A means that a certain function was not applicable for reasons we explain below.
 
@@
 \label{tab:results}
-\caption{Results of the quality checking functions (cardinality of the result set)}
+\caption{Results of the quality checking functions}
 \begin{tabular}{p{4cm}ccccccccccccccc}
@@
 
-\todo{BH,CM}{detailed interpretation}
+% Labeling and Documentation Issues
+We found labeling and documentation issues in all analyzed vocabularies.
+PXV provides labels for XX\% of its concepts, Pressinfo labels only for 1 out of 1125 concepts, and the STW thesaurus misses labels for two concepts.
+Eurovoc and NAICS use SKOS-XL labels, which are currently not supported by qSKOS.
+Incomplete Language Coverage were issues in the three analyzed vocabularies: in AGROVOC all concepts had incomplete coverage, probably because \todo{CM}{why?}, and in STW we found XX\%.
+Most vocabularies didn't document their concepts with the documentary properties defined by SKOS.
+Label conflicts, hence \todo{CM}{explain briefly} were found in several vocabularies: GTAA has many because? PXV has 7. Why given examples?
+
+% Structural Issues
+
+% Linked Data Specific Issues
 

### 2012-03-24 conclusions.tex
added acknowledgements draft and updated analyzed vocab table
structured section 2
commented ackn
added conclusions

@@
+%!TEX root = main.tex
 \section{Conclusions and Future Work}\label{sec:conclusions}
+
+In this paper we identified and defined quality issues of SKOS vocabularies and implemented them in the qSKOS quality assessment tool, which can find possible affected resources in a given SKOS vocabulary.
+We also analyzed a representative set of existing SKOS vocabularies and found real-world occurrences for all these issues.
+\todo{CM}{one more sentence highlighting what kind of issues were omnipresent.}.
+
+During our work on qSKOS and while writing this paper we were in contact with some of the creators of the vocabularies we analyzed and also reported back initial results from our analysis.
+At the time of this writing, we know that our findings lead to improvements in at least two SKOS vocabularies.
+
+We aware that the quality issues we described in this work are purely quantitative indicators that, on their own, cannot be generalized into statements about the quality of a vocabulary.
+To learn more about the real-world impact of our work, we would like to conduct a qualitative study in which we confront taxonomists with our results.
+We will also further collect community feedback, enhance the issues list, and set up a Web-based SKOS quality checking service.
+
+% \section{Acknowledgements}
+
+% Tom Dent (esd support team) for providing a dump for the IPSV vocabulary
+% Andrew Gibson for providing a dump for the Peroxisome knowledge Base and giving valuable feedback on their vocabulary structure.

### 2012-03-24 analysis.tex
added additional results
added analysis data
fixed first table

@@
 We used Sindice and available listings\footnote{\url{http://www.w3.org/2001/sw/wiki/SKOS/Datasets}} to learn about existing SKOS vocabularies.
-Table~\ref{vocabs} lists our representative vocabulary selection and shows that the vocabularies differ in size and application domain: the \emph{Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA)} is vocabulary from the media domain, \emph{Eurovoc} and the \emph{Integrated Public Sector Vocabularies (PSV)} cover public sector concepts, the \emph{Medical Subject Headings (MeSH)} and \emph{Peroxisome Knowledge Base (PXV)} are from the (bio-)medical domain, the \emph{Geonames Ontology} covers locations, the \emph{Thesaurus for Economics (STW)} and \emph{North American Industry Classification System (NAICS)} are vocabularies from the economics and business area and the \emph{DBPedia Categories} reflect Wikipedia's user-generated categorization system.
+Table~\ref{tab:vocabs} lists our representative vocabulary selection \todo{CM}{alphabetically} and shows that the vocabularies differ in size and application domain: the \emph{Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA)} is vocabulary from the media domain, \emph{Eurovoc} and the \emph{Integrated Public Sector Vocabularies (PSV)} cover public sector concepts, the \emph{Medical Subject Headings (MeSH)} and \emph{Peroxisome Knowledge Base (PXV)} are from the (bio-)medical domain, the \emph{Geonames Ontology} covers locations, the \emph{Thesaurus for Economics (STW)} and \emph{North American Industry Classification System (NAICS)} are vocabularies from the economics and business area and the \emph{DBPedia Categories} reflect Wikipedia's user-generated categorization system.
 We also include the \emph{Meketre} vocabulary, which defines Egyptology-related concepts, and the non-public \emph{Thesaurus Landesverteidigungsakademie (LVAk)}, which we generated from CSV files provided by the vocabulary maintainers.
@@
 
-\begin{table}[h]
-\label{tab:vocs}
+\begin{table}
+\label{tab:vocabs}
 \caption{Analyzed SKOS vocabularies}
-\centering
-\begin{tabular}{p{6cm}cccccccc}
-\textbf{Vocabulary} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth.
+
+\begin{center}
+
+\resizebox{\textwidth}{!} {
+
+\setlength{\extrarowheight}{5pt}
+
+\begin{tabular}{p{6cm}ccccccccc}
+
+\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbrev.}} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth.
 Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
 \toprule
-Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & 2010/08/25 & 171991 && 178776 & 50892 & 343980 & 9 & 0 \\
+Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171991 && 178776 & 50892 & 343980 & 9 & 0 \\
 \hline
-Geonames Ontology & 2.2.1 & 671 && 671 & 0 & 671 & 9 & 0 \\
+Geonames Ontology & \textbf{Geonames} & 2.2.1 & 671 & 671 & 671 & 0 & 671 & 9 & 0 \\
 \hline
-Medical Subject Headings (MeSH) & ? & 24626 && 150617 & 38858 & 0 & 0 & 0 \\
+Medical Subject Headings & \textbf{MeSH} & ? & 24626 & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
 \hline
-Peroxisome Knowledge Base (PXV) & 1.6 & 2112 && 3628 & 2695 & 1716 & 1 & 0 \\
+Peroxisome Knowledge Base & \textbf{PXV} & 1.6 & 2112 & 1686 & 3628 & 2695 & 1716 & 1 & 0 \\
 \hline
-Eurovoc & 5.0 & 6797 && 457788 & 18491 & 15512 & 128 & 0 \\
+The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6797 && 457788 & 18491 & 15512 & 128 & 0 \\
 \hline
-Integrated Public Sector Vocabulary (IPSV) & 2.00 & 4732 && 7945 & 13843 & 4483 & 3 & 0 \\
+Integrated Public Sector Vocabulary & \textbf{IPSV} & 2.00 & 4732 && 7945 & 13843 & 4483 & 3 & 0 \\
 \hline
-AGROVOC & 1.3 & 32035 && 620629 & 65934 & 32085 & 1 & 0 \\
+Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32035 && 620629 & 65934 & 32085 & 1 & 0 \\
 \hline
-DBpedia Categories & ? & 743410 && 740352 & 1490316 & 0 & 0 & 0 \\
+DBpedia Categories & \textbf{DBPedia} & ? & 743410 && 740352 & 1490316 & 0 & 0 & 0 \\
 \hline
-University of Southampton Pressinfo & 2011/02/24 & 1125 && 0 & 0 & 0 & 0 & 0 \\
+University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1125 && 0 & 0 & 0 & 0 & 0 \\
 \hline
-New York Times People (NYTP) & 2010/06/22 & 4979 && 4979 & 0 & 4979 & 1 & 0 \\
+New York Times People & \textbf{NYTP} & 2010/06/22 & 4979 && 4979 & 0 & 4979 & 1 & 0 \\
 \hline
-Library of Congress Subject Headings (LCSH) & ? & 459182 && 746076 & 595754 & 815816 & 19 & 0 \\
+Library of Congress Subject Headings & \textbf{LCSH} & ? & 459182 && 746076 & 595754 & 815816 & 19 & 0 \\
 \hline
-Meketre & 2011/07/07 & 422 && 569 & 1698 & 6 & 2 & 0 \\
+Middle Kingdom tombs of Ancient Egypt Thesaurus & \texttt{Meketre} & 2011/07/07 & 422 && 569 & 1698 & 6 & 2 & 0 \\
 \hline
-Thesaurus for Economics (STW) & 8.06 & 6524 && 31189 & 57907 & 6531 & 1 & 0 \\
+Thesaurus for Economics & \textbf{STW} & 8.06 & 6524 && 31189 & 57907 & 6531 & 1 & 0 \\
 \hline
-North American Industry Classification System (NAICS) & 2012 & 4175 && 0 & 8684 & 2235 & 1 & 0 \\
+North American Industry Classification System & \textbf{NAICS} & 2012 & 4175 && 0 & 8684 & 2235 & 1 & 0 \\
 \hline
-Thesaurus Landesverteidigungsakademie (LVAk) & n/a & 13411 && 17250 & 16346 & 0 & 0 & 0 \\
+Thesaurus Landesverteidigungsakademie & \textbf{LVAk} & n/a & 13411 && 17250 & 16346 & 0 & 0 & 0 \\
 \bottomrule
 \end{tabular}
-\label{vocabs}
+
+}
+\end{center}
 \end{table}
@@
 \toprule
-Omitted or Invalid Language Tags & 0 & 0 && 1578 & n/a & 0 & 0 & 0 & 1224 & 0 & 18 & 0 & 2 & n/a & 13411 \\
+Omitted or Invalid Language Tags & 0 & 0 & 23950 & 1578 & n/a & 0 & 0 & 0 & 1224 & 0 & 18 & 0 & 2 & n/a & 13411 \\
 
-Incomplete Language Coverage & 0 & 0 && 0 & n/a & 0 & 32035 & 0 & 0 & 0 & 0 & 420 & 6456 & n/a & 0 \\
+Incomplete Language Coverage & 0 & 0 & 0 & 0 & n/a & 0 & 32035 & 0 & 0 & 0 & 0 & 420 & 6456 & n/a & 0 \\
 
-Undocumented Concepts & 96850 & 0 && 1918 & 5341 & 4551 & 32035 & tba & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\
+Undocumented Concepts & 96850 & 0 & 1807 & 1918 & 5341 & 4551 & 32035 & tba & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\
 
@@
 
-Weakly Connected Components & 621 & 0 & & 10 & 4 & 1 & 4 & 1506 & 0 & 0 & 22131 & 5 & 1 & 1 & 11 \\
+Weakly Connected Components & 621 & 0 & 4 & 10 & 4 & 1 & 4 & 1506 & 0 & 0 & 22131 & 5 & 1 & 1 & 11 \\
 
-Cyclic Hierarchical Relations &&&&&&&&&&&&&&& \\
+Cyclic Hierarchical Relations & 0 & 0 & 4 & 0 & 0 & 0 & 0 & 1132 & 0 & 0 && 0 & 0 & 0 & 5 \\
 
-Valueless Associative Relations &&&&&&&&&&&&&&& \\
+Valueless Associative Relations & 9438 & 0 & 495 &&&&&&&&&&&& \\
 
-Solely Transitively Related Concepts &&&&&&&&&&&&&&& \\
+Solely Transitively Related Concepts & 0 & 0 & 0 &&&&&&&&&&&& \\
 
-Omitted Top Concepts &&&&&&&&&&&&&&& \\
+Omitted Top Concepts & 9 & 9 & 0 &&&&&&&&&&&& \\
 
-Top Concept Having Broader Concepts &&&&&&&&&&&&&&& \\
+Top Concept Having Broader Concepts & 0 & 0 & 0 &&&&&&&&&&&& \\
 
@@
 
-Undefined SKOS Resources &&&&&&&&&&&&&&& \\
+Undefined SKOS Resources & 0 & 0 & 1 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0  \\
 

### 2012-03-24 analysis.tex
fixed 2nd table size

@@
 Table~\ref{tab:vocabs} lists our representative vocabulary selection \todo{CM}{alphabetically} and shows that the vocabularies differ in size and application domain: the \emph{Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA)} is vocabulary from the media domain, \emph{Eurovoc} and the \emph{Integrated Public Sector Vocabularies (PSV)} cover public sector concepts, the \emph{Medical Subject Headings (MeSH)} and \emph{Peroxisome Knowledge Base (PXV)} are from the (bio-)medical domain, the \emph{Geonames Ontology} covers locations, the \emph{Thesaurus for Economics (STW)} and \emph{North American Industry Classification System (NAICS)} are vocabularies from the economics and business area and the \emph{DBPedia Categories} reflect Wikipedia's user-generated categorization system.
-We also include the \emph{Meketre} vocabulary, which defines Egyptology-related concepts, and the non-public \emph{Thesaurus Landesverteidigungsakademie (LVAk)}, which we generated from CSV files provided by the vocabulary maintainers.
+We also include the \emph{Meketre} vocabulary, which defines Egyptology-related concepts, and the non-public \emph{Austrian Armed Forces Thesaurus (LVAk)}, which we generated from CSV files provided by the vocabulary maintainers.
 A zip-file containing all 14 public vocabulariesx we used in our analysis, can be downloaded from: \url{http://www.github.com/cmader/???}.
@@
 \begin{center}
-
 \resizebox{\textwidth}{!} {
-
 \setlength{\extrarowheight}{5pt}
@@
 \hline
-Thesaurus Landesverteidigungsakademie & \textbf{LVAk} & n/a & 13411 && 17250 & 16346 & 0 & 0 & 0 \\
+Austrian Armed Forces Thesaurus & \textbf{LVAk} & n/a & 13411 && 17250 & 16346 & 0 & 0 & 0 \\
 \bottomrule
@@
 \caption{Results of the quality checking functions}
+
+\begin{center}
+\resizebox{\textwidth}{!} {
+\setlength{\extrarowheight}{5pt}
+
 \begin{tabular}{p{4cm}ccccccccccccccc}
@@
 \end{tabular}
+}
+\end{center}
 \end{table}

### 2012-03-24 analysis.tex
added some more analysis results

@@
 \hline
-Middle Kingdom tombs of Ancient Egypt Thesaurus & \texttt{Meketre} & 2011/07/07 & 422 && 569 & 1698 & 6 & 2 & 0 \\
+Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 && 569 & 1698 & 6 & 2 & 0 \\
 \hline
@@
 \begin{tabular}{p{4cm}ccccccccccccccc}
-\textbf{Metric} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
+\textbf{Issue} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
 \toprule
@@
 
-Undocumented Concepts & 96850 & 0 & 1807 & 1918 & 5341 & 4551 & 32035 & tba & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\
+Undocumented Concepts & 96850 & 0 & 1807 & 1918 & 5341 & 4551 & 32035 & 743410 & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\
 
@@
 
-Cyclic Hierarchical Relations & 0 & 0 & 4 & 0 & 0 & 0 & 0 & 1132 & 0 & 0 && 0 & 0 & 0 & 5 \\
+Cyclic Hierarchical Relations & 0 & 0 & 4 & 0 & 0 & 0 & 0 & 1132 & 0 & 0 & 0 & 0 & 0 & 0 & 5 \\
 
-Valueless Associative Relations & 9438 & 0 & 495 &&&&&&&&&&&& \\
+Valueless Associative Relations & 9438 & 0 & 495 & 0 & 1 && 282 & 8120 & 0 & 0 & 1879 && 5082 & 0 & 5 \\
 
-Solely Transitively Related Concepts & 0 & 0 & 0 &&&&&&&&&&&& \\
+Solely Transitively Related Concepts & 0 & 0 & 0 & 0 & 2652 && 0 & 0 & 0 & 0 & 0 && 0 & 2189 & 0 \\
 
-Omitted Top Concepts & 9 & 9 & 0 &&&&&&&&&&&& \\
+Omitted Top Concepts & 9 & 9 & 0 & 0 & 1 && 0 & 0 & 0 & 1 & 18 && 0 & 0 & 0 \\
 
-Top Concept Having Broader Concepts & 0 & 0 & 0 &&&&&&&&&&&& \\
+Top Concept Having Broader Concepts & 0 & 0 & 0 & 1 & 0 && 0 & 0 & 0 & 0 & 0 && 0 & 0 & 0 \\
 
@@
 
-Missing In-Links &&&&&&&&&&&&&&& \\
+Missing In-Links &&&&&&&&&&&&&&& 13411 \\
 
-Missing Out-Links &&&&&&&&&&&&&&& \\
+Missing Out-Links &&&&&&&&&&&&&&& 13411 \\
 
-Broken Links &&&&&&&&&&&&&&& \\
+Broken Links & 0 & 0 & 1 & 99 &&& 238 & 0* & 11 & 7 && 425 & 1 & 3169 & n/a \\
 

### 2012-03-24 analysis.tex
added some more numeric values, resolved some todos

@@
 \toprule
-Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171991 && 178776 & 50892 & 343980 & 9 & 0 \\
+Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171991 & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
 \hline
@@
 \hline
-University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1125 && 0 & 0 & 0 & 0 & 0 \\
+University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1125 & 1125 & 0 & 0 & 0 & 0 & 0 \\
 \hline
-New York Times People & \textbf{NYTP} & 2010/06/22 & 4979 && 4979 & 0 & 4979 & 1 & 0 \\
+New York Times People & \textbf{NYTP} & 2010/06/22 & 4979 & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
 \hline
-Library of Congress Subject Headings & \textbf{LCSH} & ? & 459182 && 746076 & 595754 & 815816 & 19 & 0 \\
+Library of Congress Subject Headings & \textbf{LCSH} & 2011/08/09 & 459182 & 407908 & 746076 & 595754 & 815816 & 19 & 0 \\
 \hline
-Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 && 569 & 1698 & 6 & 2 & 0 \\
+Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 & 422 & 569 & 1698 & 6 & 2 & 0 \\
 \hline
@@
 
-Undocumented Concepts & 96850 & 0 & 1807 & 1918 & 5341 & 4551 & 32035 & 743410 & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\
+Undocumented Concepts & 96850 & 0 & 1807 & 1918 & 5341 & 4551 & 32035 & 743410 & 1125 & 4094 & 398036 & 422 & 5236 & 3259 & 13411 \\
 
@@
 
-Valueless Associative Relations & 9438 & 0 & 495 & 0 & 1 && 282 & 8120 & 0 & 0 & 1879 && 5082 & 0 & 5 \\
+Valueless Associative Relations & 9438 & 0 & 495 & 0 & 1 && 282 & 8120 & 0 & 0 & 1879 & 0 & 5082 & 0 & 5 \\
 
-Solely Transitively Related Concepts & 0 & 0 & 0 & 0 & 2652 && 0 & 0 & 0 & 0 & 0 && 0 & 2189 & 0 \\
+Solely Transitively Related Concepts & 0 & 0 & 0 & 0 & 2652 && 0 & 0 & 0 & 0 & 0 & 36 & 0 & 2189 & 0 \\
 
-Omitted Top Concepts & 9 & 9 & 0 & 0 & 1 && 0 & 0 & 0 & 1 & 18 && 0 & 0 & 0 \\
+Omitted Top Concepts & 9 & 9 & 0 & 0 & 1 && 0 & 0 & 0 & 1 & 18 & 0 & 0 & 0 & 0 \\
 
-Top Concept Having Broader Concepts & 0 & 0 & 0 & 1 & 0 && 0 & 0 & 0 & 0 & 0 && 0 & 0 & 0 \\
+Top Concept Having Broader Concepts & 0 & 0 & 0 & 1 & 0 && 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 
@@
 
-Missing In-Links &&&&&&&&&&&&&&& 13411 \\
+Missing In-Links && 19 && 1686 &&&&& 1125 & 20 && 422 & 6516 & 2213 & 13411 \\
 
-Missing Out-Links &&&&&&&&&&&&&&& 13411 \\
+Missing Out-Links && 671 && 1472 &&&&& 1116 & 0 && 273 & 6524 & 0 & 13411 \\
 
-Broken Links & 0 & 0 & 1 & 99 &&& 238 & 0* & 11 & 7 && 425 & 1 & 3169 & n/a \\
+Broken Links & 0 & 0 & 1 & 163 &&& 238 & 0* & 11 & 7 && 425 & 1 & 3169 & n/a \\
 
@@
 Eurovoc and NAICS use SKOS-XL labels, which are currently not supported by qSKOS.
-Incomplete Language Coverage were issues in the three analyzed vocabularies: in AGROVOC all concepts had incomplete coverage, probably because \todo{CM}{why?}, and in STW we found XX\%.
+Incomplete Language Coverage were issues in the three analyzed vocabularies: in AGROVOC all concepts had incomplete coverage, probably because \todo{CM}{es gibt labels in insgesamt 25 versch sprachen und keines der konzepte ist in jeder sprache beschrieben}, and in STW we found XX\%.
 Most vocabularies didn't document their concepts with the documentary properties defined by SKOS.

### 2012-03-24 related_work.tex
added some more numeric values, resolved some todos

@@
 
-Ontology evaluation is task of measuring the quality of an ontology and has extensively been discussed by Vrandecic~[\todo{CM}{ref denny}].
-Gangemi [\todo{CM}{ref ?}] introduced structural, functional and usability-related measures for ontology evaluation, Arpinar [\todo{CM}{ref ?}] define three types of conflicts that may occur in ontologies, and also Tartir et al.[\todo{CM}{ref ?}] propose a framework for evaluation and ranking of ontologies.
+Ontology evaluation is task of measuring the quality of an ontology and has extensively been discussed by Vrandecic~\cite{Vrandecic2010}.
+Gangemi~\cite{Gangemi2006} introduced structural, functional and usability-related measures for ontology evaluation, Arpinar~\cite{Arpinar2006} define three types of conflicts that may occur in ontologies, and also Tartir et al.~\cite{Tartir2007} propose a framework for evaluation and ranking of ontologies.
 Although there are definitely overlaps between ontology evaluation and our research, the quality issues we identified are less tight to underlying data model and formal ontology definition language but, to a large extent, derived from manuals and guidelines taxonomist use in their daily work.

### 2012-03-25 analysis.tex
added numeric values
table reordering, decimal delimiters

@@
 
+\todo{BH}{I think we can remove the collections column, none of the issues involve collections}
+
 \subsection{Vocabulary Data Set}
@@
 We used Sindice and available listings\footnote{\url{http://www.w3.org/2001/sw/wiki/SKOS/Datasets}} to learn about existing SKOS vocabularies.
-Table~\ref{tab:vocabs} lists our representative vocabulary selection \todo{CM}{alphabetically} and shows that the vocabularies differ in size and application domain: the \emph{Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA)} is vocabulary from the media domain, \emph{Eurovoc} and the \emph{Integrated Public Sector Vocabularies (PSV)} cover public sector concepts, the \emph{Medical Subject Headings (MeSH)} and \emph{Peroxisome Knowledge Base (PXV)} are from the (bio-)medical domain, the \emph{Geonames Ontology} covers locations, the \emph{Thesaurus for Economics (STW)} and \emph{North American Industry Classification System (NAICS)} are vocabularies from the economics and business area and the \emph{DBPedia Categories} reflect Wikipedia's user-generated categorization system.
+Table~\ref{tab:vocabs} lists our representative vocabulary selection and shows that the vocabularies differ in size and application domain: the \emph{Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA)} is vocabulary from the media domain, \emph{Eurovoc} and the \emph{Integrated Public Sector Vocabularies (PSV)} cover public sector concepts, the \emph{Medical Subject Headings (MeSH)} and \emph{Peroxisome Knowledge Base (PXV)} are from the (bio-)medical domain, the \emph{Geonames Ontology} covers locations, the \emph{Thesaurus for Economics (STW)} and \emph{North American Industry Classification System (NAICS)} are vocabularies from the economics and business area and the \emph{DBPedia Categories} reflect Wikipedia's user-generated categorization system.
 We also include the \emph{Meketre} vocabulary, which defines Egyptology-related concepts, and the non-public \emph{Austrian Armed Forces Thesaurus (LVAk)}, which we generated from CSV files provided by the vocabulary maintainers.
 A zip-file containing all 14 public vocabulariesx we used in our analysis, can be downloaded from: \url{http://www.github.com/cmader/???}.
+In contrast to the column ``Concepts'' that shows the total number of SKOS Concepts that can be infered from the vocabulary, the column ``Authoritative Concepts`` lists only those concepts that have an URI in the namespace of the vocabulary.
 
@@
 
-\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbrev.}} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth.
+\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth.
 Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
 \toprule
-Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171991 & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
+Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32,035 & 32,035 & 620,629 & 65,934 & 32,085 & 1 & 0 \\
+\hline
+DBpedia Categories & \textbf{DBpedia} & ? & 743,410 & 743,410 & 740,352 & 1,490,316 & 0 & 0 & 0 \\
+\hline
+The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6,797 & 6,797 & 457,788 & 18,491 & 15,512 & 128 & 0 \\
 \hline
@@
 \hline
-Medical Subject Headings & \textbf{MeSH} & ? & 24626 & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
+Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171,991 & 171,991 & 178,776 & 50,892 & 343,980 & 9 & 0 \\
 \hline
-Peroxisome Knowledge Base & \textbf{PXV} & 1.6 & 2112 & 1686 & 3628 & 2695 & 1716 & 1 & 0 \\
+Integrated Public Sector Vocabulary & \textbf{IPSV} & 2.00 & 4,732 && 7,945 & 13,843 & 4,483 & 3 & 0 \\
 \hline
-The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6797 && 457788 & 18491 & 15512 & 128 & 0 \\
+Library of Congress Subject Headings & \textbf{LCSH} & 2011/08/09 & 459,182 & 407,908 & 746,076 & 595,754 & 815,816 & 19 & 0 \\
 \hline
-Integrated Public Sector Vocabulary & \textbf{IPSV} & 2.00 & 4732 && 7945 & 13843 & 4483 & 3 & 0 \\
+Austrian Armed Forces Thesaurus & \textbf{LVAk} & n/a & 13,411 & 13,411 & 17,250 & 16,346 & 0 & 0 & 0 \\
 \hline
-Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32035 && 620629 & 65934 & 32085 & 1 & 0 \\
+Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 & 422 & 569 & 1,698 & 6 & 2 & 0 \\
 \hline
-DBpedia Categories & \textbf{DBPedia} & ? & 743410 && 740352 & 1490316 & 0 & 0 & 0 \\
+Medical Subject Headings & \textbf{MeSH} & ? & 24,626 & 24,626 & 150,617 & 38,858 & 0 & 0 & 0 \\
 \hline
-University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1125 & 1125 & 0 & 0 & 0 & 0 & 0 \\
+North American Industry Classification System & \textbf{NAICS} & 2012 & 4,175 & 2,213 & 0 & 8,684 & 2,235 & 1 & 0 \\
 \hline
-New York Times People & \textbf{NYTP} & 2010/06/22 & 4979 & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
+New York Times People & \textbf{NYTP} & 2010/06/22 & 4,979 & 4,979 & 4,979 & 0 & 4,979 & 1 & 0 \\
 \hline
-Library of Congress Subject Headings & \textbf{LCSH} & 2011/08/09 & 459182 & 407908 & 746076 & 595754 & 815816 & 19 & 0 \\
+University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1,125 & 1,125 & 0 & 0 & 0 & 0 & 0 \\
 \hline
-Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 & 422 & 569 & 1698 & 6 & 2 & 0 \\
+Peroxisome Knowledge Base & \textbf{PXV} & 1.6 & 2,112 & 1,686 & 3,628 & 2,695 & 1,716 & 1 & 0 \\
 \hline
-Thesaurus for Economics & \textbf{STW} & 8.06 & 6524 && 31189 & 57907 & 6531 & 1 & 0 \\
-\hline
-North American Industry Classification System & \textbf{NAICS} & 2012 & 4175 && 0 & 8684 & 2235 & 1 & 0 \\
-\hline
-Austrian Armed Forces Thesaurus & \textbf{LVAk} & n/a & 13411 && 17250 & 16346 & 0 & 0 & 0 \\
+Thesaurus for Economics & \textbf{STW} & 8.06 & 6,524 & 6,524 & 31,189 & 57,907 & 6,531 & 1 & 0 \\
 \bottomrule
@@
 The value 0 means that we haven't found any affected resource, N/A means that a certain function was not applicable for reasons we explain below.
+An asterisk after certain numeric values indicates that due to performance reason, only an extrapolated subset containing 5\% of the respective elements (HTTP URIs or concepts) of the vocabulary has been analyzed.
 
@@
 \toprule
-Omitted or Invalid Language Tags & 0 & 0 & 23950 & 1578 & n/a & 0 & 0 & 0 & 1224 & 0 & 18 & 0 & 2 & n/a & 13411 \\
+Omitted or Invalid Language Tags & 0 & 0 & 23,950 & 1,578 & n/a & 0 & 0 & 0 & 1,224 & 0 & 18 & 0 & 2 & n/a & 13,411 \\
 
-Incomplete Language Coverage & 0 & 0 & 0 & 0 & n/a & 0 & 32035 & 0 & 0 & 0 & 0 & 420 & 6456 & n/a & 0 \\
+Incomplete Language Coverage & 0 & 0 & 0 & 0 & n/a & 0 & 32,035 & 0 & 0 & 0 & 0 & 420 & 6,456 & n/a & 0 \\
 
-Undocumented Concepts & 96850 & 0 & 1807 & 1918 & 5341 & 4551 & 32035 & 743410 & 1125 & 4094 & 398036 & 422 & 5236 & 3259 & 13411 \\
+Undocumented Concepts & 96,850 & 0 & 1,807 & 1,918 & 5,341 & 4,551 & 32,035 & 743,410 & 1,125 & 4,094 & 398,036 & 422 & 5,236 & 3,259 & 13,411 \\
 
-Label Conflicts & 12404 & 18 & 0 & 7 & n/a & 0 & 2949 & 0 & 0 & 0 & tba & 4 & 5 & n/a & 13 \\
+Label Conflicts & 12,404 & 18 & 0 & 7 & n/a & 0 & 2,949 & 0 & 0 & 0 & tba & 4 & 5 & n/a & 13 \\
 
@@
 
-Orphan Concepts & 162000 & 671 & 0 & 2 & 7 & 0 & 0 & 77062 & 1125 & 4979 & 172364 & 0 & 4 & 0 & 21 \\
+Orphan Concepts & 162,000 & 671 & 0 & 2 & 7 & 0 & 0 & 77,062 & 1,125 & 4,979 & 172,364 & 0 & 4 & 0 & 21 \\
 
-Weakly Connected Components & 621 & 0 & 4 & 10 & 4 & 1 & 4 & 1506 & 0 & 0 & 22131 & 5 & 1 & 1 & 11 \\
+Weakly Connected Components & 621 & 0 & 4 & 10 & 4 & 1 & 4 & 1,506 & 0 & 0 & 22,131 & 5 & 1 & 1 & 11 \\
 
-Cyclic Hierarchical Relations & 0 & 0 & 4 & 0 & 0 & 0 & 0 & 1132 & 0 & 0 & 0 & 0 & 0 & 0 & 5 \\
+Cyclic Hierarchical Relations & 0 & 0 & 4 & 0 & 0 & 0 & 0 & 1,132 & 0 & 0 & 0 & 0 & 0 & 0 & 5 \\
 
-Valueless Associative Relations & 9438 & 0 & 495 & 0 & 1 && 282 & 8120 & 0 & 0 & 1879 & 0 & 5082 & 0 & 5 \\
+Valueless Associative Relations & 9,438 & 0 & 495 & 0 & 1 && 282 & 8,120 & 0 & 0 & 1,879 & 0 & 5,082 & 0 & 5 \\
 
-Solely Transitively Related Concepts & 0 & 0 & 0 & 0 & 2652 && 0 & 0 & 0 & 0 & 0 & 36 & 0 & 2189 & 0 \\
+Solely Transitively Related Concepts & 0 & 0 & 0 & 0 & 2,652 && 0 & 0 & 0 & 0 & 0 & 36 & 0 & 2,189 & 0 \\
 
@@
 
-Missing In-Links && 19 && 1686 &&&&& 1125 & 20 && 422 & 6516 & 2213 & 13411 \\
+Missing In-Links && 19 && 1,686 &&&&& 1,125 & 20 && 422 & 6,516 & 2,213 & 13,411 \\
 
-Missing Out-Links && 671 && 1472 &&&&& 1116 & 0 && 273 & 6524 & 0 & 13411 \\
+Missing Out-Links & 171,991 & 671 && 1,472 & 6,797 && 32,035 & 743,410 & 1,116 & 0 & 408,198 & 273 & 6,524 & 0 & 13,411 \\
 
-Broken Links & 0 & 0 & 1 & 163 &&& 238 & 0* & 11 & 7 && 425 & 1 & 3169 & n/a \\
+Broken Links & 0 & 0 & 1 & 163 &&& 238 & 0* & 11 & 7 && 425 & 1 & 3,169 & n/a \\
 

### 2012-03-26 analysis.tex
added authoritative concepts comment
added some more analysis data
added some keywords for results interpretation

@@
 
-\todo{BH}{I think we can remove the collections column, none of the issues involve collections}
-
 \subsection{Vocabulary Data Set}
@@
 A zip-file containing all 14 public vocabulariesx we used in our analysis, can be downloaded from: \url{http://www.github.com/cmader/???}.
-In contrast to the column ``Concepts'' that shows the total number of SKOS Concepts that can be infered from the vocabulary, the column ``Authoritative Concepts`` lists only those concepts that have an URI in the namespace of the vocabulary.
 
@@
 \textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth.
-Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
+Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} \\
 \toprule
-Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32,035 & 32,035 & 620,629 & 65,934 & 32,085 & 1 & 0 \\
+Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32,035 & 32,035 & 620,629 & 65,934 & 32,085 & 1 \\
 \hline
-DBpedia Categories & \textbf{DBpedia} & ? & 743,410 & 743,410 & 740,352 & 1,490,316 & 0 & 0 & 0 \\
+DBpedia Categories & \textbf{DBpedia} & ? & 743,410 & 743,410 & 740,352 & 1,490,316 & 0 & 0 \\
 \hline
-The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6,797 & 6,797 & 457,788 & 18,491 & 15,512 & 128 & 0 \\
+The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6,797 & 6,797 & 457,788 & 18,491 & 15,512 & 128 \\
 \hline
-Geonames Ontology & \textbf{Geonames} & 2.2.1 & 671 & 671 & 671 & 0 & 671 & 9 & 0 \\
+Geonames Ontology & \textbf{Geonames} & 2.2.1 & 671 & 671 & 671 & 0 & 671 & 9 \\
 \hline
-Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171,991 & 171,991 & 178,776 & 50,892 & 343,980 & 9 & 0 \\
+Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171,991 & 171,991 & 178,776 & 50,892 & 343,980 & 9 \\
 \hline
-Integrated Public Sector Vocabulary & \textbf{IPSV} & 2.00 & 4,732 && 7,945 & 13,843 & 4,483 & 3 & 0 \\
+Integrated Public Sector Vocabulary & \textbf{IPSV} & 2.00 & 4,732 & 3,080 & 7,945 & 13,843 & 4,483 & 3 \\
 \hline
-Library of Congress Subject Headings & \textbf{LCSH} & 2011/08/09 & 459,182 & 407,908 & 746,076 & 595,754 & 815,816 & 19 & 0 \\
+Library of Congress Subject Headings & \textbf{LCSH} & 2011/08/09 & 459,182 & 407,908 & 746,076 & 595,754 & 815,816 & 19 \\
 \hline
-Austrian Armed Forces Thesaurus & \textbf{LVAk} & n/a & 13,411 & 13,411 & 17,250 & 16,346 & 0 & 0 & 0 \\
+Austrian Armed Forces Thesaurus & \textbf{LVAk} & n/a & 13,411 & 13,411 & 17,250 & 16,346 & 0 & 0 \\
 \hline
-Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 & 422 & 569 & 1,698 & 6 & 2 & 0 \\
+Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 & 422 & 569 & 1,698 & 6 & 2 \\
 \hline
-Medical Subject Headings & \textbf{MeSH} & ? & 24,626 & 24,626 & 150,617 & 38,858 & 0 & 0 & 0 \\
+Medical Subject Headings & \textbf{MeSH} & ? & 24,626 & 24,626 & 150,617 & 38,858 & 0 & 0 \\
 \hline
-North American Industry Classification System & \textbf{NAICS} & 2012 & 4,175 & 2,213 & 0 & 8,684 & 2,235 & 1 & 0 \\
+North American Industry Classification System & \textbf{NAICS} & 2012 & 4,175 & 2,213 & 0 & 8,684 & 2,235 & 1 \\
 \hline
-New York Times People & \textbf{NYTP} & 2010/06/22 & 4,979 & 4,979 & 4,979 & 0 & 4,979 & 1 & 0 \\
+New York Times People & \textbf{NYTP} & 2010/06/22 & 4,979 & 4,979 & 4,979 & 0 & 4,979 & 1 \\
 \hline
-University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1,125 & 1,125 & 0 & 0 & 0 & 0 & 0 \\
+University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1,125 & 1,125 & 0 & 0 & 0 & 0 \\
 \hline
-Peroxisome Knowledge Base & \textbf{PXV} & 1.6 & 2,112 & 1,686 & 3,628 & 2,695 & 1,716 & 1 & 0 \\
+Peroxisome Knowledge Base & \textbf{PXV} & 1.6 & 2,112 & 1,686 & 3,628 & 2,695 & 1,716 & 1 \\
 \hline
-Thesaurus for Economics & \textbf{STW} & 8.06 & 6,524 & 6,524 & 31,189 & 57,907 & 6,531 & 1 & 0 \\
+Thesaurus for Economics & \textbf{STW} & 8.06 & 6,524 & 6,524 & 31,189 & 57,907 & 6,531 & 1 \\
 \bottomrule
@@
 
-Valueless Associative Relations & 9,438 & 0 & 495 & 0 & 1 && 282 & 8,120 & 0 & 0 & 1,879 & 0 & 5,082 & 0 & 5 \\
+Valueless Associative Relations & 9,438 & 0 & 495 & 0 & 1 & 239 & 282 & 8,120 & 0 & 0 & 1,879 & 0 & 5,082 & 0 & 5 \\
 
-Solely Transitively Related Concepts & 0 & 0 & 0 & 0 & 2,652 && 0 & 0 & 0 & 0 & 0 & 36 & 0 & 2,189 & 0 \\
+Solely Transitively Related Concepts & 0 & 0 & 0 & 0 & 2,652 & 0 & 0 & 0 & 0 & 0 & 0 & 36 & 0 & 2,189 & 0 \\
 
-Omitted Top Concepts & 9 & 9 & 0 & 0 & 1 && 0 & 0 & 0 & 1 & 18 & 0 & 0 & 0 & 0 \\
+Omitted Top Concepts & 9 & 9 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 1 & 18 & 0 & 0 & 0 & 0 \\
 
-Top Concept Having Broader Concepts & 0 & 0 & 0 & 1 & 0 && 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+Top Concept Having Broader Concepts & 0 & 0 & 0 & 1 & 0 &0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 
@@
 
-Missing In-Links && 19 && 1,686 &&&&& 1,125 & 20 && 422 & 6,516 & 2,213 & 13,411 \\
+Missing In-Links & 171,980* & 19 && 1,686 & 6,796 & 3,080 & 32,035 & 733,800* & 1,125 & 20 & 404,540* & 422 & 6,516 & 2,213 & 13,411 \\
 
-Missing Out-Links & 171,991 & 671 && 1,472 & 6,797 && 32,035 & 743,410 & 1,116 & 0 & 408,198 & 273 & 6,524 & 0 & 13,411 \\
+Missing Out-Links & 171,991 & 671 && 1,472 & 6,797 & 0 & 32,035 & 743,410 & 1,116 & 0 & 408,198 & 273 & 6,524 & 0 & 13,411 \\
 
@@
 % Labeling and Documentation Issues
+\todo{BH}{this sentence is not clear, I assume you mean language tags, not labels.I'm not sure if relating language tags to concepts makes sense because a concept can be connected to multiple labels}
 We found labeling and documentation issues in all analyzed vocabularies.
@@
 Eurovoc and NAICS use SKOS-XL labels, which are currently not supported by qSKOS.
+
 Incomplete Language Coverage were issues in the three analyzed vocabularies: in AGROVOC all concepts had incomplete coverage, probably because \todo{CM}{es gibt labels in insgesamt 25 versch sprachen und keines der konzepte ist in jeder sprache beschrieben}, and in STW we found XX\%.
+
 Most vocabularies didn't document their concepts with the documentary properties defined by SKOS.
+
 Label conflicts, hence \todo{CM}{explain briefly} were found in several vocabularies: GTAA has many because? PXV has 7. Why given examples?
@@
 % Structural Issues
+orphan concepts: seem to depend on vocab use case: list of names: many orphans (gtaa,lcsh,geonames); vocabs establishing a network of terms: less to none orphan concepts
+
+wcc: "islands" of semantically related concepts; most interesting cases: vocabs having few orphan concepts but more than one wcc: vocab may split into clusters inintentionally
+
+cycles: not a common issue, dbpedia category cylces were somewhat surprising
+
+valueless associative relations: in 9 of 15 vocabs; comparatively few in relation to all semantic relations
+
+solely transitively related concepts: only 3 of 15 vocabs
+
+omitted top concepts: 11 vocabs have at least one concept scheme defined, 5 have missing top concepts; gtaa,geonames,nyt people have no top concepts for any concept scheme, eurovoc uses 128 concept schemes and only one without top concept; opposite case for lcsh: uses 19 concept schemes defined, only one has a top concept
+
+top concepts having broader concept: only pxv vocab affected in current version: in earlier version a different concept featuring this issue could be spotted: according to vocab creator this was an erroneous concept still available in the triplestore; maybe introduced by some bug in the vocab management software
 
 % Linked Data Specific Issues
+missing in-links: authoritative conceps of most vocabs aren't externally linked; exception: nyt people vocab
+
+missing out-links: many vocab's also don't provide links to other vocabs; exception: naics, nyt people
+
+broken loinks: meketre: reason server-side misconfiguration (fixed in current version); dbpedia sometimes down, link checking for some vocabs difficult: our algorithm waits 3secs when dereferencing links to not produce an uninteded DOS attack => estimation was necessary
+
+undef skos resources: seems to be a minor problems, the examined voabs seem to be well-maintained
 

### 2012-03-26 criteria.tex
added some keywords for results interpretation

@@
 % Function definition
-The function \textit{mil} estimates the number of in-links referencing a concept, by iterating over all elements in $C$ and querying the Sindice SPARQL endpoint for triples containing the concept's URI in the object part.
+To estimate the number of in-links we only take a set $AC \subseteq C$ into account which consists of all ``authoritative concepts'', i.e.
+concepts that have an URI in the namespace of the vocabulary.
+The function \textit{mil} estimates the number of in-links referencing an authoritative concept, by iterating over all elements in $AC$ and querying the Sindice SPARQL endpoint for triples containing the concept's URI in the object part.
 Empty query results are indicator for missing in-links and are thus included in the result set of this function.

### 2012-03-26 analysis.tex
rephrased results section

@@
 
-Label Conflicts & 12,404 & 18 & 0 & 7 & n/a & 0 & 2,949 & 0 & 0 & 0 & tba & 4 & 5 & n/a & 13 \\
+Label Conflicts & 12,404 & 18 & 0 & 7 & n/a & 0 & 2,949 & 0 & 0 & 0 & n/a & 4 & 5 & n/a & 13 \\
 
@@
 
-Broken Links & 0 & 0 & 1 & 163 &&& 238 & 0* & 11 & 7 && 425 & 1 & 3,169 & n/a \\
+Broken Links & 0 & 0 & 1 & 163 && 1 & 238 & 0* & 11 & 7 && 425 & 1 & 3,169 & n/a \\
 
@@
 % Labeling and Documentation Issues
-\todo{BH}{this sentence is not clear, I assume you mean language tags, not labels.I'm not sure if relating language tags to concepts makes sense because a concept can be connected to multiple labels}
 We found labeling and documentation issues in all analyzed vocabularies.
-PXV provides labels for XX\% of its concepts, Pressinfo labels only for 1 out of 1125 concepts, and the STW thesaurus misses labels for two concepts.
+In nearly half of the evaluated vocabularies, language tags are used properly while others show a significant number of untaged resources.
+Incomplete Language Coverage were issues in three analyzed vocabularies, with e.g., AGROVOC supporting in total 25 languages but none of the concepts is documented in all of them.
+Most vocabularies didn't document their concepts with the documentary properties defined by SKOS.
+Label conflicts were also frequently observed, hence \todo{CM}{explain briefly} were found in several vocabularies: GTAA has many because?
+PXV has 7.
+Why given examples?
+
+%\todo{BH}{this sentence is not clear, I assume you mean language tags, not labels.I'm not sure if relating language tags to concepts makes sense because a concept can be connected to multiple labels}PXV provides labels for XX\% of its concepts, Pressinfo labels only for 1 out of 1125 concepts, and the STW thesaurus misses labels for two concepts.
 Eurovoc and NAICS use SKOS-XL labels, which are currently not supported by qSKOS.
-
 Incomplete Language Coverage were issues in the three analyzed vocabularies: in AGROVOC all concepts had incomplete coverage, probably because \todo{CM}{es gibt labels in insgesamt 25 versch sprachen und keines der konzepte ist in jeder sprache beschrieben}, and in STW we found XX\%.
 
-Most vocabularies didn't document their concepts with the documentary properties defined by SKOS.
-
-Label conflicts, hence \todo{CM}{explain briefly} were found in several vocabularies: GTAA has many because? PXV has 7. Why given examples?
-
 % Structural Issues
-orphan concepts: seem to depend on vocab use case: list of names: many orphans (gtaa,lcsh,geonames); vocabs establishing a network of terms: less to none orphan concepts
-
-wcc: "islands" of semantically related concepts; most interesting cases: vocabs having few orphan concepts but more than one wcc: vocab may split into clusters inintentionally
-
-cycles: not a common issue, dbpedia category cylces were somewhat surprising
-
-valueless associative relations: in 9 of 15 vocabs; comparatively few in relation to all semantic relations
-
-solely transitively related concepts: only 3 of 15 vocabs
-
-omitted top concepts: 11 vocabs have at least one concept scheme defined, 5 have missing top concepts; gtaa,geonames,nyt people have no top concepts for any concept scheme, eurovoc uses 128 concept schemes and only one without top concept; opposite case for lcsh: uses 19 concept schemes defined, only one has a top concept
-
-top concepts having broader concept: only pxv vocab affected in current version: in earlier version a different concept featuring this issue could be spotted: according to vocab creator this was an erroneous concept still available in the triplestore; maybe introduced by some bug in the vocab management software
+It could be observed that vocabularies that contain person or location names (GTAA and Geonames) have more orphan concepts than other vocabularies, establishing a network of terms in a specific domain (e.g., STW).
+Regarding weakly connected components, we see that those vocabularies that only consist of orphan concepts, contain no weakly connected components.
+Three vocabularies have one weakly connected component which means that there is one ``giant component''.
+All other vocabularies split into several ``islands'' of semantically related concepts.
+Hierarchical cycles are observed not to be a common issue, however they affect DBpedia to a great extent \todo{CM}{reason?}.
+Valueless associative relations occur in 9 vocabularies, with their total number being relatively low compared to the total number of all semantic relations in the respective vocabularies.
+GTAA, Geonames, and NYTP have no top concept defined for any of the concept schemes they use.
+Eurovoc uses 128 concept schemes but only one without top concept.
+The opposite situation can be observed for LCSH which uses 19 concept schemes, but only one has a top concept.
+Only PXV vocabulary is affected by top concepts having broader concept in the current version.
+In an earlier version a different concept causing this issue could be spotted.
+According to the vocabulary creator it was an abaondoned concept, still available in the triplestore but maybe introduced by some bug in the vocabulary management software.
 
 % Linked Data Specific Issues
-missing in-links: authoritative conceps of most vocabs aren't externally linked; exception: nyt people vocab
-
-missing out-links: many vocab's also don't provide links to other vocabs; exception: naics, nyt people
-
-broken loinks: meketre: reason server-side misconfiguration (fixed in current version); dbpedia sometimes down, link checking for some vocabs difficult: our algorithm waits 3secs when dereferencing links to not produce an uninteded DOS attack => estimation was necessary
-
-undef skos resources: seems to be a minor problems, the examined voabs seem to be well-maintained
+With exception of NYTP and geonames we could observe that authoritative concepts of most vocabularies do not serve at link targets for other vocabularies.
+A slightly better situation can be found for missing out-links where most vocabularies also don't provide links to other vocabularies on the Web.
+There are three excepetions:  NYTP, IPSV and NAICS.
+Broken links are a very common issue in nearly every vocabulary.
+In the case of the Meketre vocabulary we could observe server-side misconfiguration as the cause.
+Checking this issue turned out difficult, taking into account the high number of links (over 400,000 in Eurovoc and LCSH) and our algorithm that sleeps three seconds after dereferencing each link in order to avoid an unintended DOS attack.
+So we decided to only check a subset of all links and extrapolate the results.
+Undefined SKOS resources seem to be a minor issue, we could only spot two of them in all vocabularies.
 

### 2012-03-26 conclusions.tex
added some keywords for results interpretation
rephrased results section

@@
 We also analyzed a representative set of existing SKOS vocabularies and found real-world occurrences for all these issues.
-\todo{CM}{one more sentence highlighting what kind of issues were omnipresent.}.
+
+Among the most omnipresent issues we found during analyzing the chosen set of vocabularies were missing or incomplete language information as well as orphan concepts.
+It also turned out that there is room for a more intense interlinking of SKOS vocabularies.
 
@@
 
-We aware that the quality issues we described in this work are purely quantitative indicators that, on their own, cannot be generalized into statements about the quality of a vocabulary.
+We are aware that the quality issues we described in this work are purely quantitative indicators that, on their own, cannot be generalized into statements about the quality of a vocabulary.
 To learn more about the real-world impact of our work, we would like to conduct a qualitative study in which we confront taxonomists with our results.

### 2012-03-26 analysis.tex
added mil for mesh

@@
 
-\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth.
+\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{Version/Year}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth.
 Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} \\
@@
 \hline
-DBpedia Categories & \textbf{DBpedia} & ? & 743,410 & 743,410 & 740,352 & 1,490,316 & 0 & 0 \\
+DBpedia Categories & \textbf{DBpedia} & 3.7 & 743,410 & 743,410 & 740,352 & 1,490,316 & 0 & 0 \\
 \hline
@@
 \hline
-Medical Subject Headings & \textbf{MeSH} & ? & 24,626 & 24,626 & 150,617 & 38,858 & 0 & 0 \\
+Medical Subject Headings & \textbf{MeSH} & 2006 & 24,626 & 24,626 & 150,617 & 38,858 & 0 & 0 \\
 \hline
@@
 
-Missing In-Links & 171,980* & 19 && 1,686 & 6,796 & 3,080 & 32,035 & 733,800* & 1,125 & 20 & 404,540* & 422 & 6,516 & 2,213 & 13,411 \\
+Missing In-Links & 171,980* & 19 & 24625 & 1,686 & 6,796 & 3,080 & 32,035 & 733,800* & 1,125 & 20 & 404,540* & 422 & 6,516 & 2,213 & 13,411 \\
 
-Missing Out-Links & 171,991 & 671 && 1,472 & 6,797 & 0 & 32,035 & 743,410 & 1,116 & 0 & 408,198 & 273 & 6,524 & 0 & 13,411 \\
+Missing Out-Links & 171,991 & 671 & 24626 & 1,472 & 6,797 & 0 & 32,035 & 743,410 & 1,116 & 0 & 408,198 & 273 & 6,524 & 0 & 13,411 \\
 
@@
 All other vocabularies split into several ``islands'' of semantically related concepts.
-Hierarchical cycles are observed not to be a common issue, however they affect DBpedia to a great extent \todo{CM}{reason?}.
+Hierarchical cycles are observed not to be a common issue, however they affect DBpedia to a great extent because for some reason many of the concepts are related broader to themselves.
 Valueless associative relations occur in 9 vocabularies, with their total number being relatively low compared to the total number of all semantic relations in the respective vocabularies.

### 2012-03-26 analysis.tex
fixed 4.2

--- 2012-03-26 analysis.tex
@@
 
-\subsection{The qSKOS Quality Checking Tool}
+\subsection{The qSKOS Quality Assessment Tool}
 
-The open-source qSKOS\footnote{\url{https://github.com/cmader/qSKOS/}} quality assessment tool can be used to find possible quality issues a given SKOS vocabulary.
+The open-source qSKOS\footnote{\url{https://github.com/cmader/qSKOS/}} quality assessment tool can be used to find possible quality issues in a given SKOS vocabulary.
 Users can run the tool by passing a vocabulary and selecting the quality checking functions they want to perform.
@@
 qSKOS is implemented in Java and can be used as standalone command-line tool or API in any other application.
-Its design is open for the introduction of additional quality functions.
-In our analysis, we used qSKOS version 0.2., which can be downloaded from: \url{https://github.com/cmader/qSKOS/releases/qSKOS-0.2.tar.gz}.
+Its design is open for the introduction of additional quality checking functions.
+In our analysis, we used qSKOS version 0.1., which can be downloaded from: \url{https://github.com/cmader/qSKOS/zipball/v0.1}.
 
@@
 
-We used Sindice and available listings\footnote{\url{http://www.w3.org/2001/sw/wiki/SKOS/Datasets}} to learn about existing SKOS vocabularies.
-Table~\ref{tab:vocabs} lists our representative vocabulary selection and shows that the vocabularies differ in size and application domain: the \emph{Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA)} is vocabulary from the media domain, \emph{Eurovoc} and the \emph{Integrated Public Sector Vocabularies (PSV)} cover public sector concepts, the \emph{Medical Subject Headings (MeSH)} and \emph{Peroxisome Knowledge Base (PXV)} are from the (bio-)medical domain, the \emph{Geonames Ontology} covers locations, the \emph{Thesaurus for Economics (STW)} and \emph{North American Industry Classification System (NAICS)} are vocabularies from the economics and business area and the \emph{DBPedia Categories} reflect Wikipedia's user-generated categorization system.
-We also include the \emph{Meketre} vocabulary, which defines Egyptology-related concepts, and the non-public \emph{Austrian Armed Forces Thesaurus (LVAk)}, which we generated from CSV files provided by the vocabulary maintainers.
-A zip-file containing all 14 public vocabulariesx we used in our analysis, can be downloaded from: \url{http://www.github.com/cmader/???}.
+We used Sindice and available listings\footnote{\url{http://www.w3.org/2001/sw/wiki/SKOS/Datasets}} to learn about existing SKOS vocabularies and selected a subset, which differs in vocabulary size and application domain.
+We obtained the vocabularies either via direct Web download or by contacting the vocabulary maintainers.
+Further details about our vocabulary dataset are available in zip-file, which can be downloaded from: \url{http://www.github.com/cmader/???}.
+It also contains all but the non-public LVAk and PXV vocabularies.
+
+Table~\ref{tab:vocabs} shows our selection and summarizes basic statistical properties relevant for interpreting our results: the number of concepts $C$, ``authoritative concepts'', as explained in Section~\ref{subsec:ld_issues}, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations (\texttt{Labels}), all semantic relations $SR$, as well as the number of aggregation relations and concept schemes.
 
@@
 
-\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth.
+\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{\parbox{3cm}{Version/\\Last Modified}}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth.
 Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} \\
@@
 \hline
-Austrian Armed Forces Thesaurus & \textbf{LVAk} & n/a & 13,411 & 13,411 & 17,250 & 16,346 & 0 & 0 \\
+Austrian Armed Forces Thesaurus & \textbf{LVAk} & 0.9 & 13,411 & 13,411 & 17,250 & 16,346 & 0 & 0 \\
 \hline
@@
 \hline
-Medical Subject Headings & \textbf{MeSH} & ? & 24,626 & 24,626 & 150,617 & 38,858 & 0 & 0 \\
+Medical Subject Headings & \textbf{MeSH} & \cite{van2006method} & 24,626 & 24,626 & 150,617 & 38,858 & 0 & 0 \\
 \hline

### 2012-03-26 analysis.tex
finished label and documentation issue interpretation

@@
 
-The results of this analysis are reported in Table~\ref{tab:results}, which shows the absolute number of possibly affected resources for each quality checking function and vocabulary combination.
-The value 0 means that we haven't found any affected resource, N/A means that a certain function was not applicable for reasons we explain below.
-An asterisk after certain numeric values indicates that due to performance reason, only an extrapolated subset containing 5\% of the respective elements (HTTP URIs or concepts) of the vocabulary has been analyzed.
+The results of this analysis are summarized in Table~\ref{tab:results}, which shows the absolute number of affected resources for each quality checking function and vocabulary combination.
+The value 0 means that we haven't found any affected resource, n/a means that a certain function was not applicable for reasons we explain below.
+Numbers marked with an asterisk (*) were obtained by extrapolating from subsets containing 5\% of the respective vocabulary resources.
 
@@
 
-% Labeling and Documentation Issues
+% LABELING AND DOCUMENTATION ISSUES
 We found labeling and documentation issues in all analyzed vocabularies. 
-In nearly half of the evaluated vocabularies, language tags are used properly while others show a significant number of untaged resources.
-Incomplete Language Coverage were issues in three analyzed vocabularies, with e.g., AGROVOC supporting in total 25 languages but none of the concepts is documented in all of them.
-Most vocabularies didn't document their concepts with the documentary properties defined by SKOS.
-Label conflicts were also frequently observed, hence \todo{CM}{explain briefly} were found in several vocabularies: GTAA has many because?
-PXV has 7.
-Why given examples?
+% Omitted or Invalid Language Tags
+The \texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} vocabularies omit language tags with their skos:prefLabel, \texttt{skos:altLabel}, or \texttt{skos:hiddenLabel} properties.
+The STW thesaurus doesn't use language tags with 2 \texttt{skos:definition} property instances and the LCSH vocabulary uses language tags with concepts, but not with concept schemes.
+% Incomplete Language Coverage
+\texttt{AGROVOC} covers 25 languages in total but no single concept is labelled in all languages, in \texttt{Meketre} all concepts have English but only some of them French labels assigned.
+The reason for the high number of concepts with incomplete language coverage in \texttt{STW} is that a few concepts have labels with the private, but valid language tag \texttt{x-other}.
+% Undocumented Concepts
+\texttt{Geonames} is the only vocabulary in our dataset, which has at least one documentation property assigned to all its concept.
+All other vocabularies have a significant number of undocumented concepts.
+% Label Conflicts
+We also detected possible label conflicts in half of the vocabularies.
+\texttt{PXV}, for instance, uses the string ``primary peroxisomal enzyme deficiency'' with two concepts in the same concept scheme, but once with a \texttt{skos:prefLabel} and another time with a \texttt{skos:altLabel} property.
+A similar example from AGROVOC is ``sziv\'{a}rv\'{a}nyos pisztr\'{a}ng'', which is used as \texttt{skos:altLabel} with two different concepts.
+% Other stuff
+The \texttt{Eurovoc} and \texttt{NAICS} vocabularies use SKOS-XL for its labels, which is currently not supported by qSKOS.
 
-%\todo{BH}{this sentence is not clear, I assume you mean language tags, not labels.I'm not sure if relating language tags to concepts makes sense because a concept can be connected to multiple labels}PXV provides labels for XX\% of its concepts, Pressinfo labels only for 1 out of 1125 concepts, and the STW thesaurus misses labels for two concepts.
-Eurovoc and NAICS use SKOS-XL labels, which are currently not supported by qSKOS.
-Incomplete Language Coverage were issues in the three analyzed vocabularies: in AGROVOC all concepts had incomplete coverage, probably because \todo{CM}{es gibt labels in insgesamt 25 versch sprachen und keines der konzepte ist in jeder sprache beschrieben}, and in STW we found XX\%.
-
-% Structural Issues
+% STRUCTURAL ISSUES
 It could be observed that vocabularies that contain person or location names (GTAA and Geonames) have more orphan concepts than other vocabularies, establishing a network of terms in a specific domain (e.g., STW).

### 2012-03-26 analysis.tex
contd. structure interpretation

@@
 % STRUCTURAL ISSUES
-It could be observed that vocabularies that contain person or location names (GTAA and Geonames) have more orphan concepts than other vocabularies, establishing a network of terms in a specific domain (e.g., STW).
-Regarding weakly connected components, we see that those vocabularies that only consist of orphan concepts, contain no weakly connected components.
+When analyzing the structure of existing vocabularies, we found that the results of certain quality checks can be seen as indicators for the types of vocabularies.
+% Orphan Concepts
+In the \texttt{Pressinfo} and \texttt{NYTP} vocabulary, all concepts are orphan concepts, which means that these vocabularies are authority files rather than thesauri or taxonomies.
+\texttt{GTAA} seems is a mixture of name authority file (~162K concepts) and thesaurus (~10K concepts).
+The 4 orphan concepts in \texttt{STW} hare deprecated concepts, the 21 in \texttt{LVAk} are concepts, which are obviously test data.
+% Weakly Connected Components
 Three vocabularies have one weakly connected component which means that there is one ``giant component''.
 All other vocabularies split into several ``islands'' of semantically related concepts.
-Hierarchical cycles are observed not to be a common issue, however they affect DBpedia to a great extent because for some reason many of the concepts are related broader to themselves.
+\todo{CM}{think about it}.
+% Cyclic Hierarchical Relations
+Hierarchical cycles are not a common issue except in collaboratively created DBpedia vocabulary, where many concepts have reflexive \texttt{skos:broader} relations.
+% Valuless Associative Relations
 Valueless associative relations occur in 9 vocabularies, with their total number being relatively low compared to the total number of all semantic relations in the respective vocabularies.
+% Solely Transitive Related Concepts
+\todo{CM}{describe this.}
+% Omitted Top Concepts
 GTAA, Geonames, and NYTP have no top concept defined for any of the concept schemes they use.
@@
 The opposite situation can be observed for LCSH which uses 19 concept schemes, but only one has a top concept.
+% Top Concepts Having Broader Concepts
 Only PXV vocabulary is affected by top concepts having broader concept in the current version.
@@
 
-% Linked Data Specific Issues
-With exception of NYTP and geonames we could observe that authoritative concepts of most vocabularies do not serve at link targets for other vocabularies.
-A slightly better situation can be found for missing out-links where most vocabularies also don't provide links to other vocabularies on the Web.
-There are three excepetions:  NYTP, IPSV and NAICS.
+% LINKED DATA SPECIFIC ISSUE
+
+The difference between Concepts and Authoritative Concepts in Table~\ref{tab:vocabs} already indicates which vocabularies are linked with SKOS vocabularies. 
+% Missing In-Links
+However, except \texttt{NYTP} and \texttt{Geonames} none of the analyzed vocabularies has a significant number of in-links from other web resources.
+% Missing Out-Links
+Most vocabularies also don't provide links to other vocabularies on the Web. There are three excepetions:  NYTP, IPSV and NAICS.
+
+% Broken Links
+
+% Undefined SKOS Resources
+
 Broken links are a very common issue in nearly every vocabulary.

### 2012-03-26 analysis.tex
finalized 1st results interpreation draft

@@
 \label{tab:results}
-\caption{Results of the quality checking functions}
+\caption{Results of the quality checking functions \todo{CM}{order alpha}}
 
@@
 In the \texttt{Pressinfo} and \texttt{NYTP} vocabulary, all concepts are orphan concepts, which means that these vocabularies are authority files rather than thesauri or taxonomies.
-\texttt{GTAA} seems is a mixture of name authority file (~162K concepts) and thesaurus (~10K concepts).
-The 4 orphan concepts in \texttt{STW} hare deprecated concepts, the 21 in \texttt{LVAk} are concepts, which are obviously test data.
+\texttt{GTAA} seems is a mixture of name authority file (162K concepts) and thesaurus (10K concepts).
+The 4 orphan concepts in \texttt{STW} are deprecated concepts, the 21 \texttt{LVAk} concepts are obviously test data.
 % Weakly Connected Components
@@
 % Solely Transitive Related Concepts
-\todo{CM}{describe this.}
+Solely transitive related concepts occur in 3 vocabularies, establishing relations using properties that, according to the SKOS reference documentation, should not be asserted directly.
+This indicates a possible misunderstanding of the SKOS specification and, when the vocabulary is queried without RDFS inferencing, could result in a loss in recall on hierarchical queries.
 % Omitted Top Concepts
-GTAA, Geonames, and NYTP have no top concept defined for any of the concept schemes they use.
-Eurovoc uses 128 concept schemes but only one without top concept.
-The opposite situation can be observed for LCSH which uses 19 concept schemes, but only one has a top concept.
+\texttt{GTAA}, \texttt{Geonames}, and \texttt{NYTP} have no top concept defined for any of the concept schemes they use.
+\texttt{Eurovoc} uses 128 concept schemes but has one without top concept, which simply concepts defined in the vocabulary.
+The opposite can be observed for \texttt{LCSH} which defines 19 concept schemes, but only one with a top concept.
+\todo{CM}{why?}
 % Top Concepts Having Broader Concepts
-Only PXV vocabulary is affected by top concepts having broader concept in the current version.
-In an earlier version a different concept causing this issue could be spotted.
-According to the vocabulary creator it was an abaondoned concept, still available in the triplestore but maybe introduced by some bug in the vocabulary management software.
+Only \texttt{PXV} vocabulary is affected by top concepts having broader concepts in its current version.
+The reason for this is, according to the vocabulary creator, that the broader concept was abandoned but is still available in the triplestore, maybe because of some bug in the vocabulary management software.
 
@@
 
-The difference between Concepts and Authoritative Concepts in Table~\ref{tab:vocabs} already indicates which vocabularies are linked with SKOS vocabularies. 
+The difference between Concepts and Authoritative Concepts in Table~\ref{tab:vocabs} \todo{CM}{fix table nums} already indicates which vocabularies are linked with SKOS vocabularies.
 % Missing In-Links
-However, except \texttt{NYTP} and \texttt{Geonames} none of the analyzed vocabularies has a significant number of in-links from other web resources.
+However, except \texttt{NYTP} and \texttt{Geonames}, none of the analyzed vocabularies has a significant number of in-links from other web resources.
 % Missing Out-Links
-Most vocabularies also don't provide links to other vocabularies on the Web. There are three excepetions:  NYTP, IPSV and NAICS.
-
+Most vocabularies also don't provide links to other vocabularies on the Web. The NYTP, IPSV and NAICS vocabularies are the three exceptions, which are fully linked to other Web resources. 
 % Broken Links
-
+Even though we couldn't determine the exact number of broken links because of the large number of links to resolve  (over 400,000 in Eurovoc and LCSH), we found that broken links are a common issue in most vocabularies.
 % Undefined SKOS Resources
-
-Broken links are a very common issue in nearly every vocabulary.
-In the case of the Meketre vocabulary we could observe server-side misconfiguration as the cause.
-Checking this issue turned out difficult, taking into account the high number of links (over 400,000 in Eurovoc and LCSH) and our algorithm that sleeps three seconds after dereferencing each link in order to avoid an unintended DOS attack.
-So we decided to only check a subset of all links and extrapolate the results.
-Undefined SKOS resources seem to be a minor issue, we could only spot two of them in all vocabularies.
-
-% The \textbf{Loose Concepts} metrics provides insights on the structural complexity of vocabularies.
-The large number of loose concepts in GTAA can be explained by the fact that it contains names (e.g., persons or places) that arent't connected using skos properties.
-This is also the case for Geonames, NYTP and Pressinfo where the number of total conceps is equal to the number of loose concepts, indicating that no concept is semantically related to another concept.
-% 
-% The large number of \textbf{Weakly Connected Components} in GTAA is caused by many ``minimal'' components, containing only 2 concepts connected by a \texttt{skos:related} property.
-Due to the fact that loose concepts are not counted as weakly connected components, Geonames, NYTP and Pressinfo evaluate to zero components.
+Undefined SKOS resources seem to be a minor issue, because we could only find two of them in all vocabularies: \texttt{MeSH} introduces \texttt{skos:annotation} and \texttt{IPSV} uses the deprecated \texttt{skos:prefSymbol} property.

### 2012-03-26 conclusions.tex
contd. structure interpretation
updated related work and conclusions

@@
 
-In this paper we identified and defined quality issues of SKOS vocabularies and implemented them in the qSKOS quality assessment tool, which can find possible affected resources in a given SKOS vocabulary.
-We also analyzed a representative set of existing SKOS vocabularies and found real-world occurrences for all these issues.
-
-Among the most omnipresent issues we found during analyzing the chosen set of vocabularies were missing or incomplete language information as well as orphan concepts.
-It also turned out that there is room for a more intense interlinking of SKOS vocabularies.
+In this paper we identified possible quality issues in SKOS vocabularies and implemented them as quality checking functions in our qSKOS quality assessment tool.
+We analyzed a representative set of existing SKOS vocabularies and found  issues in all of them.
+Labeling and documentation issues were omnipresent and also structural issues, which require further investigation by the vocabulary maintainers, were found in most vocabularies.
+Although SKOS is designed for Linked Data, many existing vocabularies still resemble their closed-system origin, which results in a relatively low number of in- and out-links.
+Broken links is a major issue and calls for synchronization mechanisms in order to maintain navigability between concepts.
 
@@
 We are aware that the quality issues we described in this work are purely quantitative indicators that, on their own, cannot be generalized into statements about the quality of a vocabulary.
-To learn more about the real-world impact of our work, we would like to conduct a qualitative study in which we confront taxonomists with our results.
+To learn more about the real-world impact of our work, we would like to conduct a qualitative follow-up study, in which we confront taxonomists with our results.
 We will also further collect community feedback, enhance the issues list, and set up a Web-based SKOS quality checking service.
+For larger vocabularies we will also increase the performance and efficiency of our quality checking algorithms.
 

### 2012-03-26 criteria.tex
fixed 4.2
updated related work and conclusions

@@
 
-\section{Possible Quality Issues in SKOS Vocabularies}\label{sec:criteria}
+\section{Quality Issues in SKOS Vocabularies}\label{sec:criteria}
 
@@
 
-\paragraph{QI 1: Omitted or Invalid Language Tags}
+\paragraph{Omitted or Invalid Language Tags}
 
@@
 
-\paragraph{QI 2: Incomplete Language Coverage}
+\paragraph{Incomplete Language Coverage}
 
@@
 
-\paragraph{QI 3: Undocumented Concepts}
+\paragraph{Undocumented Concepts}
 
@@
 
-\paragraph{QI 4: Label Conflicts}
+\paragraph{Label Conflicts}
 
@@
 
-\paragraph{QI 5: Orphan Concepts}
+\paragraph{Orphan Concepts}
 
@@
 
-\paragraph{QI 6: Weakly Connected Components}
+\paragraph{Weakly Connected Components}
 
@@
 
-\paragraph{QI 7: Cyclic Hierarchical Relations}
+\paragraph{Cyclic Hierarchical Relations}
 
@@
 
-\paragraph{QI 8: Valueless Associative Relations}
+\paragraph{Valueless Associative Relations}
 
@@
 
-\paragraph{QI 9: Solely Transitively Related Concepts}
+\paragraph{Solely Transitively Related Concepts}
 
@@
 
-\paragraph{QI 10: Omitted Top Concepts}
+\paragraph{Omitted Top Concepts}
 
@@
 
-\paragraph{QI 11: Top Concept Having Broader Concepts}
+\paragraph{Top Concept Having Broader Concepts}
 
@@
 
-\subsection{Linked Data Specific Issues}
+\subsection{Linked Data Specific Issues}\label{subsec:ld_issues}
 
-\paragraph{QI 12: Missing In-Links}
+\paragraph{Missing In-Links}
 
@@
 
-\paragraph{QI 13: Missing Out-Links}
+\paragraph{Missing Out-Links}
 
@@
 
-\paragraph{QI 14: Broken Links}
+\paragraph{Broken Links}
 
@@
 
-\paragraph{QI 15: Undefined SKOS Resources}
+\paragraph{Undefined SKOS Resources}
 

### 2012-03-26 related_work.tex
updated related work and conclusions

@@
 % Data quality in general
-
 The problem of ``vocabulary quality'' is closely related to the more general problem of ``data quality`'', which has intensively been discussed in data and information systems research (cf.~\cite{Batini2009}).
 Pipino et al.~\cite{Pipino2002} argue that dealing with data quality should involve both ``subjective perceptions of the individuals'' and ``objective measurements based on the data set in question''.
-We see our work as a contribution to the latter and believe that the kind of quality assessment we support must be combined with domain knowledge, and therefore human expertise, to make final quality judgements.
+We see our work as a contribution to the latter.
 
-% Quality in Linked Data
-
+% Quality in Semantic Web and Linked Data
 Data quality research has also been conducted in the Semantic Web and Linked Data research areas.
@@
 However, the authors focus on RDF datasets in general without considering SKOS-specific properties.
+Ontology evaluation is task of measuring the quality of an ontology and has extensively been discussed by Vrandecic~\cite{Vrandecic2010}.
 
@@
 
-Ontology evaluation is task of measuring the quality of an ontology and has extensively been discussed by Vrandecic~\cite{Vrandecic2010}.
-Gangemi~\cite{Gangemi2006} introduced structural, functional and usability-related measures for ontology evaluation, Arpinar~\cite{Arpinar2006} define three types of conflicts that may occur in ontologies, and also Tartir et al.~\cite{Tartir2007} propose a framework for evaluation and ranking of ontologies.
+% Gangemi~\cite{Gangemi2006} introduced structural, functional and usability-related measures for ontology evaluation, Arpinar~\cite{Arpinar2006} define three types of conflicts that may occur in ontologies, and also Tartir et al.~\cite{Tartir2007} propose a framework for evaluation and ranking of ontologies.
 Although there are definitely overlaps between ontology evaluation and our research, the quality issues we identified are less tight to underlying data model and formal ontology definition language but, to a large extent, derived from manuals and guidelines taxonomist use in their daily work.

### 2012-03-27 analysis.tex
resolved some todos

@@
 \begin{table}
+\caption{Analyzed SKOS vocabularies}
 \label{tab:vocabs}
-\caption{Analyzed SKOS vocabularies}
 
@@
 \begin{table}[h]
+\caption{Results of the quality checking functions \todo{CM}{order alpha}}
 \label{tab:results}
-\caption{Results of the quality checking functions \todo{CM}{order alpha}}
 
@@
 
-Omitted Top Concepts & 9 & 9 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 1 & 18 & 0 & 0 & 0 & 0 \\
+Omitted Top Concepts & 9 & 9 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 1 & 19 & 0 & 0 & 0 & 0 \\
 
@@
 
-Broken Links & 0 & 0 & 1 & 163 && 1 & 238 & 0* & 11 & 7 && 425 & 1 & 3,169 & n/a \\
+Broken Links & 0 & 0 & 1 & 163 & 0* & 1 & 238 & 0* & 11 & 7 && 425 & 1 & 3,169 & n/a \\
 
@@
 % Omitted or Invalid Language Tags
-The \texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} vocabularies omit language tags with their skos:prefLabel, \texttt{skos:altLabel}, or \texttt{skos:hiddenLabel} properties.
+The \texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} vocabularies omit language tags with their \texttt{skos:prefLabel}, \texttt{skos:altLabel}, or \texttt{skos:hiddenLabel} properties.
 The STW thesaurus doesn't use language tags with 2 \texttt{skos:definition} property instances and the LCSH vocabulary uses language tags with concepts, but not with concept schemes.
@@
 % Omitted Top Concepts
-\texttt{GTAA}, \texttt{Geonames}, and \texttt{NYTP} have no top concept defined for any of the concept schemes they use.
-\texttt{Eurovoc} uses 128 concept schemes but has one without top concept, which simply concepts defined in the vocabulary.
-The opposite can be observed for \texttt{LCSH} which defines 19 concept schemes, but only one with a top concept.
-\todo{CM}{why?}
+\texttt{GTAA}, \texttt{Geonames}, \texttt{NYTP}, and \textt{LCSH} have no top concept defined for any of the concept schemes they use.
+\texttt{Eurovoc} uses 128 concept schemes but has one without top concept, which simply contains all concepts defined in the vocabulary.
 % Top Concepts Having Broader Concepts
@@
 
-The difference between Concepts and Authoritative Concepts in Table~\ref{tab:vocabs} \todo{CM}{fix table nums} already indicates which vocabularies are linked with SKOS vocabularies.
+The difference between Concepts and Authoritative Concepts in Table~\ref{tab:vocabs} already indicates which vocabularies are linked with SKOS vocabularies.
 % Missing In-Links
@@
 % Missing Out-Links
-Most vocabularies also don't provide links to other vocabularies on the Web. The NYTP, IPSV and NAICS vocabularies are the three exceptions, which are fully linked to other Web resources. 
+Most vocabularies also don't provide links to other vocabularies on the Web.
+The \texttt{NYTP}, \texttt{IPSV} and \texttt{NAICS} vocabularies are the three exceptions, which are fully linked to other Web resources.
 % Broken Links
-Even though we couldn't determine the exact number of broken links because of the large number of links to resolve  (over 400,000 in Eurovoc and LCSH), we found that broken links are a common issue in most vocabularies.
+Even though we couldn't determine the exact number of broken links because of the large number of links to resolve  (over 400,000 in \texttt{Eurovoc} and \texttt{LCSH}), we found that broken links are a common issue in most vocabularies.
 % Undefined SKOS Resources

### 2012-03-27 analysis.tex
added some words about wcc interpretation

@@
 
-\begin{tabular}{p{4cm}ccccccccccccccc}
+\begin{tabular}{lccccccccccccccc}
 \textbf{Issue} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
@@
 Three vocabularies have one weakly connected component which means that there is one ``giant component''.
-All other vocabularies split into several ``islands'' of semantically related concepts.
-\todo{CM}{think about it}.
+All other vocabularies split into several clusters of semantically related concepts that represent several subtopics in the vocabularies.
+\texttt{Eurovoc} contains of 4 weakly connected components, containing 4, 5, 6 and 6775 concepts.
+The three smallest components contain concepts thematically related to ``Africa'', ``educational institutions'' and ``forecasts''.
+Weakly connected components divide the \texttt{Meketre} vocabularies into, e.g., execution-style related concepts, concepts reserved for internal use or museums.
+\texttt{GTAA} consists of 621 weakly connected components, most of them containing less than 10 concepts, representing, e.g., political parties, companies or historical periods.
+\texttt{PXV} splits into 10 weakly connecting components, topically relating e.g., ``deficiancies'', ``defects'' or ``signals''.
 % Cyclic Hierarchical Relations
@@
 % Omitted Top Concepts
-\texttt{GTAA}, \texttt{Geonames}, \texttt{NYTP}, and \textt{LCSH} have no top concept defined for any of the concept schemes they use.
+\texttt{GTAA}, \texttt{Geonames}, \texttt{NYTP}, and \texttt{LCSH} have no top concept defined for any of the concept schemes they use.
 \texttt{Eurovoc} uses 128 concept schemes but has one without top concept, which simply contains all concepts defined in the vocabulary.
@@
 % Broken Links
-Even though we couldn't determine the exact number of broken links because of the large number of links to resolve  (over 400,000 in \texttt{Eurovoc} and \texttt{LCSH}), we found that broken links are a common issue in most vocabularies.
+Even though we couldn't determine the exact number of broken links because of the large number of links to resolve  (over 400K in \texttt{Eurovoc} and \texttt{LCSH}), we found that broken links are a common issue in most vocabularies.
 % Undefined SKOS Resources

### 2012-03-27 analysis.tex
fixed table caption error
alphabetic ordering of table 2

@@
 \begin{table}[h]
-\caption{Results of the quality checking functions \todo{CM}{order alpha}}
+\caption{Results of the quality checking functions}
 \label{tab:results}
@@
 \begin{tabular}{lccccccccccccccc}
-\textbf{Issue} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
+\textbf{Issue} & \rotatebox{90}{\textbf{AGROVOC}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{LVAk}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{STW}} \\
+
 \toprule
-Omitted or Invalid Language Tags & 0 & 0 & 23,950 & 1,578 & n/a & 0 & 0 & 0 & 1,224 & 0 & 18 & 0 & 2 & n/a & 13,411 \\
+Omitted or Invalid Language Tags & 0 & 0 & n/a & 0 & 0 & 0 & 18 & 13,411 & 0 & 23,950 & n/a & 0 & 1,224 & 1,578 & 2 \\
 
-Incomplete Language Coverage & 0 & 0 & 0 & 0 & n/a & 0 & 32,035 & 0 & 0 & 0 & 0 & 420 & 6,456 & n/a & 0 \\
+Incomplete Language Coverage & 32,035 & 0 & n/a & 0 & 0 & 0 & 0 & 0 & 420 & 0 & n/a & 0 & 0 & 0 & 6,456 \\
 
-Undocumented Concepts & 96,850 & 0 & 1,807 & 1,918 & 5,341 & 4,551 & 32,035 & 743,410 & 1,125 & 4,094 & 398,036 & 422 & 5,236 & 3,259 & 13,411 \\
+Undocumented Concepts & 32,035 & 743,410 & 5,341 & 0 & 96,850 & 4,551 & 398,036 & 13,411 & 422 & 1,807 & 3,259 & 4,094 & 1,125 & 1,918 & 5,236 \\
 
-Label Conflicts & 12,404 & 18 & 0 & 7 & n/a & 0 & 2,949 & 0 & 0 & 0 & n/a & 4 & 5 & n/a & 13 \\
+Label Conflicts & 2,949 & 0 & n/a & 18 & 12,404 & 0 & n/a & 13 & 4 & 0 & n/a & 0 & 0 & 7 & 5 \\
 
@@
 
-Orphan Concepts & 162,000 & 671 & 0 & 2 & 7 & 0 & 0 & 77,062 & 1,125 & 4,979 & 172,364 & 0 & 4 & 0 & 21 \\
+Orphan Concepts & 0 & 77,062 & 7 & 671 & 162,000 & 0 & 172,364 & 21 & 0 & 0 & 0 & 4,979 & 1,125 & 2 & 4 \\
 
-Weakly Connected Components & 621 & 0 & 4 & 10 & 4 & 1 & 4 & 1,506 & 0 & 0 & 22,131 & 5 & 1 & 1 & 11 \\
+Weakly Connected Components & 4 & 1,506 & 4 & 0 & 621 & 1 & 22,131 & 11 & 5 & 4 & 1 & 0 & 0 & 10 & 1 \\
 
-Cyclic Hierarchical Relations & 0 & 0 & 4 & 0 & 0 & 0 & 0 & 1,132 & 0 & 0 & 0 & 0 & 0 & 0 & 5 \\
+Cyclic Hierarchical Relations & 0 & 1,132 & 0 & 0 & 0 & 0 & 0 & 5 & 0 & 4 & 0 & 0 & 0 & 0 & 0 \\
 
-Valueless Associative Relations & 9,438 & 0 & 495 & 0 & 1 & 239 & 282 & 8,120 & 0 & 0 & 1,879 & 0 & 5,082 & 0 & 5 \\
+Valueless Associative Relations & 282 & 8,120 & 1 & 0 & 9,438 & 239 & 1,879 & 5 & 0 & 495 & 0 & 0 & 0 & 0 & 5,082 \\
 
-Solely Transitively Related Concepts & 0 & 0 & 0 & 0 & 2,652 & 0 & 0 & 0 & 0 & 0 & 0 & 36 & 0 & 2,189 & 0 \\
+Solely Transitively Related Concepts & 0 & 0 & 2,652 & 0 & 0 & 0 & 0 & 0 & 36 & 0 & 2,189 & 0 & 0 & 0 & 0 \\
 
-Omitted Top Concepts & 9 & 9 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 1 & 19 & 0 & 0 & 0 & 0 \\
+Omitted Top Concepts & 0 & 0 & 1 & 9 & 9 & 0 & 19 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
 
-Top Concept Having Broader Concepts & 0 & 0 & 0 & 1 & 0 &0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+Top Concept Having Broader Concepts & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\
 
@@
 
-Missing In-Links & 171,980* & 19 & 24625 & 1,686 & 6,796 & 3,080 & 32,035 & 733,800* & 1,125 & 20 & 404,540* & 422 & 6,516 & 2,213 & 13,411 \\
+Missing In-Links & 32,035 & 733,800 & 6,796 & 19 & 171,980* & 3,080 & 404,540* & 13,411 & 422 & 24,625 & 2,213 & 20 & 1,125 & 1,686 & 6,516 \\
 
-Missing Out-Links & 171,991 & 671 & 24626 & 1,472 & 6,797 & 0 & 32,035 & 743,410 & 1,116 & 0 & 408,198 & 273 & 6,524 & 0 & 13,411 \\
+Missing Out-Links & 32,035 & 743,410 & 6,797 & 671 & 171,991 & 0 & 408,198 & 13,411 & 273 & 24,625 & 0 & 0 & 1,116 & 1,472 & 6,524 \\
 
-Broken Links & 0 & 0 & 1 & 163 & 0* & 1 & 238 & 0* & 11 & 7 && 425 & 1 & 3,169 & n/a \\
+Broken Links & 238 & 0* & 0* & 0 & 0 & 1 && n/a & 425 & 1 & 3,169 & 7 & 11 & 163 & 1 \\
 
-Undefined SKOS Resources & 0 & 0 & 1 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0  \\
+Undefined SKOS Resources & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
 

### 2012-03-27 background.tex
read and fixed 1-3

@@
 
-SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption.
+SKOS is a model for controlled vocabularies in the Web of Data and therefore based on the Open World Assumption.
 Established quality notions from closed-world systems, such as referential integrity or schema validation, don't hold anymore, because available information may be incomplete and non-explicitly stated facts cannot be determined as true or false.
-While trust and provenance models for Web data are being developed~\cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}.
+Content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}.
 
@@
 
-Interoperability between applications has been the major motivation for specifying in total six \textbf{SKOS integrity conditions}~\cite{Miles2005}, each of which is a statement that defines under which circumstances data are consistent with the SKOS data model.
+Interoperability between applications has been the major motivation for specifying in total six \textbf{SKOS integrity conditions}~\cite{SkosReference2008}, each of which is a statement that defines under which circumstances data are consistent with the SKOS data model.
 An example condition is ``a resource has no more than one value of \texttt{skos:prefLabel} per language tag''.
 Tools that can check whether these integrity conditions are met for given data are already available: two of the six integrity conditions are defined formally in the OWL representation of SKOS and can therefore be validated by any OWL reasoner.
-For validating a SKOS vocabulary against the integrity conditions, one can use tools such as the online \textbf{PoolParty Thesaurus Consistency Checker}, or the \textbf{Skosify} command line utility, which can validate SKOS vocabularies and also correct some detected quality problems.
+For validating a SKOS vocabulary against the integrity conditions, one can use tools such as the online \textbf{PoolParty Thesaurus Consistency Checker}, or the \textbf{Skosify} command line validator, which can also correct some detected quality problems.
 
@@
 Missing entry points to concepts in a vocabulary can impede orientation for human users.
-Proprietary term definitions can hinder queries across distinct datasets, to name some examples.
 
@@
 Thus, in order to help vocabulary and application designers in judging and improving the quality of SKOS vocabularies we must identify possible quality issues that go beyond integrity conditions defining data model consistency.
-We can identify such issues by examining quality criteria for controlled vocabularies that have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, case studies~\cite{Soergel1995}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002,Elkin2002,Kless2010}.
+We can identify such issues by examining quality criteria for controlled vocabularies that have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, tutorials~\cite{Soergel2002}, and scholarly articles \cite{Coronado2009,Soergel1997,Elkin2002,Kless2010}.
 Since we want to provide tool support for quality checking, we must formalize the identified issues into computable quality checking functions taking into account the syntax, structure and semantics of SKOS.
 This also ensures consistent implementation across tools.
-
-% TODO ADD TO THIS SECTION: a vast number of publications in the field of designing, validating and testing controlled vocabularies is available.
-Many of them propose properties \cite{Soergel1995}, design guidelines \cite{Svenonius2003,...} or metrics \cite{Elkin2002,Kless2010} aiming to improve, e.g., retrieval precision and recall, consistency and multilinguality.
-The work is based on various sources like, e.g., review of existing vocabularies~\cite{Soergel1995} or survey-based studies~\cite{Pinto2008}.
-However, there are hardly any formally defined quality indicators that can be automatically assessed without further knowledge about the application domain, targeted user group or usage scenario.
-
-%Whilst aformentioned literature also deals with online vocabulary publication and interoperability \cite{ISO25964-1:2011,Hedden2010}, covering requirements for publication on the Web of Data (as in, e.g., \cite{Heath2011,Hogan2010,Allemang2011}) goes beyond their scope.
-%On the other hand, publications targeting dataset and ontology development for the Web of Data don't elaborate on implications of the design decisions for controlled vocabularies.
-Our work seeks to narrow this gap by...
-
-% TODO: bitte hier einfach nur die referenzen auf die wir uns beziehen zusammenfassen und kategorisieren. Schau dir dazu auch nochmals die SKOSify referenzen und die aus eurem iSemantics paper an.
-
-% I think for the big picture it is not necessary to go into such details. We can do this later when introducting the metrics
-
-% The PoolParty Thesaurus Consistency Checker implements all these conditions and introduces the following new checks: \textbf{URI validation} checks for invalid characters like, e.g.
-whitespaces in the URI string.
-\textbf{Definition of labels} is tested for conceptual resources and concept schemes.
-Furthermore, SKOS labels and textual content is checked for \textbf{missing language tags} and the notion of \textbf{loose concepts} is defined: it encompasses conceptual resources that are no top concepts and have no broader concept.
-% 
-% The SKOSify tool implements three of the above mentioned SKOS integrity conditions as well as the \textbf{missing language tags} and \textbf{loose concepts} measures introduced by the PoolParty checker.
-It introduces \textbf{hierarchy cycle detection} and detection of \textbf{extra whitespace} for SKOS label or documentation properties.

### 2012-03-27 criteria.tex
read and fixed 1-3

@@
 
-We identified an initial set of possible quality issues in SKOS vocabularies by reviewing existing literature and manually examining existing vocabularies.
-We published our findings online\footnote{\url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}} and requested feedback from experts via public mailing list and informal face to face discussions.
+We identified an initial set of possible quality issues in SKOS vocabularies by reviewing literature and manually examining existing vocabularies.
+We published our findings online\footnote{\url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}} and requested feedback from experts via public mailing lists and informal face to face discussions.
 Based on the received responses, we then selected a subset of these issues and formalized them into computable \textbf{quality checking functions}.
-Each function operates on a SKOS vocabulary, which we define, for the purpose of this work, as follows:
+Each function operates on a given SKOS vocabulary, which we define, for the purpose of this work, as follows:
 
-\begin{definition}[SKOS Vocabulary] Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, ULV \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{concepts}, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating conceptual resources with one another, and $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}.
-Further, we let $V$ be the fully entailed RDFS interpretation~\cite{RDFSEM2012} of the underlying RDF graph, enriched by entailment of \texttt{owl:inverseOf} properties.
+\begin{definition}[SKOS Vocabulary] Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, ULV \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{concepts}, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, and $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}.
+Further, we let $V$ be the fully entailed RDFS interpretation of the underlying RDF graph, enriched by entailment of \texttt{owl:inverseOf} properties.
 
@@
 
-A quality checking function is applied on a given SKOS vocabulary and finds all vocabulary resources that match a certain issue and might degrade the overall quality of a vocabulary.
-Therefore, we can formalize a quality issue in terms of an abstract function $f:V \rightarrow \mathcal{P}(IR)$ that maps a given vocabulary $v \in V$ to the powerset of its resources.
+A checking function is applied on a given SKOS vocabulary and finds all vocabulary resources that match the corresponding quality issue.
+We can map each issue to an abstract function $f:V \rightarrow \mathcal{P}(IR)$ that relates a given SKOS vocabulary to a subset of its resources.
 Each quality issue we found can be implemented as a realization of that abstract function and possibly take additional parameters.
@@
 
-In the following, we explain the origins and design rationale for each quality issue (QI) and define the corresponding quality checking function.
+In the following, we explain the origins and design rationale for each quality issue and define the corresponding quality checking function.
 For better readability and due to lack of space we provide only semi-formal definitions and refer to the online documentation and the implementation source code for further details.
-We also categorized the identified quality issues into \emph{Labeling and Documentation Issues}, \emph{Structural Issues}, \emph{Linked Data Specific Issues}, and \emph{Other Issues}.
 
@@
 This includes the labeling properties \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} and subproperties thereof.
-Omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could unintentionally limit the result set of language-dependent structural queries.
+Literals should be tagged consistently~\cite{Vrandecic2010}, because omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could unintentionally limit the result set of language-dependent structural queries.
 % Function defintion
-We can check a SKOS vocabulary for omitted and invalid language tags by defining a quality checking function $oilt$ that iterates over all resources in $IR$ and finds those that have relations to plain literals (using the above mentions SKOS properties) with missing or invalid language tags, hence tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
+A SKOS vocabulary can be checked for omitted and invalid language tags by iterating over all resources in $IR$ and finding those that have relations to plain literals (using the above mentions SKOS properties) with missing or invalid language tags, hence tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
 
@@
 % Origin and rationale
-Soergel et al.~\cite{Soergel1997} point out the problem that ``...a concept lexicalized in one language may not be lexicalized in another and that the terms do exist often vary slightly in meaning, possibly giving rise to different relationships.'' As a consequence, for such cases the authors suggest revising the vocabulary structure and ``clearly instruct indexers in all languages how the term is to be used''.
+Soergel et al.~\cite{Soergel1997} point out the problem that ``...a concept lexicalized in one language may not be lexicalized in another and that the terms do exist often vary slightly in meaning, possibly giving rise to different relationships.'' For such cases, the authors suggest to revise the vocabulary structure and to ``clearly instruct indexers in all languages how the term is to be used''.
 In the context of SKOS, this means that the set of language tags used by the literal values linked with a concept should be checked to be the same for all concepts.
@@
 % Function defintion
-We identify affected the concepts by a function $ilc$ that first extracts the global set of language tags used in a vocabulary from all literal values attached to all concepts in $C$.
-In a second iteration over all concepts it identifies all concepts having a set of language tags that is not equal to the global language set.
+Affected concepts can be identified by first extracting the global set of language tags used in a vocabulary from all literal values attached to all concepts in $C$.
+In a second iteration over all concepts, all concepts having a set of language tags that is not equal to the global language set are returned.
 
@@
 % Origin and rationale
-Svenonius~\cite{Svenonius1997} advocates the ``inclusion of as much definition material as possible'' and the SKOS language specification~\cite{SkosReference2008} defines a set of properties, denoted as ``documentation properties'', that are intended to hold this kind of information.
+Svenonius~\cite{Svenonius1997} advocates the ``inclusion of as much definition material as possible'' and the SKOS Reference~\cite{SkosReference2008} defines a set of properties, denoted as ``documentation properties'', that are intended to hold this kind of information.
 % Function defintion
-To identify all undocumented concepts, we define a function $uc$ we iterate over all concepts in $C$ and by default collect those that do not use any of these documentation properties.
+To identify all undocumented concepts, we iterate over all concepts in $C$ and collect those that do not use any of these documentation properties.
 
@@
 % Origin and rationale
-This issue is an extension of a statement from the SKOS Primer~\cite{Isaac2009} that recommends that ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
+The SKOS Primer~\cite{Isaac2009} recommends that ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
 We reviewed existing vocabularies and applications and found that (i) many vocabularies don't use concept schemes and (ii) identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} can also negatively affect use cases such as auto-completion, which proposes labels based on the user input.
 % Function defintion
-Thus, we generalize this statement and define a function $lc$ that finds all concept pairs with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} property values meeting a certain similarity threshold defined by a function $sim:LV \times LV \rightarrow [0,1]$.
+Thus, we generalize this recommendation and search for all concept pairs with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} property values meeting a certain similarity threshold defined by a function $sim:LV \times LV \rightarrow [0,1]$.
 The default, built-in similarity function checks for case-insensitive string equality with a threshold equal to 1.
-The function iterates over all concept pairs $C \times C$, applies $sim$ to every possible label combination, and collects those pairs with at least one label combination that meet or exceed a specified similarity threshold.
+The function iterates over all concept pairs $C \times C$, applies $sim$ to every possible label combination, and collects those pairs with at least one label combination that meets or exceeds a specified similarity threshold.
 
@@
 % Function defintion
-In order to find orphan concepts in a SKOS vocabulary, we define a function $oc$ that iterates over all elements in $C$, filtering those not having a semantic relation to any other conceptual resource in $C$.
+Orphan concepts in a SKOS vocabulary can be found by iterating over all elements in $C$ and selecting those without any semantic relation to another conceptual resource in $C$.
 
@@
 % Origin and rationale
-indicate that a vocabulary is split into separate ``clusters'', which can be caused by incomplete data acquisition, ``forgotten'' test data, outdated terms, accidental deletion of relations, etc.
+A vocabulary can be split into separate ``clusters'', which can be caused by incomplete data acquisition, ``forgotten'' test data, outdated terms, accidental deletion of relations, etc.
 This can affect operations that rely on navigating a connected vocabulary structure, such as query expansion or suggestion of related terms.
 % Function defintion
-In order to find weakly connected components, we define a function $wcc$, which first creates an undirected graph having all non-orphan concepts (as defined above) as nodes and all semantic relations $SR$ as edges.
-It then applies ``Tarjan’s algorithm''~\cite{Hopcroft1973} to find all connected components, hence all sets of concepts that are connected by semantic relations.
+Weakly connected components are identified by first creating an undirected graph that includes all non-orphan concepts (as defined above) as nodes and all semantic relations $SR$ as edges.
+``Tarjan’s algorithm''~\cite{Hopcroft1973} can then be applied to find all connected components, hence all sets of concepts that are connected by semantic relations.
 
@@
 % Origin and rationale
-is a quality issue motivated by Soergel et al.~\cite{Soergel2002} who suggest a ``check for hierarchy cycles'' since they ``throw the program for a loop in the generation of a complete hierarchical structure''.
+is motivated by Soergel et al.~\cite{Soergel2002} who suggest a ``check for hierarchy cycles'' since they ``throw the program for a loop in the generation of a complete hierarchical structure''.
 Also Hedden~\cite{Hedden2010}, Harpring~\cite{Harpring2010} and Aitchison et al.~\cite{Aitchison2000} argue that there exist common forms like, e.g., ``generic-specific'', ``instance-of'' or ``whole-part'' where cycles would be considered a logical contradiction.
 % Function defintion
-We provide a function $chr$, which finds cyclic relations by constructing a graph with the set of nodes being $C$ and the set of edges being $I_{EXT}(\texttt{skos:broader}^\mathcal{I})$, i.e.
-all pairs of resources connected by \texttt{skos:broader} relations.
-It then identifies the sets of nodes that are involved in cycles.
+Cyclic relations can be found by constructing a graph with the set of nodes being $C$ and the set of edges being all \texttt{skos:broader} relations between these concepts.
 
@@
 % Function defintion
-The function \textit{var} identifies a set of pairs of conceptual resources that share the same broader or narrower concept while also being associatively related by the property \texttt{skos:related}.
+This issue can be checked by identifying the set of pairs of conceptual resources that share the same broader or narrower concept while also being associatively related by the property \texttt{skos:related}.
 
@@
 % Origin and rationale
-Two concepts that are explicitly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} can be regarded a quality issue because, according to \cite{SkosReference2008}, they are ``not used to make assertions''.
-Transitive hierarchical relations in SKOS are meant to be inferred by the vocabulary consumer, which is reflected in the SKOS schema by, e.g., \texttt{skos:broader} being a subproperty of \texttt{skos:broaderTransitive}.
+Two concepts that are explicitly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} can be regarded a quality issue because, according to \cite{SkosReference2008}, these properties are ``not used to make assertions''.
+Transitive hierarchical relations in SKOS are meant to be inferred by the vocabulary consumer, which is reflected in the SKOS schema by, for instance, \texttt{skos:broader} being a subproperty of \texttt{skos:broaderTransitive}.
 % Function definition
-We encode this issue in a function \textit{strc} that iterates over all concept pairs $C \times C$ that are directly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} properties and not by one of their subproperties.
+This issue can be detected by iterating over all concept pairs $C \times C$ that are directly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} properties but none of their subproperties.
 
@@
 % Origin and rationale
-The SKOS language provides concept schemes, which are a facility for grouping related concepts.
+The SKOS model provides concept schemes, which are a facility for grouping related concepts.
 This helps to provide ``efficient access''~\cite{Isaac2009} and simplifies orientation in the vocabulary.
@@
 % Function definition
-We provide a function \textit{otc} that iterates over all \texttt{skos:ConceptScheme}s in $V$ and collects those that do not occur in relations established by the properties \texttt{skos:hasTopConcept} or \texttt{skos:topConceptOf}.
+Omitted top concepts can be detected by iterating over all \texttt{skos:ConceptScheme}s and collecting those that do not occur in relations established by the properties \texttt{skos:hasTopConcept} or \texttt{skos:topConceptOf}.
 
@@
 % Function definition
-The function \textit{tchbc} iterates over all \texttt{skos:TopConcept}s defined in $V$ and collects those that are related to a resource by the \texttt{skos:broader} property.
+Affected resources can be found by iterating over all \texttt{skos:TopConcept}s and collecting those that are related to a resource via a \texttt{skos:broader} property.
 
@@
 Estimating the number of in-links and identifying the concepts without any in-links, can be an important indicator for the importance of a concept.
-The required in-links for such an estimation can be obtained from existing Linked Data indices like, e.g., Sindice\footnote{\url{http://sindice.com/}}.
 % Function definition
-To estimate the number of in-links we only take a set $AC \subseteq C$ into account which consists of all ``authoritative concepts'', i.e.
-concepts that have an URI in the namespace of the vocabulary.
-The function \textit{mil} estimates the number of in-links referencing an authoritative concept, by iterating over all elements in $AC$ and querying the Sindice SPARQL endpoint for triples containing the concept's URI in the object part.
-Empty query results are indicator for missing in-links and are thus included in the result set of this function.
+To estimate the number of in-links we only consider the set $AC \subseteq C$, which consists of all ``authoritative concepts'', hence concepts that have an URI in the vocabulary namespace.
+The number of in-links referencing an authoritative concept can be estimated by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/}} SPARQL endpoint for triples containing the concept's URI in the object part.
+Empty query results are indicators for missing in-links and are thus included in the result set of this function.
 
@@
 % Origin and rationale
-In the Linked Data context SKOS concepts should be linked with other related concepts on the Web, ``enabling seamless connections between data sets''\cite{Heath2011}.
-Similar to \emph{Missing In-Links}, this issue identifies the set of all conceptual resources that have no out-links.
+In the Linked Data context, SKOS concepts should be linked with other related concepts on the Web, ``enabling seamless connections between data sets''\cite{Heath2011}.
+Similar to \emph{Missing In-Links}, this issue identifies the set of all concepts that have no out-links.
 % Function definition
-We provide the function \textit{mol} that iterates over all elements $c \in C$ and investigates the host part of all related resource URIs.
+It can be computed by iterating over all elements $c \in C$ and checking the host part of all related resource URIs.
 If none of these host names differ from the host part of $c$'s URI, it has no out-links and is thus included in the resources identified by this issue.
@@
 % Origin and rationale
-This issue identifies vocabulary resources that return HTTP error responses or no response when being dereferenced.
+As we discussed in detail in our earlier work~\cite{Popitsch:2010:DHB:1772690.1772768}, this issue is caused by vocabulary resources that return HTTP error responses or no response when being dereferenced.
 An erroneous HTTP response in that case can be defined as a response code other than 200 when taking possible redirections into account.
@@
 % Function definition
-Broken links are identified by a function $bl$, which iterates over all resources in $IR$, dereferences each resource, follows possible redirects, and includes unavailable resources in the result set.
+Broken links are detected by iterating over all resources in $IR$, dereferencing their HTTP URIs, following possible redirects, and including unavailable resources in the result set.
 
@@
 % Origin and rationale
-SKOS defines a set of classes and properties, hence resources within the namespace \url{http://www.w3.org/2004/02/skos/core#}, for building controlled vocabularies.
+The SKOS model is defined within the namespace \url{http://www.w3.org/2004/02/skos/core#}.
 However, some vocabularies use resources from within this namespace, which are unresolvable for two main reasons: vocabulary creators ``invented'' new terms within the SKOS namespace instead of introducing them in a separate namespace, or they use ``deprecated'' SKOS properties.
 % Function definition
-In order to identify such undefined SKOS resources, we define a function $usr$  that iterates over all resources in $IR$ and returns those resources (i) that are contained in the list of deprecated resources or (ii) are identified by a URI in the SKOS namespace but are not defined in the current version of the SKOS ontology.
+Undefined SKOS resources can be identified by iterating over all resources in $IR$ and returning those resources (i) that are contained in the list of deprecated resources or (ii) are identified by a URI in the SKOS namespace but are not defined in the current version of the SKOS ontology.

### 2012-03-27 introduction.tex
read and fixed 1-3

@@
 The Simple Knowledge Organization System (SKOS)~\cite{Miles2005} is a standard model for sharing and linking controlled vocabularies on the Web.
-Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} published SKOS representations of their controlled vocabularies on the Web so that they can easily be accessed and by humans and machines.
+Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} publish SKOS representations of their controlled vocabularies on the Web so that they can easily be accessed by humans and machines.
 
 % What does "quality" mean in this context?
-Each vocabulary reflects domain- and application-specific needs and taxonomists often follow existing standards \cite{ISO25964-1:2011,Z39.19:2005} or apply their own hand-crafted checks (cf.,~\cite{Coronado2009}) to meet certain quality requirements.
-However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments.
-As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality.
-The following examples illustrate that this can affect their applicability for tasks like query expansion, faceted browsing, clustering, or auto-completion:
+Each vocabulary reflects domain- and application-specific needs and taxonomists often follow existing standards (cf.,~\cite{ISO25964-1:2011,Z39.19:2005}) or apply their own hand-crafted checks (cf.,~\cite{Coronado2009}) to meet certain quality requirements.
+However, quality requirements can differ across application domains.
+The following examples illustrate how quality issues can affect the applicability of SKOS vocabularies for tasks such as query expansion, faceted browsing, or auto-completion:
 
@@
 	\item The SKOS representation of AGROVOC defines concepts in 25 different languages.
-However, while most concepts have an English description, only 38\% of all concepts have German labels attached.
-This can be a problem for applications that use Agrovoc and rely on German translations.
+However, while most concepts have an English description, only 38\% have German labels attached.
+This can be a problem for multilingual applications that rely on label translations.
 
 	\item An earlier version (v.8.06) of the STW thesaurus contained 5 pairs of concepts with identical labels.
-As a result, the auto-complete function of the online search interface at that time suggested identical entries, without giving disambiguation information.
+As a result, the auto-complete function of the online search interface suggested identical entries, without giving disambiguation information.
 
-% Note: examples related to "defense / army & co" are always a bit tricky; maybe we find a better example.
+% Note: can we replace the LvAK with an example from a public vocabulary? Then we could simply exclude that vocabulary from that paper.
 
@@
 It defines a set of \textbf{integrity conditions} that state ``whether or not given data are consistent with respect to the SKOS data model''~\cite{Miles2005}.
-Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to verify that a given vocabulary fulfills these conditions.
+Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to validate vocabularies against these conditions.
 However, these conditions fail to capture quality aspects such as those mentioned in the examples before, aspects that go beyond integrity conditions of the SKOS data model.
@@
 
-	\item With the \textbf{qSKOS quality assessment tool} we provide a reference implementation of these filtering functions.
+	\item With the \textbf{qSKOS quality assessment tool} we provide a reference implementation of these functions.
 
-	\item We \textbf{analyzed} a representative set of 15 \textbf{existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.
+	\item We \textbf{analyzed} a representative set of \textbf{15 existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.
 
@@
 Then we introduce the quality issues we have identified and describe how we implemented them in the qSKOS quality assessment tool.
-Finally, we report on the results of an analysis we performed on 15 existing SKOS vocabularies and which shows that the quality issues we identified occur in reality.
-The reports we produced already lead to the improvement of at least two existing vocabularies.
+Finally, we report on the results of an analysis we performed on 15 existing SKOS vocabularies and which shows that the quality issues we discussed are real and can lead to the improvement of existing vocabularies.

### 2012-03-27 main.tex
updated intro
fixed first table
read and fixed 1-3

@@
 
+\usepackage{array}
+
 \usepackage{color}
@@
 
-\title{Quality Criteria for SKOS Vocabularies}
+\title{Finding Quality Issues in SKOS Vocabularies}
 \author{Christian Mader\inst{1} \and Bernhard Haslhofer\inst{2}}
@@
 However, SKOS vocabularies often differ in terms of quality, which reduces their applicability across system boundaries.
-Here we investigate how we can support taxonomists in improving the quality of SKOS vocabularies by pointing out quality issues that go beyond the integrity constraints defined in the SKOS specification.
-We identified possible \textbf{quality issues} and formalized them into computable \textbf{quality checking functions} that can find affected resources in a given SKOS vocabulary.
+Here we investigate how we can support taxonomists in improving SKOS vocabularies by pointing out quality issues that go beyond the integrity constraints defined in the SKOS specification.
+We identified potential \textbf{quality issues} and formalized them into computable \textbf{quality checking functions} that can find affected resources in a given SKOS vocabulary.
 We implemented these functions in the qSKOS quality assessment tool, analyzed 15 existing vocabularies, and found possible quality issues in all of them.
@@
 
+% \section{Acknowledgements}
+
+% Tom Dent (esd support team) for providing a dump for the IPSV vocabulary
+% Andrew Gibson for providing a dump for the Peroxisome knowledge Base and giving valuable feedback on their vocabulary structure.
+
 \bibliography{references}

### 2012-03-27 criteria.tex
incorporated comments by antoine

@@
 
-\begin{definition}[SKOS Vocabulary] Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, ULV \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{concepts}, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, and $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}.
-Further, we let $V$ be the fully entailed RDFS interpretation of the underlying RDF graph, enriched by entailment of \texttt{owl:inverseOf} properties.
-
-\end{definition}
+\paragraph{\textbf{Definition (SKOS Vocabulary).}}
+Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV, CS \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C \subseteq IR\) with \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) \todo{CM}{check exponent}being the set of \textbf{concepts}, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}, and \(CS I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})\) being the set of \textbf{concept schemes}.
+Further, we let $V$ be the fully entailed RDFS interpretation of the underlying RDF graph, enriched by entailment of \texttt{owl:inverseOf} properties as well as subproperties of \texttt{owl:TransitiveProperty} and \texttt{owl:SymmetricProperty}.
 
@@
 In the following, we explain the origins and design rationale for each quality issue and define the corresponding quality checking function.
-For better readability and due to lack of space we provide only semi-formal definitions and refer to the online documentation and the implementation source code for further details.
+For better readability and due to lack of space we provide only semi-formal definitions and refer to the \sout{online documentation and the} implementation source code\footnote{\url{https://github.com/cmader/qSKOS/}} for further details.
 
@@
 This includes the labeling properties \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} and subproperties thereof.
-Literals should be tagged consistently~\cite{Vrandecic2010}, because omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could unintentionally limit the result set of language-dependent structural queries.
+Literals should be tagged consistently~\cite{Vrandecic2010}, because omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could unintentionally limit the result set of language-dependent queries.
 % Function defintion
@@
 % Function definition
-Omitted top concepts can be detected by iterating over all \texttt{skos:ConceptScheme}s and collecting those that do not occur in relations established by the properties \texttt{skos:hasTopConcept} or \texttt{skos:topConceptOf}.
+Omitted top concepts can be detected by iterating over all concept schemes in $CS$ and collecting those that do not occur in relations established by the properties \texttt{skos:hasTopConcept} or \texttt{skos:topConceptOf}.
 

### 2012-03-27 criteria.tex
rephrased label conflicts issue

@@
 % Function defintion
-A SKOS vocabulary can be checked for omitted and invalid language tags by iterating over all resources in $IR$ and finding those that have relations to plain literals (using the above mentions SKOS properties) with missing or invalid language tags, hence tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
+A SKOS vocabulary can be checked for omitted and invalid language tags by iterating over all resources in $IR$ and finding those that have relations to plain literals (using the above mentions SKOS properties) with missing or invalid language tags, i.e., tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
 
@@
 % Origin and rationale
-Soergel et al.~\cite{Soergel1997} point out the problem that ``...a concept lexicalized in one language may not be lexicalized in another and that the terms do exist often vary slightly in meaning, possibly giving rise to different relationships.'' For such cases, the authors suggest to revise the vocabulary structure and to ``clearly instruct indexers in all languages how the term is to be used''.
+Soergel et al.~\cite{Soergel1997} point out the problem that ``...a concept lexicalized in one language may not be lexicalized in another and that the terms do exist often vary slightly in meaning...''.
+Thus, finding such cases would provide guidance for vocabulary developers for revising the vocabulary structure and to ``clearly instruct indexers in all languages how the term is to be used''.
 In the context of SKOS, this means that the set of language tags used by the literal values linked with a concept should be checked to be the same for all concepts.
@@
 % Origin and rationale
-The SKOS Primer~\cite{Isaac2009} recommends that ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
+Many constraints in~\cite{SkosReference2008,Isaac2009} are related to concept schemes, but (i) data on concept scheme membership may lack and (ii) concept scheme related constraints would be handled better with CWA, e.g., finding identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} of different concepts.
+Although being good practice for many thesauri this issue could cause problems in application scenarios such as auto-completion, which proposes labels based on the user input.
+
+%The SKOS Primer~\cite{Isaac2009} recommends that ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
 We reviewed existing vocabularies and applications and found that (i) many vocabularies don't use concept schemes and (ii) identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} can also negatively affect use cases such as auto-completion, which proposes labels based on the user input.
+
 % Function defintion
@@
 The default, built-in similarity function checks for case-insensitive string equality with a threshold equal to 1.
-The function iterates over all concept pairs $C \times C$, applies $sim$ to every possible label combination, and collects those pairs with at least one label combination that meets or exceeds a specified similarity threshold.
+To find label conflicts, we provide a function that iterates over all concept pairs $C \times C$, applies $sim$ to every possible label combination, and collects those pairs with at least one label combination that meets or exceeds a specified similarity threshold.
 
@@
 % Origin and rationale
-This issue is motivated by the notion of ``orphan terms'' in the literature (cf.,~\cite{Hedden2010}), which are are terms without any associative or hierarchical relationships.
+This issue is motivated by the notion of ``orphan terms'' in the literature~\cite{Hedden2010}, i.e., terms without any associative or hierarchical relationships.
 Checking for such terms is common in existing thesaurus development applications and also suggested by~\cite{Z39.19:2005}.
@@
 % Origin and rationale
-A vocabulary can be split into separate ``clusters'', which can be caused by incomplete data acquisition, ``forgotten'' test data, outdated terms, accidental deletion of relations, etc.
+A vocabulary can be split into separate ``clusters'', which can be caused by incomplete data acquisition, deprecated or outdated terms, accidental deletion of relations, etc.
 This can affect operations that rely on navigating a connected vocabulary structure, such as query expansion or suggestion of related terms.
@@
 % Origin and rationale
-The ISO/DIS 25964-1 standard \cite{ISO25964-1:2011} suggests that terms that share a common broader term but do not have an overlapping meaning, should not be related associatively.
+The ISO/DIS 25964-1 standard \cite{ISO25964-1:2011} suggests that terms that share a common broader term but do not have an \todo{CM}{explain "overlapping"}overlapping meaning, should not be related associatively.
 This is advocated by Hedden~\cite{Hedden2010} and Aitchison et al.~\cite{Aitchison2000} who point out ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships'', having a negative effect on precision.
@@
 Two concepts that are explicitly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} can be regarded a quality issue because, according to \cite{SkosReference2008}, these properties are ``not used to make assertions''.
-Transitive hierarchical relations in SKOS are meant to be inferred by the vocabulary consumer, which is reflected in the SKOS schema by, for instance, \texttt{skos:broader} being a subproperty of \texttt{skos:broaderTransitive}.
+Transitive hierarchical relations in SKOS are meant to be inferred by the vocabulary consumer, which is reflected in the SKOS ontology by, for instance, \texttt{skos:broader} being a subproperty of \texttt{skos:broaderTransitive}.
 % Function definition

### 2012-03-28 background.tex
merged related work into 2

@@
 
-\section{Background}\label{sec:background}
+\section{Background and Related Work}\label{sec:background}
 
-% About Quality in SKOS vocabularies
+% Data quality in general
+The problem of ``vocabulary quality'' is closely related to the more general problem of ``data quality`'' and has been discussed in data and information systems research (cf.~\cite{Batini2009}).
+Pipino et al.~\cite{Pipino2002} argue that dealing with data quality should involve both ``subjective perceptions of the individuals'' and ``objective measurements based on the data set in question''.
+We see our work as a contribution to the latter.
+
+\subsection{Quality in SKOS Vocabularies}
 
@@
 To ensure the quality of the resulting network, human judgement is supported by calculating a report of locally approximated network measures.
-\todo{BH}{ich denke antoine hat das paper gemeint: http://www.mendeley.com/download/public/18928/4084690763/56bdde328dfbba2cb8594b57152c0e132ef00a40/dl.pdf .
-Leider fehlen da etliche Details um sich ein konkretes Bild machen zu können}
 
@@
 
-% Argue why we need criteria that go beyond low-level integrity constraints and why we need to formalize them
+\subsection{Quality in Controlled Vocabularies}
 
 Typical application areas of controlled vocabularies are classification, indexing, autocompletion, query reformulation/expansion, or serving as a glossary.
-As we discussed in detail in our earlier work \cite{Nagy2011}, these application areas have specific requirements with respect to vocabulary features, such as structure, availability, and documentation of conceptual resources.
-A vocabulary that doesn't fulfill these requirements can have a negative effect on an application's output and would therefore be judged by the application designers and potentially also by users as being a low-quality vocabulary.
-Missing relations between conceptual resources, for instance, can reduce retrieval recall when a vocabulary is used for query expansion.
-Missing entry points to concepts in a vocabulary can impede orientation for human users.
+As we discussed in detail in our earlier work \cite{Nagy2011}, these areas impose specific requirements on vocabulary features, such as structure, availability, and documentation of conceptual resources.
+Quality aspects of controlled vocabularies have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, tutorials~\cite{Soergel2002}, and scholarly articles \cite{Coronado2009,Soergel1997,Elkin2002,Kless2010}.
+Our work builds on this literature and identifies possible quality issues that go beyond model-level integrity conditions.
 
-% Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
-Thus, in order to help vocabulary and application designers in judging and improving the quality of SKOS vocabularies we must identify possible quality issues that go beyond integrity conditions defining data model consistency.
-We can identify such issues by examining quality criteria for controlled vocabularies that have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, tutorials~\cite{Soergel2002}, and scholarly articles \cite{Coronado2009,Soergel1997,Elkin2002,Kless2010}.
-Since we want to provide tool support for quality checking, we must formalize the identified issues into computable quality checking functions taking into account the syntax, structure and semantics of SKOS.
-This also ensures consistent implementation across tools.
+\subsection{Quality in Semantic Web and Linked Data Research}
+
+Hogan et.
+al~\cite{Hogan2010} identify four categories of common errors and shortcomings in RDF documents and also Heath and Bizer~\cite{Heath2011} summarize best practices for publishing data on the Web.
+Also ontology evaluation, which is the task of measuring the quality of an ontology, has been discussed by Vrandecic~\cite{Vrandecic2010}.
+However, the authors focus on RDF datasets and ontologies in general without considering SKOS-specific properties.

### 2012-03-28 criteria.tex
merged related work into 2

@@
 
+\todo{CM}{use definition environment and find out how to turn of numbering}
 \paragraph{\textbf{Definition (SKOS Vocabulary).}}
-Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV, CS \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C \subseteq IR\) with \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) \todo{CM}{check exponent}being the set of \textbf{concepts}, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}, and \(CS I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})\) being the set of \textbf{concept schemes}.
+Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV, CS \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C \subseteq IR\) with \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) \todo{CM}{check exponent}being the set of \textbf{concepts}, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}, and \(CS = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})\) being the set of \textbf{concept schemes}.
 Further, we let $V$ be the fully entailed RDFS interpretation of the underlying RDF graph, enriched by entailment of \texttt{owl:inverseOf} properties as well as subproperties of \texttt{owl:TransitiveProperty} and \texttt{owl:SymmetricProperty}.
@@
 In the following, we explain the origins and design rationale for each quality issue and define the corresponding quality checking function.
-For better readability and due to lack of space we provide only semi-formal definitions and refer to the \sout{online documentation and the} implementation source code\footnote{\url{https://github.com/cmader/qSKOS/}} for further details.
+For better readability and due to lack of space we provide only semi-formal definitions and refer to the online documentation and the implementation source code\footnote{\url{https://github.com/cmader/qSKOS/}} for further details.
 

### 2012-03-28 main.tex
incorporated comments by antoine
merged related work into 2

@@
 \usepackage{color}
+%\usepackage{ulem} Why this?
 
@@
 
-% metrics = quantitative indicator of sth
+%Title ideas:
+% - How can we fix quality issues in SKOS vocabularies?
+% - Detecting quality issues in SKOS Vocabularies
+% - Computable Quality Guidlines for SKOSO Vocabularies
+% - ...
 
 \title{Finding Quality Issues in SKOS Vocabularies}
-\author{Christian Mader\inst{1} \and Bernhard Haslhofer\inst{2}}
+\subtitle{\todo{ALL}{I am still not happy with the title; better ideas?}}
+\author{Christian Mader\inst{1} \and Bernhard Haslhofer\inst{2} \and Antoine Isaac\inst{3}}
 \institute{
-	University of Vienna, Faculty of Computer Science\\\email{christian.mader@univie.ac.at}
-	\and Cornell University, Information Science\\\email{bernhard.haslhofer@cornell.edu}}
+	University of Vienna, Faculty of Computer Science, Austria\\\email{christian.mader@univie.ac.at}
+	\and Cornell University, Department of Information Science, USA\\\email{bernhard.haslhofer@cornell.edu}
+	\and Vrije Universiteit Amsterdam, The Netherlands\\\email{aisaac@few.vu.nl}
+	}
 
@@
 
-\input{related_work}
-
 \input{conclusions}

### 2012-03-28 related_work.tex
merged related work into 2

@@
 \section{Related Work}\label{sec:related_work}
-
-% Data quality in general
-The problem of ``vocabulary quality'' is closely related to the more general problem of ``data quality`'', which has intensively been discussed in data and information systems research (cf.~\cite{Batini2009}).
-Pipino et al.~\cite{Pipino2002} argue that dealing with data quality should involve both ``subjective perceptions of the individuals'' and ``objective measurements based on the data set in question''.
-We see our work as a contribution to the latter.
-
-% Quality in Semantic Web and Linked Data
-Data quality research has also been conducted in the Semantic Web and Linked Data research areas.
-Hogan et.
-al~\cite{Hogan2010} identify four categories of common errors and shortcomings in RDF documents and also Heath and Bizer~\cite{Heath2011} summarize best practices for publishing data on the Web.
-However, the authors focus on RDF datasets in general without considering SKOS-specific properties.
-Ontology evaluation is task of measuring the quality of an ontology and has extensively been discussed by Vrandecic~\cite{Vrandecic2010}.
 

### 2012-03-28 analysis.tex
incorporated some of antoines comments

@@
 
-Table~\ref{tab:vocabs} shows our selection and summarizes basic statistical properties relevant for interpreting our results: the number of concepts $C$, ``authoritative concepts'', as explained in Section~\ref{subsec:ld_issues}, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations (\texttt{Labels}), all semantic relations $SR$, as well as the number of aggregation relations and concept schemes.
+Table~\ref{tab:vocabs} shows our selection and summarizes basic statistical properties relevant for interpreting our results: the number of concepts, ``authoritative concepts'', as explained in Section~\ref{subsec:ld_issues}, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations (\texttt{Labels}), all asserted semantic relations $SR$, as well as the number of concept schemes.
 
@@
 \textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{\parbox{3cm}{Version/\\Last Modified}}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth.
-Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} \\
+Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} \\
 \toprule
-Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32,035 & 32,035 & 620,629 & 65,934 & 32,085 & 1 \\
+Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32,035 & 32,035 & 620,629 & 65,934 & 1 \\
 \hline
-DBpedia Categories & \textbf{DBpedia} & 3.7 & 743,410 & 743,410 & 740,352 & 1,490,316 & 0 & 0 \\
+DBpedia Categories & \textbf{DBpedia} & 3.7 & 743,410 & 743,410 & 740,352 & 1,490,316 & 0 \\
 \hline
-The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6,797 & 6,797 & 457,788 & 18,491 & 15,512 & 128 \\
+The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6,797 & 6,797 & 457,788 & 18,491 & 128 \\
 \hline
-Geonames Ontology & \textbf{Geonames} & 2.2.1 & 671 & 671 & 671 & 0 & 671 & 9 \\
+Geonames Ontology & \textbf{Geonames} & 2.2.1 & 671 & 671 & 671 & 0 & 9 \\
 \hline
-Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171,991 & 171,991 & 178,776 & 50,892 & 343,980 & 9 \\
+Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171,991 & 171,991 & 178,776 & 50,892 & 9 \\
 \hline
-Integrated Public Sector Vocabulary & \textbf{IPSV} & 2.00 & 4,732 & 3,080 & 7,945 & 13,843 & 4,483 & 3 \\
+Integrated Public Sector Vocabulary & \textbf{IPSV} & 2.00 & 4,732 & 3,080 & 7,945 & 13,843 & 3 \\
 \hline
-Library of Congress Subject Headings & \textbf{LCSH} & 2011/08/09 & 459,182 & 407,908 & 746,076 & 595,754 & 815,816 & 19 \\
+Library of Congress Subject Headings & \textbf{LCSH} & 2011/08/09 & 459,182 & 407,908 & 746,076 & 595,754 & 19 \\
 \hline
-Austrian Armed Forces Thesaurus & \textbf{LVAk} & 0.9 & 13,411 & 13,411 & 17,250 & 16,346 & 0 & 0 \\
+Austrian Armed Forces Thesaurus & \textbf{LVAk} & 0.9 & 13,411 & 13,411 & 17,250 & 16,346 & 0 \\
 \hline
-Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 & 422 & 569 & 1,698 & 6 & 2 \\
+Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 & 422 & 569 & 1,698 & 2 \\
 \hline
-Medical Subject Headings & \textbf{MeSH} & \cite{van2006method} & 24,626 & 24,626 & 150,617 & 38,858 & 0 & 0 \\
+Medical Subject Headings & \textbf{MeSH} & \cite{van2006method} & 24,626 & 24,626 & 150,617 & 38,858 & 0 \\
 \hline
-North American Industry Classification System & \textbf{NAICS} & 2012 & 4,175 & 2,213 & 0 & 8,684 & 2,235 & 1 \\
+North American Industry Classification System & \textbf{NAICS} & 2012 & 4,175 & 2,213 & 0 & 8,684 & 1 \\
 \hline
-New York Times People & \textbf{NYTP} & 2010/06/22 & 4,979 & 4,979 & 4,979 & 0 & 4,979 & 1 \\
+New York Times People & \textbf{NYTP} & 2010/06/22 & 4,979 & 4,979 & 4,979 & 0 & 1 \\
 \hline
-University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1,125 & 1,125 & 0 & 0 & 0 & 0 \\
+University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1,125 & 1,125 & 0 & 0 & 0 \\
 \hline
-Peroxisome Knowledge Base & \textbf{PXV} & 1.6 & 2,112 & 1,686 & 3,628 & 2,695 & 1,716 & 1 \\
+Peroxisome Knowledge Base & \textbf{PXV} & 1.6 & 2,112 & 1,686 & 3,628 & 2,695 & 1 \\
 \hline
-Thesaurus for Economics & \textbf{STW} & 8.06 & 6,524 & 6,524 & 31,189 & 57,907 & 6,531 & 1 \\
+Thesaurus for Economics & \textbf{STW} & 8.06 & 6,524 & 6,524 & 31,189 & 57,907 & 1 \\
 \bottomrule

### 2012-03-28 criteria.tex
incorporated some of antoines comments

@@
 \paragraph{\textbf{Definition (SKOS Vocabulary).}}
-Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV, CS \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C \subseteq IR\) with \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) \todo{CM}{check exponent}being the set of \textbf{concepts}, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}, and \(CS = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})\) being the set of \textbf{concept schemes}.
-Further, we let $V$ be the fully entailed RDFS interpretation of the underlying RDF graph, enriched by entailment of \texttt{owl:inverseOf} properties as well as subproperties of \texttt{owl:TransitiveProperty} and \texttt{owl:SymmetricProperty}.
+Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV, CS \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C \subseteq IR\) with \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{concepts}, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}, and \(CS = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})\) being the set of \textbf{concept schemes}.
+Further, we let $V$ be the fully entailed RDFS interpretation of the underlying RDF graph, enriched by entailment of \texttt{owl:inverseOf} properties as well as instances of \texttt{owl:TransitiveProperty} and \texttt{owl:SymmetricProperty}.
 
@@
 % Function definition
-To estimate the number of in-links we only consider the set $AC \subseteq C$, which consists of all ``authoritative concepts'', hence concepts that have an URI in the vocabulary namespace.
-The number of in-links referencing an authoritative concept can be estimated by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/}} SPARQL endpoint for triples containing the concept's URI in the object part.
+To estimate the number of in-links we only consider the set $AC \subseteq C$, which consists of all ``authoritative concepts'', i.e.
+concepts that have an URI in the vocabulary namespace.
+The number of in-links referencing an authoritative concept can be estimated by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/} indexes RDF data from various sources on the Web (e.g., dataset dumps, RDFa data, microformats).
+In June 2011 the Sindice dataset contained over 230M documents with over 11 billion triples (cf.
+\url{http://data.sindice.com/trec2011/statistics.html})} SPARQL endpoint for triples containing the concept's URI in the object part.
 Empty query results are indicators for missing in-links and are thus included in the result set of this function.
@@
 In the Linked Data context, SKOS concepts should be linked with other related concepts on the Web, ``enabling seamless connections between data sets''\cite{Heath2011}.
-Similar to \emph{Missing In-Links}, this issue identifies the set of all concepts that have no out-links.
+Similar to \emph{Missing In-Links}, this issue identifies the set of all authoritative concepts that have no out-links.
 % Function definition
@@
 As we discussed in detail in our earlier work~\cite{Popitsch:2010:DHB:1772690.1772768}, this issue is caused by vocabulary resources that return HTTP error responses or no response when being dereferenced.
-An erroneous HTTP response in that case can be defined as a response code other than 200 when taking possible redirections into account.
+An erroneous HTTP response in that case can be defined as a response code other than 200 after possible redirections.
 Just as in the ``document'' Web, these ``broken links'' hinder navigability also in the Linked Data Web and and should therefore be avoided.
@@
 The SKOS model is defined within the namespace \url{http://www.w3.org/2004/02/skos/core#}.
-However, some vocabularies use resources from within this namespace, which are unresolvable for two main reasons: vocabulary creators ``invented'' new terms within the SKOS namespace instead of introducing them in a separate namespace, or they use ``deprecated'' SKOS properties.
+However, some vocabularies use resources from within this namespace, which are unresolvable for two main reasons: vocabulary creators ``invented'' new terms within the SKOS namespace instead of introducing them in a separate namespace, or they use ``deprecated'' SKOS properties like, e.g., \texttt{skos:subject}.
 % Function definition

### 2012-03-28 main.tex
update intro

@@
 	\and Cornell University, Department of Information Science, USA\\\email{bernhard.haslhofer@cornell.edu}
-	\and Vrije Universiteit Amsterdam, The Netherlands\\\email{aisaac@few.vu.nl}
+	\and Europeana \& Vrije Universiteit Amsterdam, The Netherlands\\\email{aisaac@few.vu.nl}
 	}
@@
 
-The Simple Knowledge Organization System (SKOS) has become a standard model for controlled vocabularies on the Web.
+The Simple Knowledge Organization System (SKOS) is a standard model for controlled vocabularies on the Web.
 However, SKOS vocabularies often differ in terms of quality, which reduces their applicability across system boundaries.

### 2012-03-28 criteria.tex
minor changes

@@
 
-\todo{CM}{use definition environment and find out how to turn of numbering}
-\paragraph{\textbf{Definition (SKOS Vocabulary).}}
+\spnewtheorem*{mydef}{Definition}{\bfseries}{\itshape}
+\begin{mydef}[SKOS Vocabulary]
 Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV, CS \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C \subseteq IR\) with \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{concepts}, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}, and \(CS = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})\) being the set of \textbf{concept schemes}.
 Further, we let $V$ be the fully entailed RDFS interpretation of the underlying RDF graph, enriched by entailment of \texttt{owl:inverseOf} properties as well as instances of \texttt{owl:TransitiveProperty} and \texttt{owl:SymmetricProperty}.
+\end{mydef}
 
@@
 % Origin and rationale
-The ISO/DIS 25964-1 standard \cite{ISO25964-1:2011} suggests that terms that share a common broader term but do not have an \todo{CM}{explain "overlapping"}overlapping meaning, should not be related associatively.
+The ISO/DIS 25964-1 standard \cite{ISO25964-1:2011} suggests that terms that share a common broader term should not be related associatively if this relation is only justified by the fact that they are siblings.
 This is advocated by Hedden~\cite{Hedden2010} and Aitchison et al.~\cite{Aitchison2000} who point out ``the risk that thesaurus compilers may overload the thesaurus with valueless relationships'', having a negative effect on precision.

### 2012-03-28 introduction.tex

@@
 % What is SKOS?
-The Simple Knowledge Organization System (SKOS)~\cite{Miles2005} is a standard model for sharing and linking controlled vocabularies on the Web.
-Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} publish SKOS representations of their controlled vocabularies on the Web so that they can easily be accessed by humans and machines.
+The Simple Knowledge Organization System (SKOS)~\cite{SkosReference2008} is a standard model for sharing and linking controlled vocabularies (thesauri, classification systems\ldots) on the Web.
+Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} publish SKOS representations of their vocabularies on the Web so that they can easily be accessed by humans and machines.
 
-% What does "quality" mean in this context?
-Each vocabulary reflects domain- and application-specific needs and taxonomists often follow existing standards (cf.,~\cite{ISO25964-1:2011,Z39.19:2005}) or apply their own hand-crafted checks (cf.,~\cite{Coronado2009}) to meet certain quality requirements.
-However, quality requirements can differ across application domains.
-The following examples illustrate how quality issues can affect the applicability of SKOS vocabularies for tasks such as query expansion, faceted browsing, or auto-completion:
+However, quality issues can affect the applicability of SKOS vocabularies for tasks such as query expansion, faceted browsing, or auto-completion, as in the following examples:
 
@@
 
-	\item The SKOS representation of AGROVOC defines concepts in 25 different languages.
-However, while most concepts have an English description, only 38\% have German labels attached.
+	\item AGROVOC defines concepts in 25 different languages.
+However, while most concepts have English labels attached, only 38\% have German labels.
 This can be a problem for multilingual applications that rely on label translations.
 
-	\item An earlier version (v.8.06) of the STW thesaurus contained 5 pairs of concepts with identical labels.
-As a result, the auto-complete function of the online search interface suggested identical entries, without giving disambiguation information.
+	\item An earlier version of the STW thesaurus contained 5 pairs of concepts with identical labels.
+As a result, the auto-complete function of the online search interface suggested identical entries without disambiguation information.
 
@@
 
-	\item The non-public vocabulary developed by the Austrian Armed Forces (LVAk) contains 11 disconnected concept clusters.
-When we confronted the thesaurus maintainers with these structures, they recognized them as ``forgotten'' test data that has no practical significance.
+	\item The non-public vocabulary of the Austrian Armed Forces (LVAk) contains 11 disconnected concept clusters.
+When confronted with these structures, the thesaurus maintainers recognized them as ``forgotten'' test data that has no practical significance.
 
@@
 
-The SKOS specification doesn't make any explicit statements about vocabulary quality.
-It defines a set of \textbf{integrity conditions} that state ``whether or not given data are consistent with respect to the SKOS data model''~\cite{Miles2005}.
+The SKOS specification defines a set of \textbf{integrity conditions} that state whether given data patterns are consistent with the SKOS model.
 Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to validate vocabularies against these conditions.
-However, these conditions fail to capture quality aspects such as those mentioned in the examples before, aspects that go beyond integrity conditions of the SKOS data model.
-Existing guidelines and manuals consider these aspects but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger, possibly linked vocabularies on the Web.
+
+Yet the SKOS integrity conditions fail to capture quality aspects like the ones above.
+The main reason lies in SKOS' ``minimal commitment'' approach.
+Each vocabulary reflects domain- and application-specific needs and taxonomists often follow standard guidelines specific to given types of vocabularies (cf.,~\cite{ISO25964-1:2011,Z39.19:2005}) for thesauri) or apply their own hand-crafted checks~\cite{Coronado2009}.
+A standard that aims at cross-domain interoperability should refrain from defining constraints that impose on one domain the requirements of another.
+SKOS is thus very liberal with respect to data integrity.
+
+On the other hand, existing guidelines consider these aspects, but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger vocabularies \todo{AI}{Refer to Spero's example if there is space}.
+The SKOS context, in which vocabularies can be linked on the Web to other resources, also brings new issues, hitherto unforeseen by ``traditional'' quality checking approaches.
 
@@
 
-The goal of our work is to help taxonomists in identifying possible quality issues in SKOS vocabularies, which go beyond data model integrity conditions.
-We want to given them a set of computable quality checking functions that, in combination with the taxonomists' experience and domain expertise, can serve as quality indicators for vocabularies.
+We aim at contributing to the ongoing efforts of the community to bridge that gap\todo{Bernhard, Christian}{I'm not so happy with my sentence here.
+We can remove it if there's no better alternative to send the message we can remove it!}.
+Our goal is to help taxonomists in identifying possible quality issues in SKOS vocabularies, which go beyond data model integrity conditions while still applying to a wide range of cases.
+We want to give them a set of computable quality checking functions that, in combination with the taxonomists' experience and domain expertise, can serve as quality indicators for vocabularies.
 Finding such quality issues also gives important feedback on the overall vocabulary design process and should, at the end, lead to better vocabularies.
@@
 
-	\item We identified 15 \textbf{quality issues} for SKOS vocabularies by examining existing guidelines and formalized them into computable \textbf{quality checking functions} that identify possibly affected resources in a given SKOS vocabulary.
+	\item We identified 15 \textbf{quality issues} for SKOS vocabularies by examining existing guidelines and formalized them into computable \textbf{quality checking functions} that identify possibly affected resources in a vocabulary.
 
@@
 
-	\item We \textbf{analyzed} a representative set of \textbf{15 existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.
+	\item We \textbf{tested} these functions by \textbf{analyzing} a representative set of \textbf{15 existing SKOS vocabularies} to learn about possible quality issues.
 

### 2012-03-28 analysis.tex
minor changes

@@
 \texttt{GTAA} seems is a mixture of name authority file (162K concepts) and thesaurus (10K concepts).
-The 4 orphan concepts in \texttt{STW} are deprecated concepts, the 21 \texttt{LVAk} concepts are obviously test data.
+The 4 orphan concepts in \texttt{STW} are deprecated concepts.
+
+%the 21 \texttt{LVAk} concepts are obviously test data. <- CM: we should skip this, the preflabels of the concepts seem OK, I have no explanations why they are there
+
 % Weakly Connected Components
-Three vocabularies have one weakly connected component which means that there is one ``giant component''.
+Consisting of one weakly connected component (``giant component''), three vocabularies represent what is often considered as the ideal vocabulary structure.
 All other vocabularies split into several clusters of semantically related concepts that represent several subtopics in the vocabularies.
@@
 Weakly connected components divide the \texttt{Meketre} vocabularies into, e.g., execution-style related concepts, concepts reserved for internal use or museums.
-\texttt{GTAA} consists of 621 weakly connected components, most of them containing less than 10 concepts, representing, e.g., political parties, companies or historical periods.
+\texttt{GTAA} consists of 621 weakly connected components with the largest one supposed to be a subject thesaurus containing 8413 concepts.
+Most  other components contain less than 10 concepts, representing, e.g., locations, person names, maker names and genres.
 \texttt{PXV} splits into 10 weakly connecting components, topically relating e.g., ``deficiancies'', ``defects'' or ``signals''.

### 2012-03-28 criteria.tex
minor changes

@@
 % Function definition
-It can be computed by iterating over all elements $c \in C$ and checking the host part of all related resource URIs.
-If none of these host names differ from the host part of $c$'s URI, it has no out-links and is thus included in the resources identified by this issue.
+It can be computed by iterating over all elements $ac \in AC$ and checking the host part of all related resource URIs.
+If none of these host names differ from the host part of $ac$'s URI, it has no out-links and is thus included in the resources identified by this issue.
 

### 2012-03-28 introduction.tex
updated background (and intro)

@@
 
-On the other hand, existing guidelines consider these aspects, but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger vocabularies \todo{AI}{Refer to Spero's example if there is space}.
-The SKOS context, in which vocabularies can be linked on the Web to other resources, also brings new issues, hitherto unforeseen by ``traditional'' quality checking approaches.
+On the other hand, existing guidelines consider these aspects, but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger vocabularies.
+The SKOS context, where vocabularies can be linked together on the Web, also brings issues hitherto unforeseen by traditional checking approaches.
 
@@
 
-We aim at contributing to the ongoing efforts of the community to bridge that gap\todo{Bernhard, Christian}{I'm not so happy with my sentence here.
+We aim to contribute to the ongoing efforts of the community to bridge that gap\todo{BH, CM}{I'm not so happy with my sentence here.
 We can remove it if there's no better alternative to send the message we can remove it!}.

### 2012-03-28 analysis.tex
incorporated antoines comments

@@
 % Undocumented Concepts
-\texttt{Geonames} is the only vocabulary in our dataset, which has at least one documentation property assigned to all its concept.
+\texttt{Geonames}, which is an ontology including a concept scheme of ``feature codes'', is the only vocabulary in our dataset, which has at least one documentation property assigned to all of its concept.
 All other vocabularies have a significant number of undocumented concepts.

### 2012-03-28 background.tex

@@
 % Data quality in general
-The problem of ``vocabulary quality'' is closely related to the more general problem of ``data quality`'' and has been discussed in data and information systems research (cf.~\cite{Batini2009}).
-Pipino et al.~\cite{Pipino2002} argue that dealing with data quality should involve both ``subjective perceptions of the individuals'' and ``objective measurements based on the data set in question''.
+The problem of ``vocabulary quality'' is closely related to the more general one of ``data quality`'' and has been discussed in data and information systems research~\cite{Batini2009}.
+Pipino et al.~\cite{Pipino2002} argue that dealing with data quality should involve both ``subjective perceptions of the individuals'' and ``objective measurements based on the data''.
 We see our work as a contribution to the latter.
 
-\subsection{Quality in SKOS Vocabularies}
+\paragraph{Quality in Semantic Web and Linked Data Research}
 
-SKOS is a model for controlled vocabularies in the Web of Data and therefore based on the Open World Assumption.
+Hogan et.
+al~\cite{Hogan2010} identify four categories of common errors and shortcomings in RDF documents and Heath and Bizer~\cite{Heath2011} summarize best practices for publishing data on the Web.
+Ontology evaluation, i.e., measuring the quality of an ontology, has also been discussed extensively~\cite{Vrandecic2010}.
+However, the authors focus on RDF datasets and ontologies in general.
+While we could use some criteria suggested here, these need to be completed by considering SKOS-specific properties.
+\todo{CM, BH}{I suppose that the in-links etc come from that kind of work, no?}
+
+\paragraph{Quality in SKOS Vocabularies}
+
+SKOS specifies in total six \textbf{integrity conditions}~\cite{SkosReference2008}, each of which is a statement that defines under which circumstances data are consistent with the SKOS data model.
+For example, ``a resource has no more than one value of \texttt{skos:prefLabel} per language tag''.
+Tools that can check whether these conditions are met are already available: two of the six conditions are defined formally in the OWL representation of SKOS and can therefore be validated by any OWL reasoner.
+For validating a SKOS vocabulary against the other integrity conditions, one can use tools such as the \textbf{PoolParty Thesaurus Consistency Checker}, or the \textbf{Skosify} validator, which can also correct some detected quality problems.
+
+One issue when assessing the quality of SKOS data is the so-called ``Open World Assumption'', which underlies the Web of Data itself.
 Established quality notions from closed-world systems, such as referential integrity or schema validation, don't hold anymore, because available information may be incomplete and non-explicitly stated facts cannot be determined as true or false.
-Content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}.
+\todo{AI}{Add ref to DCAM and Pellet, if we have 3 lines available for that.} Work-arounds, often ad-hoc, are thus currently used to evaluate quality in Linked Data sets~\cite{Heath2011}, as is done in the (rule-based) SKOS tools mentioned above.
 
@@
 
-Interoperability between applications has been the major motivation for specifying in total six \textbf{SKOS integrity conditions}~\cite{SkosReference2008}, each of which is a statement that defines under which circumstances data are consistent with the SKOS data model.
-An example condition is ``a resource has no more than one value of \texttt{skos:prefLabel} per language tag''.
-Tools that can check whether these integrity conditions are met for given data are already available: two of the six integrity conditions are defined formally in the OWL representation of SKOS and can therefore be validated by any OWL reasoner.
-For validating a SKOS vocabulary against the integrity conditions, one can use tools such as the online \textbf{PoolParty Thesaurus Consistency Checker}, or the \textbf{Skosify} command line validator, which can also correct some detected quality problems.
+\paragraph{Quality in Controlled Vocabularies}
 
-\subsection{Quality in Controlled Vocabularies}
-
-Typical application areas of controlled vocabularies are classification, indexing, autocompletion, query reformulation/expansion, or serving as a glossary.
-As we discussed in detail in our earlier work \cite{Nagy2011}, these areas impose specific requirements on vocabulary features, such as structure, availability, and documentation of conceptual resources.
+Typical applications of controlled vocabularies are classification, indexing, autocompletion, query reformulation, or serving as a glossary.
+As we discussed in detail in earlier work~\cite{Nagy2011}, these areas impose specific requirements on vocabulary features, such as structure, availability, and documentation.
 Quality aspects of controlled vocabularies have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, tutorials~\cite{Soergel2002}, and scholarly articles \cite{Coronado2009,Soergel1997,Elkin2002,Kless2010}.
-Our work builds on this literature and identifies possible quality issues that go beyond model-level integrity conditions.
-
-\subsection{Quality in Semantic Web and Linked Data Research}
-
-Hogan et.
-al~\cite{Hogan2010} identify four categories of common errors and shortcomings in RDF documents and also Heath and Bizer~\cite{Heath2011} summarize best practices for publishing data on the Web.
-Also ontology evaluation, which is the task of measuring the quality of an ontology, has been discussed by Vrandecic~\cite{Vrandecic2010}.
-However, the authors focus on RDF datasets and ontologies in general without considering SKOS-specific properties.
+Our work builds on this literature, but focuses on the less intellectually loaded checks, which can be automatized to assist vocabulary users or publishers.
+\todo{AI}{In fact Spero's example can be put here}

### 2012-03-28 background.tex
polished intro

@@
 Tools that can check whether these conditions are met are already available: two of the six conditions are defined formally in the OWL representation of SKOS and can therefore be validated by any OWL reasoner.
-For validating a SKOS vocabulary against the other integrity conditions, one can use tools such as the \textbf{PoolParty Thesaurus Consistency Checker}, or the \textbf{Skosify} validator, which can also correct some detected quality problems.
+For validating a SKOS vocabulary against the other integrity conditions, one can use tools such as the \textbf{PoolParty Thesaurus Consistency Checker}\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}}, or the \textbf{Skosify}\footnote{\url{http://code.google.com/p/skosify/}} validator, which can also correct some detected quality problems.
 

### 2012-03-28 introduction.tex
polished intro

@@
 % What is SKOS?
-The Simple Knowledge Organization System (SKOS)~\cite{SkosReference2008} is a standard model for sharing and linking controlled vocabularies (thesauri, classification systems\ldots) on the Web.
+The Simple Knowledge Organization System (SKOS)~\cite{SkosReference2008} is a standard model for sharing and linking controlled vocabularies (thesauri, classification systems, etc.) on the Web.
 Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} publish SKOS representations of their vocabularies on the Web so that they can easily be accessed by humans and machines.
@@
 
-% Note: can we replace the LvAK with an example from a public vocabulary? Then we could simply exclude that vocabulary from that paper.
-
 	\item The non-public vocabulary of the Austrian Armed Forces (LVAk) contains 11 disconnected concept clusters.
 When confronted with these structures, the thesaurus maintainers recognized them as ``forgotten'' test data that has no practical significance.
-
-    % \item In the DBpedia category\footnote{\url{http://downloads.dbpedia.org/3.7/en/skos_categories_en.nt.bz2}} hierarchy, more than 10 percent of the categories not linked to any other category.
-When other vocabularies link to the DBPedia categories, e.g., to enable query expansion, it can negatively affect recall and reduce navigability.
 
@@
 The SKOS specification defines a set of \textbf{integrity conditions} that state whether given data patterns are consistent with the SKOS model.
-Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to validate vocabularies against these conditions.
-
 Yet the SKOS integrity conditions fail to capture quality aspects like the ones above.
 The main reason lies in SKOS' ``minimal commitment'' approach.
-Each vocabulary reflects domain- and application-specific needs and taxonomists often follow standard guidelines specific to given types of vocabularies (cf.,~\cite{ISO25964-1:2011,Z39.19:2005}) for thesauri) or apply their own hand-crafted checks~\cite{Coronado2009}.
 A standard that aims at cross-domain interoperability should refrain from defining constraints that impose on one domain the requirements of another.
@@
 
-On the other hand, existing guidelines consider these aspects, but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger vocabularies.
+On the other hand, each vocabulary should fulfill domain- and application-specific quality aspects and taxonomists often follow standard guidelines specific to given types of vocabularies (cf.,~\cite{ISO25964-1:2011,Z39.19:2005}) for thesauri) or apply their own hand-crafted checks~\cite{Coronado2009}.
+Existing guidelines consider these aspects, but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger vocabularies.
 The SKOS context, where vocabularies can be linked together on the Web, also brings issues hitherto unforeseen by traditional checking approaches.
@@
 
-We aim to contribute to the ongoing efforts of the community to bridge that gap\todo{BH, CM}{I'm not so happy with my sentence here.
-We can remove it if there's no better alternative to send the message we can remove it!}.
-Our goal is to help taxonomists in identifying possible quality issues in SKOS vocabularies, which go beyond data model integrity conditions while still applying to a wide range of cases.
-We want to give them a set of computable quality checking functions that, in combination with the taxonomists' experience and domain expertise, can serve as quality indicators for vocabularies.
+We aim at contributing to the ongoing community efforts to bridge that gap between model-level integrity constraints and domain-specific quality aspects.
+Our goal is to help taxonomists in identifying possible quality issues in SKOS vocabularies and to give them a set of computable quality checking functions that, in combination with the taxonomists' experience and domain expertise, can serve as quality indicators for vocabularies.
 Finding such quality issues also gives important feedback on the overall vocabulary design process and should, at the end, lead to better vocabularies.

### 2012-03-29 background.tex
polished background

@@
 % Data quality in general
-The problem of ``vocabulary quality'' is closely related to the more general one of ``data quality`'' and has been discussed in data and information systems research~\cite{Batini2009}.
+The problem of ``vocabulary quality'' is closely related to the more general one of ``data quality`'' and has been discussed in data and information systems research (cf.~\cite{Batini2009}).
 Pipino et al.~\cite{Pipino2002} argue that dealing with data quality should involve both ``subjective perceptions of the individuals'' and ``objective measurements based on the data''.
@@
 
-\paragraph{Quality in Semantic Web and Linked Data Research}
-
-Hogan et.
-al~\cite{Hogan2010} identify four categories of common errors and shortcomings in RDF documents and Heath and Bizer~\cite{Heath2011} summarize best practices for publishing data on the Web.
-Ontology evaluation, i.e., measuring the quality of an ontology, has also been discussed extensively~\cite{Vrandecic2010}.
-However, the authors focus on RDF datasets and ontologies in general.
-While we could use some criteria suggested here, these need to be completed by considering SKOS-specific properties.
-\todo{CM, BH}{I suppose that the in-links etc come from that kind of work, no?}
-
-\paragraph{Quality in SKOS Vocabularies}
-
-SKOS specifies in total six \textbf{integrity conditions}~\cite{SkosReference2008}, each of which is a statement that defines under which circumstances data are consistent with the SKOS data model.
+The SKOS specification doesn't mention the notion of quality, but defines in total six \textbf{integrity conditions}~\cite{SkosReference2008}, each of which is a statement that defines under which circumstances data are consistent with the SKOS data model.
 For example, ``a resource has no more than one value of \texttt{skos:prefLabel} per language tag''.
@@
 
-\paragraph{Quality in Controlled Vocabularies}
-
 Typical applications of controlled vocabularies are classification, indexing, autocompletion, query reformulation, or serving as a glossary.
@@
 \todo{AI}{In fact Spero's example can be put here}
+
+% Quality in SW / Linked Data Research
+
+Data quality is also being discussed in Semantic Web and Linked Data research.
+Hogan et.
+al~\cite{Hogan2010} identify four categories of common errors and shortcomings in RDF documents and Heath and Bizer~\cite{Heath2011} summarize best practices for publishing data on the Web.
+Ontology evaluation, i.e., measuring the quality of an ontology, has also been discussed extensively~\cite{Vrandecic2010}.
+However, the authors focus on RDF datasets and ontologies in general.
+While we could use some criteria suggested here, such as consistent tagging of literals, these need to be completed by considering SKOS-specific properties.

### 2012-03-29 criteria.tex
fixed stuff in section 3; added TODOs for CM

@@
 We identified an initial set of possible quality issues in SKOS vocabularies by reviewing literature and manually examining existing vocabularies.
-We published our findings online\footnote{\url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}} and requested feedback from experts via public mailing lists and informal face to face discussions.
-Based on the received responses, we then selected a subset of these issues and formalized them into computable \textbf{quality checking functions}.
-Each function operates on a given SKOS vocabulary, which we define, for the purpose of this work, as follows:
+We published our findings in the qSKOS Wiki and requested feedback from experts via public mailing lists and informal face to face discussions.
+Based on the received responses, we then selected a subset of these issues and translated them into computable \textbf{quality checking functions}.
+Each function takes a given SKOS vocabulary as input and finds all vocabulary resources that match the corresponding quality issue.
+For the purpose of this work, we define a SKOS vocabulary as follows:
 
@@
 Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV, CS \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C \subseteq IR\) with \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{concepts}, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}, and \(CS = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})\) being the set of \textbf{concept schemes}.
-Further, we let $V$ be the fully entailed RDFS interpretation of the underlying RDF graph, enriched by entailment of \texttt{owl:inverseOf} properties as well as instances of \texttt{owl:TransitiveProperty} and \texttt{owl:SymmetricProperty}.
+Further, we let $V$ be the fully entailed RDFS interpretation of the underlying RDF graph.
+We enrich $V$ by entailment of \texttt{owl:inverseOf} properties as well as instances of \texttt{owl:TransitiveProperty} and \texttt{owl:SymmetricProperty}, because SKOS these properties in its formal model.
 \end{mydef}
 
-A checking function is applied on a given SKOS vocabulary and finds all vocabulary resources that match the corresponding quality issue.
+\todo{CM}{are you sure about IEXT and ICEXT; isn't I enough?}
+
+%A checking function is applied on a given SKOS vocabulary and finds all vocabulary resources that match the corresponding quality issue.
 We can map each issue to an abstract function $f:V \rightarrow \mathcal{P}(IR)$ that relates a given SKOS vocabulary to a subset of its resources.
@@
 
-In the following, we explain the origins and design rationale for each quality issue and define the corresponding quality checking function.
-For better readability and due to lack of space we provide only semi-formal definitions and refer to the online documentation and the implementation source code\footnote{\url{https://github.com/cmader/qSKOS/}} for further details.
+In the following, we explain the origins and design rationale for each quality issue and explain how the corresponding quality checking function works.
+For better readability and due to lack of space we provide only semi-formal definitions and refer to the source code of the qSKOS tool for further details.
 
@@
 % Function defintion
-A SKOS vocabulary can be checked for omitted and invalid language tags by iterating over all resources in $IR$ and finding those that have relations to plain literals (using the above mentions SKOS properties) with missing or invalid language tags, i.e., tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
+A SKOS vocabulary can be checked for omitted and invalid language tags by iterating over all resources in $IR$ and finding those that have relations to plain literals (using the above mentioned SKOS properties) with missing or invalid language tags, i.e., tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
 
@@
 % Origin and rationale
-Soergel et al.~\cite{Soergel1997} point out the problem that ``...a concept lexicalized in one language may not be lexicalized in another and that the terms do exist often vary slightly in meaning...''.
-Thus, finding such cases would provide guidance for vocabulary developers for revising the vocabulary structure and to ``clearly instruct indexers in all languages how the term is to be used''.
-In the context of SKOS, this means that the set of language tags used by the literal values linked with a concept should be checked to be the same for all concepts.
-If this is not true for a vocabulary, appropriate actions like, e.g., splitting concepts or introducing scope notes should be taken by the creators.
+%Soergel et al.~\cite{Soergel1997} point out the problem that ``...a concept lexicalized in one language may not be lexicalized in another and that the terms do exist often vary slightly in meaning...''.
+Thus, finding concepts with incomplete language coverage can help taxonomists in revising the vocabulary and ``clearly instruct indexers in all languages how the term is to be used''.
+
+In the context of SKOS, incomplete language coverage means that the set of language tags used by the literal values linked with a concept should be the same for all concepts.
+If this is not the case, appropriate actions like, e.g., splitting concepts or introducing scope notes should be taken by the creators.
 This is particularly important for applications that rely on internationalization and translation use cases.
@@
 % Origin and rationale
-Svenonius~\cite{Svenonius1997} advocates the ``inclusion of as much definition material as possible'' and the SKOS Reference~\cite{SkosReference2008} defines a set of properties, denoted as ``documentation properties'', that are intended to hold this kind of information.
+Svenonius~\cite{Svenonius1997} advocates the ``inclusion of as much definition material as possible'' and the SKOS Reference~\cite{SkosReference2008} defines a set of ``documentation properties'' intended to hold this kind of information.
 % Function defintion
@@
 % Origin and rationale
-Many constraints in~\cite{SkosReference2008,Isaac2009} are related to concept schemes, but (i) data on concept scheme membership may lack and (ii) concept scheme related constraints would be handled better with CWA, e.g., finding identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} of different concepts.
+Many constraints in~\cite{SkosReference2008,Isaac2009} are related to concept schemes, but (i) data on concept scheme membership may lack and (ii) concept scheme related constraints would be handled better with the Closed World Assumption (CWA), e.g., finding identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} of different concepts.
 Although being good practice for many thesauri this issue could cause problems in application scenarios such as auto-completion, which proposes labels based on the user input.
-
 %The SKOS Primer~\cite{Isaac2009} recommends that ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
 We reviewed existing vocabularies and applications and found that (i) many vocabularies don't use concept schemes and (ii) identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} can also negatively affect use cases such as auto-completion, which proposes labels based on the user input.
-
 % Function defintion
@@
 
+\todo{CM}{check top concept issue!}
+
 % LINKED-DATA SPECIFIC ISSUES
@@
 % Function definition
-To estimate the number of in-links we only consider the set $AC \subseteq C$, which consists of all ``authoritative concepts'', i.e.
-concepts that have an URI in the vocabulary namespace.
-The number of in-links referencing an authoritative concept can be estimated by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/} indexes RDF data from various sources on the Web (e.g., dataset dumps, RDFa data, microformats).
-In June 2011 the Sindice dataset contained over 230M documents with over 11 billion triples (cf.
-\url{http://data.sindice.com/trec2011/statistics.html})} SPARQL endpoint for triples containing the concept's URI in the object part.
+To estimate the number of in-links we only consider the set of ``authoritative concepts'' $AC \subseteq C$, which consists of all concepts that are identified by URIs in the vocabulary namespace.
+\todo{CM}{given an example for an authoritative concept, maybe from LCSH} The number of in-links referencing an authoritative concept can be estimated by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/} indexes structured Web data and covers approximately 230M documents with over 11 billion triples} SPARQL endpoint for triples containing the concept's URI in the object part.
 Empty query results are indicators for missing in-links and are thus included in the result set of this function.
@@
 % Function definition
-It can be computed by iterating over all elements $ac \in AC$ and checking the host part of all related resource URIs.
+It can be computed by iterating over all elements $ac \in AC$ and checking the host part of all related resource URIs \todo{CM}{authoritative concepts?}.
 If none of these host names differ from the host part of $ac$'s URI, it has no out-links and is thus included in the resources identified by this issue.

### 2012-03-29 analysis.tex
some power editing on Section 4

@@
 
-To learn about possible quality issues in real-world vocabularies, we implemented the previously described quality checking function in the qSKOS tool and applied each function on a set of existing SKOS vocabularies.
-
-\subsection{The qSKOS Quality Assessment Tool}
-
-The open-source qSKOS\footnote{\url{https://github.com/cmader/qSKOS/}} quality assessment tool can be used to find possible quality issues in a given SKOS vocabulary.
-Users can run the tool by passing a vocabulary and selecting the quality checking functions they want to perform.
-As a result, they obtain detailed reports listing possibly affected resources alongside with the potential cause of the issue.
-qSKOS is implemented in Java and can be used as standalone command-line tool or API in any other application.
-Its design is open for the introduction of additional quality checking functions.
-In our analysis, we used qSKOS version 0.1., which can be downloaded from: \url{https://github.com/cmader/qSKOS/zipball/v0.1}.
+We used our open-source qSKOS quality assessment tool to find possible quality issues in existing SKOS vocabularies.
+From each quality checking function we obtained detailed reports listing possibly affected resources alongside with the potential cause of the issue.
 
@@
 
-We used Sindice and available listings\footnote{\url{http://www.w3.org/2001/sw/wiki/SKOS/Datasets}} to learn about existing SKOS vocabularies and selected a subset, which differs in vocabulary size and application domain.
-We obtained the vocabularies either via direct Web download or by contacting the vocabulary maintainers.
-Further details about our vocabulary dataset are available in zip-file, which can be downloaded from: \url{http://www.github.com/cmader/???}.
-It also contains all but the non-public LVAk and PXV vocabularies.
-
-Table~\ref{tab:vocabs} shows our selection and summarizes basic statistical properties relevant for interpreting our results: the number of concepts, ``authoritative concepts'', as explained in Section~\ref{subsec:ld_issues}, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations (\texttt{Labels}), all asserted semantic relations $SR$, as well as the number of concept schemes.
+Our vocabulary selection is shown in Table~\ref{tab:vocabs}, which also summarizes basic statistical properties relevant for interpreting our results: the number of concepts, ``authoritative concepts'', as explained in Section~\ref{subsec:ld_issues}, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations (\texttt{Labels}), all asserted semantic relations $SR$, as well as the number of concept schemes.
 
@@
 \toprule
-Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32,035 & 32,035 & 620,629 & 65,934 & 1 \\
+United Nations Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32,035 & 32,035 & 620,629 & 65,934 & 1 \\
 \hline

### 2012-03-29 criteria.tex
fixed todos for section 3

@@
 % Function definition
-Affected resources can be found by iterating over all \texttt{skos:TopConcept}s and collecting those that are related to a resource via a \texttt{skos:broader} property.
-
-\todo{CM}{check top concept issue!}
+Affected resources can be found by iterating over all top concepts and collecting those that are related to a resource via a \texttt{skos:broader} property that is no \texttt{skos:mappingRelation}.
 
@@
 To estimate the number of in-links we only consider the set of ``authoritative concepts'' $AC \subseteq C$, which consists of all concepts that are identified by URIs in the vocabulary namespace.
-\todo{CM}{given an example for an authoritative concept, maybe from LCSH} The number of in-links referencing an authoritative concept can be estimated by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/} indexes structured Web data and covers approximately 230M documents with over 11 billion triples} SPARQL endpoint for triples containing the concept's URI in the object part.
+For example, \texttt{PXV} links the concept \url{http://www.peroxisomekb.nl/v1.6/pxv/C000297} to \url{http://www.bioexpert.nl/mesh/2010/concept/M0028264} using \texttt{skos:closeMatch}.
+Both resources can be infered as being \texttt{skos:Concept}s, but the latter is no authoritative concept because it's URI doesn't belong to the \texttt{PXV} namespace.
+The number of in-links referencing an authoritative concept can be estimated by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/} indexes structured Web data and covers approximately 230M documents with over 11 billion triples} SPARQL endpoint for triples containing the concept's URI in the object part.
 Empty query results are indicators for missing in-links and are thus included in the result set of this function.
@@
 % Function definition
-It can be computed by iterating over all elements $ac \in AC$ and checking the host part of all related resource URIs \todo{CM}{authoritative concepts?}.
-If none of these host names differ from the host part of $ac$'s URI, it has no out-links and is thus included in the resources identified by this issue.
+It can be computed by iterating over all elements $ac \in AC$ and checking the URIs of all related resources.
+If none of these URI's namespace differs from the namespace of $ac$'s URI, $ac$ has no out-links and is thus included in the resources identified by this issue.
 

### 2012-03-29 analysis.tex
fixed mol values

@@
 
-Missing Out-Links & 32,035 & 743,410 & 6,797 & 671 & 171,991 & 0 & 408,198 & 13,411 & 273 & 24,625 & 0 & 0 & 1,116 & 1,472 & 6,524 \\
+Missing Out-Links & 32,035 & 743,410 & 6,797 & 671 & 171,991 & 0 & 356,924 & 13,411 & 273 & 24,625 & 1 & 0 & 1,116 & 1,046 & 6,524 \\
 
@@
 Most vocabularies also don't provide links to other vocabularies on the Web.
-The \texttt{NYTP}, \texttt{IPSV} and \texttt{NAICS} vocabularies are the three exceptions, which are fully linked to other Web resources.
+The \texttt{NYTP}, \texttt{IPSV} vocabularies are two exceptions, which are fully linked to other Web resources.
+The one concept with missing links in \texttt{NAICS} is only used as object in \texttt{skos:broaderTransitive} assertions.
 % Broken Links

### 2012-03-29 criteria.tex
fixed mol values

@@
 Further, we let $V$ be the fully entailed RDFS interpretation of the underlying RDF graph.
-We enrich $V$ by entailment of \texttt{owl:inverseOf} properties as well as instances of \texttt{owl:TransitiveProperty} and \texttt{owl:SymmetricProperty}, because SKOS these properties in its formal model.
+We enrich $V$ by entailment of \texttt{owl:inverseOf} properties as well as instances of \texttt{owl:TransitiveProperty} and \texttt{owl:SymmetricProperty} defined by the formal OWL semantics of SKOS.
 \end{mydef}
 
-\todo{CM}{are you sure about IEXT and ICEXT; isn't I enough?}
+\todo{CM}{are you sure about IEXT and ICEXT; isn't I enough?
+yes; in fact IR definition is taken from Hitzler, so I think we can define, e.g., CS in the same way; btw, shouldn't we cite Hitzler or at least the RDF semantics document?}
 

### 2012-03-29 analysis.tex
fixed some analysis value(s)
updated analysis for LCSH

@@
 \hline
-Library of Congress Subject Headings & \textbf{LCSH} & 2011/08/09 & 459,182 & 407,908 & 746,076 & 595,754 & 19 \\
+Library of Congress Subject Headings & \textbf{LCSH} & 2012/03/29 & 443,164 & 408,009 & 750,219 & 598,134 & 1 \\
 \hline
@@
 \toprule
-Omitted or Invalid Language Tags & 0 & 0 & n/a & 0 & 0 & 0 & 18 & 13,411 & 0 & 23,950 & n/a & 0 & 1,224 & 1,578 & 2 \\
+Omitted or Invalid Language Tags & 0 & 0 & n/a & 0 & 0 & 0 & 100,316 & 13,411 & 0 & 23,950 & n/a & 0 & 1,224 & 1,578 & 2 \\
 
@@
 
-Undocumented Concepts & 32,035 & 743,410 & 5,341 & 0 & 96,850 & 4,551 & 398,036 & 13,411 & 422 & 1,807 & 3,259 & 4,094 & 1,125 & 1,918 & 5,236 \\
+Undocumented Concepts & 32,035 & 743,410 & 5,341 & 0 & 96,850 & 4,551 & 342,848 & 13,411 & 422 & 1,807 & 3,259 & 4,094 & 1,125 & 1,918 & 5,236 \\
 
@@
 
-Orphan Concepts & 0 & 77,062 & 7 & 671 & 162,000 & 0 & 172,364 & 21 & 0 & 0 & 0 & 4,979 & 1,125 & 2 & 4 \\
+Orphan Concepts & 0 & 77,062 & 7 & 671 & 162,000 & 0 & 180,909 & 21 & 0 & 0 & 0 & 4,979 & 1,125 & 2 & 4 \\
 
-Weakly Connected Components & 4 & 1,506 & 4 & 0 & 621 & 1 & 22,131 & 11 & 5 & 4 & 1 & 0 & 0 & 10 & 1 \\
+Weakly Connected Components & 4 & 1,506 & 4 & 0 & 621 & 1 & 22,343 & 11 & 5 & 4 & 1 & 0 & 0 & 10 & 1 \\
 
@@
 
-Valueless Associative Relations & 282 & 8,120 & 1 & 0 & 9,438 & 239 & 1,879 & 5 & 0 & 495 & 0 & 0 & 0 & 0 & 5,082 \\
+Valueless Associative Relations & 282 & 8,120 & 1 & 0 & 9,438 & 239 & 0 & 5 & 0 & 495 & 0 & 0 & 0 & 0 & 5,082 \\
 
@@
 
-Omitted Top Concepts & 0 & 0 & 1 & 9 & 9 & 0 & 19 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
+Omitted Top Concepts & 0 & 0 & 1 & 9 & 9 & 0 & 1 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
 
@@
 
-Missing In-Links & 32,035 & 733,800 & 6,796 & 19 & 171,980* & 3,080 & 404,540* & 13,411 & 422 & 24,625 & 2,213 & 20 & 1,125 & 1,686 & 6,516 \\
+Missing In-Links & 32,035 & 733,800 & 6,796 & 19 & 171,980* & 3,080 & ?* & 13,411 & 422 & 24,625 & 2,213 & 20 & 1,125 & 1,686 & 6,516 \\
 
-Missing Out-Links & 32,035 & 743,410 & 6,797 & 671 & 171,991 & 0 & 356,924 & 13,411 & 273 & 24,625 & 1 & 0 & 1,116 & 1,046 & 6,524 \\
+Missing Out-Links & 32,035 & 743,410 & 6,797 & 671 & 171,991 & 0 & 344,054 & 13,411 & 273 & 24,626 & 1 & 0 & 1,116 & 1,046 & 6,524 \\
 
-Broken Links & 238 & 0* & 0* & 0 & 0 & 1 && n/a & 425 & 1 & 3,169 & 7 & 11 & 163 & 1 \\
+Broken Links & 238 & 0* & 0* & 0 & 0 & 1 &?& n/a & 425 & 1 & 3,169 & 7 & 11 & 163 & 1 \\
 
@@
 % Omitted or Invalid Language Tags
-The \texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} vocabularies omit language tags with their \texttt{skos:prefLabel}, \texttt{skos:altLabel}, or \texttt{skos:hiddenLabel} properties.
-The STW thesaurus doesn't use language tags with 2 \texttt{skos:definition} property instances and the LCSH vocabulary uses language tags with concepts, but not with concept schemes.
+The \texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} vocabularies omit language tags with their \texttt{skos:prefLabel}, \texttt{skos:altLabel}, or \texttt{skos:hiddenLabel} properties, \texttt{LCSH} with the \texttt{skos:note} property.
+The STW thesaurus doesn't use language tags with 2 \texttt{skos:definition} property instances.
 % Incomplete Language Coverage
@@
 % Omitted Top Concepts
-\texttt{GTAA}, \texttt{Geonames}, \texttt{NYTP}, and \texttt{LCSH} have no top concept defined for any of the concept schemes they use.
+\texttt{GTAA} and \texttt{Geonames} have no top concept defined for any of the concept schemes they use.
 \texttt{Eurovoc} uses 128 concept schemes but has one without top concept, which simply contains all concepts defined in the vocabulary.
+Such an ``umbrella concept scheme'' without is also present in \texttt{LCSH} and \texttt{NYTP}.
 % Top Concepts Having Broader Concepts
@@
 % Broken Links
-Even though we couldn't determine the exact number of broken links because of the large number of links to resolve  (over 400K in \texttt{Eurovoc} and \texttt{LCSH}), we found that broken links are a common issue in most vocabularies.
+Even though we couldn't determine the exact number of broken links because of the large number of links to resolve  (over 400K in \texttt{Eurovoc}, over 500K in \texttt{LCSH}), we found that broken links are a common issue in most vocabularies.
 % Undefined SKOS Resources

### 2012-03-30 background.tex
minor changes in abstract, intro, and background

@@
 
-The SKOS specification doesn't mention the notion of quality, but defines in total six \textbf{integrity conditions}~\cite{SkosReference2008}, each of which is a statement that defines under which circumstances data are consistent with the SKOS data model.
+The SKOS specification doesn't mention the notion of quality, but defines in total six integrity conditions~\cite{SkosReference2008}, each of which is a statement that defines under which circumstances data are consistent with the SKOS data model.
 For example, ``a resource has no more than one value of \texttt{skos:prefLabel} per language tag''.
 Tools that can check whether these conditions are met are already available: two of the six conditions are defined formally in the OWL representation of SKOS and can therefore be validated by any OWL reasoner.
-For validating a SKOS vocabulary against the other integrity conditions, one can use tools such as the \textbf{PoolParty Thesaurus Consistency Checker}\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}}, or the \textbf{Skosify}\footnote{\url{http://code.google.com/p/skosify/}} validator, which can also correct some detected quality problems.
+For validating a SKOS vocabulary against the other integrity conditions, one can use tools such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}}, or the Skosify\footnote{\url{http://code.google.com/p/skosify/}} validator, which can also correct some detected quality problems.
 

### 2012-03-30 introduction.tex
fixed stuff in section 3; added TODOs for CM
minor changes in abstract, intro, and background

@@
 
-The SKOS specification defines a set of \textbf{integrity conditions} that state whether given data patterns are consistent with the SKOS model.
+The SKOS specification defines a set of integrity conditions that state whether given data patterns are consistent with the SKOS model.
 Yet the SKOS integrity conditions fail to capture quality aspects like the ones above.
@@
 On the other hand, each vocabulary should fulfill domain- and application-specific quality aspects and taxonomists often follow standard guidelines specific to given types of vocabularies (cf.,~\cite{ISO25964-1:2011,Z39.19:2005}) for thesauri) or apply their own hand-crafted checks~\cite{Coronado2009}.
-Existing guidelines consider these aspects, but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger vocabularies.
+Existing guidelines consider these aspects, but currently rely on human judgement, which is subjective and does not scale for larger vocabularies.
 The SKOS context, where vocabularies can be linked together on the Web, also brings issues hitherto unforeseen by traditional checking approaches.
@@
 
-	\item We identified 15 \textbf{quality issues} for SKOS vocabularies by examining existing guidelines and formalized them into computable \textbf{quality checking functions} that identify possibly affected resources in a vocabulary.
+	\item We identified 15 quality issues for SKOS vocabularies by examining existing guidelines and formalized them into computable quality checking functions that identify possibly affected resources in a vocabulary.
 
-	\item With the \textbf{qSKOS quality assessment tool} we provide a reference implementation of these functions.
+	\item With the qSKOS quality assessment tool we provide a reference implementation of these functions.
 
-	\item We \textbf{tested} these functions by \textbf{analyzing} a representative set of \textbf{15 existing SKOS vocabularies} to learn about possible quality issues.
+	\item We tested these functions by analyzing a representative set of 15 existing SKOS vocabularies to learn about possible quality issues.
 
@@
 
-In the following, we will first discuss what \emph{quality} means in the context of SKOS vocabularies and how it is currently support by the SKOS specification and existing tools.
+In the following, we will first discuss what ``quality'' means in the context of SKOS vocabularies and how it is currently supported by the SKOS specification and existing tools.
 Then we introduce the quality issues we have identified and describe how we implemented them in the qSKOS quality assessment tool.
-Finally, we report on the results of an analysis we performed on 15 existing SKOS vocabularies and which shows that the quality issues we discussed are real and can lead to the improvement of existing vocabularies.
+Finally, we report on the results of an analysis we performed on 15 existing SKOS vocabularies and show that the quality issues we discussed are real and can lead to the improvement of existing vocabularies.
+All supplemental materials are available at \url{https://github.com/cmader/qSKOS/} (qSKOS tool, wiki pages) and \url{https://github.com/cmader/qSKOS-data/} (vocabulary dataset).

### 2012-03-30 main.tex
minor changes
polished intro
minor changes in abstract, intro, and background

@@
 \title{Finding Quality Issues in SKOS Vocabularies}
-\subtitle{\todo{ALL}{I am still not happy with the title; better ideas?}}
 \author{Christian Mader\inst{1} \and Bernhard Haslhofer\inst{2} \and Antoine Isaac\inst{3}}
@@
 Here we investigate how we can support taxonomists in improving SKOS vocabularies by pointing out quality issues that go beyond the integrity constraints defined in the SKOS specification.
-We identified potential \textbf{quality issues} and formalized them into computable \textbf{quality checking functions} that can find affected resources in a given SKOS vocabulary.
+We identified potential quality issues and formalized them into computable quality checking functions that can find affected resources in a given SKOS vocabulary.
 We implemented these functions in the qSKOS quality assessment tool, analyzed 15 existing vocabularies, and found possible quality issues in all of them.

### 2012-03-30 criteria.tex
polished section 3

@@
 We published our findings in the qSKOS Wiki and requested feedback from experts via public mailing lists and informal face to face discussions.
-Based on the received responses, we then selected a subset of these issues and translated them into computable \textbf{quality checking functions}.
+Based on the received responses, we then selected a subset of these issues and translated them into computable quality checking functions.
 Each function takes a given SKOS vocabulary as input and finds all vocabulary resources that match the corresponding quality issue.
@@
 \end{mydef}
-
-\todo{CM}{are you sure about IEXT and ICEXT; isn't I enough?
-yes; in fact IR definition is taken from Hitzler, so I think we can define, e.g., CS in the same way; btw, shouldn't we cite Hitzler or at least the RDF semantics document?}
-
-%A checking function is applied on a given SKOS vocabulary and finds all vocabulary resources that match the corresponding quality issue.
-We can map each issue to an abstract function $f:V \rightarrow \mathcal{P}(IR)$ that relates a given SKOS vocabulary to a subset of its resources.
-Each quality issue we found can be implemented as a realization of that abstract function and possibly take additional parameters.
-Statistical analysis can be computed on top of the result set.
 
@@
 % Function defintion
-A SKOS vocabulary can be checked for omitted and invalid language tags by iterating over all resources in $IR$ and finding those that have relations to plain literals (using the above mentioned SKOS properties) with missing or invalid language tags, i.e., tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
+A SKOS vocabulary can be checked for omitted and invalid language tags by iterating over all resources in $IR$ and finding those that have labeling or documentation property relations to plain literals in $LV$ with missing or invalid language tags, i.e., tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
 
@@
 % Origin and rationale
-%Soergel et al.~\cite{Soergel1997} point out the problem that ``...a concept lexicalized in one language may not be lexicalized in another and that the terms do exist often vary slightly in meaning...''.
-Thus, finding concepts with incomplete language coverage can help taxonomists in revising the vocabulary and ``clearly instruct indexers in all languages how the term is to be used''.
-
-In the context of SKOS, incomplete language coverage means that the set of language tags used by the literal values linked with a concept should be the same for all concepts.
+The set of language tags used by the literal values linked with a concept should be the same for all concepts.
 If this is not the case, appropriate actions like, e.g., splitting concepts or introducing scope notes should be taken by the creators.
@@
 % Function defintion
-Affected concepts can be identified by first extracting the global set of language tags used in a vocabulary from all literal values attached to all concepts in $C$.
-In a second iteration over all concepts, all concepts having a set of language tags that is not equal to the global language set are returned.
+Affected concepts can be identified by first extracting the global set of language tags used in a vocabulary from all literal values in $LV$, which are attached to a concept in $C$.
+In a second iteration over all concepts, those having a set of language tags that is not equal to the global language tag set are returned.
 
@@
 Many constraints in~\cite{SkosReference2008,Isaac2009} are related to concept schemes, but (i) data on concept scheme membership may lack and (ii) concept scheme related constraints would be handled better with the Closed World Assumption (CWA), e.g., finding identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} of different concepts.
-Although being good practice for many thesauri this issue could cause problems in application scenarios such as auto-completion, which proposes labels based on the user input.
-%The SKOS Primer~\cite{Isaac2009} recommends that ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
-We reviewed existing vocabularies and applications and found that (i) many vocabularies don't use concept schemes and (ii) identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} can also negatively affect use cases such as auto-completion, which proposes labels based on the user input.
+Although being good practice for many thesauri this issue could affect application scenarios such as auto-completion, which proposes labels based on the user input.
 % Function defintion
@@
 The default, built-in similarity function checks for case-insensitive string equality with a threshold equal to 1.
-To find label conflicts, we provide a function that iterates over all concept pairs $C \times C$, applies $sim$ to every possible label combination, and collects those pairs with at least one label combination that meets or exceeds a specified similarity threshold.
+Label conflicts can be found by iterating over all concept pairs $C \times C$, applying $sim$ to every possible label combination, and collecting those pairs with at least one label combination meeting or exceeding a specified similarity threshold.
 
@@
 % Origin and rationale
-This issue is motivated by the notion of ``orphan terms'' in the literature~\cite{Hedden2010}, i.e., terms without any associative or hierarchical relationships.
-Checking for such terms is common in existing thesaurus development applications and also suggested by~\cite{Z39.19:2005}.
+are motivated by the notion of ``orphan terms'' in the literature~\cite{Hedden2010}, i.e., terms without any associative or hierarchical relationships.
+Checking for such terms is common in thesaurus development and also suggested by~\cite{Z39.19:2005}.
 Since SKOS is concept-centric, we understand an orphan concept as being a concept that has no semantic relation $sr \in SR$ with any other concept.
@@
 % Function defintion
-Orphan concepts in a SKOS vocabulary can be found by iterating over all elements in $C$ and selecting those without any semantic relation to another conceptual resource in $C$.
+Orphan concepts in a SKOS vocabulary can be found by iterating over all elements in $C$ and selecting those without any semantic relation to another concept in $C$.
 
@@
 % Origin and rationale
-A vocabulary can be split into separate ``clusters'', which can be caused by incomplete data acquisition, deprecated or outdated terms, accidental deletion of relations, etc.
+A vocabulary can be split into separate ``clusters'' because of incomplete data acquisition, deprecated terms, accidental deletion of relations, etc.
 This can affect operations that rely on navigating a connected vocabulary structure, such as query expansion or suggestion of related terms.
@@
 % Function defintion
-Cyclic relations can be found by constructing a graph with the set of nodes being $C$ and the set of edges being all \texttt{skos:broader} relations between these concepts.
+Cyclic relations can be found by constructing a graph with the set of nodes being $C$ and the set of edges being all \texttt{skos:broader} relations.
 
@@
 % Function defintion
-This issue can be checked by identifying the set of pairs of conceptual resources that share the same broader or narrower concept while also being associatively related by the property \texttt{skos:related}.
+This issue can be checked by identifying concept pairs $C \times C$ that share the same broader or narrower concept while also being associatively related by the property \texttt{skos:related}.
 
@@
 % Function definition
-This issue can be detected by iterating over all concept pairs $C \times C$ that are directly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} properties but none of their subproperties.
+This issue can be detected by finding all concept pairs $C \times C$ that are directly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} properties but none of their subproperties.
 
@@
 % Origin and rationale
-SKOS concepts become linkable resources, when vocabularies are being published on the Web.
-Estimating the number of in-links and identifying the concepts without any in-links, can be an important indicator for the importance of a concept.
+When vocabularies are being published on the Web, SKOS concepts become linkable resources.
+Estimating the number of in-links and identifying the concepts without any in-links, can indicate the importance of a concept.
 % Function definition
@@
 For example, \texttt{PXV} links the concept \url{http://www.peroxisomekb.nl/v1.6/pxv/C000297} to \url{http://www.bioexpert.nl/mesh/2010/concept/M0028264} using \texttt{skos:closeMatch}.
-Both resources can be infered as being \texttt{skos:Concept}s, but the latter is no authoritative concept because it's URI doesn't belong to the \texttt{PXV} namespace.
-The number of in-links referencing an authoritative concept can be estimated by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/} indexes structured Web data and covers approximately 230M documents with over 11 billion triples} SPARQL endpoint for triples containing the concept's URI in the object part.
-Empty query results are indicators for missing in-links and are thus included in the result set of this function.
+Both resources can be inferred as being \texttt{skos:Concept}s, but the latter is no authoritative concept because it's URI doesn't belong to the \texttt{PXV} namespace.
+We estimate the number of in-links by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/} indexes structured Web data and covers approximately 230M documents with over 11 billion triples} SPARQL endpoint for triples containing the concept's URI in the object part.
+Empty query results are indicators for missing in-links.
 
@@
 % Origin and rationale
-In the Linked Data context, SKOS concepts should be linked with other related concepts on the Web, ``enabling seamless connections between data sets''\cite{Heath2011}.
+In the Linked Data context, SKOS concepts should also be linked with other related concepts on the Web, ``enabling seamless connections between data sets''\cite{Heath2011}.
 Similar to \emph{Missing In-Links}, this issue identifies the set of all authoritative concepts that have no out-links.
 % Function definition
-It can be computed by iterating over all elements $ac \in AC$ and checking the URIs of all related resources.
-If none of these URI's namespace differs from the namespace of $ac$'s URI, $ac$ has no out-links and is thus included in the resources identified by this issue.
+It can be computed by iterating over all elements in $AC$ and returning those that are not linked with any non-authoritative resource.
 

### 2012-03-30 analysis.tex
added mil for LCSH
polished section 4

@@
 
-Our vocabulary selection is shown in Table~\ref{tab:vocabs}, which also summarizes basic statistical properties relevant for interpreting our results: the number of concepts, ``authoritative concepts'', as explained in Section~\ref{subsec:ld_issues}, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations (\texttt{Labels}), all asserted semantic relations $SR$, as well as the number of concept schemes.
+Our vocabulary selection is shown in Table~\ref{tab:vocabs}, which also summarizes basic statistical properties relevant for interpreting our results: the number of concepts, ``authoritative concepts'', as explained in Section~\ref{subsec:ld_issues}, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations (\texttt{Labels}), all asserted semantic relations, as well as the number of concept schemes.
 
@@
 
-\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{\parbox{3cm}{Version/\\Last Modified}}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth.
-Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} \\
+\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{\parbox{3cm}{Version/\\Last Modified}}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{\parbox{3.5cm}{Authoritative\\Concepts}}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{\parbox{3cm}{Semantic\\Relations}}} & \rotatebox{90}{\textbf{\parbox{3cm}{Concept\\Schemes}}} \\
 \toprule
@@
 \hline
-The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6,797 & 6,797 & 457,788 & 18,491 & 128 \\
+The EU's Multilingual Thesaurus & \textbf{Eurovoc} & 5.0 & 6,797 & 6,797 & 457,788 & 18,491 & 128 \\
 \hline
@@
 \hline
-Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 & 422 & 569 & 1,698 & 2 \\
+Middle Kingdom Tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 & 422 & 569 & 1,698 & 2 \\
 \hline
@@
 
-The results of this analysis are summarized in Table~\ref{tab:results}, which shows the absolute number of affected resources for each quality checking function and vocabulary combination.
+The results of this analysis are summarized in Table~\ref{tab:results}, which shows the absolute number of possibly affected resources for each quality checking function and vocabulary combination.
 The value 0 means that we haven't found any affected resource, n/a means that a certain function was not applicable for reasons we explain below.
@@
 
-Missing In-Links & 32,035 & 733,800 & 6,796 & 19 & 171,980* & 3,080 & ?* & 13,411 & 422 & 24,625 & 2,213 & 20 & 1,125 & 1,686 & 6,516 \\
+Missing In-Links & 32,035 & 733,800 & 6,796 & 19 & 171,980* & 3,080 & 408,000* & 13,411 & 422 & 24,625 & 2,213 & 20 & 1,125 & 1,686 & 6,516 \\
 
@@
 % Omitted or Invalid Language Tags
-The \texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} vocabularies omit language tags with their \texttt{skos:prefLabel}, \texttt{skos:altLabel}, or \texttt{skos:hiddenLabel} properties, \texttt{LCSH} with the \texttt{skos:note} property.
+The \texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} vocabularies omit language tags with their labeling properties, \texttt{LCSH} with the \texttt{skos:note} property.
 The STW thesaurus doesn't use language tags with 2 \texttt{skos:definition} property instances.
@@
 % Label Conflicts
-We also detected possible label conflicts in half of the vocabularies.
+We also detected possible label issues in half of the vocabularies.
 \texttt{PXV}, for instance, uses the string ``primary peroxisomal enzyme deficiency'' with two concepts in the same concept scheme, but once with a \texttt{skos:prefLabel} and another time with a \texttt{skos:altLabel} property.
-A similar example from AGROVOC is ``sziv\'{a}rv\'{a}nyos pisztr\'{a}ng'', which is used as \texttt{skos:altLabel} with two different concepts.
+An example from AGROVOC is ``sziv\'{a}rv\'{a}nyos pisztr\'{a}ng'', which is used as \texttt{skos:altLabel} with two different concepts.
 % Other stuff
@@
 % STRUCTURAL ISSUES
-When analyzing the structure of existing vocabularies, we found that the results of certain quality checks can be seen as indicators for the types of vocabularies.
+When analyzing the vocabularies for structural issues, we found that certain results can be seen as indicators for the types of vocabularies.
 % Orphan Concepts
 In the \texttt{Pressinfo} and \texttt{NYTP} vocabulary, all concepts are orphan concepts, which means that these vocabularies are authority files rather than thesauri or taxonomies.
-\texttt{GTAA} seems is a mixture of name authority file (162K concepts) and thesaurus (10K concepts).
+\texttt{GTAA} is a mixture of name authority file ( approx.~162K concepts) and thesaurus (approx.~10K concepts).
 The 4 orphan concepts in \texttt{STW} are deprecated concepts.
@@
 % Weakly Connected Components
-Consisting of one weakly connected component (``giant component''), three vocabularies represent what is often considered as the ideal vocabulary structure.
-All other vocabularies split into several clusters of semantically related concepts that represent several subtopics in the vocabularies.
-\texttt{Eurovoc} contains of 4 weakly connected components, containing 4, 5, 6 and 6775 concepts.
+Three vocabularies (\texttt{IPSW}, \texttt{NAICS}, \texttt{STW}) consist of only one ``giant component'', which is often considered as being the ideal vocabulary structure.
+All other vocabularies split into several clusters of semantically related concepts, each of which represents a certain subtopic in the vocabularies.
+\texttt{Eurovoc}, for instance, contains of 4 weakly connected components, containing 4, 5, 6 and 6775 concepts.
 The three smallest components contain concepts thematically related to ``Africa'', ``educational institutions'' and ``forecasts''.
-Weakly connected components divide the \texttt{Meketre} vocabularies into, e.g., execution-style related concepts, concepts reserved for internal use or museums.
-\texttt{GTAA} consists of 621 weakly connected components with the largest one supposed to be a subject thesaurus containing 8413 concepts.
-Most  other components contain less than 10 concepts, representing, e.g., locations, person names, maker names and genres.
-\texttt{PXV} splits into 10 weakly connecting components, topically relating e.g., ``deficiancies'', ``defects'' or ``signals''.
+Weakly connected components divide the \texttt{Meketre} vocabularies into, e.g., topics, and concepts reserved for internal use or museums.
+\texttt{GTAA} consists of 621 weakly connected components with the largest one being a subject thesaurus containing 8413 concepts.
+Most of the other components contain less than 10 concepts, representing, e.g., locations, person names, and genres.
+\texttt{PXV} splits into 10 topic-related weakly connected components, such as ``deficiancies'', ``defects'' or ``signals''.
+
 % Cyclic Hierarchical Relations
-Hierarchical cycles are not a common issue except in collaboratively created DBpedia vocabulary, where many concepts have reflexive \texttt{skos:broader} relations.
+Hierarchical cycles are not a common issue except in the collaboratively created DBpedia vocabulary, where many concepts have reflexive \texttt{skos:broader} relations.
 % Valuless Associative Relations
@@
 Solely transitive related concepts occur in 3 vocabularies, establishing relations using properties that, according to the SKOS reference documentation, should not be asserted directly.
-This indicates a possible misunderstanding of the SKOS specification and, when the vocabulary is queried without RDFS inferencing, could result in a loss in recall on hierarchical queries.
+This indicates a possible misinterpretation of the SKOS specification and could result in a loss in recall on hierarchical queries when the vocabulary is queried without RDFS inferencing.
 % Omitted Top Concepts
-\texttt{GTAA} and \texttt{Geonames} have no top concept defined for any of the concept schemes they use.
+\texttt{GTAA} and \texttt{Geonames} omit top concepts in all concept schemes they define.
 \texttt{Eurovoc} uses 128 concept schemes but has one without top concept, which simply contains all concepts defined in the vocabulary.
-Such an ``umbrella concept scheme'' without is also present in \texttt{LCSH} and \texttt{NYTP}.
+Such an ``umbrella concept scheme'' without top concept is also present in \texttt{LCSH} and \texttt{NYTP}.
 % Top Concepts Having Broader Concepts
-Only \texttt{PXV} vocabulary is affected by top concepts having broader concepts in its current version.
+Only the \texttt{PXV} vocabulary is affected by top concepts having broader concepts in its current version.
 The reason for this is, according to the vocabulary creator, that the broader concept was abandoned but is still available in the triplestore, maybe because of some bug in the vocabulary management software.
@@
 
-The difference between Concepts and Authoritative Concepts in Table~\ref{tab:vocabs} already indicates which vocabularies are linked with SKOS vocabularies.
+The difference between the number of concepts and the number of authoritative concepts in Table~\ref{tab:vocabs} already indicates which vocabularies are linked with other SKOS vocabularies.
 % Missing In-Links
@@
 Most vocabularies also don't provide links to other vocabularies on the Web.
-The \texttt{NYTP}, \texttt{IPSV} vocabularies are two exceptions, which are fully linked to other Web resources.
-The one concept with missing links in \texttt{NAICS} is only used as object in \texttt{skos:broaderTransitive} assertions.
+The \texttt{NYTP}, \texttt{IPSV} vocabularies are the two exceptions, which are fully linked to other Web resources.
+The one concept with missing out-links in \texttt{NAICS} is the object of a \texttt{skos:broaderTransitive} relation.
 % Broken Links

### 2012-03-30 conclusions.tex
read and fixed 1-3
minor modifications in conclusion

@@
 
-In this paper we identified possible quality issues in SKOS vocabularies and implemented them as quality checking functions in our qSKOS quality assessment tool.
+In this paper we presented possible quality issues in SKOS vocabularies and described how we implemented them as quality checking functions in our qSKOS quality assessment tool.
 We analyzed a representative set of existing SKOS vocabularies and found  issues in all of them.
@@
 Although SKOS is designed for Linked Data, many existing vocabularies still resemble their closed-system origin, which results in a relatively low number of in- and out-links.
-Broken links is a major issue and calls for synchronization mechanisms in order to maintain navigability between concepts.
+Broken links is a major issue and calls for synchronization mechanisms in order to maintain navigability between concepts in different vocabularies.
 
-During our work on qSKOS and while writing this paper we were in contact with some of the creators of the vocabularies we analyzed and also reported back initial results from our analysis.
-At the time of this writing, we know that our findings lead to improvements in at least two SKOS vocabularies.
+During our work on qSKOS and while writing this paper we reported initial results from our analysis to some of the maintainers of the vocabularies we analyzed.
+At the time of this writing, we know that our findings led to improvements in at least two SKOS vocabularies.
 
@@
 We will also further collect community feedback, enhance the issues list, and set up a Web-based SKOS quality checking service.
-For larger vocabularies we will also increase the performance and efficiency of our quality checking algorithms.
-
-% \section{Acknowledgements}
-
-% Tom Dent (esd support team) for providing a dump for the IPSV vocabulary
-% Andrew Gibson for providing a dump for the Peroxisome knowledge Base and giving valuable feedback on their vocabulary structure.
+For larger vocabularies we also need to increase the performance and efficiency of our quality checking algorithms.

### 2012-03-30 analysis.tex
editorial changes

@@
 % Incomplete Language Coverage
-\texttt{AGROVOC} covers 25 languages in total but no single concept is labelled in all languages, in \texttt{Meketre} all concepts have English but only some of them French labels assigned.
+\texttt{AGROVOC} covers 25 languages in total but no single concept is labeled in all languages, in \texttt{Meketre} all concepts have English but only some of them French labels assigned.
 The reason for the high number of concepts with incomplete language coverage in \texttt{STW} is that a few concepts have labels with the private, but valid language tag \texttt{x-other}.

### 2012-03-30 background.tex
editorial changes

@@
 
-The SKOS specification doesn't mention the notion of quality, but defines in total six integrity conditions~\cite{SkosReference2008}, each of which is a statement that defines under which circumstances data are consistent with the SKOS data model.
+The SKOS specification does not mention the notion of quality, but defines in total six integrity conditions~\cite{SkosReference2008}, each of which is a statement that defines under which circumstances data are consistent with the SKOS data model.
 For example, ``a resource has no more than one value of \texttt{skos:prefLabel} per language tag''.
@@
 One issue when assessing the quality of SKOS data is the so-called ``Open World Assumption'', which underlies the Web of Data itself.
-Established quality notions from closed-world systems, such as referential integrity or schema validation, don't hold anymore, because available information may be incomplete and non-explicitly stated facts cannot be determined as true or false.
+Established quality notions from closed-world systems, such as referential integrity or schema validation, do not hold anymore, because available information may be incomplete and non-explicitly stated facts cannot be determined as true or false.
 \todo{AI}{Add ref to DCAM and Pellet, if we have 3 lines available for that.} Work-arounds, often ad-hoc, are thus currently used to evaluate quality in Linked Data sets~\cite{Heath2011}, as is done in the (rule-based) SKOS tools mentioned above.

### 2012-03-30 conclusions.tex
editorial changes

@@
 We are aware that the quality issues we described in this work are purely quantitative indicators that, on their own, cannot be generalized into statements about the quality of a vocabulary.
-To learn more about the real-world impact of our work, we would like to conduct a qualitative follow-up study, in which we confront taxonomists with our results.
+To learn more about the real-world impact of our work, we would like to conduct a qualitative follow-up study, in which we confront more taxonomists with our results.
 We will also further collect community feedback, enhance the issues list, and set up a Web-based SKOS quality checking service.

### 2012-03-30 criteria.tex
editorial changes

@@
 Based on the received responses, we then selected a subset of these issues and translated them into computable quality checking functions.
-Each function takes a given SKOS vocabulary as input and finds all vocabulary resources that match the corresponding quality issue.
+Each function takes a given SKOS vocabulary as input and finds all resources that match the corresponding quality criterion.
 For the purpose of this work, we define a SKOS vocabulary as follows:
@@
 Further, we let $V$ be the fully entailed RDFS interpretation of the underlying RDF graph.
-We enrich $V$ by entailment of \texttt{owl:inverseOf} properties as well as instances of \texttt{owl:TransitiveProperty} and \texttt{owl:SymmetricProperty} defined by the formal OWL semantics of SKOS.
+We enrich $V$ by entailment of \texttt{owl:inverseOf} properties as well as instances of \texttt{owl:TransitiveProperty} and \texttt{owl:SymmetricProperty} defined by the formal OWL semantics of SKOS~\cite{SkosReference2008}.
 \end{mydef}
@@
 Weakly connected components are identified by first creating an undirected graph that includes all non-orphan concepts (as defined above) as nodes and all semantic relations $SR$ as edges.
-``Tarjan’s algorithm''~\cite{Hopcroft1973} can then be applied to find all connected components, hence all sets of concepts that are connected by semantic relations.
+``Tarjan's algorithm''~\cite{Hopcroft1973} can then be applied to find all connected components, i.e., all sets of concepts that are connected together by (chains of) semantic relations.
 
@@
 % Function definition
-This issue can be detected by finding all concept pairs $C \times C$ that are directly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} properties but none of their subproperties.
+This issue can be detected by finding all concept pairs $C \times C$ that are directly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} properties but not by (a chain of) their \texttt{skos:broader} and \texttt{skos:narrower} subproperties.
 
@@
 % Function definition
-Affected resources can be found by iterating over all top concepts and collecting those that are related to a resource via a \texttt{skos:broader} property that is no \texttt{skos:mappingRelation}.
+Affected resources are found by collecting all top concepts that are related to a resource via a \texttt{skos:broader} property and not via \texttt{skos:broadMatch}---mappings are not part of a vocabulary's ``intrinsic'' definition and a top concept in one vocabulary may perfectly have a broader concept in another vocabulary.
 
@@
 To estimate the number of in-links we only consider the set of ``authoritative concepts'' $AC \subseteq C$, which consists of all concepts that are identified by URIs in the vocabulary namespace.
-For example, \texttt{PXV} links the concept \url{http://www.peroxisomekb.nl/v1.6/pxv/C000297} to \url{http://www.bioexpert.nl/mesh/2010/concept/M0028264} using \texttt{skos:closeMatch}.
-Both resources can be inferred as being \texttt{skos:Concept}s, but the latter is no authoritative concept because it's URI doesn't belong to the \texttt{PXV} namespace.
+For example, \texttt{PXV} links \url{http://www.peroxisomekb.nl/v1.6/pxv/C000297} to \url{http://www.bioexpert.nl/mesh/2010/concept/M0028264} using \texttt{skos:closeMatch}.
+Both are \texttt{skos:Concept}s, but the latter is no authoritative concept because its URI does not belong to the \texttt{PXV} namespace.
 We estimate the number of in-links by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/} indexes structured Web data and covers approximately 230M documents with over 11 billion triples} SPARQL endpoint for triples containing the concept's URI in the object part.
@@
 The SKOS model is defined within the namespace \url{http://www.w3.org/2004/02/skos/core#}.
-However, some vocabularies use resources from within this namespace, which are unresolvable for two main reasons: vocabulary creators ``invented'' new terms within the SKOS namespace instead of introducing them in a separate namespace, or they use ``deprecated'' SKOS properties like, e.g., \texttt{skos:subject}.
+However, some vocabularies use resources from within this namespace, which are unresolvable for two main reasons: vocabulary creators ``invented'' new terms within the SKOS namespace instead of introducing them in a separate namespace, or they use ``deprecated'' SKOS element like \texttt{skos:subject}.
 % Function definition
-Undefined SKOS resources can be identified by iterating over all resources in $IR$ and returning those resources (i) that are contained in the list of deprecated resources or (ii) are identified by a URI in the SKOS namespace but are not defined in the current version of the SKOS ontology.
+Undefined SKOS resources can be identified by iterating over all resources in $IR$ and returning those resources (i) that are contained in the list of deprecated resources\footnote{See \url{http://www.w3.org/TR/skos-reference/#namespace}} or (ii) are identified by a URI in the SKOS namespace but are not defined in the current version of the SKOS ontology.

### 2012-03-30 background.tex
handled TODOs in sec 2

@@
 Established quality notions from closed-world systems, such as referential integrity or schema validation, do not hold anymore, because available information may be incomplete and non-explicitly stated facts cannot be determined as true or false.
-\todo{AI}{Add ref to DCAM and Pellet, if we have 3 lines available for that.} Work-arounds, often ad-hoc, are thus currently used to evaluate quality in Linked Data sets~\cite{Heath2011}, as is done in the (rule-based) SKOS tools mentioned above.
+Work-arounds, often ad-hoc, are thus currently used to evaluate quality in Linked Data sets~\cite{Heath2011}, as is done in the (rule-based) SKOS tools mentioned above, or the Pellet ICV, which re-interprets OWL axioms with integrity constraint semantics\footnote{\url{http://clarkparsia.com/pellet/icv/}}.
 
@@
 Quality aspects of controlled vocabularies have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, tutorials~\cite{Soergel2002}, and scholarly articles \cite{Coronado2009,Soergel1997,Elkin2002,Kless2010}.
+These most often rely on manual, precise analysis of individual statements in the data, as in~\cite{spero2008}.
 Our work builds on this literature, but focuses on the less intellectually loaded checks, which can be automatized to assist vocabulary users or publishers.
-\todo{AI}{In fact Spero's example can be put here}
 

### 2012-03-30 analysis.tex
added explanations to mil and mol issues

@@
 
-Valueless Associative Relations & 282 & 8,120 & 1 & 0 & 9,438 & 239 & 0 & 5 & 0 & 495 & 0 & 0 & 0 & 0 & 5,082 \\
+Valueless Associative Relations & 282 & 8,839 & 6 & 0 & 9,448 & 253 & 0 & 5 & 0 & 550 & 0 & 0 & 0 & 0 & 5,139 \\
 
@@
 
-Broken Links & 238 & 0* & 0* & 0 & 0 & 1 &?& n/a & 425 & 1 & 3,169 & 7 & 11 & 163 & 1 \\
+Broken Links & 238 & 0* & 0* & 0 & 0 & 1 & 148800 & n/a & 425 & 1 & 3,169 & 7 & 11 & 163 & 1 \\
 
@@
 The \texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} vocabularies omit language tags with their labeling properties, \texttt{LCSH} with the \texttt{skos:note} property.
-The STW thesaurus doesn't use language tags with 2 \texttt{skos:definition} property instances.
+The \texttt{STW} thesaurus doesn't use language tags with 2 \texttt{skos:definition} property instances.
 % Incomplete Language Coverage
@@
 % Undocumented Concepts
-\texttt{Geonames}, which is an ontology including a concept scheme of ``feature codes'', is the only vocabulary in our dataset, which has at least one documentation property assigned to all of its concept.
+\texttt{Geonames}, which is an ontology including a concept scheme of ``feature codes'', is the only vocabulary in our dataset, which has at least one documentation property assigned to all of its concepts.
 All other vocabularies have a significant number of undocumented concepts.
@@
 % Valuless Associative Relations
-Valueless associative relations occur in 9 vocabularies, with their total number being relatively low compared to the total number of all semantic relations in the respective vocabularies.
+Valueless associative relations occur in 8 vocabularies, with their total number being relatively low compared to the total number of all semantic relations in the respective vocabularies.
 % Solely Transitive Related Concepts
@@
 However, except \texttt{NYTP} and \texttt{Geonames}, none of the analyzed vocabularies has a significant number of in-links from other web resources.
+Estimation of these numbers is rather unaccurate since currently we only rely on the Sindice index.
 % Missing Out-Links
@@
 The one concept with missing out-links in \texttt{NAICS} is the object of a \texttt{skos:broaderTransitive} relation.
+Some vocabularies, e.g., \texttt{STW}, \texttt{AGROVOC} publish mapping information to other vocabularies as separate files, thus the ``main'' vocabulary lacks this data.
+A missing in-link count equal to the number of authoritative concepts indicates that mapping information is either not available at all or has to be obtained separately.
 % Broken Links

### 2012-03-30 background.tex
polished background and issues

@@
 Established quality notions from closed-world systems, such as referential integrity or schema validation, do not hold anymore, because available information may be incomplete and non-explicitly stated facts cannot be determined as true or false.
-Work-arounds, often ad-hoc, are thus currently used to evaluate quality in Linked Data sets~\cite{Heath2011}, as is done in the (rule-based) SKOS tools mentioned above, or the Pellet ICV, which re-interprets OWL axioms with integrity constraint semantics\footnote{\url{http://clarkparsia.com/pellet/icv/}}.
+Work-arounds, often ad-hoc, are thus currently used to evaluate quality in Linked Data sets~\cite{Heath2011}, as is done in the (rule-based) SKOS tools mentioned above, or the Pellet ICV\footnote{\url{http://clarkparsia.com/pellet/icv/}}, which re-interprets OWL axioms with integrity constraint semantics.
 

### 2012-03-30 criteria.tex
polished background and issues

@@
 % Origin and rationale
-Many constraints in~\cite{SkosReference2008,Isaac2009} are related to concept schemes, but (i) data on concept scheme membership may lack and (ii) concept scheme related constraints would be handled better with the Closed World Assumption (CWA), e.g., finding identical \texttt{skos:altLabels} or \texttt{skos:hiddenLabels} of different concepts.
-Although being good practice for many thesauri this issue could affect application scenarios such as auto-completion, which proposes labels based on the user input.
+The SKOS Primer~\cite{Isaac2009} recommends that ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
+Although being good practice for many thesauri, this issue could affect application scenarios such as auto-completion, which proposes labels based on user input.
 % Function defintion
-Thus, we generalize this recommendation and search for all concept pairs with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} property values meeting a certain similarity threshold defined by a function $sim:LV \times LV \rightarrow [0,1]$.
+Since data on concept scheme membership may lack because of the Open World Assumption, we handle this issue under the Closed World Assumption, generalize the above recommendation and search for all concept pairs with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} property values meeting a certain similarity threshold defined by a function $sim:LV \times LV \rightarrow [0,1]$.
 The default, built-in similarity function checks for case-insensitive string equality with a threshold equal to 1.
@@
 % Function definition
-Affected resources are found by collecting all top concepts that are related to a resource via a \texttt{skos:broader} property and not via \texttt{skos:broadMatch}---mappings are not part of a vocabulary's ``intrinsic'' definition and a top concept in one vocabulary may perfectly have a broader concept in another vocabulary.
+Affected resources are found by collecting all top concepts that are related to a resource via a \texttt{skos:broader} statement and not via \texttt{skos:broadMatch}---mappings are not part of a vocabulary's ``intrinsic'' definition and a top concept in one vocabulary may perfectly have a broader concept in another vocabulary.
 
@@
 % Function definition
-To estimate the number of in-links we only consider the set of ``authoritative concepts'' $AC \subseteq C$, which consists of all concepts that are identified by URIs in the vocabulary namespace.
+We compute this by considering only the set of ``authoritative concepts'' $AC \subseteq C$, which consists of all concepts that are identified by URIs in the vocabulary namespace.
 For example, \texttt{PXV} links \url{http://www.peroxisomekb.nl/v1.6/pxv/C000297} to \url{http://www.bioexpert.nl/mesh/2010/concept/M0028264} using \texttt{skos:closeMatch}.
 Both are \texttt{skos:Concept}s, but the latter is no authoritative concept because its URI does not belong to the \texttt{PXV} namespace.
-We estimate the number of in-links by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/} indexes structured Web data and covers approximately 230M documents with over 11 billion triples} SPARQL endpoint for triples containing the concept's URI in the object part.
+We estimate the number of in-links by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/} indexes the Web of Data, which is composed of pages with semantic markup in RDF, RDFa, Microformats, or Microdata.
+Currently it covers approximately 230M documents with over 11 billion triples.} SPARQL endpoint for triples containing the concept's URI in the object part.
 Empty query results are indicators for missing in-links.

### 2012-03-30 analysis.tex
polished beginning of section 4

@@
 
-We used our open-source qSKOS quality assessment tool to find possible quality issues in existing SKOS vocabularies.
-From each quality checking function we obtained detailed reports listing possibly affected resources alongside with the potential cause of the issue.
+We used the qSKOS quality assessment tool to find possible quality issues in existing SKOS vocabularies.
+From each quality checking function we obtained detailed reports listing possibly affected resources.
 
@@
 
-Our vocabulary selection is shown in Table~\ref{tab:vocabs}, which also summarizes basic statistical properties relevant for interpreting our results: the number of concepts, ``authoritative concepts'', as explained in Section~\ref{subsec:ld_issues}, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations (\texttt{Labels}), all asserted semantic relations, as well as the number of concept schemes.
+The basic statistical properties of our vocabulary selection are summarized in Table~\ref{tab:vocabs}: the number of concepts, ``authoritative concepts'', as explained in Section~\ref{subsec:ld_issues}, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations (\texttt{Labels}), all asserted semantic relations, as well as the number of concept schemes.
+From these properties we can, for instance, already see that approximately 3,000 \texttt{DBPedia Categories} concepts don't have labels (e.g., \url{Category:South_Korean_social_scientists}), which indicates that the same amount of Wikipedia categories misses natural language descriptions.
 
@@
 \label{tab:vocabs}
-
 \begin{center}
@@
 
-\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{\parbox{3cm}{Version/\\Last Modified}}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{\parbox{3.5cm}{Authoritative\\Concepts}}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{\parbox{3cm}{Semantic\\Relations}}} & \rotatebox{90}{\textbf{\parbox{3cm}{Concept\\Schemes}}} \\
+\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Version/\\Last Modified}}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Authoritative\\Concepts}}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Semantic\\Relations}}} & \rotatebox{90}{\textbf{\parbox{2.53cm}{Concept\\Schemes}}} \\
 \toprule
@@
 \end{tabular}
-
 }

### 2012-03-30 analysis.tex
explained wcc=0

@@
 The results of this analysis are summarized in Table~\ref{tab:results}, which shows the absolute number of possibly affected resources for each quality checking function and vocabulary combination.
-The value 0 means that we haven't found any affected resource, n/a means that a certain function was not applicable for reasons we explain below.
+n/a means that a certain function was not applicable for reasons we explain below.
 Numbers marked with an asterisk (*) were obtained by extrapolating from subsets containing 5\% of the respective vocabulary resources.
@@
 
-Broken Links & 238 & 0* & 0* & 0 & 0 & 1 & 148800 & n/a & 425 & 1 & 3,169 & 7 & 11 & 163 & 1 \\
+Broken Links & 238 & 0* & 0* & 0 & 0 & 1 & 148800 & 0 & 425 & 1 & 3,169 & 7 & 11 & 163 & 1 \\
 
@@
 % Other stuff
-The \texttt{Eurovoc} and \texttt{NAICS} vocabularies use SKOS-XL for its labels, which is currently not supported by qSKOS.
+\todo{CM}{The \texttt{Eurovoc} and \texttt{NAICS} vocabularies use SKOS-XL for its labels, which is currently not supported by qSKOS.
+For computing possible label conflicts for the large number of LCSH labels, we first need to improve our similarity algorithm.}
 
@@
 % Orphan Concepts
-In the \texttt{Pressinfo} and \texttt{NYTP} vocabulary, all concepts are orphan concepts, which means that these vocabularies are authority files rather than thesauri or taxonomies.
-\texttt{GTAA} is a mixture of name authority file ( approx.~162K concepts) and thesaurus (approx.~10K concepts).
+In the \texttt{Pressinfo}, \texttt{Geonames}, and \texttt{NYTP} vocabulary, all concepts are orphan concepts, which means that these vocabularies are authority files rather than thesauri or taxonomies.
+This also implies that these vocabularies have no weakly connected components.
+\texttt{GTAA} is a mixture of name authority file (approx.~162K concepts) and thesaurus (approx.~10K concepts).
 The 4 orphan concepts in \texttt{STW} are deprecated concepts.

### 2012-03-30 analysis.tex
added label numbers for eurovoc
added lc for eurovoc
polished anaylssis

@@
 The results of this analysis are summarized in Table~\ref{tab:results}, which shows the absolute number of possibly affected resources for each quality checking function and vocabulary combination.
-n/a means that a certain function was not applicable for reasons we explain below.
+n/a means that a certain function could not be computed with the current version of qSKOS because of algorithm complexity or missing support of SKOS-XL.
 Numbers marked with an asterisk (*) were obtained by extrapolating from subsets containing 5\% of the respective vocabulary resources.
@@
 \toprule
-Omitted or Invalid Language Tags & 0 & 0 & n/a & 0 & 0 & 0 & 100,316 & 13,411 & 0 & 23,950 & n/a & 0 & 1,224 & 1,578 & 2 \\
+Omitted or Invalid Language Tags & 0 & 0 & 219 & 0 & 0 & 0 & 100,316 & 13,411 & 0 & 23,950 & n/a & 0 & 1,224 & 1,578 & 2 \\
 
-Incomplete Language Coverage & 32,035 & 0 & n/a & 0 & 0 & 0 & 0 & 0 & 420 & 0 & n/a & 0 & 0 & 0 & 6,456 \\
+Incomplete Language Coverage & 32,035 & 0 & 6370 & 0 & 0 & 0 & 0 & 0 & 420 & 0 & n/a & 0 & 0 & 0 & 6,456 \\
 
@@
 
-Label Conflicts & 2,949 & 0 & n/a & 18 & 12,404 & 0 & n/a & 13 & 4 & 0 & n/a & 0 & 0 & 7 & 5 \\
+Label Conflicts & 2,949 & 0 & 48 & 18 & 12,404 & 0 & n/a & 13 & 4 & 0 & n/a & 0 & 0 & 7 & 5 \\
 
@@
 
-Broken Links & 238 & 0* & 0* & 0 & 0 & 1 & 148800 & 0 & 425 & 1 & 3,169 & 7 & 11 & 163 & 1 \\
+Broken Links & 238 & 0* & 0* & 0 & 0 & 1 & 780 & 0 & 425 & 1 & 3,169 & 7 & 11 & 163 & 1 \\
 
@@
 % LABELING AND DOCUMENTATION ISSUES
-We found labeling and documentation issues in all analyzed vocabularies.
+We found labeling and documentation issues in all vocabularies.
 % Omitted or Invalid Language Tags
-The \texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} vocabularies omit language tags with their labeling properties, \texttt{LCSH} with the \texttt{skos:note} property.
-The \texttt{STW} thesaurus doesn't use language tags with 2 \texttt{skos:definition} property instances.
+\texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} omit language tags with their labeling properties, \texttt{LCSH} with the \texttt{skos:note} property.
+\texttt{STW} doesn't use language tags with 2 instances of \texttt{skos:definition}.
 % Incomplete Language Coverage
-\texttt{AGROVOC} covers 25 languages in total but no single concept is labeled in all languages, in \texttt{Meketre} all concepts have English but only some of them French labels assigned.
+\texttt{AGROVOC} covers 25 languages but no single concept is labeled in all languages, in \texttt{Meketre} all concepts have English but only some of them French labels assigned.
 The reason for the high number of concepts with incomplete language coverage in \texttt{STW} is that a few concepts have labels with the private, but valid language tag \texttt{x-other}.
@@
 \texttt{PXV}, for instance, uses the string ``primary peroxisomal enzyme deficiency'' with two concepts in the same concept scheme, but once with a \texttt{skos:prefLabel} and another time with a \texttt{skos:altLabel} property.
-An example from AGROVOC is ``sziv\'{a}rv\'{a}nyos pisztr\'{a}ng'', which is used as \texttt{skos:altLabel} with two different concepts.
-% Other stuff
-\todo{CM}{The \texttt{Eurovoc} and \texttt{NAICS} vocabularies use SKOS-XL for its labels, which is currently not supported by qSKOS.
-For computing possible label conflicts for the large number of LCSH labels, we first need to improve our similarity algorithm.}
+%An example from AGROVOC is ``sziv\'{a}rv\'{a}nyos pisztr\'{a}ng'', which is used as \texttt{skos:altLabel} with two different concepts.
 
@@
 \texttt{PXV} splits into 10 topic-related weakly connected components, such as ``deficiancies'', ``defects'' or ``signals''.
+The \texttt{LVAk} thesaurus contains 11 concept clusters, which are obviously forgotten test data.
 
@@
 However, except \texttt{NYTP} and \texttt{Geonames}, none of the analyzed vocabularies has a significant number of in-links from other web resources.
-Estimation of these numbers is rather unaccurate since currently we only rely on the Sindice index.
+Estimation of these numbers is rather inaccurate since currently we only rely on the Sindice index.
 % Missing Out-Links
@@
 The one concept with missing out-links in \texttt{NAICS} is the object of a \texttt{skos:broaderTransitive} relation.
-Some vocabularies, e.g., \texttt{STW}, \texttt{AGROVOC} publish mapping information to other vocabularies as separate files, thus the ``main'' vocabulary lacks this data.
-A missing in-link count equal to the number of authoritative concepts indicates that mapping information is either not available at all or has to be obtained separately.
+One reason for a high number of missing out-links could also be that the links were not available in the main thesaurus file.
+We know that this is the case for \texttt{STW} and \texttt{AGROVOC} need to further investigate this.
 % Broken Links

### 2012-03-30 conclusions.tex
polished conclusion

--- 2012-03-30 conclusions.tex
@@
 
+We are aware that these issues are purely quantitative indicators and not statements about the quality of a vocabulary.
+To learn more about the real-world impact of our work, we will conduct a qualitative follow-up study, in which we discuss these results with more taxonomists.
+We will also further collect community feedback, enhance the issues list, and set up a Web-based SKOS quality checking service.
+We also need to increase the performance and efficiency of our quality checking algorithms.
+
 During our work on qSKOS and while writing this paper we reported initial results from our analysis to some of the maintainers of the vocabularies we analyzed.
 At the time of this writing, we know that our findings led to improvements in at least two SKOS vocabularies.
-
-We are aware that the quality issues we described in this work are purely quantitative indicators that, on their own, cannot be generalized into statements about the quality of a vocabulary.
-To learn more about the real-world impact of our work, we would like to conduct a qualitative follow-up study, in which we confront taxonomists with our results.
-We will also further collect community feedback, enhance the issues list, and set up a Web-based SKOS quality checking service.
-For larger vocabularies we also need to increase the performance and efficiency of our quality checking algorithms.

### 2012-03-30 criteria.tex
fixed label conflict description in section 3

@@
 The SKOS Primer~\cite{Isaac2009} recommends that ``no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme''.
-Although being good practice for many thesauri, this issue could affect application scenarios such as auto-completion, which proposes labels based on user input.
+This issue could affect application scenarios such as auto-completion, which proposes labels based on user input.
+Although these extra cases are acceptable for some thesauri, we generalize the above recommendation and search for all concept pairs with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} property values meeting a certain similarity threshold defined by a function $sim:LV \times LV \rightarrow [0,1]$.
 % Function defintion
-Since data on concept scheme membership may lack because of the Open World Assumption, we handle this issue under the Closed World Assumption, generalize the above recommendation and search for all concept pairs with their respective \texttt{skos:prefLabel}, \texttt{skos:altLabel} or \texttt{skos:hiddenLabel} property values meeting a certain similarity threshold defined by a function $sim:LV \times LV \rightarrow [0,1]$.
 The default, built-in similarity function checks for case-insensitive string equality with a threshold equal to 1.
 Label conflicts can be found by iterating over all concept pairs $C \times C$, applying $sim$ to every possible label combination, and collecting those pairs with at least one label combination meeting or exceeding a specified similarity threshold.
+Since data on concept scheme membership may lack because of the Open World Assumption, we handle this issue under the Closed World Assumption.
 

### 2012-04-01 analysis.tex
fixed oc and wcc values for LCSH because of buggy SPARQL 1.1 support in openRDF 2.6.3
fixed lncs oc and wcc numbers

@@
 
-\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Version/\\Last Modified}}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Authoritative\\Concepts}}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Semantic\\Relations}}} & \rotatebox{90}{\textbf{\parbox{2.53cm}{Concept\\Schemes}}} \\
+\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Version/\\Last Modified}}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Authoritative\\Concepts}}} & \rotatebox{90}{\textbf{Concept Labels}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Semantic\\Relations}}} & \rotatebox{90}{\textbf{\parbox{2.53cm}{Concept\\Schemes}}} \\
 \toprule
@@
 
-Orphan Concepts & 0 & 77,062 & 7 & 671 & 162,000 & 0 & 180,909 & 21 & 0 & 0 & 0 & 4,979 & 1,125 & 2 & 4 \\
+Orphan Concepts & 0 & 77,062 & 7 & 671 & 162,000 & 0 & 173,149 & 21 & 0 & 0 & 0 & 4,979 & 1,125 & 2 & 4 \\
 

### 2012-04-02 analysis.tex
added lcsh label conflict count
fixed typos

@@
 
-The basic statistical properties of our vocabulary selection are summarized in Table~\ref{tab:vocabs}: the number of concepts, ``authoritative concepts'', as explained in Section~\ref{subsec:ld_issues}, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations (\texttt{Labels}), all asserted semantic relations, as well as the number of concept schemes.
-From these properties we can, for instance, already see that approximately 3,000 \texttt{DBPedia Categories} concepts don't have labels (e.g., \url{Category:South_Korean_social_scientists}), which indicates that the same amount of Wikipedia categories misses natural language descriptions.
+The basic statistical properties of our vocabulary selection are summarized in Table~\ref{tab:vocabs}: the number of concepts, ``authoritative concepts'', as explained in Section~\ref{subsec:ld_issues}, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations involving concepts (\texttt{Concept Labels}), all asserted semantic relations, as well as the number of concept schemes.
+From these properties we can, for instance, already see that approximately 3,000 \texttt{DBpedia Categories} concepts do not have labels (e.g., \url{Category:South_Korean_social_scientists}), which indicates that the same amount of Wikipedia categories misses natural language descriptions.
 
@@
 
-\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Version/\\Last Modified}}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Authoritative\\Concepts}}} & \rotatebox{90}{\textbf{Concept Labels}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Semantic\\Relations}}} & \rotatebox{90}{\textbf{\parbox{2.53cm}{Concept\\Schemes}}} \\
+\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Version/\\Last Modified}}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Authoritative\\Concepts}}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Concept\\Labels}}} & \rotatebox{90}{\textbf{\parbox{2.5cm}{Semantic\\Relations}}} & \rotatebox{90}{\textbf{\parbox{2.53cm}{Concept\\Schemes}}} \\
 \toprule
@@
 
-Label Conflicts & 2,949 & 0 & 48 & 18 & 12,404 & 0 & n/a & 13 & 4 & 0 & n/a & 0 & 0 & 7 & 5 \\
+Label Conflicts & 2,949 & 0 & 48 & 18 & 12,404 & 0 & 11,975 & 13 & 4 & 0 & n/a & 0 & 0 & 7 & 5 \\
 
@@
 \texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} omit language tags with their labeling properties, \texttt{LCSH} with the \texttt{skos:note} property.
-\texttt{STW} doesn't use language tags with 2 instances of \texttt{skos:definition}.
+\texttt{STW} does not use language tags with 2 instances of \texttt{skos:definition}.
 % Incomplete Language Coverage
@@
 % Weakly Connected Components
-Three vocabularies (\texttt{IPSW}, \texttt{NAICS}, \texttt{STW}) consist of only one ``giant component'', which is often considered as being the ideal vocabulary structure.
+Three vocabularies (\texttt{IPSV}, \texttt{NAICS}, \texttt{STW}) consist of only one ``giant component'', which is often considered as being the ideal vocabulary structure.
 All other vocabularies split into several clusters of semantically related concepts, each of which represents a certain subtopic in the vocabularies.
@@
 % Cyclic Hierarchical Relations
-Hierarchical cycles are not a common issue except in the collaboratively created DBpedia vocabulary, where many concepts have reflexive \texttt{skos:broader} relations.
+Hierarchical cycles are not a common issue except in the collaboratively created \texttt{DBpedia} vocabulary, where many concepts have reflexive \texttt{skos:broader} relations.
 % Valuless Associative Relations
@@
 % Missing Out-Links
-Most vocabularies also don't provide links to other vocabularies on the Web.
+Most vocabularies also do not provide links to other vocabularies on the Web.
 The \texttt{NYTP}, \texttt{IPSV} vocabularies are the two exceptions, which are fully linked to other Web resources.
@@
 One reason for a high number of missing out-links could also be that the links were not available in the main thesaurus file.
-We know that this is the case for \texttt{STW} and \texttt{AGROVOC} need to further investigate this.
+We know that this is the case for \texttt{STW} and \texttt{AGROVOC} and need to further investigate this.
 % Broken Links
-Even though we couldn't determine the exact number of broken links because of the large number of links to resolve  (over 400K in \texttt{Eurovoc}, over 500K in \texttt{LCSH}), we found that broken links are a common issue in most vocabularies.
+Even though we could not determine the exact number of broken links because of the large number of links to resolve  (over 400K in \texttt{Eurovoc}, over 500K in \texttt{LCSH}), we found that broken links are a common issue in most vocabularies.
 % Undefined SKOS Resources

### 2012-04-02 criteria.tex
fixed typos

@@
 % Function definition
-This issue can be detected by finding all concept pairs $C \times C$ that are directly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} properties but not by (a chain of) their \texttt{skos:broader} and \texttt{skos:narrower} subproperties.
+This issue can be detected by finding all concept pairs $C \times C$ that are directly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} properties but not by their \texttt{skos:broader} and \texttt{skos:narrower} subproperties.
 
@@
 The SKOS model is defined within the namespace \url{http://www.w3.org/2004/02/skos/core#}.
-However, some vocabularies use resources from within this namespace, which are unresolvable for two main reasons: vocabulary creators ``invented'' new terms within the SKOS namespace instead of introducing them in a separate namespace, or they use ``deprecated'' SKOS element like \texttt{skos:subject}.
+However, some vocabularies use resources from within this namespace, which are unresolvable for two main reasons: vocabulary creators ``invented'' new terms within the SKOS namespace instead of introducing them in a separate namespace, or they use ``deprecated'' SKOS elements like \texttt{skos:subject}.
 % Function definition

### 2012-04-02 introduction.tex
editorial changes
fixed typos

@@
 A standard that aims at cross-domain interoperability should refrain from defining constraints that impose on one domain the requirements of another.
-SKOS is thus very liberal with respect to data integrity.
+SKOS is thus very liberal with respect to data quality.
 
 On the other hand, each vocabulary should fulfill domain- and application-specific quality aspects and taxonomists often follow standard guidelines specific to given types of vocabularies (cf.,~\cite{ISO25964-1:2011,Z39.19:2005}) for thesauri) or apply their own hand-crafted checks~\cite{Coronado2009}.
-Existing guidelines consider these aspects, but currently rely on human judgement, which is subjective and does not scale for larger vocabularies.
+Existing guidelines consider these aspects, but currently rely on human judgment, which is subjective and does not scale for larger vocabularies.
 The SKOS context, where vocabularies can be linked together on the Web, also brings issues hitherto unforeseen by traditional checking approaches.

### 2012-04-02 analysis.tex
fixed typos
added AC to definition, changed lc computation to use only AC, updated numbers for STW 8.10 including available mappings

@@
 
-The basic statistical properties of our vocabulary selection are summarized in Table~\ref{tab:vocabs}: the number of concepts, ``authoritative concepts'', as explained in Section~\ref{subsec:ld_issues}, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations involving concepts (\texttt{Concept Labels}), all asserted semantic relations, as well as the number of concept schemes.
+The basic statistical properties of our vocabulary selection are summarized in Table~\ref{tab:vocabs}: the number of concepts and authoritative concepts, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations involving concepts (\texttt{Concept Labels}), all asserted semantic relations, as well as the number of concept schemes.
 From these properties we can, for instance, already see that approximately 3,000 \texttt{DBpedia Categories} concepts do not have labels (e.g., \url{Category:South_Korean_social_scientists}), which indicates that the same amount of Wikipedia categories misses natural language descriptions.
@@
 \hline
-Thesaurus for Economics & \textbf{STW} & 8.06 & 6,524 & 6,524 & 31,189 & 57,907 & 1 \\
+Thesaurus for Economics & \textbf{STW} & 8.10 & 25,107 & 6,789 & 58,441 & 91,816 & 3 \\
 \bottomrule
@@
 The results of this analysis are summarized in Table~\ref{tab:results}, which shows the absolute number of possibly affected resources for each quality checking function and vocabulary combination.
-n/a means that a certain function could not be computed with the current version of qSKOS because of algorithm complexity or missing support of SKOS-XL.
 Numbers marked with an asterisk (*) were obtained by extrapolating from subsets containing 5\% of the respective vocabulary resources.
@@
 \toprule
-Omitted or Invalid Language Tags & 0 & 0 & 219 & 0 & 0 & 0 & 100,316 & 13,411 & 0 & 23,950 & n/a & 0 & 1,224 & 1,578 & 2 \\
+Omitted or Invalid Language Tags & 0 & 0 & 219 & 0 & 0 & 0 & 100,316 & 13,411 & 0 & 23,950 & !0! & 0 & 1,224 & 1,578 & 2 \\
 
-Incomplete Language Coverage & 32,035 & 0 & 6370 & 0 & 0 & 0 & 0 & 0 & 420 & 0 & n/a & 0 & 0 & 0 & 6,456 \\
+Incomplete Language Coverage & 32,035 & 0 & 6370 & 0 & 0 & 0 & 0 & 0 & 420 & 0 & !0! & 0 & 0 & 0 & 25,050 \\
 
-Undocumented Concepts & 32,035 & 743,410 & 5,341 & 0 & 96,850 & 4,551 & 342,848 & 13,411 & 422 & 1,807 & 3,259 & 4,094 & 1,125 & 1,918 & 5,236 \\
+Undocumented Concepts & 32,035 & 743,410 & 5,341 & 0 & 96,850 & 4,551 & 342,848 & 13,411 & 422 & 1,807 & 3,259 & 4,094 & 1,125 & 1,918 & 23,752 \\
 
-Label Conflicts & 2,949 & 0 & 48 & 18 & 12,404 & 0 & 11,975 & 13 & 4 & 0 & n/a & 0 & 0 & 7 & 5 \\
+Label Conflicts & 2,949 & 0 & 48 & 18 & 12,404 & 0 & 11,975 & 13 & 4 & 0 & 0 & 0 & 0 & 7 & 0 \\
 
@@
 
-Orphan Concepts & 0 & 77,062 & 7 & 671 & 162,000 & 0 & 173,149 & 21 & 0 & 0 & 0 & 4,979 & 1,125 & 2 & 4 \\
+Orphan Concepts & 0 & 77,062 & 7 & 671 & 162,000 & 0 & 173,149 & 21 & 0 & 0 & 0 & 4,979 & 1,125 & 2 & 70 \\
 
-Weakly Connected Components & 4 & 1,506 & 4 & 0 & 621 & 1 & 22,343 & 11 & 5 & 4 & 1 & 0 & 0 & 10 & 1 \\
+Weakly Connected Components & 4 & 1,506 & 4 & 0 & 621 & 1 & 22,343 & 11 & 5 & 4 & 1 & 0 & 0 & 10 & 141 \\
 
@@
 
-Valueless Associative Relations & 282 & 8,839 & 6 & 0 & 9,448 & 253 & 0 & 5 & 0 & 550 & 0 & 0 & 0 & 0 & 5,139 \\
+Valueless Associative Relations & 282 & 8,839 & 6 & 0 & 9,448 & 253 & 0 & 5 & 0 & 550 & 0 & 0 & 0 & 0 & 5,004 \\
 
@@
 
-Omitted Top Concepts & 0 & 0 & 1 & 9 & 9 & 0 & 1 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
+Omitted Top Concepts & 0 & 0 & 1 & 9 & 9 & 0 & 1 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 2 \\
 
@@
 
-Missing In-Links & 32,035 & 733,800 & 6,796 & 19 & 171,980* & 3,080 & 408,000* & 13,411 & 422 & 24,625 & 2,213 & 20 & 1,125 & 1,686 & 6,516 \\
+Missing In-Links & 32,035 & 733,800 & 6,796 & 19 & 171,980* & 3,080 & 408,000* & 13,411 & 422 & 24,625 & 2,213 & 20 & 1,125 & 1,686 & 6,781 \\
 
-Missing Out-Links & 32,035 & 743,410 & 6,797 & 671 & 171,991 & 0 & 344,054 & 13,411 & 273 & 24,626 & 1 & 0 & 1,116 & 1,046 & 6,524 \\
+Missing Out-Links & 32,035 & 743,410 & 6,797 & 671 & 171,991 & 0 & 344,054 & 13,411 & 273 & 24,626 & 1 & 0 & 1,116 & 1,046 & 0 \\
 
@@
 The three smallest components contain concepts thematically related to ``Africa'', ``educational institutions'' and ``forecasts''.
-Weakly connected components divide the \texttt{Meketre} vocabularies into, e.g., topics, and concepts reserved for internal use or museums.
+Weakly connected components divide the \texttt{Meketre} vocabulary into different topics, e.g., museums of concepts reserved for internal use.
 \texttt{GTAA} consists of 621 weakly connected components with the largest one being a subject thesaurus containing 8413 concepts.

### 2012-04-02 criteria.tex
added AC to definition, changed lc computation to use only AC, updated numbers for STW 8.10 including available mappings

@@
 \begin{mydef}[SKOS Vocabulary]
-Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, SR, LV, CS \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C \subseteq IR\) with \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{concepts}, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}, and \(CS = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})\) being the set of \textbf{concept schemes}.
+Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, AC, SR, LV, CS \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C \subseteq IR\) with \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{concepts}, \(AC \subseteq C\) being the set of authoritative concepts, i.e.
+all concepts that are identified by URIs in the vocabulary namespace, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}, and \(CS = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})\) being the set of \textbf{concept schemes}.
 Further, we let $V$ be the fully entailed RDFS interpretation of the underlying RDF graph.
@@
 For better readability and due to lack of space we provide only semi-formal definitions and refer to the source code of the qSKOS tool for further details.
+
+% where to put the example for authoritative concepts?
+%For example, \texttt{PXV} links \url{http://www.peroxisomekb.nl/v1.6/pxv/C000297} to \url{http://www.bioexpert.nl/mesh/2010/concept/M0028264} using \texttt{skos:closeMatch}.
+Both are \texttt{skos:Concept}s, but the latter is no authoritative concept because its URI does not belong to the \texttt{PXV} namespace.
 
@@
 The default, built-in similarity function checks for case-insensitive string equality with a threshold equal to 1.
-Label conflicts can be found by iterating over all concept pairs $C \times C$, applying $sim$ to every possible label combination, and collecting those pairs with at least one label combination meeting or exceeding a specified similarity threshold.
+Label conflicts can be found by iterating over all concept pairs $AC \times AC$, applying $sim$ to every possible label combination, and collecting those pairs with at least one label combination meeting or exceeding a specified similarity threshold.
 Since data on concept scheme membership may lack because of the Open World Assumption, we handle this issue under the Closed World Assumption.
@@
 % Function definition
-We compute this by considering only the set of ``authoritative concepts'' $AC \subseteq C$, which consists of all concepts that are identified by URIs in the vocabulary namespace.
-For example, \texttt{PXV} links \url{http://www.peroxisomekb.nl/v1.6/pxv/C000297} to \url{http://www.bioexpert.nl/mesh/2010/concept/M0028264} using \texttt{skos:closeMatch}.
-Both are \texttt{skos:Concept}s, but the latter is no authoritative concept because its URI does not belong to the \texttt{PXV} namespace.
 We estimate the number of in-links by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/} indexes the Web of Data, which is composed of pages with semantic markup in RDF, RDFa, Microformats, or Microdata.

### 2012-04-02 analysis.tex
changed text according to new stw dataset

@@
 \texttt{AGROVOC} covers 25 languages but no single concept is labeled in all languages, in \texttt{Meketre} all concepts have English but only some of them French labels assigned.
-The reason for the high number of concepts with incomplete language coverage in \texttt{STW} is that a few concepts have labels with the private, but valid language tag \texttt{x-other}.
+The reasons for the high number of concepts with incomplete language coverage in \texttt{STW} are that many concepts (i) link to non-authoritative concepts that are only labeld in German and (ii) lack labels tagged with the private, but valid language tag \texttt{x-other} that few concepts pull in.
 % Undocumented Concepts
@@
 \texttt{GTAA} is a mixture of name authority file (approx.~162K concepts) and thesaurus (approx.~10K concepts).
-The 4 orphan concepts in \texttt{STW} are deprecated concepts.
+The 70 orphan concepts in \texttt{STW} are deprecated concepts.
 
@@
 % Weakly Connected Components
-Three vocabularies (\texttt{IPSV}, \texttt{NAICS}, \texttt{STW}) consist of only one ``giant component'', which is often considered as being the ideal vocabulary structure.
+Three vocabularies (\texttt{IPSV}, \texttt{NAICS}) consist of only one ``giant component'', which is often considered as being the ideal vocabulary structure.
+\texttt{STW} also consists of one giant component (containing 24572 concepts), but also 140 additional weakly connected components, mapping otherwisely unconnected authoritative concepts to non-authoritative concepts.
 All other vocabularies split into several clusters of semantically related concepts, each of which represents a certain subtopic in the vocabularies.
@@
 Most vocabularies also do not provide links to other vocabularies on the Web.
-The \texttt{NYTP}, \texttt{IPSV} vocabularies are the two exceptions, which are fully linked to other Web resources.
+The \texttt{NYTP}, \texttt{IPSV}, and \texttt{STW} vocabularies are the three exceptions, which are fully linked to other Web resources.
 The one concept with missing out-links in \texttt{NAICS} is the object of a \texttt{skos:broaderTransitive} relation.
-One reason for a high number of missing out-links could also be that the links were not available in the main thesaurus file.
-We know that this is the case for \texttt{STW} and \texttt{AGROVOC} and need to further investigate this.
+One reason for a high number of missing out-links could also be that the links were not available in the main thesaurus file, which is at least the case for \texttt{AGROVOC}.
 % Broken Links

### 2012-04-02 criteria.tex
updated criteria

@@
 Based on the received responses, we then selected a subset of these issues and translated them into computable quality checking functions.
-Each function takes a given SKOS vocabulary as input and finds all resources that match the corresponding quality criterion.
+Each function takes a given SKOS vocabulary and a vocabulary namespace (e.g., \url{http://zbw.eu/stw/}) as input and finds all resources that match the corresponding quality criterion.
 For the purpose of this work, we define a SKOS vocabulary as follows:
@@
 \begin{mydef}[SKOS Vocabulary]
-Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, AC, SR, LV, CS \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C \subseteq IR\) with \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{concepts}, \(AC \subseteq C\) being the set of authoritative concepts, i.e.
-all concepts that are identified by URIs in the vocabulary namespace, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}, and \(CS = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})\) being the set of \textbf{concept schemes}.
+Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, AC, SR, LV, CS \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C \subseteq IR\) with \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{concepts}, \(AC \subseteq C\) being the set of authoritative concepts, which are all concepts that are identified by URIs in the vocabulary namespace, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}, and \(CS = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})\) being the set of \textbf{concept schemes}.
 Further, we let $V$ be the fully entailed RDFS interpretation of the underlying RDF graph.
@@
 Label conflicts can be found by iterating over all concept pairs $AC \times AC$, applying $sim$ to every possible label combination, and collecting those pairs with at least one label combination meeting or exceeding a specified similarity threshold.
-Since data on concept scheme membership may lack because of the Open World Assumption, we handle this issue under the Closed World Assumption.
+We handle this issue under the Closed World Assumption, because data on concept scheme membership may lack and concepts may be linked to concepts with similar labels in other vocabularies.
+% Since data on concept scheme membership may lack because of the Open World Assumption, we handle this issue under the Closed World Assumption.
 

### 2012-04-02 analysis.tex
fixed analysis results

@@
 \texttt{AGROVOC} covers 25 languages but no single concept is labeled in all languages, in \texttt{Meketre} all concepts have English but only some of them French labels assigned.
-The reasons for the high number of concepts with incomplete language coverage in \texttt{STW} are that many concepts (i) link to non-authoritative concepts that are only labeld in German and (ii) lack labels tagged with the private, but valid language tag \texttt{x-other} that few concepts pull in.
+STW, which is expressed mainly in English and German, has many concepts with incomplete language coverage because it (i) links to non-authoritative concepts that are only labeled in German and (ii) uses the private, but valid language tag \texttt{x-other} with some of its concept labels.
+%The reasons for the high number of concepts with incomplete language coverage in \texttt{STW} are that many concepts (i) link to non-authoritative concepts that are only labeld in German and (ii) lack labels tagged with the private, but valid language tag \texttt{x-other} that few concepts pull in.
 % Undocumented Concepts
@@
 Three vocabularies (\texttt{IPSV}, \texttt{NAICS}) consist of only one ``giant component'', which is often considered as being the ideal vocabulary structure.
-\texttt{STW} also consists of one giant component (containing 24572 concepts), but also 140 additional weakly connected components, mapping otherwisely unconnected authoritative concepts to non-authoritative concepts.
+\texttt{STW} forms one giant component (containing 24,572 concepts), but has also 140 additional weakly connected components, which all contain linked authoritative and non-authoritative concepts.
 All other vocabularies split into several clusters of semantically related concepts, each of which represents a certain subtopic in the vocabularies.
-\texttt{Eurovoc}, for instance, contains of 4 weakly connected components, containing 4, 5, 6 and 6775 concepts.
+\texttt{Eurovoc}, for instance, contains 4 weakly connected components, containing 4, 5, 6 and 6775 concepts.
 The three smallest components contain concepts thematically related to ``Africa'', ``educational institutions'' and ``forecasts''.
@@
 Only the \texttt{PXV} vocabulary is affected by top concepts having broader concepts in its current version.
-The reason for this is, according to the vocabulary creator, that the broader concept was abandoned but is still available in the triplestore, maybe because of some bug in the vocabulary management software.
+The reason for this is, according to the vocabulary creator, that the broader concept was abandoned but is still available in the triple store, maybe because of some bug in the vocabulary management software.
 
@@
 % Missing In-Links
-However, except \texttt{NYTP} and \texttt{Geonames}, none of the analyzed vocabularies has a significant number of in-links from other web resources.
-Estimation of these numbers is rather inaccurate since currently we only rely on the Sindice index.
+However, except \texttt{NYTP} and \texttt{Geonames}, none of the analyzed vocabularies has a significant estimated number of estimated in-links from other web resources.
+%Estimation of these numbers is rather inaccurate since currently we only rely on the Sindice index. 
 % Missing Out-Links
@@
 Even though we could not determine the exact number of broken links because of the large number of links to resolve  (over 400K in \texttt{Eurovoc}, over 500K in \texttt{LCSH}), we found that broken links are a common issue in most vocabularies.
+\todo{CM}{fix these numbers!}
 % Undefined SKOS Resources

### 2012-04-02 criteria.tex
fixed analysis results

@@
 Based on the received responses, we then selected a subset of these issues and translated them into computable quality checking functions.
-Each function takes a given SKOS vocabulary and a vocabulary namespace (e.g., \url{http://zbw.eu/stw/}) as input and finds all resources that match the corresponding quality criterion.
+Each function takes a given SKOS vocabulary and an optional vocabulary namespace (e.g., \url{http://zbw.eu/stw/}) as input and finds all resources that match the corresponding quality criterion.
 For the purpose of this work, we define a SKOS vocabulary as follows:

### 2012-04-03 analysis.tex
changed lc values for LCSH due to different computation method (now including only auth concepts)
added naics description for lc; extended oilc by rdfs:label

@@
 \toprule
-Omitted or Invalid Language Tags & 0 & 0 & 219 & 0 & 0 & 0 & 100,316 & 13,411 & 0 & 23,950 & !0! & 0 & 1,224 & 1,578 & 2 \\
+Omitted or Invalid Language Tags & 0 & 0 & 219 & 0 & 0 & 0 & 100,316 & 13,411 & 0 & 23,950 & 0 & 0 & 1,224 & 1,578 & 2 \\
 
-Incomplete Language Coverage & 32,035 & 0 & 6370 & 0 & 0 & 0 & 0 & 0 & 420 & 0 & !0! & 0 & 0 & 0 & 25,050 \\
+Incomplete Language Coverage & 32,035 & 0 & 6370 & 0 & 0 & 0 & 0 & 0 & 420 & 0 & 0 & 0 & 0 & 0 & 25,050 \\
 
@@
 
-Label Conflicts & 2,949 & 0 & 48 & 18 & 12,404 & 0 & 11,975 & 13 & 4 & 0 & 0 & 0 & 0 & 7 & 0 \\
+Label Conflicts & 2,949 & 0 & 48 & 18 & 12,404 & 0 & 10,862 & 13 & 4 & 0 & 0 & 0 & 0 & 7 & 0 \\
 
@@
 \texttt{PXV}, for instance, uses the string ``primary peroxisomal enzyme deficiency'' with two concepts in the same concept scheme, but once with a \texttt{skos:prefLabel} and another time with a \texttt{skos:altLabel} property.
+For every concept in \texttt{NAICS}, a \texttt{rdfs:label} as well as a \texttt{skosxl:prefLabel} is defined.
+However, objects of the \texttt{prefLabel} triples are plain literals which seems to be a misunderstanding of SKOS-XL by the vocabulary creators.
+Thus, this information is not processed and no conflicts are found.
 %An example from AGROVOC is ``sziv\'{a}rv\'{a}nyos pisztr\'{a}ng'', which is used as \texttt{skos:altLabel} with two different concepts.

### 2012-04-03 criteria.tex
added naics description for lc; extended oilc by rdfs:label

@@
 SKOS defines a set of properties that link resources with RDF Literals, which are plain text natural language strings with an optional language tag.
-This includes the labeling properties \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} and subproperties thereof.
+This includes the labeling properties \texttt{rdfs:label}, \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} and subproperties thereof.
 Literals should be tagged consistently~\cite{Vrandecic2010}, because omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could unintentionally limit the result set of language-dependent queries.

### 2012-04-03 analysis.tex
fixed typo

@@
 % Weakly Connected Components
-Three vocabularies (\texttt{IPSV}, \texttt{NAICS}) consist of only one ``giant component'', which is often considered as being the ideal vocabulary structure.
+Two vocabularies (\texttt{IPSV}, \texttt{NAICS}) consist of only one ``giant component'', which is often considered as being the ideal vocabulary structure.
 \texttt{STW} forms one giant component (containing 24,572 concepts), but has also 140 additional weakly connected components, which all contain linked authoritative and non-authoritative concepts.

### 2012-04-03 analysis.tex
added stw mapping description

@@
 From these properties we can, for instance, already see that approximately 3,000 \texttt{DBpedia Categories} concepts do not have labels (e.g., \url{Category:South_Korean_social_scientists}), which indicates that the same amount of Wikipedia categories misses natural language descriptions.
+\textcolor{red}{The vocabularies have been received as bulk downloads from the respective websites or directly from the creators.
+We further added available mapping files to the base \texttt{STW} vocabulary to accurately measure the number of out-links.}
 
@@
 \texttt{PXV}, for instance, uses the string ``primary peroxisomal enzyme deficiency'' with two concepts in the same concept scheme, but once with a \texttt{skos:prefLabel} and another time with a \texttt{skos:altLabel} property.
-For every concept in \texttt{NAICS}, a \texttt{rdfs:label} as well as a \texttt{skosxl:prefLabel} is defined.
+\textcolor{red}{For every concept in \texttt{NAICS}, a \texttt{rdfs:label} as well as a \texttt{skosxl:prefLabel} is defined.
 However, objects of the \texttt{prefLabel} triples are plain literals which seems to be a misunderstanding of SKOS-XL by the vocabulary creators.
-Thus, this information is not processed and no conflicts are found.
+Thus, this information is not processed and no conflicts are found.}
 %An example from AGROVOC is ``sziv\'{a}rv\'{a}nyos pisztr\'{a}ng'', which is used as \texttt{skos:altLabel} with two different concepts.

### 2012-04-03 criteria.tex
added stw mapping description

--- 2012-04-02 criteria.tex
@@
 SKOS defines a set of properties that link resources with RDF Literals, which are plain text natural language strings with an optional language tag.
-This includes the labeling properties \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} and subproperties thereof.
+This includes the labeling properties \textcolor{red}{\texttt{rdfs:label}}, \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} and subproperties thereof.
 Literals should be tagged consistently~\cite{Vrandecic2010}, because omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could unintentionally limit the result set of language-dependent queries.

### 2012-04-03 analysis.tex
shortened analysis

--- 2012-04-03 analysis.tex
@@
 
-The basic statistical properties of our vocabulary selection are summarized in Table~\ref{tab:vocabs}: the number of concepts and authoritative concepts, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations involving concepts (\texttt{Concept Labels}), all asserted semantic relations, as well as the number of concept schemes.
-From these properties we can, for instance, already see that approximately 3,000 \texttt{DBpedia Categories} concepts do not have labels (e.g., \url{Category:South_Korean_social_scientists}), which indicates that the same amount of Wikipedia categories misses natural language descriptions.
+Table~\ref{tab:vocabs} summarizes some basic statistical properties of our vocabulary selection: the number of concepts and authoritative concepts, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations involving concepts (\texttt{Concept Labels}), all asserted semantic relations, as well as the number of concept schemes.
+From these properties we can, for instance, already see that approximately 3,000 \texttt{DBpedia Categories} concepts do not have labels (e.g., \url{Category:South_Korean_social_scientists}), which is an indicator for missing natural language descriptions in some Wikipedia categories.
 
@@
 % Undocumented Concepts
-\texttt{Geonames}, which is an ontology including a concept scheme of ``feature codes'', is the only vocabulary in our dataset, which has at least one documentation property assigned to all of its concepts.
+\texttt{Geonames}, which defines a concept scheme of ``feature codes'', is the only vocabulary in our dataset, which has at least one documentation property assigned to all of its concepts.
 All other vocabularies have a significant number of undocumented concepts.
 % Label Conflicts
-We also detected possible label issues in half of the vocabularies.
+We also detected possible label conflicts in half of the vocabularies.
 \texttt{PXV}, for instance, uses the string ``primary peroxisomal enzyme deficiency'' with two concepts in the same concept scheme, but once with a \texttt{skos:prefLabel} and another time with a \texttt{skos:altLabel} property.
-For every concept in \texttt{NAICS}, a \texttt{rdfs:label} as well as a \texttt{skosxl:prefLabel} is defined.
+In \texttt{NAICS} we couldn't detect any labeling issues but found that it expresses statements with \texttt{skosxl:prefLabel} as predicate and plain literals as object, which contradicts the SKOS-XL specification.
+
+%\textcolor{red}{For every concept in \texttt{NAICS}, a \texttt{rdfs:label} as well as a \texttt{skosxl:prefLabel} is defined.
 However, objects of the \texttt{prefLabel} triples are plain literals which seems to be a misunderstanding of SKOS-XL by the vocabulary creators.
-Thus, this information is not processed and no conflicts are found.
-%An example from AGROVOC is ``sziv\'{a}rv\'{a}nyos pisztr\'{a}ng'', which is used as \texttt{skos:altLabel} with two different concepts.
+Thus, this information is not processed and no conflicts are found.}
 
@@
 \texttt{STW} forms one giant component (containing 24,572 concepts), but has also 140 additional weakly connected components, which all contain linked authoritative and non-authoritative concepts.
-All other vocabularies split into several clusters of semantically related concepts, each of which represents a certain subtopic in the vocabularies.
+All other vocabularies split into several clusters of semantically related concepts, each of which represents a certain subtopic.
 \texttt{Eurovoc}, for instance, contains 4 weakly connected components, containing 4, 5, 6 and 6775 concepts.
@@
 Most of the other components contain less than 10 concepts, representing, e.g., locations, person names, and genres.
-\texttt{PXV} splits into 10 topic-related weakly connected components, such as ``deficiancies'', ``defects'' or ``signals''.
+\texttt{PXV} splits into 10 topic-related weakly connected components, such as ``deficiencies'', ``defects'' or ``signals''.
 The \texttt{LVAk} thesaurus contains 11 concept clusters, which are obviously forgotten test data.
@@
 % Missing In-Links
-However, except \texttt{NYTP} and \texttt{Geonames}, none of the analyzed vocabularies has a significant estimated number of estimated in-links from other web resources.
+However, except \texttt{NYTP} and \texttt{Geonames}, no vocabulary has a high number of estimated in-links from other web resources.
 %Estimation of these numbers is rather inaccurate since currently we only rely on the Sindice index. 
 % Missing Out-Links
-Most vocabularies also do not provide links to other vocabularies on the Web.
-The \texttt{NYTP}, \texttt{IPSV}, and \texttt{STW} vocabularies are the three exceptions, which are fully linked to other Web resources.
+Also the number of out-links is rather low: \texttt{NYTP}, \texttt{IPSV}, and \texttt{STW} are the three exceptions, which are fully linked to other Web resources.
 The one concept with missing out-links in \texttt{NAICS} is the object of a \texttt{skos:broaderTransitive} relation.
@@
 Even though we could not determine the exact number of broken links because of the large number of links to resolve  (over 400K in \texttt{Eurovoc}, over 500K in \texttt{LCSH}), we found that broken links are a common issue in most vocabularies.
-\todo{CM}{fix these numbers!}
 % Undefined SKOS Resources

### 2012-04-03 conclusions.tex
shortened analysis

@@
 
-We are aware that these issues are purely quantitative indicators and not statements about the quality of a vocabulary.
+We are aware that these issues are purely quantitative quality indicators.
 To learn more about the real-world impact of our work, we will conduct a qualitative follow-up study, in which we discuss these results with more taxonomists.
@@
 
-During our work on qSKOS and while writing this paper we reported initial results from our analysis to some of the maintainers of the vocabularies we analyzed.
+We already reported initial results from our analysis to some of the maintainers of the vocabularies we analyzed.
 At the time of this writing, we know that our findings led to improvements in at least two SKOS vocabularies.

### 2012-04-03 criteria.tex
shortened analysis

--- 2012-04-02 criteria.tex
@@
 SKOS defines a set of properties that link resources with RDF Literals, which are plain text natural language strings with an optional language tag.
-This includes the labeling properties \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} and subproperties thereof.
+This includes the labeling properties {\texttt{rdfs:label}, \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} and subproperties thereof.
 Literals should be tagged consistently~\cite{Vrandecic2010}, because omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could unintentionally limit the result set of language-dependent queries.

### 2012-04-04 analysis.tex
minor changes, typo fixes

@@
 
-Broken Links & 238 & 0* & 0* & 0 & 0 & 1 & 780 & 0 & 425 & 1 & 3,169 & 7 & 11 & 163 & 1 \\
+Broken Links & 238 & 0* & 0* & 0 & 0 & 1 & 780 & 0 & 425 & 1 & 3,169 & 7 & 11 & 163 & 575 \\
 
@@
 \texttt{AGROVOC} covers 25 languages but no single concept is labeled in all languages, in \texttt{Meketre} all concepts have English but only some of them French labels assigned.
-STW, which is expressed mainly in English and German, has many concepts with incomplete language coverage because it (i) links to non-authoritative concepts that are only labeled in German and (ii) uses the private, but valid language tag \texttt{x-other} with some of its concept labels.
+\texttt{STW}, which is expressed mainly in English and German, has many concepts with incomplete language coverage because it (i) links to non-authoritative concepts that are only labeled in German and (ii) uses the private, but valid language tag \texttt{x-other} with some of its concept labels.
 %The reasons for the high number of concepts with incomplete language coverage in \texttt{STW} are that many concepts (i) link to non-authoritative concepts that are only labeld in German and (ii) lack labels tagged with the private, but valid language tag \texttt{x-other} that few concepts pull in.
@@
 The three smallest components contain concepts thematically related to ``Africa'', ``educational institutions'' and ``forecasts''.
-Weakly connected components divide the \texttt{Meketre} vocabulary into different topics, e.g., museums of concepts reserved for internal use.
+Weakly connected components divide the \texttt{Meketre} vocabulary into different topics, e.g., museums or concepts reserved for internal use.
 \texttt{GTAA} consists of 621 weakly connected components with the largest one being a subject thesaurus containing 8413 concepts.
@@
 Only the \texttt{PXV} vocabulary is affected by top concepts having broader concepts in its current version.
-The reason for this is, according to the vocabulary creator, that the broader concept was abandoned but is still available in the triple store, maybe because of some bug in the vocabulary management software.
+In earlier versions more of them could be found which were, according to the vocabulary creator, abandoned but still available in the triple store, probably caused by some bug in the vocabulary management software.
 

### 2012-04-04 criteria.tex
minor changes, typo fixes

@@
 \begin{mydef}[SKOS Vocabulary]
-Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, AC, SR, LV, CS \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C \subseteq IR\) with \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{concepts}, \(AC \subseteq C\) being the set of authoritative concepts, which are all concepts that are identified by URIs in the vocabulary namespace, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}, and \(CS = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})\) being the set of \textbf{concept schemes}.
+Let a SKOS vocabulary be a tuple of the form $V = \langle IR, C, AC, SR, LV, CS \rangle$, with \(IR = I_{CEXT}(\texttt{rdfs:Resource}^\mathcal{I})\) being the set of \textbf{resources}, \(C \subseteq IR\) with \(C = I_{CEXT}(\texttt{skos:Concept}^\mathcal{I})\) being the set of \textbf{concepts}, \(AC \subseteq C\) being the set of \textbf{authoritative concepts}, which are all concepts that are identified by URIs in the vocabulary namespace, \(SR = I_{EXT}(\texttt{skos:semanticRelation}^\mathcal{I})\) being the set of \textbf{semantic relations} associating concepts with one another, $LV \subseteq I_{CEXT}(\texttt{rdfs:Literal}^\mathcal{I})$ being the set of untyped \textbf{plain literals}, and \(CS = I_{CEXT}(\texttt{skos:ConceptScheme}^\mathcal{I})\) being the set of \textbf{concept schemes}.
 Further, we let $V$ be the fully entailed RDFS interpretation of the underlying RDF graph.

### 2012-04-04 introduction.tex
updated criteria
minor changes, typo fixes

@@
 
-	\item An earlier version of the STW thesaurus contained 5 pairs of concepts with identical labels.
+	\item An earlier version of the STW thesaurus (v8.06) contained 5 pairs of concepts with identical labels.
 As a result, the auto-complete function of the online search interface suggested identical entries without disambiguation information.
@@
 
-On the other hand, each vocabulary should fulfill domain- and application-specific quality aspects and taxonomists often follow standard guidelines specific to given types of vocabularies (cf.,~\cite{ISO25964-1:2011,Z39.19:2005}) for thesauri) or apply their own hand-crafted checks~\cite{Coronado2009}.
+On the other hand, each vocabulary should fulfill domain- and application-specific quality aspects and taxonomists often follow standard guidelines specific to given types of vocabularies (cf.,~\cite{ISO25964-1:2011,Z39.19:2005} for thesauri) or apply their own hand-crafted checks~\cite{Coronado2009}.
 Existing guidelines consider these aspects, but currently rely on human judgment, which is subjective and does not scale for larger vocabularies.

### 2012-05-29 conclusions.tex
minor changes, typo fixes
added todos for camera ready version

@@
 Although SKOS is designed for Linked Data, many existing vocabularies still resemble their closed-system origin, which results in a relatively low number of in- and out-links.
-Broken links is a major issue and calls for synchronization mechanisms in order to maintain navigability between concepts in different vocabularies.
+Broken links are a major issue and call for synchronization mechanisms in order to maintain navigability between concepts in different vocabularies.
 
@@
 At the time of this writing, we know that our findings led to improvements in at least two SKOS vocabularies.
+
+\todo{add relative importance of the issues as future work}

### 2012-05-30 acknowledgements.tex
added ackn and minor comments

%!TEX root = main.tex
\section{Acknowledgements}

The authors would like to thank \todo{CM}{Names} for \todo{CM}{what?}. The work has partly been supported by \todo{CM}{FWF Grant} and an EU Marie Curie International Outgoing Fellowship, grant no. 252206. \todo{CM}{ask Antoine about necessary Ackn.}

### 2012-05-30 main.tex
added acknowledgements section, adjusted todos
added ackn and minor comments

@@
 \newcommand{\todo}[2]{\textbf{\textcolor{red}{(TODO [#1]: #2)}}}
-
-%Title ideas:
-% - How can we fix quality issues in SKOS vocabularies?
-% - Detecting quality issues in SKOS Vocabularies
-% - Computable Quality Guidlines for SKOSO Vocabularies
-% - ...
 
@@
 Here we investigate how we can support taxonomists in improving SKOS vocabularies by pointing out quality issues that go beyond the integrity constraints defined in the SKOS specification.
-We identified potential quality issues and formalized them into computable quality checking functions that can find affected resources in a given SKOS vocabulary.
+We identified potential \todo{ALL}{quantifiable?} quality issues and formalized them into computable quality checking functions that can find affected resources in a given SKOS vocabulary.
 We implemented these functions in the qSKOS quality assessment tool, analyzed 15 existing vocabularies, and found possible quality issues in all of them.
@@
 
+\input{acknowledgements}
+
 % \section{Acknowledgements}

### 2012-05-30 acknowledgements.tex
added acknowledgement details

@@
 
-The authors would like to thank \todo{CM}{Names} for \todo{CM}{what?}.
-The work has partly been supported by \todo{CM}{FWF Grant} and an EU Marie Curie International Outgoing Fellowship, grant no.
+The authors would like to thank Andrew Gibson and Tom Dent for providing dumps of the PXV and IPSV vocabularies as well as Joachim Neubert for valuable feedback on the found issues.
+The work has partly been supported by the FWF-funded Meketre project (P21571) and an EU Marie Curie International Outgoing Fellowship, grant no.
 252206.

### 2012-05-30 conclusions.tex
added acknowledgements section, adjusted todos
fixed some todos

@@
 We are aware that these issues are purely quantitative quality indicators.
-To learn more about the real-world impact of our work, we will conduct a qualitative follow-up study, in which we discuss these results with more taxonomists.
+To learn more about the real-world impact of our work like, e.g., the relative importance of the identified quality issues, we will conduct a qualitative follow-up study, in which we discuss these results with more taxonomists.
 We will also further collect community feedback, enhance the issues list, and set up a Web-based SKOS quality checking service.
@@
 At the time of this writing, we know that our findings led to improvements in at least two SKOS vocabularies.
-
-\todo{add relative importance of the issues as future work}

### 2012-05-31 background.tex
fixed typos
addressed some todos

@@
 
-Typical applications of controlled vocabularies are classification, indexing, autocompletion, query reformulation, or serving as a glossary.
+Typical applications of controlled vocabularies are classification, indexing, auto-completion, query reformulation, or serving as a glossary.
 As we discussed in detail in earlier work~\cite{Nagy2011}, these areas impose specific requirements on vocabulary features, such as structure, availability, and documentation.
-Quality aspects of controlled vocabularies have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, tutorials~\cite{Soergel2002}, and scholarly articles \cite{Coronado2009,Soergel1997,Elkin2002,Kless2010}.
+Quality aspects of controlled vocabularies have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, tutorials~\cite{Soergel2002}, and scholarly articles \cite{Coronado2009,Kless2010}.
 These most often rely on manual, precise analysis of individual statements in the data, as in~\cite{spero2008}.

### 2012-05-31 introduction.tex
added todos for camera ready version
more todos for cr version
added acknowledgements section, adjusted todos
addressed some todos

@@
 Finding such quality issues also gives important feedback on the overall vocabulary design process and should, at the end, lead to better vocabularies.
+With defining computable quality checking functions we tackle the problem of quality assessment from an objective perspective.
+Subjective perception of quality is not within the scope of this work.
 The main contributions of this work can be summarized as follows:
@@
 Finally, we report on the results of an analysis we performed on 15 existing SKOS vocabularies and show that the quality issues we discussed are real and can lead to the improvement of existing vocabularies.
-All supplemental materials are available at \url{https://github.com/cmader/qSKOS/} (qSKOS tool, wiki pages) and \url{https://github.com/cmader/qSKOS-data/} (vocabulary dataset).
+All supplemental materials (qSKOS\footnote{\url{https://github.com/cmader/qSKOS/}}, wiki\footnote{\url{https://github.com/cmader/qSKOS/wiki}} and dataset\footnote{\url{https://github.com/cmader/qSKOS-data/}}) are available online.

### 2012-05-31 main.tex
removed todo

@@
 Here we investigate how we can support taxonomists in improving SKOS vocabularies by pointing out quality issues that go beyond the integrity constraints defined in the SKOS specification.
-We identified potential \todo{ALL}{quantifiable?} quality issues and formalized them into computable quality checking functions that can find affected resources in a given SKOS vocabulary.
+We identified potential quantifiable quality issues and formalized them into computable quality checking functions that can find affected resources in a given SKOS vocabulary.
 We implemented these functions in the qSKOS quality assessment tool, analyzed 15 existing vocabularies, and found possible quality issues in all of them.

### 2012-06-01 criteria.tex
added todos for camera ready version
added acknowledgements section, adjusted todos
fixed some todos
minor changes to save some space

@@
 We identified an initial set of possible quality issues in SKOS vocabularies by reviewing literature and manually examining existing vocabularies.
+In our studies we strictly focused on issues that can be formally expressed and thus automatically measured.
 We published our findings in the qSKOS Wiki and requested feedback from experts via public mailing lists and informal face to face discussions.
 Based on the received responses, we then selected a subset of these issues and translated them into computable quality checking functions.
-Each function takes a given SKOS vocabulary and an optional vocabulary namespace (e.g., \url{http://zbw.eu/stw/}) as input and finds all resources that match the corresponding quality criterion.
+Each function takes a given SKOS vocabulary and an optional vocabulary namespace (e.g., \url{http://zbw.eu/stw/}) as input and finds all resources that match the corresponding quality issue.
 For the purpose of this work, we define a SKOS vocabulary as follows:

### 2012-06-01 introduction.tex
minor changes to save some space

@@
 The Simple Knowledge Organization System (SKOS)~\cite{SkosReference2008} is a standard model for sharing and linking controlled vocabularies (thesauri, classification systems, etc.) on the Web.
-Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} publish SKOS representations of their vocabularies on the Web so that they can easily be accessed by humans and machines.
+Organizations like, e.g., the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} publish SKOS representations of their vocabularies on the Web so that they can easily be accessed by humans and machines.
 
@@
 	\item AGROVOC defines concepts in 25 different languages.
-However, while most concepts have English labels attached, only 38\% have German labels.
+While most concepts have English labels attached, only 38\% have German labels.
 This can be a problem for multilingual applications that rely on label translations.
@@
 
-	\item The non-public vocabulary of the Austrian Armed Forces (LVAk) contains 11 disconnected concept clusters.
-When confronted with these structures, the thesaurus maintainers recognized them as ``forgotten'' test data that has no practical significance.
+	\item The non-public thesaurus of the Austrian Armed Forces (LVAk) contains 11 disconnected concept clusters.
+When confronted with these structures, the maintainers recognized them as data without practical significance.
 
@@
 SKOS is thus very liberal with respect to data quality.
-
-On the other hand, each vocabulary should fulfill domain- and application-specific quality aspects and taxonomists often follow standard guidelines specific to given types of vocabularies (cf.,~\cite{ISO25964-1:2011,Z39.19:2005} for thesauri) or apply their own hand-crafted checks~\cite{Coronado2009}.
+On the other hand, each vocabulary should fulfill domain- and application-specific quality aspects and taxonomists often follow standard guidelines specific to given types of vocabularies (cf.,~\cite{ISO25964-1:2011,Z39.19:2005}) or apply their own hand-crafted checks~\cite{Coronado2009}.
 Existing guidelines consider these aspects, but currently rely on human judgment, which is subjective and does not scale for larger vocabularies.
@@
 Finally, we report on the results of an analysis we performed on 15 existing SKOS vocabularies and show that the quality issues we discussed are real and can lead to the improvement of existing vocabularies.
-All supplemental materials (qSKOS\footnote{\url{https://github.com/cmader/qSKOS/}}, wiki\footnote{\url{https://github.com/cmader/qSKOS/wiki}} and dataset\footnote{\url{https://github.com/cmader/qSKOS-data/}}) are available online.
+All supplemental materials\footnote{qSKOS: \url{https://github.com/cmader/qSKOS/}, wiki: \url{https://github.com/cmader/qSKOS/wiki}, dataset: \url{https://github.com/cmader/qSKOS-data/}} are available online.

### 2012-06-02 criteria.tex
minor changes to meet page limit

@@
 In our studies we strictly focused on issues that can be formally expressed and thus automatically measured.
-We published our findings in the qSKOS Wiki and requested feedback from experts via public mailing lists and informal face to face discussions.
+We published our findings in the qSKOS wiki and requested feedback from experts via public mailing lists and informal face to face discussions.
 Based on the received responses, we then selected a subset of these issues and translated them into computable quality checking functions.
-Each function takes a given SKOS vocabulary and an optional vocabulary namespace (e.g., \url{http://zbw.eu/stw/}) as input and finds all resources that match the corresponding quality issue.
+Each function takes a given SKOS vocabulary and an optional vocabulary namespace as input and finds all resources that match the corresponding quality issue.
 For the purpose of this work, we define a SKOS vocabulary as follows:

### 2012-06-04 analysis.tex
more todos for cr version
changes according to antoine's comments

@@
 
-\subsection{Results}
+\subsection{Results and Discussion}
 
-The results of this analysis are summarized in Table~\ref{tab:results}, which shows the absolute number of possibly affected resources for each quality checking function and vocabulary combination.
+The results of this analysis are summarized in Table~\ref{tab:results}, which shows the absolute number of possibly affected resources for each quality checking function and vocabulary.
 Numbers marked with an asterisk (*) were obtained by extrapolating from subsets containing 5\% of the respective vocabulary resources.
@@
 \texttt{PXV}, for instance, uses the string ``primary peroxisomal enzyme deficiency'' with two concepts in the same concept scheme, but once with a \texttt{skos:prefLabel} and another time with a \texttt{skos:altLabel} property.
-In \texttt{NAICS} we couldn't detect any labeling issues but found that it expresses statements with \texttt{skosxl:prefLabel} as predicate and plain literals as object, which contradicts the SKOS-XL specification.
+In \texttt{NAICS} we could not detect any labeling issues but found that it expresses statements with \texttt{skosxl:prefLabel} as predicate and plain literals as object, which contradicts the SKOS-XL specification.
 
@@
 The one concept with missing out-links in \texttt{NAICS} is the object of a \texttt{skos:broaderTransitive} relation.
-One reason for a high number of missing out-links could also be that the links were not available in the main thesaurus file, which is at least the case for \texttt{AGROVOC}.
+One reason for a high number of missing out-links is that the links were not available in the main thesaurus file, which is at least the case for \texttt{AGROVOC}.
 % Broken Links

### 2012-06-04 background.tex
changes according to antoine's comments

@@
 % Data quality in general
-The problem of ``vocabulary quality'' is closely related to the more general one of ``data quality`'' and has been discussed in data and information systems research (cf.~\cite{Batini2009}).
+The problem of ``vocabulary quality'' is closely related to the more general one of ``data quality'' and has been discussed in data and information systems research (cf.~\cite{Batini2009}).
 Pipino et al.~\cite{Pipino2002} argue that dealing with data quality should involve both ``subjective perceptions of the individuals'' and ``objective measurements based on the data''.
@@
 For validating a SKOS vocabulary against the other integrity conditions, one can use tools such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}}, or the Skosify\footnote{\url{http://code.google.com/p/skosify/}} validator, which can also correct some detected quality problems.
-
-One issue when assessing the quality of SKOS data is the so-called ``Open World Assumption'', which underlies the Web of Data itself.
-Established quality notions from closed-world systems, such as referential integrity or schema validation, do not hold anymore, because available information may be incomplete and non-explicitly stated facts cannot be determined as true or false.
-Work-arounds, often ad-hoc, are thus currently used to evaluate quality in Linked Data sets~\cite{Heath2011}, as is done in the (rule-based) SKOS tools mentioned above, or the Pellet ICV\footnote{\url{http://clarkparsia.com/pellet/icv/}}, which re-interprets OWL axioms with integrity constraint semantics.
 
@@
 As we discussed in detail in earlier work~\cite{Nagy2011}, these areas impose specific requirements on vocabulary features, such as structure, availability, and documentation.
-Quality aspects of controlled vocabularies have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, tutorials~\cite{Soergel2002}, and scholarly articles \cite{Coronado2009,Kless2010}.
+Quality aspects of controlled vocabularies have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Aitchison2000,Harpring2010,Hedden2010,Svenonius2003}, tutorials~\cite{Soergel2002}, and scholarly articles \cite{Coronado2009,Kless2010}.
 These most often rely on manual, precise analysis of individual statements in the data, as in~\cite{spero2008}.
@@
 While we could use some criteria suggested here, such as consistent tagging of literals, these need to be completed by considering SKOS-specific properties.
+
+One issue when assessing the quality of SKOS data is the so-called ``Open World Assumption'', which underlies the Web of Data itself.
+Established quality notions from closed-world systems, such as referential integrity or schema validation, do not hold anymore, because available information may be incomplete and non-explicitly stated facts cannot be determined as true or false.
+Work-arounds, often ad-hoc, are thus currently used to evaluate quality in Linked Data sets~\cite{Heath2011}, as is done in the (rule-based) SKOS tools mentioned above, or the Pellet ICV\footnote{\url{http://clarkparsia.com/pellet/icv/}}, which re-interprets OWL axioms with integrity constraint semantics.

### 2012-06-04 criteria.tex
changes according to antoine's comments

@@
 % Function defintion
-A SKOS vocabulary can be checked for omitted and invalid language tags by iterating over all resources in $IR$ and finding those that have labeling or documentation property relations to plain literals in $LV$ with missing or invalid language tags, i.e., tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
+A SKOS vocabulary can be checked for omitted and invalid language tags by iterating over all resources in $IR$ and finding those that have labeling or documentation property relations to plain literals in $LV$ with missing or invalid language tags, i.e., tags that are not defined in RFC3066\footnote{Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
 
@@
 The default, built-in similarity function checks for case-insensitive string equality with a threshold equal to 1.
-Label conflicts can be found by iterating over all concept pairs $AC \times AC$, applying $sim$ to every possible label combination, and collecting those pairs with at least one label combination meeting or exceeding a specified similarity threshold.
+Label conflicts can be found by iterating over all (authoritative) concept pairs $AC \times AC$, applying $sim$ to every possible label combination, and collecting those pairs with at least one label combination meeting or exceeding a specified similarity threshold.
 We handle this issue under the Closed World Assumption, because data on concept scheme membership may lack and concepts may be linked to concepts with similar labels in other vocabularies.
@@
 % Origin and rationale
-When vocabularies are being published on the Web, SKOS concepts become linkable resources.
+When vocabularies are published on the Web, SKOS concepts become linkable resources.
 Estimating the number of in-links and identifying the concepts without any in-links, can indicate the importance of a concept.
@@
 % Function definition
-Undefined SKOS resources can be identified by iterating over all resources in $IR$ and returning those resources (i) that are contained in the list of deprecated resources\footnote{See \url{http://www.w3.org/TR/skos-reference/#namespace}} or (ii) are identified by a URI in the SKOS namespace but are not defined in the current version of the SKOS ontology.
+Undefined SKOS resources can be identified by iterating over all resources in $IR$ and returning those (i) that are contained in the list of deprecated resources\footnote{See \url{http://www.w3.org/TR/skos-reference/#namespace}} or (ii) are identified by a URI in the SKOS namespace but are not defined in the current version of the SKOS ontology.

### 2012-06-04 introduction.tex
changes according to antoine's comments

@@
 The Simple Knowledge Organization System (SKOS)~\cite{SkosReference2008} is a standard model for sharing and linking controlled vocabularies (thesauri, classification systems, etc.) on the Web.
-Organizations like, e.g., the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} publish SKOS representations of their vocabularies on the Web so that they can easily be accessed by humans and machines.
+Organizations like, e.g., the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/standards/agrovoc/about}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} publish SKOS representations of their vocabularies on the Web so that they can easily be accessed by humans and machines.
 
@@
 Our goal is to help taxonomists in identifying possible quality issues in SKOS vocabularies and to give them a set of computable quality checking functions that, in combination with the taxonomists' experience and domain expertise, can serve as quality indicators for vocabularies.
-Finding such quality issues also gives important feedback on the overall vocabulary design process and should, at the end, lead to better vocabularies.
+Finding such quality issues also gives important feedback on the overall vocabulary design process and should, in the end, lead to better vocabularies.
 With defining computable quality checking functions we tackle the problem of quality assessment from an objective perspective.
 Subjective perception of quality is not within the scope of this work.
-The main contributions of this work can be summarized as follows:
+Our contribution can be summarized as follows:
 

### 2012-06-04 analysis.tex
added sentence about doc quality future work
incorporated antoine's comments

@@
 \begin{center}
-\resizebox{\textwidth}{!} {
+\resizebox{10cm}{!} {
 \setlength{\extrarowheight}{5pt}
@@
 All other vocabularies have a significant number of undocumented concepts.
+\textcolor{red}{A finer-grained evaluation on documentation quality indicators like, e.g., average number or length of documentation statements per concept will be subject of future work.}
 % Label Conflicts
@@
 \texttt{PXV} splits into 10 topic-related weakly connected components, such as ``deficiencies'', ``defects'' or ``signals''.
-The \texttt{LVAk} thesaurus contains 11 concept clusters, which are obviously forgotten test data.
+The \texttt{LVAk} thesaurus contains 11 concept clusters, \textcolor{red}{some of them are obviously forgotten test data.}
 
@@
 Solely transitive related concepts occur in 3 vocabularies, establishing relations using properties that, according to the SKOS reference documentation, should not be asserted directly.
-This indicates a possible misinterpretation of the SKOS specification and could result in a loss in recall on hierarchical queries when the vocabulary is queried without RDFS inferencing.
+This indicates a possible misinterpretation of the SKOS specification and could result in a loss in recall on hierarchical queries.
 % Omitted Top Concepts

### 2012-06-04 criteria.tex
incorporated antoine's comments

@@
 
+\textcolor{red}{
 We identified an initial set of possible quality issues in SKOS vocabularies by reviewing literature and manually examining existing vocabularies.
-In our studies we strictly focused on issues that can be formally expressed and thus automatically measured.
+We strictly focused on issues that can be formally expressed and thus automatically measured.
+However, general graph measures like, e.g.
+hierarchy depth or node centrality have been omitted due to lack of evidence on their relevance for vocabulary quality.}
 We published our findings in the qSKOS wiki and requested feedback from experts via public mailing lists and informal face to face discussions.

### 2012-06-04 criteria.tex
minor change in issue implementation formulation

@@
 % Function definition
-This issue can be detected by finding all concept pairs $C \times C$ that are directly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} properties but not by their \texttt{skos:broader} and \texttt{skos:narrower} subproperties.
+This issue can be detected by finding all concept pairs $C \times C$ that are directly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} properties but not by chains of \texttt{skos:broader} and \texttt{skos:narrower} subproperties.
 

### 2012-06-05 acknowledgements.tex
minor changes to meet page limit
further changes based on antoine's comments

--- 2012-05-30 acknowledgements.tex
@@
 %!TEX root = main.tex
-\section{Acknowledgements}
+\subsection*{Acknowledgements}
 
-The authors would like to thank \todo{CM}{Names} for \todo{CM}{what?}.
-The work has partly been supported by \todo{CM}{FWF Grant} and an EU Marie Curie International Outgoing Fellowship, grant no.
+Andrew Gibson and Tom Dent provided PXV and IPSV data and Joachim Neubert, valuable feedback on the found issues.
+The work is supported by the FWF P21571 Meketre project and EU Marie Curie Fellowship no.
 252206.
-\todo{CM}{ask Antoine about necessary Ackn.}
+
+%The authors would like to thank Andrew Gibson and Tom Dent for providing dumps of the PXV and IPSV vocabularies as well as Joachim Neubert for valuable feedback on the found issues.
+The work has partly been supported by the FWF-funded Meketre project (P21571) and an EU Marie Curie International Outgoing Fellowship, grant no.
+252206.

### 2012-06-05 analysis.tex
further changes based on antoine's comments

@@
 All other vocabularies have a significant number of undocumented concepts.
-\textcolor{red}{A finer-grained evaluation on documentation quality indicators like, e.g., average number or length of documentation statements per concept will be subject of future work.}
 % Label Conflicts
@@
 \texttt{PXV} splits into 10 topic-related weakly connected components, such as ``deficiencies'', ``defects'' or ``signals''.
-The \texttt{LVAk} thesaurus contains 11 concept clusters, \textcolor{red}{some of them are obviously forgotten test data.}
+The \texttt{LVAk} thesaurus contains 11 concept clusters, some of them are obviously forgotten test data.
 

### 2012-06-05 conclusions.tex
incorporated antoine's comments
further changes based on antoine's comments

@@
 To learn more about the real-world impact of our work like, e.g., the relative importance of the identified quality issues, we will conduct a qualitative follow-up study, in which we discuss these results with more taxonomists.
-We will also further collect community feedback, enhance the issues list, and set up a Web-based SKOS quality checking service.
-We also need to increase the performance and efficiency of our quality checking algorithms.
+We will also set up a Web-based SKOS quality checking service to further collect community feedback and enhance the issues list.
+These enhancements may encompass a finer-grained evaluation on some issues like, e.g., documentation quality indicators which could also include average number or length of documentation statements and their standard deviation across concepts.
 

### 2012-06-05 criteria.tex
further changes based on antoine's comments

--- 2012-06-04 criteria.tex
@@
 We identified an initial set of possible quality issues in SKOS vocabularies by reviewing literature and manually examining existing vocabularies.
-In our studies we strictly focused on issues that can be formally expressed and thus automatically measured.
+We strictly focused on issues that can be formally expressed and thus automatically measured.
+However, common graph measures like, e.g.
+hierarchy depth or node centrality have been omitted due to lack of evidence on their general influence on vocabulary quality.
 We published our findings in the qSKOS wiki and requested feedback from experts via public mailing lists and informal face to face discussions.
@@
 % Function definition
-This issue can be detected by finding all concept pairs $C \times C$ that are directly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} properties but not by their \texttt{skos:broader} and \texttt{skos:narrower} subproperties.
+This issue can be detected by finding all concept pairs $C \times C$ that are directly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} properties but not by (chains of) \texttt{skos:broader} and \texttt{skos:narrower} subproperties.
 

### 2012-06-05 analysis.tex
added skosxl footnote

@@
 \texttt{PXV}, for instance, uses the string ``primary peroxisomal enzyme deficiency'' with two concepts in the same concept scheme, but once with a \texttt{skos:prefLabel} and another time with a \texttt{skos:altLabel} property.
-In \texttt{NAICS} we could not detect any labeling issues but found that it expresses statements with \texttt{skosxl:prefLabel} as predicate and plain literals as object, which contradicts the SKOS-XL specification.
-
-%\textcolor{red}{For every concept in \texttt{NAICS}, a \texttt{rdfs:label} as well as a \texttt{skosxl:prefLabel} is defined.
-However, objects of the \texttt{prefLabel} triples are plain literals which seems to be a misunderstanding of SKOS-XL by the vocabulary creators.
-Thus, this information is not processed and no conflicts are found.}
+In \texttt{NAICS} we could not detect any labeling issues but found that it expresses statements with \texttt{skosxl:prefLabel} as predicate and plain literals as object, which contradicts the SKOS-XL\footnote{The SKOS eXtension for Labels (SKOS-XL) provides additional support for identifying, describing and linking lexical entities.~\cite{SkosReference2008}} specification.
 
@@
 % Weakly Connected Components
+Three vocabularies show no weakly connected components (WCCs) because all concepts are orphan concepts and thus no relations between them are established.
 Two vocabularies (\texttt{IPSV}, \texttt{NAICS}) consist of only one ``giant component'', which is often considered as being the ideal vocabulary structure.
-\texttt{STW} forms one giant component (containing 24,572 concepts), but has also 140 additional weakly connected components, which all contain linked authoritative and non-authoritative concepts.
+\texttt{STW} forms one giant component (containing 24,572 concepts), but has also 140 additional WCCs, which all contain linked authoritative and non-authoritative concepts.
 All other vocabularies split into several clusters of semantically related concepts, each of which represents a certain subtopic.
-\texttt{Eurovoc}, for instance, contains 4 weakly connected components, containing 4, 5, 6 and 6775 concepts.
+\texttt{Eurovoc}, for instance, contains 4 WCCs, containing 4, 5, 6 and 6775 concepts.
 The three smallest components contain concepts thematically related to ``Africa'', ``educational institutions'' and ``forecasts''.
-Weakly connected components divide the \texttt{Meketre} vocabulary into different topics, e.g., museums or concepts reserved for internal use.
-\texttt{GTAA} consists of 621 weakly connected components with the largest one being a subject thesaurus containing 8413 concepts.
+WCCs divide the \texttt{Meketre} vocabulary into different topics, e.g., museums or concepts reserved for internal use.
+\texttt{GTAA} consists of 621 WCCs with the largest one being a subject thesaurus containing 8413 concepts.
 Most of the other components contain less than 10 concepts, representing, e.g., locations, person names, and genres.
-\texttt{PXV} splits into 10 topic-related weakly connected components, such as ``deficiencies'', ``defects'' or ``signals''.
+\texttt{PXV} splits into 10 topic-related WCCs, such as ``deficiencies'', ``defects'' or ``signals''.
 The \texttt{LVAk} thesaurus contains 11 concept clusters, some of them are obviously forgotten test data.

### 2012-06-05 analysis.tex
added WCC and cylce comments

@@
 
+\vspace{-.3cm}
 \begin{table}[h]
 \caption{Results of the quality checking functions}
+\vspace{-.3cm}
 \label{tab:results}
@@
 \end{table}
+\vspace{-.5cm}
 
@@
 \texttt{Eurovoc}, for instance, contains 4 WCCs, containing 4, 5, 6 and 6775 concepts.
-The three smallest components contain concepts thematically related to ``Africa'', ``educational institutions'' and ``forecasts''.
+It is organized into numerous micro-thesauri and domains, using a custom ontology.
+Concepts contained in different micro-thesauri or domains are connected by \texttt{skos:related} properties, but this is not the case for the three small WCCs, indicating a quality flaw.
 WCCs divide the \texttt{Meketre} vocabulary into different topics, e.g., museums or concepts reserved for internal use.
@@
 Hierarchical cycles are not a common issue except in the collaboratively created \texttt{DBpedia} vocabulary, where many concepts have reflexive \texttt{skos:broader} relations.
+Also some of the cycles in \texttt{MeSH} indicate badly-defined relations and those in \texttt{LVAk} may be revised regarding hierarchy changes or replacement by associative relations or synonym definitions.
 % Valuless Associative Relations

### 2012-06-05 conclusions.tex
added WCC and cylce comments

@@
 
-In this paper we presented possible quality issues in SKOS vocabularies and described how we implemented them as quality checking functions in our qSKOS quality assessment tool.
+We presented possible quality issues in SKOS vocabularies and described how we implemented them as quality checking functions in our qSKOS quality assessment tool.
 We analyzed a representative set of existing SKOS vocabularies and found  issues in all of them.

### 2012-06-05 analysis.tex
added changes by antoine and bernhard

@@
 
-\vspace{-.3cm}
+\vspace{-.5cm}
 \begin{table}[h]
 \caption{Results of the quality checking functions}
-\vspace{-.3cm}
+\vspace{-.5cm}
 \label{tab:results}
@@
 \end{table}
-\vspace{-.5cm}
+\vspace{-1cm}
 
@@
 Three vocabularies show no weakly connected components (WCCs) because all concepts are orphan concepts and thus no relations between them are established.
-Two vocabularies (\texttt{IPSV}, \texttt{NAICS}) consist of only one ``giant component'', which is often considered as being the ideal vocabulary structure.
+Two vocabularies (\texttt{IPSV}, \texttt{NAICS}) consist of only one ``giant component'', which is often considered the ideal vocabulary structure.
 \texttt{STW} forms one giant component (containing 24,572 concepts), but has also 140 additional WCCs, which all contain linked authoritative and non-authoritative concepts.
@@
 WCCs divide the \texttt{Meketre} vocabulary into different topics, e.g., museums or concepts reserved for internal use.
-\texttt{GTAA} consists of 621 WCCs with the largest one being a subject thesaurus containing 8413 concepts.
-Most of the other components contain less than 10 concepts, representing, e.g., locations, person names, and genres.
+\texttt{GTAA} consists of 621 highly unbalanced WCCs.
+One component contains 8413 subjects from a thesaurus with carefully curated semantic relations.
+Most of the other components contain less than 10 entities from other categories, e.g., locations, person names, and genres, for which the ``traditional'' information management practices involve much less explicit linking.
 \texttt{PXV} splits into 10 topic-related WCCs, such as ``deficiencies'', ``defects'' or ``signals''.
@@
 Hierarchical cycles are not a common issue except in the collaboratively created \texttt{DBpedia} vocabulary, where many concepts have reflexive \texttt{skos:broader} relations.
-Also some of the cycles in \texttt{MeSH} indicate badly-defined relations and those in \texttt{LVAk} may be revised regarding hierarchy changes or replacement by associative relations or synonym definitions.
+We believe that some of the cycles in \texttt{MeSH} and \texttt{LVAk} require revision from domain experts.
+They could possibly be resolved by changing the hierarchy or introducing associative relations or synonym definitions.
 % Valuless Associative Relations
@@
 % Solely Transitive Related Concepts
-Solely transitive related concepts occur in 3 vocabularies, establishing relations using properties that, according to the SKOS reference documentation, should not be asserted directly.
+Solely transitive related concepts occur in 3 vocabularies, establishing relations using properties that, according to~\cite{SkosReference2008}, should not be asserted directly.
 This indicates a possible misinterpretation of the SKOS specification and could result in a loss in recall on hierarchical queries.

### 2012-06-06 analysis.tex
final power editing round

@@
 \begin{center}
-\resizebox{10cm}{!} {
+\resizebox{12cm}{!} {
 \setlength{\extrarowheight}{5pt}
@@
 
-\vspace{-.5cm}
+\vspace{-.3cm}
 \begin{table}[h]
 \caption{Results of the quality checking functions}
+\label{tab:results}
 \vspace{-.5cm}
-\label{tab:results}
-
 \begin{center}
@@
 \end{table}
-\vspace{-1cm}
+\vspace{-.3cm}
 
@@
 All other vocabularies split into several clusters of semantically related concepts, each of which represents a certain subtopic.
-\texttt{Eurovoc}, for instance, contains 4 WCCs, containing 4, 5, 6 and 6775 concepts.
-It is organized into numerous micro-thesauri and domains, using a custom ontology.
-Concepts contained in different micro-thesauri or domains are connected by \texttt{skos:related} properties, but this is not the case for the three small WCCs, indicating a quality flaw.
+\texttt{Eurovoc}, for instance, has 4 WCCs, containing 4, 5, 6 and 6775 concepts.
+In the large WCC it uses a custom ontology to organized numerous micro-thesauri and domains and cross-connects concepts by \texttt{skos:related} properties.
+However, this is not the case for the three small WCCs, indicating a quality flaw.
 WCCs divide the \texttt{Meketre} vocabulary into different topics, e.g., museums or concepts reserved for internal use.
@@
 \texttt{PXV} splits into 10 topic-related WCCs, such as ``deficiencies'', ``defects'' or ``signals''.
-The \texttt{LVAk} thesaurus contains 11 concept clusters, some of them are obviously forgotten test data.
+Some of the 11 concept clusters contained in the \texttt{LVAk} thesaurus are obviously forgotten test data.
 
@@
 Hierarchical cycles are not a common issue except in the collaboratively created \texttt{DBpedia} vocabulary, where many concepts have reflexive \texttt{skos:broader} relations.
-We believe that some of the cycles in \texttt{MeSH} and \texttt{LVAk} require revision from domain experts.
-They could possibly be resolved by changing the hierarchy or introducing associative relations or synonym definitions.
+The cycles in \texttt{MeSH} and \texttt{LVAk} could, in our opinion, be resolved by replacing hierarchical with associative relations or synonym definitions.
 % Valuless Associative Relations

### 2012-06-06 criteria.tex
final power editing round

@@
 
-We identified an initial set of possible quality issues in SKOS vocabularies by reviewing literature and manually examining existing vocabularies.
-We strictly focused on issues that can be formally expressed and thus automatically measured.
-However, common graph measures like, e.g.
-hierarchy depth or node centrality have been omitted due to lack of evidence on their general influence on vocabulary quality.
+We identified an initial set of possible quality issues in SKOS vocabularies by reviewing literature, manually examining existing vocabularies, and focusing on issues that can be measured automatically.
+Some measures, such as hierarchy depth or node centrality, have been omitted due to lack of evidence on their general influence on vocabulary quality.
 We published our findings in the qSKOS wiki and requested feedback from experts via public mailing lists and informal face to face discussions.
-Based on the received responses, we then selected a subset of these issues and translated them into computable quality checking functions.
+Based on the received responses, we translated a subset of these issues into computable quality checking functions.
 Each function takes a given SKOS vocabulary and an optional vocabulary namespace as input and finds all resources that match the corresponding quality issue.
@@
 % Origin and rationale
-In the Linked Data context, SKOS concepts should also be linked with other related concepts on the Web, ``enabling seamless connections between data sets''\cite{Heath2011}.
+%In the Linked Data context, 
+SKOS concepts should also be linked with other related concepts on the Web, ``enabling seamless connections between data sets''\cite{Heath2011}.
 Similar to \emph{Missing In-Links}, this issue identifies the set of all authoritative concepts that have no out-links.
